### 2019-07-19 iclr2020_conference.tex
Initial Overleaf Import

\documentclass{article} % For LaTeX2e
\usepackage{iclr2020_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}

\title{Formatting Instructions for ICLR 2020 \\ Conference Submissions}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.

\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
about author (webpage, alternative address)---\emph{not} for acknowledging
funding agencies.  Funding acknowledgements go at the end of the paper.} \\
Department of Computer Science\\
Cranberry-Lemon University\\
Pittsburgh, PA 15213, USA \\
\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
\And
Ji Q. Ren \& Yevgeny LeNet \\
Department of Computational Neuroscience \\
University of the Witwatersrand \\
Joburg, South Africa \\
\texttt{\{robot,net\}@wits.ac.za} \\
\AND
Coauthor \\
Affiliation \\
Address \\
\texttt{email}
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}

\maketitle

\begin{abstract}
The abstract paragraph should be indented 1/2~inch (3~picas) on both left and
right-hand margins. Use 10~point type, with a vertical spacing of 11~points.
The word \textsc{Abstract} must be centered, in small caps, and in point size 12. Two
line spaces precede the abstract. The abstract must be limited to one
paragraph.
\end{abstract}

\section{Submission of conference papers to ICLR 2020}

ICLR requires electronic submissions, processed by
\url{https://openreview.net/}. See ICLR's website for more instructions.

If your paper is ultimately accepted, the statement {\tt
  {\textbackslash}iclrfinalcopy} should be inserted to adjust the
format to the camera ready requirements.

The format for the submissions is a variant of the NIPS format.
Please read carefully the instructions below, and follow them
faithfully.

\subsection{Style}

Papers to be submitted to ICLR 2020 must be prepared according to the
instructions presented here.

%% Please note that we have introduced automatic line number generation
%% into the style file for \LaTeXe. This is to help reviewers
%% refer to specific lines of the paper when they make their comments. Please do
%% NOT refer to these line numbers in your paper as they will be removed from the
%% style file for the final version of accepted papers.

Authors are required to use the ICLR \LaTeX{} style files obtainable at the
ICLR website. Please make sure you use the current files and
not previous versions. Tweaking the style files may be grounds for rejection.

\subsection{Retrieval of style files}

The style files for ICLR and other conference information are available online at:
\begin{center}
   \url{http://www.iclr.cc/}
\end{center}
The file \verb+iclr2020_conference.pdf+ contains these
instructions and illustrates the
various formatting requirements your ICLR paper must satisfy.
Submissions must be made using \LaTeX{} and the style files
\verb+iclr2020_conference.sty+ and \verb+iclr2020_conference.bst+ (to be used with \LaTeX{}2e). The file
\verb+iclr2020_conference.tex+ may be used as a ``shell'' for writing your paper. All you
have to do is replace the author, title, abstract, and text of the paper with
your own.

The formatting instructions contained in these style files are summarized in
sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas) wide and
9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).
Use 10~point type with a vertical spacing of 11~points. Times New Roman is the
preferred typeface throughout. Paragraphs are separated by 1/2~line space,
with no indentation.

Paper title is 17~point, in small caps and left-aligned.
All pages should start at 1~inch (6~picas) from the top of the page.

Authors' names are
set in boldface, and each name is placed above its corresponding
address. The lead author's name is to be listed first, and
the co-authors' names are set to follow. Authors sharing the
same address can be on the same line.

Please pay special attention to the instructions in section \ref{others}
regarding figures, tables, acknowledgments, and references.

The recommended paper length is 8 pages, with unlimited additional pages for
citations.  There will be a strict upper limit of 10 pages for the main text.
Reviewers will be instructed to apply a higher standard to papers in excess of 8
pages.  Authors may use as many pages of appendices (after the bibliography) as
they wish, but reviewers are not required to read these.

\section{Headings: first level}
\label{headings}

First level headings are in small caps,
flush left and in point size 12. One line space before the first level
heading and 1/2~line space after the first level heading.

\subsection{Headings: second level}

Second level headings are in small caps,
flush left and in point size 10. One line space before the second level
heading and 1/2~line space after the second level heading.

\subsubsection{Headings: third level}

Third level headings are in small caps,
flush left and in point size 10. One line space before the third level
heading and 1/2~line space after the third level heading.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone, regardless of the formatter being used.

\subsection{Citations within the text}

Citations within the text should be based on the \texttt{natbib} package
and include the authors' last names and year (with the ``et~al.'' construct
for more than two authors). When the authors or the publication are
included in the sentence, the citation should not be in parenthesis using \verb|\citet{}| (as
in ``See \citet{Hinton06} for more information.''). Otherwise, the citation
should be in parenthesis using \verb|\citep{}| (as in ``Deep learning shows promise to make progress 
towards AI~\citep{Bengio+chapter2007}.'').

The corresponding references are to be listed in alphabetical order of
authors, in the \textsc{References} section. As to the format of the
references themselves, any style is acceptable as long as it is used
consistently.

\subsection{Footnotes}

Indicate footnotes with a number\footnote{Sample of the first footnote} in the
text. Place the footnotes at the bottom of the page on which they appear.
Precede the footnote with a horizontal rule of 2~inches
(12~picas).\footnote{Sample of the second footnote}

\subsection{Figures}

All artwork must be neat, clean, and legible. Lines should be dark
enough for purposes of reproduction; art work should not be
hand-drawn. The figure number and caption always appear after the
figure. Place one line space before the figure caption, and one line
space after the figure. The figure caption is lower case (except for
first word and proper nouns); figures are numbered consecutively.

Make sure the figure caption does not get separated from the figure.
Leave sufficient space to avoid splitting the figure and figure caption.

You may use color figures.
However, it is best for the
figure captions and the paper body to make sense if the paper is printed
either in black/white or in color.
\begin{figure}[h]
\begin{center}
%\framebox[4.0in]{$\;$}
\fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
\end{center}
\caption{Sample figure caption.}
\end{figure}

\subsection{Tables}

All tables must be centered, neat, clean and legible. Do not use hand-drawn
tables. The table number and title always appear before the table. See
Table~\ref{sample-table}.

Place one line space before the table title, one line space after the table
title, and one line space after the table. The table title must be lower case
(except for first word and proper nouns); tables are numbered consecutively.

\begin{table}[t]
\caption{Sample table title}
\label{sample-table}
\begin{center}
\begin{tabular}{ll}
\multicolumn{1}{c}{\bf PART}  &\multicolumn{1}{c}{\bf DESCRIPTION}
\\ \hline \\
Dendrite         &Input terminal \\
Axon             &Output terminal \\
Soma             &Cell body (contains cell nucleus) \\
\end{tabular}
\end{center}
\end{table}

\section{Default Notation}

In an attempt to encourage standardized notation, we have included the
notation file from the textbook, \textit{Deep Learning}
\cite{goodfellow2016deep} available at
\url{https://github.com/goodfeli/dlbook_notation/}.  Use of this style
is not required and can be disabled by commenting out
\texttt{math\_commands.tex}.

\centerline{\bf Numbers and Arrays}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{p{1in}p{3.25in}}
$\displaystyle a$ & A scalar (integer or real)\\
$\displaystyle \va$ & A vector\\
$\displaystyle \mA$ & A matrix\\
$\displaystyle \tA$ & A tensor\\
$\displaystyle \mI_n$ & Identity matrix with $n$ rows and $n$ columns\\
$\displaystyle \mI$ & Identity matrix with dimensionality implied by context\\
$\displaystyle \ve^{(i)}$ & Standard basis vector $[0,\dots,0,1,0,\dots,0]$ with a 1 at position $i$\\
$\displaystyle \text{diag}(\va)$ & A square, diagonal matrix with diagonal entries given by $\va$\\
$\displaystyle \ra$ & A scalar random variable\\
$\displaystyle \rva$ & A vector-valued random variable\\
$\displaystyle \rmA$ & A matrix-valued random variable\\
\end{tabular}
\egroup
\vspace{0.25cm}

\centerline{\bf Sets and Graphs}
\bgroup
\def\arraystretch{1.5}

\begin{tabular}{p{1.25in}p{3.25in}}
$\displaystyle \sA$ & A set\\
$\displaystyle \R$ & The set of real numbers \\
$\displaystyle \{0, 1\}$ & The set containing 0 and 1 \\
$\displaystyle \{0, 1, \dots, n \}$ & The set of all integers between $0$ and $n$\\
$\displaystyle [a, b]$ & The real interval including $a$ and $b$\\
$\displaystyle (a, b]$ & The real interval excluding $a$ but including $b$\\
$\displaystyle \sA \backslash \sB$ & Set subtraction, i.e., the set containing the elements of $\sA$ that are not in $\sB$\\
$\displaystyle \gG$ & A graph\\
$\displaystyle \parents_\gG(\ervx_i)$ & The parents of $\ervx_i$ in $\gG$
\end{tabular}
\vspace{0.25cm}

\centerline{\bf Indexing}
\bgroup
\def\arraystretch{1.5}

\begin{tabular}{p{1.25in}p{3.25in}}
$\displaystyle \eva_i$ & Element $i$ of vector $\va$, with indexing starting at 1 \\
$\displaystyle \eva_{-i}$ & All elements of vector $\va$ except for element $i$ \\
$\displaystyle \emA_{i,j}$ & Element $i, j$ of matrix $\mA$ \\
$\displaystyle \mA_{i, :}$ & Row $i$ of matrix $\mA$ \\
$\displaystyle \mA_{:, i}$ & Column $i$ of matrix $\mA$ \\
$\displaystyle \etA_{i, j, k}$ & Element $(i, j, k)$ of a 3-D tensor $\tA$\\
$\displaystyle \tA_{:, :, i}$ & 2-D slice of a 3-D tensor\\
$\displaystyle \erva_i$ & Element $i$ of the random vector $\rva$ \\
\end{tabular}
\egroup
\vspace{0.25cm}

\centerline{\bf Calculus}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{p{1.25in}p{3.25in}}
% NOTE: the [2ex] on the next line adds extra height to that row of the table.
% Without that command, the fraction on the first line is too tall and collides
% with the fraction on the second line.
$\displaystyle\frac{d y} {d x}$ & Derivative of $y$ with respect to $x$\\ [2ex]
$\displaystyle \frac{\partial y} {\partial x} $ & Partial derivative of $y$ with respect to $x$ \\
$\displaystyle \nabla_\vx y $ & Gradient of $y$ with respect to $\vx$ \\
$\displaystyle \nabla_\mX y $ & Matrix derivatives of $y$ with respect to $\mX$ \\
$\displaystyle \nabla_\tX y $ & Tensor containing derivatives of $y$ with respect to $\tX$ \\
$\displaystyle \frac{\partial f}{\partial \vx} $ & Jacobian matrix $\mJ \in \R^{m\times n}$ of $f: \R^n \rightarrow \R^m$\\
$\displaystyle \nabla_\vx^2 f(\vx)\text{ or }\mH( f)(\vx)$ & The Hessian matrix of $f$ at input point $\vx$\\
$\displaystyle \int f(\vx) d\vx $ & Definite integral over the entire domain of $\vx$ \\
$\displaystyle \int_\sS f(\vx) d\vx$ & Definite integral with respect to $\vx$ over the set $\sS$ \\
\end{tabular}
\egroup
\vspace{0.25cm}

\centerline{\bf Probability and Information Theory}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{p{1.25in}p{3.25in}}
$\displaystyle P(\ra)$ & A probability distribution over a discrete variable\\
$\displaystyle p(\ra)$ & A probability distribution over a continuous variable, or over
a variable whose type has not been specified\\
$\displaystyle \ra \sim P$ & Random variable $\ra$ has distribution $P$\\% so thing on left of \sim should always be a random variable, with name beginning with \r
$\displaystyle  \E_{\rx\sim P} [ f(x) ]\text{ or } \E f(x)$ & Expectation of $f(x)$ with respect to $P(\rx)$ \\
$\displaystyle \Var(f(x)) $ &  Variance of $f(x)$ under $P(\rx)$ \\
$\displaystyle \Cov(f(x),g(x)) $ & Covariance of $f(x)$ and $g(x)$ under $P(\rx)$\\
$\displaystyle H(\rx) $ & Shannon entropy of the random variable $\rx$\\
$\displaystyle \KL ( P \Vert Q ) $ & Kullback-Leibler divergence of P and Q \\
$\displaystyle \mathcal{N} ( \vx ; \vmu , \mSigma)$ & Gaussian distribution %
over $\vx$ with mean $\vmu$ and covariance $\mSigma$ \\
\end{tabular}
\egroup
\vspace{0.25cm}

\centerline{\bf Functions}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{p{1.25in}p{3.25in}}
$\displaystyle f: \sA \rightarrow \sB$ & The function $f$ with domain $\sA$ and range $\sB$\\
$\displaystyle f \circ g $ & Composition of the functions $f$ and $g$ \\
  $\displaystyle f(\vx ; \vtheta) $ & A function of $\vx$ parametrized by $\vtheta$.
  (Sometimes we write $f(\vx)$ and omit the argument $\vtheta$ to lighten notation) \\
$\displaystyle \log x$ & Natural logarithm of $x$ \\
$\displaystyle \sigma(x)$ & Logistic sigmoid, $\displaystyle \frac{1} {1 + \exp(-x)}$ \\
$\displaystyle \zeta(x)$ & Softplus, $\log(1 + \exp(x))$ \\
$\displaystyle || \vx ||_p $ & $\normlp$ norm of $\vx$ \\
$\displaystyle || \vx || $ & $\normltwo$ norm of $\vx$ \\
$\displaystyle x^+$ & Positive part of $x$, i.e., $\max(0,x)$\\
$\displaystyle \1_\mathrm{condition}$ & is 1 if the condition is true, 0 otherwise\\
\end{tabular}
\egroup
\vspace{0.25cm}

\section{Final instructions}
Do not change any aspects of the formatting parameters in the style files.
In particular, do not modify the width or length of the rectangle the text
should fit into, and do not change font sizes (except perhaps in the
\textsc{References} section; see below). Please note that pages should be
numbered.

\section{Preparing PostScript or PDF files}

Please prepare PostScript or PDF files with paper size ``US Letter'', and
not, for example, ``A4''. The -t
letter option on dvips will produce US Letter files.

Consider directly generating PDF files using \verb+pdflatex+
(especially if you are a MiKTeX user).
PDF figures must be substituted for EPS figures, however.

Otherwise, please generate your PostScript and PDF files with the following commands:
\begin{verbatim}
dvips mypaper.dvi -t letter -Ppdf -G0 -o mypaper.ps
ps2pdf mypaper.ps mypaper.pdf
\end{verbatim}

\subsection{Margins in LaTeX}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+
from the graphicx package. Always specify the figure width as a multiple of
the line width as in the example below using .eps graphics
\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.eps}
\end{verbatim}
or % Apr 2009 addition
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
for .pdf graphics.
See section~4.4 in the graphics bundle documentation (\url{http://www.ctan.org/tex-archive/macros/latex/required/graphics/grfguide.ps})

A number of width problems arise when LaTeX cannot properly hyphenate a
line. Please give LaTeX hyphenation hints using the \verb+\-+ command.

\subsubsection*{Author Contributions}
If you'd like to, you may include  a section for author contributions as is done
in many journals. This is optional and at the discretion of the authors.

\subsubsection*{Acknowledgments}
Use unnumbered third level headings for the acknowledgments. All
acknowledgments, including those to funding agencies, go at the end of the paper.

\bibliography{references}
\bibliographystyle{iclr2020_conference}

\appendix
\section{Appendix}
You may include other additional sections here.

\end{document}

### 2019-07-19 main.tex
Initial Overleaf Import

--- 2019-07-19 iclr2020_conference.tex
@@
 
-\title{Formatting Instructions for ICLR 2020 \\ Conference Submissions}
+\title{Which spherical CNN should you use?\\ DeepSphere V2}
 
@@
 % Non-anonymous submissions will be rejected without review. 
-
-\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
-about author (webpage, alternative address)---\emph{not} for acknowledging
+\author{Michaël Defferrard, Martino Milani, Frédérick Gusset,  Nathanaël Perraudin \thanks{ Use footnote for providing further information about author (webpage, alternative address)---\emph{not} for acknowledging
 funding agencies.  Funding acknowledgements go at the end of the paper.} \\
@@
 \begin{abstract}
-The abstract paragraph should be indented 1/2~inch (3~picas) on both left and
-right-hand margins. Use 10~point type, with a vertical spacing of 11~points.
-The word \textsc{Abstract} must be centered, in small caps, and in point size 12. Two
-line spaces precede the abstract. The abstract must be limited to one
-paragraph.
+No
 \end{abstract}
 
-\section{Submission of conference papers to ICLR 2020}
+\section{Introduction [2 pages]}
+Get inspiration from DeepSphere V1
 
-ICLR requires electronic submissions, processed by
-\url{https://openreview.net/}. See ICLR's website for more instructions.
+Why are spherical CNNs important? What are the application?
+See DeepSphere workshop paper
 
-If your paper is ultimately accepted, the statement {\tt
-  {\textbackslash}iclrfinalcopy} should be inserted to adjust the
-format to the camera ready requirements.
+Desiderata:
+* respect the domain
+  * rotational equivariance
+  * deformation (e.g., on the icosahedron for gauge)
+* powerful / generality => isotropic vs anisotropic
+* scale: computational cost \& memory usage (feature maps)
+* flexible (samplings, irregular), simplicity (implementation)
 
-The format for the submissions is a variant of the NIPS format.
-Please read carefully the instructions below, and follow them
-faithfully.
-
-\subsection{Style}
-
-Papers to be submitted to ICLR 2020 must be prepared according to the
-instructions presented here.
-
-%% Please note that we have introduced automatic line number generation
-%% into the style file for \LaTeXe. This is to help reviewers
-%% refer to specific lines of the paper when they make their comments. Please do
-%% NOT refer to these line numbers in your paper as they will be removed from the
-%% style file for the final version of accepted papers.
-
-Authors are required to use the ICLR \LaTeX{} style files obtainable at the
-ICLR website. Please make sure you use the current files and
-not previous versions. Tweaking the style files may be grounds for rejection.
-
-\subsection{Retrieval of style files}
-
-The style files for ICLR and other conference information are available online at:
-\begin{center}
-   \url{http://www.iclr.cc/}
-\end{center}
-The file \verb+iclr2020_conference.pdf+ contains these
-instructions and illustrates the
-various formatting requirements your ICLR paper must satisfy.
-Submissions must be made using \LaTeX{} and the style files
-\verb+iclr2020_conference.sty+ and \verb+iclr2020_conference.bst+ (to be used with \LaTeX{}2e). The file
-\verb+iclr2020_conference.tex+ may be used as a ``shell'' for writing your paper. All you
-have to do is replace the author, title, abstract, and text of the paper with
-your own.
-
-The formatting instructions contained in these style files are summarized in
-sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.
-
-\section{General formatting instructions}
-\label{gen_inst}
-
-The text must be confined within a rectangle 5.5~inches (33~picas) wide and
-9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).
-Use 10~point type with a vertical spacing of 11~points. Times New Roman is the
-preferred typeface throughout. Paragraphs are separated by 1/2~line space,
-with no indentation.
-
-Paper title is 17~point, in small caps and left-aligned.
-All pages should start at 1~inch (6~picas) from the top of the page.
-
-Authors' names are
-set in boldface, and each name is placed above its corresponding
-address. The lead author's name is to be listed first, and
-the co-authors' names are set to follow. Authors sharing the
-same address can be on the same line.
-
-Please pay special attention to the instructions in section \ref{others}
-regarding figures, tables, acknowledgments, and references.
-
-The recommended paper length is 8 pages, with unlimited additional pages for
-citations.  There will be a strict upper limit of 10 pages for the main text.
-Reviewers will be instructed to apply a higher standard to papers in excess of 8
-pages.  Authors may use as many pages of appendices (after the bibliography) as
-they wish, but reviewers are not required to read these.
-
-\section{Headings: first level}
-\label{headings}
-
-First level headings are in small caps,
-flush left and in point size 12. One line space before the first level
-heading and 1/2~line space after the first level heading.
-
-\subsection{Headings: second level}
-
-Second level headings are in small caps,
-flush left and in point size 10. One line space before the second level
-heading and 1/2~line space after the second level heading.
-
-\subsubsection{Headings: third level}
-
-Third level headings are in small caps,
-flush left and in point size 10. One line space before the third level
-heading and 1/2~line space after the third level heading.
-
-\section{Citations, figures, tables, references}
-\label{others}
-
-These instructions apply to everyone, regardless of the formatter being used.
-
-\subsection{Citations within the text}
-
-Citations within the text should be based on the \texttt{natbib} package
-and include the authors' last names and year (with the ``et~al.'' construct
-for more than two authors). When the authors or the publication are
-included in the sentence, the citation should not be in parenthesis using \verb|\citet{}| (as
-in ``See \citet{Hinton06} for more information.''). Otherwise, the citation
-should be in parenthesis using \verb|\citep{}| (as in ``Deep learning shows promise to make progress 
-towards AI~\citep{Bengio+chapter2007}.'').
-
-The corresponding references are to be listed in alphabetical order of
-authors, in the \textsc{References} section. As to the format of the
-references themselves, any style is acceptable as long as it is used
-consistently.
-
-\subsection{Footnotes}
-
-Indicate footnotes with a number\footnote{Sample of the first footnote} in the
-text. Place the footnotes at the bottom of the page on which they appear.
-Precede the footnote with a horizontal rule of 2~inches
-(12~picas).\footnote{Sample of the second footnote}
-
-\subsection{Figures}
-
-All artwork must be neat, clean, and legible. Lines should be dark
-enough for purposes of reproduction; art work should not be
-hand-drawn. The figure number and caption always appear after the
-figure. Place one line space before the figure caption, and one line
-space after the figure. The figure caption is lower case (except for
-first word and proper nouns); figures are numbered consecutively.
-
-Make sure the figure caption does not get separated from the figure.
-Leave sufficient space to avoid splitting the figure and figure caption.
-
-You may use color figures.
-However, it is best for the
-figure captions and the paper body to make sense if the paper is printed
-either in black/white or in color.
-\begin{figure}[h]
-\begin{center}
-%\framebox[4.0in]{$\;$}
-\fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
-\end{center}
-\caption{Sample figure caption.}
-\end{figure}
-
-\subsection{Tables}
-
-All tables must be centered, neat, clean and legible. Do not use hand-drawn
-tables. The table number and title always appear before the table. See
-Table~\ref{sample-table}.
-
-Place one line space before the table title, one line space after the table
-title, and one line space after the table. The table title must be lower case
-(except for first word and proper nouns); tables are numbered consecutively.
-
-\begin{table}[t]
-\caption{Sample table title}
-\label{sample-table}
-\begin{center}
-\begin{tabular}{ll}
-\multicolumn{1}{c}{\bf PART}  &\multicolumn{1}{c}{\bf DESCRIPTION}
-\\ \hline \\
-Dendrite         &Input terminal \\
-Axon             &Output terminal \\
-Soma             &Cell body (contains cell nucleus) \\
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{l|c|c|c|c}
+         & Scale & Generality& equivariance & Flexibility \\
+         \hline
+        Cohen & & & &  \\
+         \hline
+        Gauge & & & &  \\
+         \hline
+        Esteves & & & &  \\
+         \hline
+        Jiang & & & &  \\
+         \hline
+        2D CNN (cubed sphere) & & & &  \\
+         \hline
+        Ours & & & &  \\
     \end{tabular}
-\end{center}
+    \caption{Caption}
+    \label{tab:my_label}
 \end{table}
 
-\section{Default Notation}
+Present the different spherical CNNs with pro and cons => mostly scale vs generality
+* 2D CNN => doesn't respect geometry and equivariance
+* Cohen spherical CNN => most general, but doesn't scale
+* Cohen gauge => fixes scale, at the price of deformation (sphere => icosahedron)
+* Esteves => ?
+* Jiang => need a global coordinate system (ok for planets, not projections like cosmo)
 
-In an attempt to encourage standardized notation, we have included the
-notation file from the textbook, \textit{Deep Learning}
-\cite{goodfellow2016deep} available at
-\url{https://github.com/goodfeli/dlbook_notation/}.  Use of this style
-is not required and can be disabled by commenting out
-\texttt{math\_commands.tex}.
+\cite{perraudin2019deepsphere}
 
-\centerline{\bf Numbers and Arrays}
-\bgroup
-\def\arraystretch{1.5}
-\begin{tabular}{p{1in}p{3.25in}}
-$\displaystyle a$ & A scalar (integer or real)\\
-$\displaystyle \va$ & A vector\\
-$\displaystyle \mA$ & A matrix\\
-$\displaystyle \tA$ & A tensor\\
-$\displaystyle \mI_n$ & Identity matrix with $n$ rows and $n$ columns\\
-$\displaystyle \mI$ & Identity matrix with dimensionality implied by context\\
-$\displaystyle \ve^{(i)}$ & Standard basis vector $[0,\dots,0,1,0,\dots,0]$ with a 1 at position $i$\\
-$\displaystyle \text{diag}(\va)$ & A square, diagonal matrix with diagonal entries given by $\va$\\
-$\displaystyle \ra$ & A scalar random variable\\
-$\displaystyle \rva$ & A vector-valued random variable\\
-$\displaystyle \rmA$ & A matrix-valued random variable\\
-\end{tabular}
-\egroup
-\vspace{0.25cm}
+\section{Method [2 pages]}
 
-\centerline{\bf Sets and Graphs}
-\bgroup
-\def\arraystretch{1.5}
+* HEALPix: improvement from DeepSphere v1
+* equiangular: Renata \& Pascal
 
-\begin{tabular}{p{1.25in}p{3.25in}}
-$\displaystyle \sA$ & A set\\
-$\displaystyle \R$ & The set of real numbers \\
-$\displaystyle \{0, 1\}$ & The set containing 0 and 1 \\
-$\displaystyle \{0, 1, \dots, n \}$ & The set of all integers between $0$ and $n$\\
-$\displaystyle [a, b]$ & The real interval including $a$ and $b$\\
-$\displaystyle (a, b]$ & The real interval excluding $a$ but including $b$\\
-$\displaystyle \sA \backslash \sB$ & Set subtraction, i.e., the set containing the elements of $\sA$ that are not in $\sB$\\
-$\displaystyle \gG$ & A graph\\
-$\displaystyle \parents_\gG(\ervx_i)$ & The parents of $\ervx_i$ in $\gG$
-\end{tabular}
-\vspace{0.25cm}
+\section{Rotation equivariance [2 pages]}
+\subsection{Link with the Laplace-Beltrami Operator}
 
-\centerline{\bf Indexing}
-\bgroup
-\def\arraystretch{1.5}
+\subsection{Convergence theorem}
 
-\begin{tabular}{p{1.25in}p{3.25in}}
-$\displaystyle \eva_i$ & Element $i$ of vector $\va$, with indexing starting at 1 \\
-$\displaystyle \eva_{-i}$ & All elements of vector $\va$ except for element $i$ \\
-$\displaystyle \emA_{i,j}$ & Element $i, j$ of matrix $\mA$ \\
-$\displaystyle \mA_{i, :}$ & Row $i$ of matrix $\mA$ \\
-$\displaystyle \mA_{:, i}$ & Column $i$ of matrix $\mA$ \\
-$\displaystyle \etA_{i, j, k}$ & Element $(i, j, k)$ of a 3-D tensor $\tA$\\
-$\displaystyle \tA_{:, :, i}$ & 2-D slice of a 3-D tensor\\
-$\displaystyle \erva_i$ & Element $i$ of the random vector $\rva$ \\
-\end{tabular}
-\egroup
-\vspace{0.25cm}
+\section{Experiments [2 pages]}
 
-\centerline{\bf Calculus}
-\bgroup
-\def\arraystretch{1.5}
-\begin{tabular}{p{1.25in}p{3.25in}}
-% NOTE: the [2ex] on the next line adds extra height to that row of the table.
-% Without that command, the fraction on the first line is too tall and collides
-% with the fraction on the second line.
-$\displaystyle\frac{d y} {d x}$ & Derivative of $y$ with respect to $x$\\ [2ex]
-$\displaystyle \frac{\partial y} {\partial x} $ & Partial derivative of $y$ with respect to $x$ \\
-$\displaystyle \nabla_\vx y $ & Gradient of $y$ with respect to $\vx$ \\
-$\displaystyle \nabla_\mX y $ & Matrix derivatives of $y$ with respect to $\mX$ \\
-$\displaystyle \nabla_\tX y $ & Tensor containing derivatives of $y$ with respect to $\tX$ \\
-$\displaystyle \frac{\partial f}{\partial \vx} $ & Jacobian matrix $\mJ \in \R^{m\times n}$ of $f: \R^n \rightarrow \R^m$\\
-$\displaystyle \nabla_\vx^2 f(\vx)\text{ or }\mH( f)(\vx)$ & The Hessian matrix of $f$ at input point $\vx$\\
-$\displaystyle \int f(\vx) d\vx $ & Definite integral over the entire domain of $\vx$ \\
-$\displaystyle \int_\sS f(\vx) d\vx$ & Definite integral with respect to $\vx$ over the set $\sS$ \\
-\end{tabular}
-\egroup
-\vspace{0.25cm}
+\subsection{3D object recognition}
 
-\centerline{\bf Probability and Information Theory}
-\bgroup
-\def\arraystretch{1.5}
-\begin{tabular}{p{1.25in}p{3.25in}}
-$\displaystyle P(\ra)$ & A probability distribution over a discrete variable\\
-$\displaystyle p(\ra)$ & A probability distribution over a continuous variable, or over
-a variable whose type has not been specified\\
-$\displaystyle \ra \sim P$ & Random variable $\ra$ has distribution $P$\\% so thing on left of \sim should always be a random variable, with name beginning with \r
-$\displaystyle  \E_{\rx\sim P} [ f(x) ]\text{ or } \E f(x)$ & Expectation of $f(x)$ with respect to $P(\rx)$ \\
-$\displaystyle \Var(f(x)) $ &  Variance of $f(x)$ under $P(\rx)$ \\
-$\displaystyle \Cov(f(x),g(x)) $ & Covariance of $f(x)$ and $g(x)$ under $P(\rx)$\\
-$\displaystyle H(\rx) $ & Shannon entropy of the random variable $\rx$\\
-$\displaystyle \KL ( P \Vert Q ) $ & Kullback-Leibler divergence of P and Q \\
-$\displaystyle \mathcal{N} ( \vx ; \vmu , \mSigma)$ & Gaussian distribution %
-over $\vx$ with mean $\vmu$ and covariance $\mSigma$ \\
-\end{tabular}
-\egroup
-\vspace{0.25cm}
+* same perf as other spherical CNNs, but 40 times faster
+* compare the two samplings => not much difference
 
-\centerline{\bf Functions}
-\bgroup
-\def\arraystretch{1.5}
-\begin{tabular}{p{1.25in}p{3.25in}}
-$\displaystyle f: \sA \rightarrow \sB$ & The function $f$ with domain $\sA$ and range $\sB$\\
-$\displaystyle f \circ g $ & Composition of the functions $f$ and $g$ \\
-  $\displaystyle f(\vx ; \vtheta) $ & A function of $\vx$ parametrized by $\vtheta$.
-  (Sometimes we write $f(\vx)$ and omit the argument $\vtheta$ to lighten notation) \\
-$\displaystyle \log x$ & Natural logarithm of $x$ \\
-$\displaystyle \sigma(x)$ & Logistic sigmoid, $\displaystyle \frac{1} {1 + \exp(-x)}$ \\
-$\displaystyle \zeta(x)$ & Softplus, $\log(1 + \exp(x))$ \\
-$\displaystyle || \vx ||_p $ & $\normlp$ norm of $\vx$ \\
-$\displaystyle || \vx || $ & $\normltwo$ norm of $\vx$ \\
-$\displaystyle x^+$ & Positive part of $x$, i.e., $\max(0,x)$\\
-$\displaystyle \1_\mathrm{condition}$ & is 1 if the condition is true, 0 otherwise\\
-\end{tabular}
-\egroup
-\vspace{0.25cm}
+\subsection{cosmo}
 
-\section{Final instructions}
-Do not change any aspects of the formatting parameters in the style files.
-In particular, do not modify the width or length of the rectangle the text
-should fit into, and do not change font sizes (except perhaps in the
-\textsc{References} section; see below). Please note that pages should be
-numbered.
+other sphercial CNNs cannot scale to 10M pixels (tested on 10k at most)
 
-\section{Preparing PostScript or PDF files}
+\subsection{Climate event detection}
 
-Please prepare PostScript or PDF files with paper size ``US Letter'', and
-not, for example, ``A4''. The -t
-letter option on dvips will produce US Letter files.
+* small: better perf than gauge and Jiang. due to icosahedron distortion? to be confirmed
+* cannot compare with Mudigonda (16 vs 1 input channel)
+* full: we scale => lead to better perf?
 
-Consider directly generating PDF files using \verb+pdflatex+
-(especially if you are a MiKTeX user).
-PDF figures must be substituted for EPS figures, however.
+\section{Conclusion}
 
-Otherwise, please generate your PostScript and PDF files with the following commands:
-\begin{verbatim}
-dvips mypaper.dvi -t letter -Ppdf -G0 -o mypaper.ps
-ps2pdf mypaper.ps mypaper.pdf
-\end{verbatim}
+* DeepSphere seems to be in the sweet spot of tradeoffs. Recall the desiderata.
+  * Not the most general, but sufficient empirically
+  * scales linearly => cannot do better ($n^1.25$ for HEALPix)
+  * flexible => independent of the sampsamples can be 
+* anisotropy (most general) doesn't help. research question: when can it be useful?
 
-\subsection{Margins in LaTeX}
+future work:
+* when anisotropy needed?
+* irregular sampling while respecting the geometry
+* beyond the sphere, any manifold
 
-Most of the margin problems come from figures positioned by hand using
-\verb+\special+ or other commands. We suggest using the command
-\verb+\includegraphics+
-from the graphicx package. Always specify the figure width as a multiple of
-the line width as in the example below using .eps graphics
-\begin{verbatim}
-   \usepackage[dvips]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]{myfile.eps}
-\end{verbatim}
-or % Apr 2009 addition
-\begin{verbatim}
-   \usepackage[pdftex]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]{myfile.pdf}
-\end{verbatim}
-for .pdf graphics.
-See section~4.4 in the graphics bundle documentation (\url{http://www.ctan.org/tex-archive/macros/latex/required/graphics/grfguide.ps})
-
-A number of width problems arise when LaTeX cannot properly hyphenate a
-line. Please give LaTeX hyphenation hints using the \verb+\-+ command.
+\newpage
 
@@
 
+\newpage
+
 \appendix
 \section{Appendix}
-You may include other additional sections here.
+
+\subsection{}
 

### 2019-07-19 main.tex
general story

@@
 \begin{abstract}
-No
+story / main point:
+
+* method development: tool that solve a need (balance btw the desiderata: equiv vs cost)\\
+* research question: anisotropy (highlight from the start or leave it as a dangling question in the end)\\
+
+contributions:\\
+* theory => convergence (better graph)\\
+* experiments on relevant problems (not spherical MNIST) => check the desiderata\\
+  * surprising: anisotropy doesn't seem useful\\
+
 \end{abstract}
@@
 \section{Introduction [2 pages]}
-Get inspiration from DeepSphere V1
+Get inspiration from DeepSphere V1\\
 
-Why are spherical CNNs important? What are the application?
-See DeepSphere workshop paper
+Why are spherical CNNs important? What are the application?\\
+See DeepSphere workshop paper\\
 
-Desiderata:
-* respect the domain
-  * rotational equivariance
-  * deformation (e.g., on the icosahedron for gauge)
-* powerful / generality => isotropic vs anisotropic
-* scale: computational cost \& memory usage (feature maps)
-* flexible (samplings, irregular), simplicity (implementation)
+Desiderata:\\
+* respect the domain\\
+  * rotational equivariance\\
+  * deformation (e.g., on the icosahedron for gauge)\\
+* powerful / generality => isotropic vs anisotropic\\
+* scale: computational cost \& memory usage (feature maps)\\
+* flexible (samplings, irregular), simplicity (implementation)\\
 
@@
 
-Present the different spherical CNNs with pro and cons => mostly scale vs generality
-* 2D CNN => doesn't respect geometry and equivariance
-* Cohen spherical CNN => most general, but doesn't scale
-* Cohen gauge => fixes scale, at the price of deformation (sphere => icosahedron)
+On the one side, we have Cohen which is computationally very expensive but perfectly equivariant, on the other we have cube sphere which computationl very good but not equivariant at all.
+Other methods are tradedoff between these two.
+What is a good tradeoff?
+We think that DeepSphere is
+
+Present the different spherical CNNs with pro and cons => mostly scale vs generality\\
+* 2D CNN => doesn't respect geometry and equivariance\\
+* Cohen spherical CNN => most general, but doesn't scale\\
+* Cohen gauge => fixes scale, at the price of deformation (sphere => icosahedron)\\
 * Esteves => ?
-* Jiang => need a global coordinate system (ok for planets, not projections like cosmo)
+* Jiang => need a global coordinate system (ok for planets, not projections like cosmo)\\
 
-\cite{perraudin2019deepsphere}
+\section{Method [1 pages]}
 
-\section{Method [2 pages]}
-
-* HEALPix: improvement from DeepSphere v1
+* HEALPix: improvement from DeepSphere v1 \cite{perraudin2019deepsphere}
 * equiangular: Renata \& Pascal
 
-\section{Rotation equivariance [2 pages]}
+\section{Rotation equivariance [2.5 pages]}
+
 \subsection{Link with the Laplace-Beltrami Operator}
@@
 
+\subsection{Equivariance error}
+
+* define a measure of equiv error\\
+* show convergence empirically\\
+* improved upon V1\\
+* no difference in practice (see experiment xx) => NNs are resilient to equiv error\\
+
 \section{Experiments [2 pages]}
+Which experience show that DeepSphere V1 and V2 are equivalent in practice.
 
@@
 
-* small: better perf than gauge and Jiang. due to icosahedron distortion? to be confirmed
-* cannot compare with Mudigonda (16 vs 1 input channel)
-* full: we scale => lead to better perf?
+* small: better perf than gauge and Jiang. due to icosahedron distortion? to be confirmed\\
+* cannot compare with Mudigonda (16 vs 1 input channel)\\
+* full: we scale (50B pixels, 20TB) => lead to better perf?\\
 
-\section{Conclusion}
+\subsection{GHCN}
 
-* DeepSphere seems to be in the sweet spot of tradeoffs. Recall the desiderata.
-  * Not the most general, but sufficient empirically
-  * scales linearly => cannot do better ($n^1.25$ for HEALPix)
-  * flexible => independent of the sampsamples can be 
-* anisotropy (most general) doesn't help. research question: when can it be useful?
+* task is artificial, but it shows DeepSphere's flexibility\\
+* structure (looking around) help for prediction\\
 
-future work:
-* when anisotropy needed?
-* irregular sampling while respecting the geometry
-* beyond the sphere, any manifold
+\section{Conclusion [0.5 pages]}
+
+* DeepSphere seems to be in the sweet spot of tradeoffs. Recall the desiderata.\\
+  * respect geometry: No need for a very precise equivariance, i.e. a very good graph...\\
+  * Not the most general (restricted to isotropic filters), but didn't hurt perf in any experiment\\
+  * scales linearly => cannot do better ($n^1.25$ for best HEALPix, linear for not optimal)\\
+  * flexible => independent of the sampling\\
+
+future work:\\
+* when anisotropy useful? (research question)\\
+* irregular sampling while respecting the geometry\\
+* beyond the sphere, any manifold\\
 
@@
 
+{\LARGE \sc {Title of the paper: Supplementary Material}}
 \appendix
-\section{Appendix}
+\section{Proof of theorem}
 
-\subsection{}
+\section{Experiments details}
 

### 2019-07-22 main.tex
small updates (mdeff)

@@
 \begin{abstract}
-story / main point:
+
+story: there are tradeoffs when designing a spherical CNN
 
@@
 * Cohen gauge => fixes scale, at the price of deformation (sphere => icosahedron)\\
-* Esteves => ?
+* Esteves => ? \\
 * Jiang => need a global coordinate system (ok for planets, not projections like cosmo)\\
@@
 
-\subsection{Convergence theorem}
+\subsection{HEALPix: convergence theorem}
+
+\subsection{Equiangular}
+
+explain rapidly Renata \& Pascal
 
@@
 * define a measure of equiv error\\
-* show convergence empirically\\
+* show convergence empirically (for Nside up to 1024) \\
 * improved upon V1\\
@@
 \section{Experiments [2 pages]}
-Which experience show that DeepSphere V1 and V2 are equivalent in practice.
+
+Show: \\
+* meet the desiderata \\
+* DeepSphere V1 and V2 are equivalent in practice \\
+* anisotropy doesn't help \\
 
@@
 
-* same perf as other spherical CNNs, but 40 times faster
-* compare the two samplings => not much difference
+* same perf as other spherical CNNs, but 40 times faster \\
+* compare the two samplings => not much difference \\
 
@@
 
-other sphercial CNNs cannot scale to 10M pixels (tested on 10k at most)
+* other sphercial CNNs cannot scale to 10M pixels (tested on 10k at most) \\
+* redo the experiment with the optimal graph (cannot just copy the old results) and compare \\
 
@@
 \newpage
-
 \subsubsection*{Author Contributions}
-If you'd like to, you may include  a section for author contributions as is done
-in many journals. This is optional and at the discretion of the authors.
+Left blank for anonymity reason
+% If you'd like to, you may include  a section for author contributions as is done
+% in many journals. This is optional and at the discretion of the authors.
 
 \subsubsection*{Acknowledgments}
-Use unnumbered third level headings for the acknowledgments. All
-acknowledgments, including those to funding agencies, go at the end of the paper.
+Left blank for anonymity reason
+% Use unnumbered third level headings for the acknowledgments. All
+% acknowledgments, including those to funding agencies, go at the end of the paper.
 
@@
 \appendix
+
 \section{Proof of theorem}

### 2019-08-26 main.tex
add som tables

@@
 
+\begin{table}[ht]
+    \centering
+    \begin{tabular}{l|c c r r}
+        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{2}{c}{speed}\\
+        \cmidrule(lr){2-3} \cmidrule(lr){5-6}
+        \multicolumn{1}{l}{Method} & Accuracy & F1-score & inference & training \\ \hline
+        Cohen \emph{s2cnn} & - & - & 38ms & 50h\\
+        % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
+        Esteves \emph{sphericalcnn} & 79.18 & 79.36 & 9.8ms & 2h52\\ \hline
+        Deepsphere \emph{Equiangular} & 79.25 & 79.36 & 0.98ms & 2h33m \\
+        Deepsphere \emph{HEALPix} & 80.42 & 80.65 & 1.0ms & 48m
+    \end{tabular}
+    \caption{Performance of different models}
+    \label{tab:SHREC17_class}
+\end{table}
+
+\begin{table}[ht]
+    \centering
+    \begin{tabular}{l|c c c c|c c c c}
+     & \multicolumn{4}{c|}{micro (label average)} & \multicolumn{4}{c}{macro (instance average)} \\
+    Method & P@N & R@N & F1@N & mAP & P@N & R@N & F1@N & mAP \\ \hline
+    Cohen \emph{s2cnn} & 0.701 & 0.711 & 0.699 & 0.676 & - & - & - & - \\
+    % Cohen \emph{s2cnn\_simple} & 0.704 & 0.701 & 0.696 & 0.665 & 0.430 & 0.480 & 0.429 & 0.385\\
+    Esteves \emph{sphericalcnn} & 0.717 & 0.737 & - & 0.685 & 0.450 & 0.550 & - & 0.444\\ \hline
+    Deepsphere \emph{Equiangular} & 0.709 & 0.700 & 0.698 & 0.665 & 0.439 & 0.489 & 0.439 & 0.403 \\
+    Deepsphere \emph{HEALPix} & 0.725 & 0.717 & 0.715 & 0.686 & 0.475 & 0.508 & 0.468 & 0.428
+    \end{tabular}
+    \caption{Performance of different models over SHREC17 perturbed dataset as a retrieval task, using the official script of the competition.}
+    \label{tab:SHREC17_retriev}
+\end{table}
+* add MN40 too?
+* add improved graph results too?
+
 \subsection{cosmo}
@@
 
+\begin{table}[!ht]
+\begin{tabular}{l|c c c c c c c c c}
+        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
+        \cmidrule(lr){2-5}\cmidrule(lr){6-8}\cmidrule(lr){9-10}
+        \multicolumn{1}{l}{Method} & BG & TC & AR & mean & TC & AR & mean & inference & training \\ \hline
+        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
+        Jiang et al. & 97 & 94 & 93 & 94.67 & - & - & - & - & -\\
+        Jiang (bsize 64) & 95.2 & 93.9 & 95.7 & 94.95 & 11.08 & 65.21 & 38.41 & 10.2 ms & 10h14m\\
+        % 328'339
+        Cohen et al. (S2R) & 97.3 & 97.8 & 97.3 & 97.5 & - & -& 68.6\\
+        Cohen et al. (R2R) & 97.4 & 97.9 & 97.8 & 97.7 & - & -& 75.9\\ \hline
+        DS (ico) & $98.2\pm 0.5$ & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $97.8\pm 0.3$ & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 25 ms & 25h \\
+        %DS (non-weighted) & 99.8 & 73.3 & 90.2 & 87.81 & 79.29 & 97.93 & 88.61 & 30ms & 3h50m\\
+        DS (non-weighted) & 99.6 & 66.6 & 96.1 & 87.41 & 83.66 & 97.57 & 90.62 & 30ms & 12h20m\\ \hline
+        % 12'926'432
+        DeepSphere (equi non-weighted) & 99.9 & 31.3 & 75.2 & 68.80 & 55.53 & 94.85 & 75.19 & 567 ms & 48h
+    \end{tabular}
+    \caption{Climate pattern segmentation accuracy (\%) for BG, TC
+and AR classes plus mean accuracy, average precision for positive classes and mean as well.}
+\end{table}
+
+trade off between AP and accuracy in the case of TC class, it seems.
+
 \subsection{GHCN}
@@
 * structure (looking around) help for prediction\\
+
+dense regression
+\begin{table}[!ht]
+    \centering
+    \begin{tabular}{c|ccc}
+        order & MSE & MAE & R2 \\ \hline 
+        0 & 10.88 & 2.42 & 0.896\\
+        1 & 8.91 & 2.20 & 0.906\\
+        4 & 8.20 & 2.11 & 0.919\\
+        9 & 8.38 & 2.12 & 0.915\\
+    \end{tabular}
+    \caption{The task is to find the temperature for the day T, knowing the temperature of the 5 previous days. Evolution of performance in respect of the order of the filter}
+    \label{tab:future_results}
+    ~\\[1cm]
+    \begin{tabular}{c|ccc}
+        order & MSE & MAE & R2 \\ \hline 
+        1 & 134.01 & 10.51 & -0.319\\
+        4 & 129.48 & 10.31 & -0.274\\
+        9 & 141.68 & 10.82 & -0.389\\
+    \end{tabular}
+    \caption{Predicting the present day (T-1) instead of the future day T}
+    \label{tab:present_results}
+\end{table}
+
+global regression
+\begin{table}[!ht]
+    \centering
+    \begin{tabular}{c|ccc}
+        order & MSE & MAE & R2 \\ \hline 
+        0 & 0.58 & 0.42 & -0.92\\
+        4 & 0.50 & 0.18 & 0.597\\
+    \end{tabular}
+    \caption{Find day in year using precipitation}
+    \label{tab:future_results}
+    ~\\[1cm]
+    \begin{tabular}{c|ccc}
+        order & MSE & MAE & R2 \\ \hline 
+        0 & 0.10 & 0.10 & 0.881\\
+        4 & - & - & -\\
+    \end{tabular}
+    \caption{Using temperature feature that are already periodical}
+    \label{tab:present_results}
+\end{table}
 
@@
 \section{Experiments details}
+* Network architecture and details
+\subsection{3D object Recognition}
+HEALPix sampling, Nside = 32
+
+\subsection{cosmo}
+HEALPix sampling, Nside = 1024, with improved graph
+
+\subsection{climate event detection}
+icosahedron sampling, level-5 resolution
+
+\subsection{GHCN}
+non-regular sampling
 

### 2019-08-28 main.tex
Updates from Overleaf

@@
 \usepackage{url}
+\usepackage{breqn}
+\usepackage{booktabs}
+
+% ------ Martino's usepackage ------
+\usepackage{graphicx}
+\usepackage{amsthm}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\newtheorem{definition}{Definition}[section]
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{prop}{Proposition}
+\newtheorem*{remark}{Remark}
+\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
+% ----------------------------------
 
@@
 \subsection{HEALPix: convergence theorem}
+We need now to define some geometrical quantities that we'll need.
+Given a sampling $x_0, ..., x_{n-1}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to the $i$th point of the sampling, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing the i-th patch.
+Define $d^{(n)} := \max_{i=0, ..., n}d_i$ and $A^{(n)}=\max_{i=0, ..., n}A_i$.\\
+	\begin{theorem}
+		For a sampling $\mathcal P = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi area and such that $d^{(n)})\leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian operator $\frac{|\mathbb S^2|}{4\pi t_n}L^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\triangle_{\mathbb S^2}$  for $n\to\infty$:
+		$$ \lim_{n\to\infty}\frac{|\mathbb S^2|}{4\pi t_n} L_n^{t_n}f(y) =  \triangle_{\mathbb S^2}f(y).$$
+		\label{theo:pointwise convergence in the healpix case}
+	\end{theorem}
 
 \subsection{Equiangular}
+Khasanova et al.
+\cite{Frossard2017GraphBasedCO} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling.
+They studied a way to build a graph to analyze images produced by omnidirectional cameras.
+In their work they assume that the image is sampled on the sphere on the equiangular sampling.
+They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes.
+In other words, they solve the minimization problem
 
-explain rapidly Renata \& Pascal
+\begin{equation}\label{eq:minimization frossard}
+	\min_{W\in\mathcal G} \left|\mathcal{F}\left(\mathbf{y}\left(v_{ e}\right)\right)-\mathcal{F}\left(\mathbf{y}\left(v_{ i}\right)\right)\right|
+\end{equation}
+for the adjacency matrix $W$, where $\mathbf y(v_i)$ is the image of the object on the sphere centered on the vertex $v_i$, and $\mathcal F (\mathbf y(v_e))$ is the response of the filter at the vertex $v_e$ that lies at the same longitude of the vertex $v_i$ but on the equator.
+In their work they prove that the optimal weights solving the minimization problem (\ref{eq:minimization frossard}) are given by weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
+\begin{equation}\label{eq:frossard weights}
+	w_{ij} = \frac{1}{\norm{x_i-x_j}}
+\end{equation}
+This construction is interesting since it is adapted to the equiangular sampling, and leads to a very sparse graph with only 4 neighbors per vertex.
+Furthermore, to obtain the weights (\ref{eq:frossard weights}) every calculation was done in the \textit{spatial domain}, without any consideration about the spectral interpretation of the filter.
+In order to compare it to the HKGL we show the equivariance error by spherical harmonic degree in figure \ref{fig:Equivariance error of the Frossard-Khasanove graph}.
+It can be appreciated how this construction performs a little worse that the full HKGL for low bandwidth samplings, but converges faster than the \textit{full} HKGL, and its spectrum looks much more similar to the one of $\Delta_{\mathbb S^2}$.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{figures/KhasanovaFrossardgraphonequiangularsampling.png}
+
+	\caption{\label{fig:Equivariance error of the Frossard-Khasanove graph}Equivariance error of the Khasanova-Frossard graph on the equiangular sampling with bandwidth $b=8$ by spherical harmonic degree $\ell$.}
+\end{figure}
+
+The Khasanova-Frossard graph showed us that it is possible to do better than the HKGL on the equiangular sampling.
+We asked ourself if there's a general way of building a more equivariant graph than the HKGL that is straightforward to implement on any sampling scheme of the sphere.
+To answer this question in the next section we study a more complex way to approximate the Laplace-Beltrami operator $\Delta_{\mathbb S^2}$: the linear FEM Laplacian.
+We will see that the comparison between the FEM Laplacian and the graph Laplacian will give us precious insights to better understand the limitations of graph Laplacians when it comes to deal with non uniform samplings of the sphere.
 
@@
 * define a measure of equiv error\\
+Take a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, ..., n\}$ of the sphere, a weighted undirected graph $G(V, E, \mathbf W)$, a signal $f: \mathbb S^2\to\mathbb R$ and its sampled representation $\mathbf f:\ f_i=f(v_i)$.
+Suppose that there exists a sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \mathbf f$ defined on a suitable subspace $F$ of $L^2(\mathbb S^2)$ such that it is invertible, i.e., we can unambiguously reconstruct the function $f\in F$ from its sampled values $\mathbf f$.
+The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing \cite{Driscoll:1994:CFT:184069.184073}.
+Define the rotation operator $\Lambda(g), g\in SO(3)$: $\Lambda(g) f(\omega)=f\left(g^{-1} \omega\right)$.\\
+
+We now want to understand how to set the edges and the weights of $G$ such that
+\begin{equation}\label{eq:equivariance}
+T \Lambda(g) T^{-1} \Omega_k T f = \Omega_k T \Lambda(g) f
+\end{equation}
+i.e., the graph convolution $\Omega_k$ and any rotation $\Lambda(g)$ commute.
+
+Verifying equation (\ref{eq:equivariance}) is really hard in practice, due to the fact that for almost all samplings schemes $V$ it is not known if there exists a space $F$ in which $T$ is invertible.
+A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds \cite{Driscoll:1994:CFT:184069.184073}.
+With all the other sampling schemes, there are no sampling theorems available, but there are implementations of discrete SHT to reconstruct a sampled signal $\mathbf f$, thus providing a way to approximate $T^{-1}$.
+Thanks to this we are able, for a given sampling, a given function $f$, a given rotation $g$, and a given kernel $k$, to compute the \textit{normalized equivariance error}
+\begin{equation}\label{eq:equivariance error}
+E_{G}(f, g) = \left(\frac{ \norm {T \Lambda(g) T^{-1} \Omega_k Tf - \Omega_k T \Lambda(g) f}_{L^2(\mathbb R^2)}}{\norm {Tf}_{L^2(\mathbb R^2)}}\right)^2
+\end{equation}
+where $T^{-1}$ is substituted with a discrete SHT in case $T$ is not invertible.
+A measure of how equivariant a graph is with respect to rotations will then be given by the \textit{mean equivariance error}
+\begin{equation}\label{eq:mean equivariance error}
+\overline E_G = \mathbb E_{f, g}\ 	E_G(f, g) 
+\end{equation}
+In practice the expected value is obtained by averaging over a finite number of random functions and random rotations.
+The mean equivariance error $\overline E_G$ gives us an indication of how close the graph $G$ is from being equivariant to rotations.
+Now we state an intuitive concept that explains how to construct rotation invariant graphs, i.e.
+graphs such that $\overline{E_G}$ is small.
+The mean equivariance error $\overline{E_G}$ will be small if the scalar product $\mathbf f^T \mathbf v_{i(\ell, m)}$ well approximates $\hat {f}(\ell,m)$ i.e., the $L^2$ scalar product of the continuous signal \\
+	$\hat {f}(\ell,m)= \int_{\eta \in \mathbb S^2}f(\eta)Y_\ell^m(\eta)d\mu(\eta)$.
+
+	\textit{If $V$ is an equal area sampling scheme}, i.e.
+the area around each pixel $v_i$ is the same, $\overline{E_G}$ will be small if the graph Laplacian $\mathbf L$ is such that its eigenvectors $\mathbf v_i$ well approximate the eigenfunctions of the Laplace-Beltrami operator $\Delta_{\mathbb S^2}$ evaluated in the points of the sampling scheme, i.e.,
+	$$
+	\mathbf v_{i(\ell, m)} \approx Y_\ell^m(x_i)
+	$$
+
+In this way we framed the problem of constructing a rotation invariant graph with the more general problem of coming up with a matrix $\mathbf L$ with some specific spectral properties.
+
 * show convergence empirically (for Nside up to 1024) \\
 * improved upon V1\\
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{figures/DeepSphereonHEALPix.png}	
+	\includegraphics[width=\textwidth]{figures/OptimalHKGLonHEALPix.png}	
+	\caption{\label{fig:DeepSphere equivariance error}Mean equivariance error of the diffusion filter $\exp(-\Lambda)$ for $G$, $G'$ and the full HKGL, by spherical harmonic degree.
+Notice the difference in the scale of the y axis for DeepSphere, that reaches errors up to 30\%.}
+\end{figure}
+
 * no difference in practice (see experiment xx) => NNs are resilient to equiv error\\
@@
         \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{2}{c}{speed}\\
-        \cmidrule(lr){2-3} \cmidrule(lr){5-6}
+        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
         \multicolumn{1}{l}{Method} & Accuracy & F1-score & inference & training \\ \hline
@@
 
+% jiang like correct: 99.81631631, 13.18655162, 52.62412867, 55.20899887;  0.3990812 , 0.80056251, 0.59982186; 4 ms; 2h40
+% more feat: 99.67871329, 38.78607557, 66.37910064, 68.2812965: 0.99981102, 0.60714174, 0.83236147, 0.71975161; 12ms; 6h20
+
 \subsection{GHCN}
@@
     \caption{Find day in year using precipitation}
-    \label{tab:future_results}
+    \label{tab:glob_prec}
     ~\\[1cm]
@@
     \caption{Using temperature feature that are already periodical}
-    \label{tab:present_results}
+    \label{tab:glob_all}
 \end{table}
@@
 
+\begin{definition}{}(Heat Kernel Graph Laplacian operator)\\
+	\label{def:Heat Kernel Graph Laplacian operator}
+	\text{Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of the manifold we define the \textbf{operator} }$L_n^t$ such that
+	$$L_n^tf(y) := \frac{1}{n}\left[ \sum_{i=0}^{n-1} \exp{-\frac{||x_i-y||^2}{4t}}\left(f(y)-f(x_i)\right)\right]$$
+\end{definition}
+\begin{definition}{}(from \cite[Belkin et al.
+]{Belkin:2005:TTF:2138147.2138189}Functional approximation to the Laplace-Beltrami operator)\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, where $\text{vol}(\mathcal M)$ is the volume of $\mathcal M$.
+We define the functional approximation to the Laplace-Beltrami operator to be the operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
+	\label{def:Functional approximation to the Laplace-Beltrami operator}
+	$$ L^tf(y) = \int_{\mathcal M}e^{-\frac{||y-x||^2}{4t}}\left(f(y)-f(x)\right)d\mu(x)$$
+\end{definition}
+
+The core of the work of Belkin et al. is the proof, that we will not discuss, of the following proposition.
+
+\begin{prop} 	Let $\mathcal M$ be a $k$-dimensional compact smooth manifold embedded in some euclidean space $\mathbb R^N$, and fix $p\in\mathcal M$.
+Let the data points $x_1, ...
+x_n$ be sampled form a uniform distribution on the manifold $\mathcal M$.
+Set $t_n=n^{-\frac{1}{k+2+\alpha}}$, for any $\alpha>0$ and let $f\in\mathcal C_\infty(\mathcal M)$.
+Then
+	$$\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(p) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\triangle_{\mathcal M}f(p).$$
+	\label{prop:3}
+\end{prop}
+
+Our first goal is to prove the following Proposition: 
+\vspace{0.5cm}
+\begin{prop}\label{prop:1}
+	For an equal area sampling $\{x_i\in\mathbb S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the euclidean distance $||\cdot||$ with Lipschitz constant $\mathcal L_f$
+	$$
+	\left| \int_{\mathbb S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right|\leq \mathcal L_fd^{(n)}.
+	$$
+	Furthermore, for all $y\in\mathbb S^2$ the Heat Kernel Graph Laplacian operator $L^t_n$ converges pointwise to the functional approximation of the Laplace Beltrami operator $L^t$
+	$$ L_n^tf(y)\xrightarrow{n\to\infty} L^tf(y).$$
+\end{prop} 
+\vspace{0.5cm}
+
+\begin{proof}
+
+	Let us assume that the function $f:\mathbb R^3\rightarrow \mathbb R$ is Lipschitz with Lipschitz constant $\mathcal L_f$, we have
+
+	$$\left| \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right| \leq \mathcal L_fd^{(n)}\frac{1}{n} $$
+
+	So, by triangular inequality and by summing all the contributions of all the $n$ patches
+	$$\left| \int_{\mathbb S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right| \leq \sum_i \left| \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right|\leq n  \mathcal L_fd^{(n)}\frac{1}{n} = \mathcal L_fd^{(n)}$$
+	Thanks to this result, we have the following two pointwise convergences
+
+	$$\forall f \text{ Lipschiz,}\quad \forall y\in\mathbb S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}\rightarrow \int e^{-\frac{||x-y||^2}{4t}}d\mu(x)$$
+	$$\forall f \text{ Lipschiz,}\quad \forall y\in\mathbb S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}f(x_i)\rightarrow \int e^{-\frac{||x-y||^2}{4t}}f(x)d\mu(x)$$
+
+	Definitions \ref{def:Heat Kernel Graph Laplacian operator} and \ref{def:Functional approximation to the Laplace-Beltrami operator} end the proof.
+\end{proof}
+\vspace{0.5cm}
+
+Now, we just proved that \textit{keeping t fixed} $L_n^tf(x)\rightarrow L^tf(x)$. Now our goal is to prove that:
+
+\vspace{0.5cm}
+\begin{prop}\label{prop:2}
+	Given a sampling regular enough i.e., for which we assume $A_i=A_j \ \forall i,j\text{ and }d^{(n)}\leq \frac{C}{\sqrt{n}}$, for a fixed $t>0$, a fixed Lipschitz function $f$ and a fixed point $y\in\mathbb S^2$ there exists a sequence $t_n = n^\beta, \beta<0$ such that
+$$
+\forall f \text{ Lipschitz, } \forall x\in\mathbb S^2 \quad \left|\frac{1}{4\pi t_n^2}\left(L_n^{t_n}f(x) - L^{t_n}f(x)\right)\right|\xrightarrow{n\to \infty}0.
+$$
+\end{prop}
+\vspace{0.5cm}
+
+The main result of this section, theorem  \ref{theo:pointwise convergence in the healpix case}, is then an immediate consequence of Proposition \ref{prop:2} and Proposition \ref{prop:3}.
+
+\begin{proof}[Proof of Proposition \ref{prop:2}]
+
+We define for simplicity of notation
+\begin{align}
+	\phi^t(x;y) &:= e^{-\frac{||x-y||^2}{4t}}\left(f(y)-f(x)\right)\\
+	K^t(x,y) &:=  e^{-\frac{||x-y||^2}{4t}}
+\end{align}
+We start by writing the following chain of inequalities
+\begin{align*}
+	||L_n^tf-L^tf||_\infty &= \max _{y\in \mathbb S^2} \left|L_n^tf(y)-L^tf(y)\right|\\
+	&= \max _{y\in \mathbb S^2} \left| \frac{1}{n} \sum_{i=1}^n \phi^t(x_i; y)- \int_{\mathbb S^2} \phi^t(x;y)d\mu(x) \right|\\
+	&\leq \max _{y\in \mathbb S^2}  \sum_{i=1}^n   \left| \frac{1}{n}  \phi^t(x_i; y)- \int_{\sigma_i} \phi^t(x;y)d\mu(x) \right|\\
+	&\leq  \max _{y\in \mathbb S^2} \left[\mathcal L_{\phi^t_y}d^{(n)} \right]\\
+\end{align*}
+where $\mathcal L_{\phi^t_y}$ is the Lipschitz constant of $x \rightarrow \phi^t(x, y)$ and where we used for the last inequality Proposition \ref{prop:1}.
+If we assume $d^{(n)}\leq \frac{C}{\sqrt{n}}$ we have that
+
+$$||L_n^tf-L^tf||_\infty  \leq  \max _{y\in \mathbb S^2} \left[ \mathcal L_{\phi^t_y} \frac{C}{\sqrt{n}} \right]$$
+
+Let's now find the explicit dependence $t\rightarrow \mathcal L_{\phi^t_y}$
+\begin{align*}
+	\mathcal L_{\phi^t_y} &= ||\partial_x\phi^t(\cdot;y)||_\infty\\&
+	= ||\partial_x\left(K^t(\cdot;y)f\right)||_\infty\\&
+	= ||\partial_x K^t(\cdot;y)f + K^t(\cdot;y)\partial_x f||_\infty\\&
+	\leq ||\partial_x K^t(\cdot;y)f||_\infty + ||K^t(\cdot;y)\partial_x f||_\infty\\&
+	\leq  ||\partial_x K^t(\cdot;y)||_\infty||f||_\infty + ||K^t(\cdot;y)||_\infty||\partial_x f||_\infty\\&
+	= ||\partial_x K^t(\cdot;y)||_\infty||f||_\infty + ||\partial_x f||_\infty\\&
+	= \mathcal L_{K^t_y} ||f||_\infty + ||\partial_xf||_\infty\\&
+	= \mathcal L_{K^t_y} ||f||_\infty + \mathcal L_f
+\end{align*}
+where $\mathcal L_{K^t_y}$ is the Lipschitz constant of $x\rightarrow K^t(x;y)$. We can observe that such constant does not depend on $y$:
+
+$\mathcal L_{K^t_y} = \norm{\partial_x e^{-\frac{x^2}{4t}}}_\infty = \norm{\frac{x}{2t}e^{-\frac{x^2}{4t}}}_\infty = \left.
+\frac{x}{2t}e^{-\frac{x^2}{4t}}\right|_{x=\sqrt{2t}}=(2et)^{-\frac{1}{2}}\propto t ^ {-\frac{1}{2}}$
+
+So we can continue
+$$\begin{aligned}
+	\max _{y\in \mathbb S^2} \left[  \mathcal L_{\phi^t_y} \frac{C}{\sqrt{n}} \right]
+	&\leq  \frac{C}{\sqrt{n}} \left( (2et)^{-\frac{1}{2}} \norm{f}_\infty + \mathcal L_f \right)\\
+	&\leq \frac{C\norm{f}_\infty}{\sqrt{n}(2et)^{1/2}} +   \frac{C}{\sqrt{n}}\mathcal L_f\\
+\end{aligned}$$
+So we have that, rescaling by a factor $\frac{1}{4\pi t^2}$
+\begin{align*}
+	\norm{\frac{1}{4\pi t^2}\left(L_n^tf-L^tf\right)}_\infty&\leq \frac{1}{4\pi t^2}\norm{\left(L_n^tf-L^tf\right)}_\infty \\
+	&\leq \frac{C}{4\pi}\left[\frac{\norm{f}_\infty}{\sqrt{2e}}\frac{1}{\sqrt{n}t^{5/2}} + \frac{\mathcal L_f}{\sqrt{n}t^2}\right]
+\end{align*}
+
+we want $\begin{cases}
+t \rightarrow 0\\
+n \rightarrow \infty\\
+\sqrt{n}t^{5/2} \rightarrow \infty\\
+\sqrt{n}t^2 \rightarrow \infty
+\end{cases}$ in order for $ \frac{C}{4\pi}\left[\frac{\norm{f}_\infty}{\sqrt{2e}}\frac{1}{\sqrt{n}t^{5/2}} + \frac{\mathcal L_f}{\sqrt{n}t^2}\right] \xrightarrow[t\to 0 ]{n\to\infty}0$
+
+This is true if $\begin{cases}
+t(n) = n^\beta, &\beta\in(-\frac{1}{5}, 0) \\
+t(n) = n^\beta, &\beta\in(-\frac{1}{4}, 0)
+\end{cases} \implies t(n) = n^\beta, \quad \beta\in(-\frac{1}{5}, 0)$
+
+Indeed
+
+$\sqrt{n}t^{5/2}=n^{5/2\beta+1/2}\xrightarrow{n \to \infty} \infty$ since $\frac{5}{2}\beta+1/2>0 \iff \beta>-\frac{1}{5}$
+
+$\sqrt{n}t^2=n^{2\beta+1/2}\xrightarrow {N \to \infty} \infty$ since $2\beta+1/2>0 \iff \beta>-\frac{1}{4}$
+
+So, for $t=n^\beta$ with $\beta\in(-\frac{1}{5}, 0)$ we have that
+
+$$\begin{cases}
+(t_n)\xrightarrow{n\to\infty}0\\
+\norm{\frac{1}{4\pi t_n^2}L_n^{t_n}f-\frac{1}{4\pi t_n^2}L^{t_n}f}_\infty  \xrightarrow{n\to\infty}0
+\end{cases}$$
+
+\end{proof}
+
+The proof of theorem \ref{theo:pointwise convergence in the healpix case} is now trivial:
+\begin{proof}[Proof of Theorem \ref{theo:pointwise convergence in the healpix case}]
+	Thanks to Proposition \ref{prop:2} and Proposition \ref{prop:3}	we conclude that $\forall y\in\mathbb S^2 $
+	$$\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) =  \lim_{n\to\infty}\frac{1}{4\pi t_n^2} L^{t_n}f(y) = \frac{1}{|\mathbb S^2|}\triangle_{\mathbb S^2}f(y) $$
+\end{proof}
+
+The proof of this result is instructive since it shows that we need to impose some regularity conditions on the sampling.
+If the sampling is equal area as HEALPix, meaning that all the patches $\sigma_i$ have the same area, then we need to impose that $ d^{(n)}\leq \frac{1}{\sqrt{n}}$.
+If the sampling is not equal area, meaning that in general $A_i\neq A_j$, it can be shown that we need a slightly more complex condition: $\max_{i=0,...,n-1}d_iA_i\leq Cn^{-\frac{3}{2}}$.\\
+In the work of Belkin et al.
+\cite{Belkin:2005:TTF:2138147.2138189} the sampling is drawn form a uniform random distribution on the sphere, and their proof heavily relies on the uniformity properties of the distribution from which the sampling is drawn.
+In our case the sampling is deterministic, and the fact that for a sphere there doesn't exist a regular sampling with more than 12 points (the vertices of a icosahedron) is indeed a problem that we need to overcome by imposing the regularity conditions above.
+
+To conclude, we can see that the result obtained has the same form than the result obtained in \cite{Belkin:2005:TTF:2138147.2138189}.
+Given the kernel density $t(n)=n^\beta$, if Belkin et al.
+proved convergence in the random case for $\beta \in (-\frac{1}{4}, 0)$, we proved convergence in the HEALPix case for $\beta \in (-\frac{1}{5}, 0)$.
+This kind of result can be interpreted in the following way.
+In order to have this pointwise convergence, we need to reduce the kernel width but \textit{not so fast} compared to the resolution of the graph.
+In other words, the kernel width has to be reduced but is somewhat limited by the resolution of the graph.
+In the next section we'll see how to set in practice a good kernel width $t$ given a graph resolution $n$.
+\begin{remark}
+	Pointwise convergence is just a necessary condition for spectral convergence.  Theorem \ref{theo:pointwise convergence in the healpix case} does not imply convergence of eigenvalues and eigenvectors.
+\end{remark}
+
 \section{Experiments details}
@@
 \subsection{3D object Recognition}
-HEALPix sampling, Nside = 32
+\subsubsection*{HEALPix}
+HEALPix sampling, input signal at Nside = 32
 
+CNN having 5 convolutional layers, a global average pooling layer and a fully-connected layer at the end, such as this:
+\begin{dmath}
+    [GC_{16}\, +\, BN\, +\, ReLU]_{nside32}\, +\, \textrm{Pool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{nside16}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{nside8}\, +\, \textrm{Pool}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{nside4}\, +\,\textrm{Pool}\, +\, [GC_{256}\, +\, BN\, +\, ReLU]_{nside2}\, +\, \textrm{Pool}\, +\, GAP\, +\, FCN\, +\, \textrm{softmax}
+\end{dmath}
+Each convolutional layer has a graph convolution using Chebyshev polynomial approximation, batch normalization and ReLU activation.
+The order of the Chebyshev polynomial is 4 for each layer, the number of feature maps are [16, 32, 64, 128, 256] respectively and down-sampling to the immediate smaller resolution for each layer.
+
+number of parameter: 190k TODO exact number?
+
+batch size 32, adam optimizer, constant learning rate of $5 \cdot 10^{-2}$
+cross-entropy loss, and add triplet loss from ``Esteves et al.´´
+\subsubsection*{Equiangular}
+Equiangular sampling with bandwidth of 64 in longitude and latitude.
+The architecture of the Neural Network is exactly the same, with a stride of [2, 2] for each pooling layer
 \subsection{cosmo}
@@
 \subsection{climate event detection}
+\subsubsection*{Icosahedron}
 icosahedron sampling, level-5 resolution
 
+CNN with encoder decoder architecture
+encoder:\\
+\begin{dmath}
+    [GC_{32}\, +\, BN\, +\, ReLU]_{L5}\,+\, [GC_{64}\, +\, BN\, +\, ReLU]_{L5}\, +\, \textrm{Pool}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L4}\, +\, \textrm{Pool}\, +\, [GC_{256}\, +\, BN\, +\, ReLU]_{L3}\, +\,\textrm{Pool}\, +\, [GC_{512}\, +\, BN\, +\, ReLU]_{L2} +\,\textrm{Pool}\, +\, [GC_{512}\, +\, BN\, +\, ReLU]_{L1} +\,\textrm{Pool}\, +\, [GC_{512}]_{L0}
+\end{dmath}
+decoder:\\
+\begin{dmath}
+    \textrm{Unpool}\, +\,[GC_{512}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{concat}\, +\, [GC_{512}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Unpool}\, +\, [GC_{256}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{concat}\, +\, [GC_{256}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{Unpool}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{concat}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L3}\, +\,\textrm{Unpool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L4}\,+\, \textrm{concat}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L4}\, +\,\textrm{Unpool}\,  +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L5}\,+ \, [GC_3]_{L5}
+\end{dmath}
+number of parameters: 2,2M
+
+concat the results of the corresponding encoder layer after the pooling. Not similar to Jiang and 4 times the feature maps. Redo experiment WIP
+
+batch size 64, adam optimizer, constant learning rate of $1 \cdot 10{-3}$, cross-entropy loss, both weighted and non weighted.
+Weight chosen with scikit-learn "compute\_class\_weight" on the training set
+\subsubsection*{Correct Icosahedron}
+encoder:\\
+\begin{dmath}
+    [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{Pool}\,+\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\, \textrm{Pool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\,\textrm{Pool}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Pool}\,  +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L0}
+\end{dmath}
+decoder:\\
+\begin{dmath}
+    \textrm{Unpool}\, +\,[GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{concat}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Unpool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{concat}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{Unpool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{concat}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\,\textrm{Unpool}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\,+\, \textrm{concat}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\,\textrm{Unpool}\,  +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{concat}\, +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\, + \,[GC_3]_{L5}
+\end{dmath}
+number of parameters: 590'976  % more feat is 16 times more
+
+concat the results of the corresponding encoder layer after the graph convolution. Similar to ``Jiang et al.´´
+\subsubsection*{Equiangular}
+Equiangular sampling, with a latitude bandwidth 384 and longitude bandwidth 576.
+
+Due to memory problem, could not use the same architecture
+
+encoder:\\
+\begin{dmath}
+    [GC_{16}\, +\, BN\, +\, ReLU]_{bw}\,+\, [GC_{16}\, +\, BN\, +\, ReLU]_{bw}\, +\, \textrm{Pool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{bw/16}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{bw/64}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{bw/64}
+\end{dmath}
+decoder:\\
+\begin{dmath}
+    \textrm{Unpool}\, +\,[GC_{128}\, +\, BN\, +\, ReLU]_{bw/64}\, +\, \textrm{concat}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{bw/64}\, +\, \textrm{Unpool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{bw/64}\, +\, \textrm{concat}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{bw/64}\, +\, \textrm{Unpool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{bw/16}\, +\, \textrm{concat}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{bw/16}\, +\,\textrm{Unpool}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{bw}\,+\, \textrm{concat}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{bw}\, +\,\textrm{Unpool}\,  +\, [GC_{16}\, +\, BN\, +\, ReLU]_{bw}\,+\,[GC_3]_{bw}
+\end{dmath}
+
+batch size 1
 \subsection{GHCN}
-non-regular sampling
+non-regular sampling, thus no pooling was used
 
+batch size 64, RMSprop optimizer, constant learning rate of $1 \cdot 10{-3}$, MSE loss, order of 5 for all layers
+\subsection*{Dense}
+
+\begin{dmath}
+    [GC_{50}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{1}\, +\, BN\, +\, ReLU]
+\end{dmath}
+
+\subsubsection*{Global}
+
+\begin{dmath}
+    [GC_{50}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, GAP\, +\, FCN
+\end{dmath}
 \end{document}

### 2019-09-02 main.tex
proof and details appendix

@@
 \subsection{HEALPix: convergence theorem}
-We need now to define some geometrical quantities that we'll need.
-Given a sampling $x_0, ..., x_{n-1}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to the $i$th point of the sampling, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing the i-th patch.
+Given a sampling $x_0, ..., x_{n-1}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to the $i$th point of the sampling, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing the $i$th patch.
 Define $d^{(n)} := \max_{i=0, ..., n}d_i$ and $A^{(n)}=\max_{i=0, ..., n}A_i$.\\
@@
 \cite{Frossard2017GraphBasedCO} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling.
-They studied a way to build a graph to analyze images produced by omnidirectional cameras.
-In their work they assume that the image is sampled on the sphere on the equiangular sampling.
 They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes.
@@
 
-The Khasanova-Frossard graph showed us that it is possible to do better than the HKGL on the equiangular sampling.
-We asked ourself if there's a general way of building a more equivariant graph than the HKGL that is straightforward to implement on any sampling scheme of the sphere.
-To answer this question in the next section we study a more complex way to approximate the Laplace-Beltrami operator $\Delta_{\mathbb S^2}$: the linear FEM Laplacian.
-We will see that the comparison between the FEM Laplacian and the graph Laplacian will give us precious insights to better understand the limitations of graph Laplacians when it comes to deal with non uniform samplings of the sphere.
-
 \subsection{Equivariance error}
@@
 
-Verifying equation (\ref{eq:equivariance}) is really hard in practice, due to the fact that for almost all samplings schemes $V$ it is not known if there exists a space $F$ in which $T$ is invertible.
-A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds \cite{Driscoll:1994:CFT:184069.184073}.
-With all the other sampling schemes, there are no sampling theorems available, but there are implementations of discrete SHT to reconstruct a sampled signal $\mathbf f$, thus providing a way to approximate $T^{-1}$.
+Verifying equation (\ref{eq:equivariance}) is really hard in practice, due to the fact that for almost all sampling schemes $V$ it is not known if there exists a space $F$ in which $T$ is invertible.
+A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds \cite{Driscoll:1994:CFT:184069.184073}, and thus we have a closed form of $T^{-1}$.
+For sampling schemes where no such sampling theorem is available, there are implementations of discrete SHT to reconstruct a sampled signal $\mathbf f$, thus providing a way to approximate $T^{-1}$.
 Thanks to this we are able, for a given sampling, a given function $f$, a given rotation $g$, and a given kernel $k$, to compute the \textit{normalized equivariance error}
@@
 Now we state an intuitive concept that explains how to construct rotation invariant graphs, i.e.
-graphs such that $\overline{E_G}$ is small.
-The mean equivariance error $\overline{E_G}$ will be small if the scalar product $\mathbf f^T \mathbf v_{i(\ell, m)}$ well approximates $\hat {f}(\ell,m)$ i.e., the $L^2$ scalar product of the continuous signal \\
-	$\hat {f}(\ell,m)= \int_{\eta \in \mathbb S^2}f(\eta)Y_\ell^m(\eta)d\mu(\eta)$.
+graphs such that $\overline{E_G}$ is small.\\
+The mean equivariance error $\overline{E_G}$ will be small if the scalar product $\mathbf f^T \mathbf v_{i(\ell, m)}$ well approximates $\hat {f}(\ell,m)$ i.e., the $L^2$ scalar product of the continuous signal $\hat {f}(\ell,m)= \int_{\eta \in \mathbb S^2}f(\eta)Y_\ell^m(\eta)d\mu(\eta)$.
 
@@
 \end{table}
-* add MN40 too?
-* add improved graph results too?
+* add MN40 too? \\
+* add improved graph results too? \\
 
@@
 \begin{table}[!ht]
-\begin{tabular}{l|c c c c c c c c c}
-        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
-        \cmidrule(lr){2-5}\cmidrule(lr){6-8}\cmidrule(lr){9-10}
-        \multicolumn{1}{l}{Method} & BG & TC & AR & mean & TC & AR & mean & inference & training \\ \hline
+\begin{tabular}{l|c c c c}
+        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy}\\
+        \cmidrule(lr){2-5}
+        \multicolumn{1}{l}{Method} & BG & TC & AR & mean \\ \hline
         %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
-        Jiang et al. & 97 & 94 & 93 & 94.67 & - & - & - & - & -\\
-        Jiang (bsize 64) & 95.2 & 93.9 & 95.7 & 94.95 & 11.08 & 65.21 & 38.41 & 10.2 ms & 10h14m\\
+        Jiang et al. & 97 & 94 & 93 & 94.67\\
+        Jiang (bsize 64) & 95.2 & 93.9 & 95.7 & 94.95\\
         % 328'339
-        Cohen et al. (S2R) & 97.3 & 97.8 & 97.3 & 97.5 & - & -& 68.6\\
-        Cohen et al. (R2R) & 97.4 & 97.9 & 97.8 & 97.7 & - & -& 75.9\\ \hline
-        DS (ico) & $98.2\pm 0.5$ & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $97.8\pm 0.3$ & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 25 ms & 25h \\
+        Cohen et al. (S2R) & 97.3 & 97.8 & 97.3 & 97.5\\
+        Cohen et al. (R2R) & 97.4 & 97.9 & 97.8 & 97.7\\ \hline
+        DS (ico) & $98.2\pm 0.5$ & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $97.8\pm 0.3$ \\
         %DS (non-weighted) & 99.8 & 73.3 & 90.2 & 87.81 & 79.29 & 97.93 & 88.61 & 30ms & 3h50m\\
-        DS (non-weighted) & 99.6 & 66.6 & 96.1 & 87.41 & 83.66 & 97.57 & 90.62 & 30ms & 12h20m\\ \hline
+        DS (non-weighted) & $99.7\pm 0.1$ & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $87.8\pm 0.5$ \\ \hline
+        % DS (non-weighted) & 99.6 & 66.6 & 96.1 & 87.41\\ \hline
         % 12'926'432
-        DeepSphere (equi non-weighted) & 99.9 & 31.3 & 75.2 & 68.80 & 55.53 & 94.85 & 75.19 & 567 ms & 48h
+        DeepSphere (equi non-weighted) & 99.9 & 31.3 & 75.2 & 68.80
     \end{tabular}
     \caption{Climate pattern segmentation accuracy (\%) for BG, TC
-and AR classes plus mean accuracy, average precision for positive classes and mean as well.}
+and AR classes plus mean accuracy.}
+\end{table}
+
+\begin{table}[!ht]
+\begin{tabular}{l|c c c c c}
+        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
+        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
+        \multicolumn{1}{l}{Method} & TC & AR & mean & inference & training \\ \hline
+        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
+        Jiang (bsize 64) & 11.08 & 65.21 & 38.41 & 10.2 ms & 10h14m\\
+        % 328'339
+        Cohen et al. (S2R) & - & -& 68.6 & - & - \\
+        Cohen et al. (R2R) & - & -& 75.9 & - & -\\ \hline
+        DS (ico) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 25 ms & 25h \\
+        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 30 ms & 13h \\ \hline
+        % DS (non-weighted) & 83.66 & 97.57 & 90.62 & 30ms & 13h\\ \hline
+        % 12'926'432
+        DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
+    \end{tabular}
+    \caption{Climate pattern segmentation average precision for positive classes and mean as wel, plus speed performance for inference (one training pass for one instance)  and training time.}
 \end{table}
@@
 cross-entropy loss, and add triplet loss from ``Esteves et al.´´
+
+30 epochs with augmented dataset, 3 random translation perturbation, or 90 epochs over dataset that can be augmented
 \subsubsection*{Equiangular}
@@
 
-concat the results of the corresponding encoder layer after the pooling. Not similar to Jiang and 4 times the feature maps. Redo experiment WIP
+concat the results of the corresponding encoder layer after the pooling. Not similar to Jiang and 4 times the feature maps.
 
@@
 Weight chosen with scikit-learn "compute\_class\_weight" on the training set
+
+30 epochs
 \subsubsection*{Correct Icosahedron}
@@
 
+8 epochs
+
 encoder:\\
@@
 batch size 64, RMSprop optimizer, constant learning rate of $1 \cdot 10{-3}$, MSE loss, order of 5 for all layers
+
+250 epochs with no augmentation
 \subsection*{Dense}

### 2019-09-03 main.tex
Updates from Overleaf

@@
         % 12'926'432
+        % non-weighted: accuracy (99.28, 33.60, 93.56, mean: 75.4819);AP (46.15, 93.87, mean: 70.01)
+        % weighted:        accuracy (96.52, 97.13, 97.59, mean: 97.08); AP (49.71, 89.23, mean: 69.47)
         DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
@@
 
-trade off between AP and accuracy in the case of TC class, it seems.
+* trade off between AP and accuracy in the case of TC class, it seems.\\
+* change base, influence\\
+*
 
@@
 
-dense regression
+* non-regular sampling with different density over the globe (continent vs ocean)\\
+* resulting graph is not rotation equivariant\\
+* Two different tasks: a dense regression and a global regression\\
+
+\subsubsection*{dense regression - future temperature estimation}
+* Task is to find the temperature at day T, knowing the temperature of the 5 previous days.\\
+* Goal is to change the order of the chebyshev filter to find the influence of the structure.\\
+* order 0 is the same as time series, as the pixel have no information of its neighborhood.\\
+* increasing order is good until threshold.\\
+* The NN indeed predicts the correct temperature at day T, and not day T-1 (baseline) even though there is small difference.\\
+
 \begin{table}[!ht]
     \centering
+    \begin{minipage}{0.48\linewidth}
     \begin{tabular}{c|ccc}
@@
     \end{tabular}
-    \caption{The task is to find the temperature for the day T, knowing the temperature of the 5 previous days. Evolution of performance in respect of the order of the filter}
+    \caption{Future temperature estimation task. Evolution of performance in respect of the order of the graph filter}
     \label{tab:future_results}
-    ~\\[1cm]
+    \end{minipage}
+    \hfill
+    %~\\[1cm]
+    \begin{minipage}{0.48\linewidth}
     \begin{tabular}{c|ccc}
@@
     \end{tabular}
-    \caption{Predicting the present day (T-1) instead of the future day T}
+    \caption{Baseline: testing with the present day (T-1) instead of the future day T}
     \label{tab:present_results}
+    \end{minipage}
 \end{table}
 
-global regression
+\subsubsection*{global regression - day in year estimation}
+* days represented by a sine to represent the periodic nature of the year.\\
+* task too easy, features already periodic\\
+* structure is still helping\\
+
 \begin{table}[!ht]
     \centering
+    \begin{minipage}{0.48\linewidth}
     \begin{tabular}{c|ccc}
@@
     \label{tab:glob_prec}
-    ~\\[1cm]
+    \end{minipage}
+    \hfill
+    %~\\[1cm]
+    \begin{minipage}{0.48\linewidth}
     \begin{tabular}{c|ccc}
@@
         0 & 0.10 & 0.10 & 0.881\\
-        4 & - & - & -\\
+        4 & 0.05 & 0.05 & 0.969\\
     \end{tabular}
-    \caption{Using temperature feature that are already periodical}
+    \caption{Using temperature feature that is already periodical}
     \label{tab:glob_all}
+    \end{minipage}
 \end{table}
@@
   * Not the most general (restricted to isotropic filters), but didn't hurt perf in any experiment\\
-  * scales linearly => cannot do better ($n^1.25$ for best HEALPix, linear for not optimal)\\
+  * scales linearly => cannot do better ($n^{1.25}$ for best HEALPix, linear for not optimal)\\
   * flexible => independent of the sampling\\
@@
 
-concat the results of the corresponding encoder layer after the pooling. Not similar to Jiang and 4 times the feature maps.
+concat the results of the corresponding encoder layer before the graph convolution. Not similar to Jiang and 4 times the feature maps.
 
@@
 30 epochs
-\subsubsection*{Correct Icosahedron}
+\subsubsection*{Jiang Icosahedron}
 encoder:\\

### 2019-09-03 main.tex
move full tables to appendix

@@
 
+\subsubsection*{SHREC17}
+
 \begin{table}[ht]
     \centering
-    \begin{tabular}{l|c c r r}
-        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{2}{c}{speed}\\
-        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
-        \multicolumn{1}{l}{Method} & Accuracy & F1-score & inference & training \\ \hline
-        Cohen \emph{s2cnn} & - & - & 38ms & 50h\\
+    \begin{tabular}{l|c c c c c}
+        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed}\\
+        \cmidrule(lr){2-3} \cmidrule(lr){4-4} \cmidrule(lr){5-6}
+        \multicolumn{1}{l}{Method} & F1-score & mAP & params & inference [ms] & training \\ \hline
+        \cite{cohen_spherical_2018} & 78.85 & 67.6 & 1.4M & 38 & 50h\\
         % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
-        Esteves \emph{sphericalcnn} & 79.18 & 79.36 & 9.8ms & 2h52\\ \hline
-        Deepsphere \emph{Equiangular} & 79.25 & 79.36 & 0.98ms & 2h33m \\
-        Deepsphere \emph{HEALPix} & 80.42 & 80.65 & 1.0ms & 48m
+        \cite{esteves_learning_2017} & 79.36 & 68.5 & 500k & 10 & 2h52\\ \hline
+        DeepSphere \emph{Equiangular} & 79.36 & 66.5 & 190k & 1 & 2h33m \\
+        DeepSphere \emph{HEALPix} & 80.65 & 68.6 & 190k & 1 & 48m\\
+        DeepSphere \emph{Improved HEALPix} & ? & ? & 190k & ? & ?
     \end{tabular}
-    \caption{Performance of different models}
+    \caption{Performance of different models for SHREC'17 task. F1-score computed with sklearn, mAP from the official script of the competition.}
     \label{tab:SHREC17_class}
@@
 
-\begin{table}[ht]
-    \centering
-    \begin{tabular}{l|c c c c|c c c c}
-     & \multicolumn{4}{c|}{micro (label average)} & \multicolumn{4}{c}{macro (instance average)} \\
-    Method & P@N & R@N & F1@N & mAP & P@N & R@N & F1@N & mAP \\ \hline
-    Cohen \emph{s2cnn} & 0.701 & 0.711 & 0.699 & 0.676 & - & - & - & - \\
-    % Cohen \emph{s2cnn\_simple} & 0.704 & 0.701 & 0.696 & 0.665 & 0.430 & 0.480 & 0.429 & 0.385\\
-    Esteves \emph{sphericalcnn} & 0.717 & 0.737 & - & 0.685 & 0.450 & 0.550 & - & 0.444\\ \hline
-    Deepsphere \emph{Equiangular} & 0.709 & 0.700 & 0.698 & 0.665 & 0.439 & 0.489 & 0.439 & 0.403 \\
-    Deepsphere \emph{HEALPix} & 0.725 & 0.717 & 0.715 & 0.686 & 0.475 & 0.508 & 0.468 & 0.428
-    \end{tabular}
-    \caption{Performance of different models over SHREC17 perturbed dataset as a retrieval task, using the official script of the competition.}
-    \label{tab:SHREC17_retriev}
-\end{table}
-* add MN40 too? \\
-* add improved graph results too? \\
+* inference speed = time for a single instance to do a single training pass\\
+* training speed = time for the neural net to train to peak performance\\
+
+* add improved graph results too? ==> improved graph unnecessary (main information in low frequency) \\
+* diminish resolution ==> no change in result until nside=8, no change for high resolution => info in the low freq\\
+* same conclusion, anisotropy unnecessary cost to pay\\
+* Limited by representation of data?\\
+
+\subsubsection*{ModelNet 40}
+* in appendix now\\
 
@@
 \begin{tabular}{l|c c c c}
-        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy}\\
-        \cmidrule(lr){2-5}
-        \multicolumn{1}{l}{Method} & BG & TC & AR & mean \\ \hline
+        \multicolumn{1}{l}{} & Accuracy & Average Precision & \multicolumn{2}{c}{Speed}\\
+        \cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-5} 
+        \multicolumn{1}{l}{Method} & mean & mean & inference [ms] & training \\ \hline
         %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
-        Jiang et al. & 97 & 94 & 93 & 94.67\\
-        Jiang (bsize 64) & 95.2 & 93.9 & 95.7 & 94.95\\
+        \cite{jiang_spherical_2019} & 94.67 & - & - & -\\
+        \cite{jiang_spherical_2019} \emph{rerun} & 94.95 & 38.41 & 10.2 & 10h14m\\
         % 328'339
-        Cohen et al. (S2R) & 97.3 & 97.8 & 97.3 & 97.5\\
-        Cohen et al. (R2R) & 97.4 & 97.9 & 97.8 & 97.7\\ \hline
-        DS (ico) & $98.2\pm 0.5$ & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $97.8\pm 0.3$ \\
-        %DS (non-weighted) & 99.8 & 73.3 & 90.2 & 87.81 & 79.29 & 97.93 & 88.61 & 30ms & 3h50m\\
-        DS (non-weighted) & $99.7\pm 0.1$ & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $87.8\pm 0.5$ \\ \hline
-        % DS (non-weighted) & 99.6 & 66.6 & 96.1 & 87.41\\ \hline
+        \cite{cohen_gauge_2019} (S2R) & 97.5 & 68.6 & - & -\\
+        \cite{cohen_gauge_2019} (R2R) & 97.7 & 75.9 & - & -\\ \hline
+        % unknown
+        DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 25 ms & 25h \\
+        DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 30 ms & 13h\\
         % 12'926'432
-        DeepSphere (equi non-weighted) & 99.9 & 31.3 & 75.2 & 68.80
     \end{tabular}
-    \caption{Climate pattern segmentation accuracy (\%) for BG, TC
-and AR classes plus mean accuracy.}
+    \caption{Climate pattern segmentation mean accuracy (\%), mean Average Precision (\%) and speed for different models run on the icosahedron dataset from \cite{jiang_spherical_2019}}
 \end{table}
 
-\begin{table}[!ht]
-\begin{tabular}{l|c c c c c}
-        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
-        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
-        \multicolumn{1}{l}{Method} & TC & AR & mean & inference & training \\ \hline
-        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
-        Jiang (bsize 64) & 11.08 & 65.21 & 38.41 & 10.2 ms & 10h14m\\
-        % 328'339
-        Cohen et al. (S2R) & - & -& 68.6 & - & - \\
-        Cohen et al. (R2R) & - & -& 75.9 & - & -\\ \hline
-        DS (ico) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 25 ms & 25h \\
-        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 30 ms & 13h \\ \hline
-        % DS (non-weighted) & 83.66 & 97.57 & 90.62 & 30ms & 13h\\ \hline
-        % 12'926'432
-        % non-weighted: accuracy (99.28, 33.60, 93.56, mean: 75.4819);AP (46.15, 93.87, mean: 70.01)
-        % weighted:        accuracy (96.52, 97.13, 97.59, mean: 97.08); AP (49.71, 89.23, mean: 69.47)
-        DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
-    \end{tabular}
-    \caption{Climate pattern segmentation average precision for positive classes and mean as wel, plus speed performance for inference (one training pass for one instance)  and training time.}
-\end{table}
+* Jiang rerun with a batch size of 64 instead of 256 due to memory limit.\\
+* cross entropy loss between parenthesis\\
+* 5 runs for each loss to obtain mean and std\\
 
 * trade off between AP and accuracy in the case of TC class, it seems.\\
-* change base, influence\\
-*
+* change base, influence?\\
+
+* full dataset not enough memory to run a correct model
 
@@
 
-\subsubsection*{dense regression - future temperature estimation}
+\paragraph*{dense regression - future temperature estimation}~\\
 * Task is to find the temperature at day T, knowing the temperature of the 5 previous days.\\
@@
 
-\begin{table}[!ht]
-    \centering
-    \begin{minipage}{0.48\linewidth}
-    \begin{tabular}{c|ccc}
-        order & MSE & MAE & R2 \\ \hline 
-        0 & 10.88 & 2.42 & 0.896\\
-        1 & 8.91 & 2.20 & 0.906\\
-        4 & 8.20 & 2.11 & 0.919\\
-        9 & 8.38 & 2.12 & 0.915\\
-    \end{tabular}
-    \caption{Future temperature estimation task. Evolution of performance in respect of the order of the graph filter}
-    \label{tab:future_results}
-    \end{minipage}
-    \hfill
-    %~\\[1cm]
-    \begin{minipage}{0.48\linewidth}
-    \begin{tabular}{c|ccc}
-        order & MSE & MAE & R2 \\ \hline 
-        1 & 134.01 & 10.51 & -0.319\\
-        4 & 129.48 & 10.31 & -0.274\\
-        9 & 141.68 & 10.82 & -0.389\\
-    \end{tabular}
-    \caption{Baseline: testing with the present day (T-1) instead of the future day T}
-    \label{tab:present_results}
-    \end{minipage}
-\end{table}
-
-\subsubsection*{global regression - day in year estimation}
+\paragraph*{global regression - day in year estimation}~\\
 * days represented by a sine to represent the periodic nature of the year.\\
-* task too easy, features already periodic\\
+* task too easy, temperature feature already periodic ==> second experiment with only precipitation feature\\
 * structure is still helping\\
@@
     \centering
-    \begin{minipage}{0.48\linewidth}
     \begin{tabular}{c|ccc}
-        order & MSE & MAE & R2 \\ \hline 
-        0 & 0.58 & 0.42 & -0.92\\
-        4 & 0.50 & 0.18 & 0.597\\
+        order & future temp & day (temperature) & day (precipitations) \\ \hline 
+        0 & 0.896 & 0.881 & - 0.920\\
+        4 & 0.919 & 0.969 & 0.597\\
     \end{tabular}
-    \caption{Find day in year using precipitation}
-    \label{tab:glob_prec}
-    \end{minipage}
-    \hfill
-    %~\\[1cm]
-    \begin{minipage}{0.48\linewidth}
-    \begin{tabular}{c|ccc}
-        order & MSE & MAE & R2 \\ \hline 
-        0 & 0.10 & 0.10 & 0.881\\
-        4 & 0.05 & 0.05 & 0.969\\
-    \end{tabular}
-    \caption{Using temperature feature that is already periodical}
-    \label{tab:glob_all}
-    \end{minipage}
+    \caption{R2 coefficient for different tasks on the GHCN dataset}
+    \label{tab:GHCN_results}
 \end{table}
@@
 \subsection{3D object Recognition}
+\subsubsection*{Detailed results}
+\paragraph*{SHREC17}
+\begin{table}[!ht]
+    \centering
+    \begin{tabular}{l|c c r r}
+        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{2}{c}{speed}\\
+        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
+        \multicolumn{1}{l}{Method} & Accuracy & F1-score & inference & training \\ \hline
+        Cohen \emph{s2cnn} & - & - & 38ms & 50h\\
+        % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
+        Esteves \emph{sphericalcnn} & 79.18 & 79.36 & 9.8ms & 2h52\\ \hline
+        DeepSphere \emph{Equiangular} & 79.25 & 79.36 & 0.98ms & 2h33m \\
+        DeepSphere \emph{HEALPix} & 80.42 & 80.65 & 1.0ms & 48m\\
+        DeepSphere \emph{Improved HEALPix} & 80.76 & & & 
+    \end{tabular}
+    \caption{Performance of different models}
+    \label{tab:SHREC17_class}
+\end{table}
+
+\begin{table}[!ht]
+    \centering
+    \begin{tabular}{l|c c c c|c c c c}
+     & \multicolumn{4}{c|}{micro (label average)} & \multicolumn{4}{c}{macro (instance average)} \\
+    Method & P@N & R@N & F1@N & mAP & P@N & R@N & F1@N & mAP \\ \hline
+    Cohen \emph{s2cnn} & 0.701 & 0.711 & 0.699 & 0.676 & - & - & - & - \\
+    % Cohen \emph{s2cnn\_simple} & 0.704 & 0.701 & 0.696 & 0.665 & 0.430 & 0.480 & 0.429 & 0.385\\
+    Esteves \emph{sphericalcnn} & 0.717 & 0.737 & - & 0.685 & 0.450 & 0.550 & - & 0.444\\ \hline
+    DeepSphere \emph{Equiangular} & 0.709 & 0.700 & 0.698 & 0.665 & 0.439 & 0.489 & 0.439 & 0.403 \\
+    DeepSphere \emph{HEALPix} & 0.725 & 0.717 & 0.715 & 0.686 & 0.475 & 0.508 & 0.468 & 0.428\\
+    DeepSphere \emph{Improved HEALPix} & & & & &
+    \end{tabular}
+    \caption{Performance of different models over SHREC17 perturbed dataset as a retrieval task, using the official script of the competition.}
+    \label{tab:SHREC17_retriev}
+\end{table}
+
+\paragraph*{ModelNet 40}
+\begin{table}[!ht]
+    \centering
+    \begin{tabular}{c|cccc}
+         &  x/x & z/z & SO3/SO3 & z/SO3 \\ \hline
+Cohen & 85.0 & - & - & - \\
+Jiang & 90.5 & - & - & - \\
+Esteves \emph{scnn} & - & 88.9 & 86.9 & 78.6 \\
+%Esteves \emph{MVCNN} & 94.69 & - & - & - \\
+DeepSphere & 87.8 & 86.8 & 86.7 & 76.9
+    \end{tabular}
+    \caption{Accuracy (in percent) on test set, for different models. The x dataset has no augmentation, the z dataset is augmented with rotation around Z-axis, and SO3 with ZYZ rotations.}
+    \label{tab:mn40_results}
+\end{table}
 \subsubsection*{HEALPix}
+
 HEALPix sampling, input signal at Nside = 32
@@
 \subsection{climate event detection}
+\subsubsection*{Results}
+\begin{table}[!ht]
+\begin{tabular}{l|c c c c}
+        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy}\\
+        \cmidrule(lr){2-5}
+        \multicolumn{1}{l}{Method} & TC & AR & BG & mean \\ \hline
+        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
+        \cite{jiang_spherical_2019} & 94 & 93 & 97 & 94.67\\
+        \cite{jiang_spherical_2019} \emph{rerun} & 93.9 & 95.7 & 95.2 & 94.95\\
+        % 328'339
+        \cite{cohen_gauge_2019} (S2R) & 97.3 & 97.3 & 97.8 & 97.5\\
+        \cite{cohen_gauge_2019} (R2R) & 97.8 & 97.4 & 97.9 & 97.7\\ \hline
+        DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ \\
+        DS (non-weighted) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ \\ \hline
+        % 12'926'432
+        DS-Jiang (weighted) & 97.1 & 97.6 & 96.5 & 97.1\\
+        DS-Jiang (non-weighted) & 33.6 & 93.6 & 99.3 & 75.5
+        % 590k
+        % DeepSphere (equi non-weighted) & 99.9 & 31.3 & 75.2 & 68.80
+    \end{tabular}
+    \caption{Climate pattern segmentation accuracy (\%) for BG, TC
+and AR classes plus mean accuracy.}
+\end{table}
+
+* DS-jiang is the similar architecture as \cite{jiang_spherical_2019}.\\
+
+\begin{table}[!ht]
+\begin{tabular}{l|c c c c c}
+        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
+        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
+        \multicolumn{1}{l}{Method} & TC & AR & mean & inference [ms] & training \\ \hline
+        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
+        \cite{jiang_spherical_2019} \emph{rerun} & 11.08 & 65.21 & 38.41 & 10.2 & 10h14m\\
+        % 328'339
+        \cite{cohen_gauge_2019} (S2R) & - & -& 68.6 & - & - \\
+        \cite{cohen_gauge_2019} (R2R) & - & -& 75.9 & - & -\\ \hline
+        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 25 & 25h \\
+        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 30 & 13h \\ \hline
+        % 12'926'432
+        DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 & 5 & 3h06m\\
+        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 & 5 & 3h04m
+        % 590k
+        % DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
+    \end{tabular}
+    \caption{Climate pattern segmentation average precision for positive classes and mean as well, plus speed performance for inference (one training pass for one instance)  and training time.}
+\end{table}
 \subsubsection*{Icosahedron}
@@
 30 epochs
-\subsubsection*{Jiang Icosahedron}
+\subsubsection*{DS-jiang}
 encoder:\\
@@
 250 epochs with no augmentation
-\subsection*{Dense}
+\subsubsection*{Results}
+\begin{table}[!ht]
+    \centering
+    \begin{tabular}{c|ccc}
+        order & MSE & MAE & R2 \\ \hline 
+        0 & 10.88 & 2.42 & 0.896\\
+        1 & 8.91 & 2.20 & 0.906\\
+        4 & 8.20 & 2.11 & 0.919\\
+        9 & 8.38 & 2.12 & 0.915\\
+    \end{tabular}
+    \caption{Future temperature estimation task. Evolution of performance in respect of the order of the graph filter}
+    \label{tab:future_results}
+    \hfill
+    %~\\[1cm]
+    % \begin{minipage}{0.48\linewidth}
+    % \begin{tabular}{c|ccc}
+    %     order & MSE & MAE & R2 \\ \hline 
+    %     1 & 134.01 & 10.51 & -0.319\\
+    %     4 & 129.48 & 10.31 & -0.274\\
+    %     9 & 141.68 & 10.82 & -0.389\\
+    % \end{tabular}
+    % \caption{Baseline: testing with the present day (T-1) instead of the future day T}
+    % \label{tab:present_results}
+    % \end{minipage}
+\end{table}
+
+\begin{table}[!ht]
+    \centering
+    \begin{minipage}{0.48\linewidth}
+    \begin{tabular}{c|ccc}
+        order & MSE & MAE & R2 \\ \hline 
+        0 & 0.58 & 0.42 & -0.92\\
+        4 & 0.50 & 0.18 & 0.597\\
+    \end{tabular}
+    \caption{Find day in year using precipitation}
+    \label{tab:glob_prec}
+    \end{minipage}
+    \hfill
+    %~\\[1cm]
+    \begin{minipage}{0.48\linewidth}
+    \begin{tabular}{c|ccc}
+        order & MSE & MAE & R2 \\ \hline 
+        0 & 0.10 & 0.10 & 0.881\\
+        4 & 0.05 & 0.05 & 0.969\\
+    \end{tabular}
+    \caption{Using temperature feature that is already periodical}
+    \label{tab:glob_all}
+    \end{minipage}
+\end{table}
+
+\subsubsection*{Dense}
 

### 2019-09-04 main.tex
fix quotes
title

@@
 
-\title{Which spherical CNN should you use?\\ DeepSphere V2}
+%\title{Which spherical CNN should you use?\\ DeepSphere V2}
+\title{DeepSphere: an efficient graph-based spherical CNN}
+%\title{DeepSphere, an efficient (& equivariant) graph-based spherical CNN}
 
@@
 batch size 32, adam optimizer, constant learning rate of $5 \cdot 10^{-2}$
-cross-entropy loss, and add triplet loss from ``Esteves et al.´´
+cross-entropy loss, and add triplet loss from ``Esteves et al.''
 
@@
 
-concat the results of the corresponding encoder layer after the graph convolution. Similar to ``Jiang et al.´´
+concat the results of the corresponding encoder layer after the graph convolution. Similar to ``Jiang et al.''
 \subsubsection*{Equiangular}
@@
 \end{dmath}
+
 \end{document}

### 2019-09-04 main.tex
affiliations

@@
 
-% Authors must not appear in the submitted version. They should be hidden
-% as long as the \iclrfinalcopy macro remains commented out below.
-% Non-anonymous submissions will be rejected without review. 
-\author{Michaël Defferrard, Martino Milani, Frédérick Gusset,  Nathanaël Perraudin \thanks{ Use footnote for providing further information about author (webpage, alternative address)---\emph{not} for acknowledging
-funding agencies.  Funding acknowledgements go at the end of the paper.} \\
-Department of Computer Science\\
-Cranberry-Lemon University\\
-Pittsburgh, PA 15213, USA \\
-\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
-\And
-Ji Q. Ren \& Yevgeny LeNet \\
-Department of Computational Neuroscience \\
-University of the Witwatersrand \\
-Joburg, South Africa \\
-\texttt{\{robot,net\}@wits.ac.za} \\
+\author{Michaël Defferrard, Martino Milani \& Frédérick Gusset \\
+Institute of Electrical Engineering, EPFL, Lausanne, Switzerland \\
+\texttt{\{michael.defferrard,martino.milani,frederick.gusset\}@epfl.ch}
 \AND
-Coauthor \\
-Affiliation \\
-Address \\
-\texttt{email}
+Nathanaël Perraudin \\
+Swiss Data Science Center (SDSC), Zurich, Switzerland \\
+\texttt{nathanael.perraudin@sdsc.ethz.ch}
 }
-
-% The \author macro works with any number of authors. There are two commands
-% used to separate the names and addresses of multiple authors: \And and \AND.
-%
-% Using \And between authors leaves it to \LaTeX{} to determine where to break
-% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
-% puts 3 of 4 authors names on the first line, and the last on the second
-% line, try using \AND instead of \And before the third author name.
 

### 2019-09-05 main.tex
cleanup and first pass

@@
 %\title{Which spherical CNN should you use?\\ DeepSphere V2}
-\title{DeepSphere: an efficient graph-based spherical CNN}
+\title{DeepSphere: a graph-based spherical CNN}
+%\title{DeepSphere: an efficient graph-based spherical CNN}
 %\title{DeepSphere, an efficient (& equivariant) graph-based spherical CNN}
@@
 \newcommand{\new}{\marginpar{NEW}}
+\newcommand{\todo}[1]{{\color[rgb]{.6,.1,.6}{#1}}}
 
@@
 contributions:\\
-* theory => convergence (better graph)\\
-* experiments on relevant problems (not spherical MNIST) => check the desiderata\\
+* theory $\Rightarrow$ convergence (better graph)\\
+* experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata\\
   * surprising: anisotropy doesn't seem useful\\
@@
 \end{abstract}
+
+\todo{
+	* adjacency matrix: $A$ instead of $W$? \\
+}
 
@@
   * deformation (e.g., on the icosahedron for gauge)\\
-* powerful / generality => isotropic vs anisotropic\\
+* powerful / generality $\Rightarrow$ isotropic vs anisotropic\\
 * scale: computational cost \& memory usage (feature maps)\\
@@
 
-\begin{table}[h!]
+\begin{table}[b]
     \centering
@@
 
-On the one side, we have Cohen which is computationally very expensive but perfectly equivariant, on the other we have cube sphere which computationl very good but not equivariant at all.
+On the one side, we have Cohen which is computationally very expensive but perfectly equivariant most general, on the other we have cube sphere which computationl very good but not equivariant at all.
 Other methods are tradedoff between these two.
@@
 
-Present the different spherical CNNs with pro and cons => mostly scale vs generality\\
-* 2D CNN => doesn't respect geometry and equivariance\\
-* Cohen spherical CNN => most general, but doesn't scale\\
-* Cohen gauge => fixes scale, at the price of deformation (sphere => icosahedron)\\
-* Esteves => ? \\
-* Jiang => need a global coordinate system (ok for planets, not projections like cosmo)\\
+Present the different spherical CNNs with pro and cons $\Rightarrow$ mostly scale vs generality\\
+* 2D CNN $\Rightarrow$ doesn't respect geometry and equivariance\\
+* Cohen spherical CNN $\Rightarrow$ most general, but doesn't scale\\
+* Cohen gauge $\Rightarrow$ fixes scale, at the price of deformation (sphere $\Rightarrow$ icosahedron)\\
+* Esteves $\Rightarrow$ ? \\
+* Jiang $\Rightarrow$ need a global coordinate system (ok for planets, not projections like cosmo)\\
 
@@
 
-* HEALPix: improvement from DeepSphere v1 \cite{perraudin2019deepsphere}
+* HEALPix: improvement from DeepSphere v1 \cite{perraudin2019deepsphere} \\
 * equiangular: Renata \& Pascal
@@
 \subsection{HEALPix: convergence theorem}
-Given a sampling $x_0, ..., x_{n-1}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to the $i$th point of the sampling, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing the $i$th patch.
-Define $d^{(n)} := \max_{i=0, ..., n}d_i$ and $A^{(n)}=\max_{i=0, ..., n}A_i$.\\
+
+Given a sampling $x_0, \dots, x_{n-1}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to the $i$-th point of the sampling, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing the $i$-th patch.
+Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
+
 \begin{theorem}
-		For a sampling $\mathcal P = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi area and such that $d^{(n)})\leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian operator $\frac{|\mathbb S^2|}{4\pi t_n}L^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\triangle_{\mathbb S^2}$  for $n\to\infty$:
+	For a sampling $\mathcal P = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian operator $\frac{|\mathbb S^2|}{4\pi t_n}L^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\triangle_{\mathbb S^2}$  for $n\to\infty$:
 	$$ \lim_{n\to\infty}\frac{|\mathbb S^2|}{4\pi t_n} L_n^{t_n}f(y) =  \triangle_{\mathbb S^2}f(y).$$
@@
 \subsection{Equiangular}
-Khasanova et al.
-\cite{Frossard2017GraphBasedCO} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling.
+
+\cite{khasanova2017graphomni} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling.
 They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes.
 In other words, they solve the minimization problem
-
-\begin{equation}\label{eq:minimization frossard}
+\begin{equation} \label{eq:minimization frossard}
 	\min_{W\in\mathcal G} \left|\mathcal{F}\left(\mathbf{y}\left(v_{ e}\right)\right)-\mathcal{F}\left(\mathbf{y}\left(v_{ i}\right)\right)\right|
@@
 In their work they prove that the optimal weights solving the minimization problem (\ref{eq:minimization frossard}) are given by weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
-\begin{equation}\label{eq:frossard weights}
+\begin{equation} \label{eq:frossard weights}
 	w_{ij} = \frac{1}{\norm{x_i-x_j}}
@@
 
-\begin{figure}[h!]
+\begin{figure}
 	\centering
 	\includegraphics[width=\textwidth]{figures/KhasanovaFrossardgraphonequiangularsampling.png}
-
-	\caption{\label{fig:Equivariance error of the Frossard-Khasanove graph}Equivariance error of the Khasanova-Frossard graph on the equiangular sampling with bandwidth $b=8$ by spherical harmonic degree $\ell$.}
+	\caption{Equivariance error of the Khasanova-Frossard graph on the equiangular sampling with bandwidth $b=8$ by spherical harmonic degree $\ell$.}
+	\label{fig:Equivariance error of the Frossard-Khasanove graph}
 \end{figure}
@@
 
-* define a measure of equiv error\\
-Take a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, ..., n\}$ of the sphere, a weighted undirected graph $G(V, E, \mathbf W)$, a signal $f: \mathbb S^2\to\mathbb R$ and its sampled representation $\mathbf f:\ f_i=f(v_i)$.
+\todo{
+* define a measure of equiv error \\
+* show convergence empirically (for Nside up to 1024) \\
+* improved upon V1 \\
+* no difference in practice (see experiment xx) $\Rightarrow$ NNs are resilient to equiv error \\
+}
+
+Take a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere, a weighted undirected graph $G(V, E, \mathbf W)$, a signal $f: \mathbb S^2\to\mathbb R$ and its sampled representation $\mathbf f:\ f_i=f(v_i)$.
 Suppose that there exists a sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \mathbf f$ defined on a suitable subspace $F$ of $L^2(\mathbb S^2)$ such that it is invertible, i.e., we can unambiguously reconstruct the function $f\in F$ from its sampled values $\mathbf f$.
 The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing \cite{Driscoll:1994:CFT:184069.184073}.
-Define the rotation operator $\Lambda(g), g\in SO(3)$: $\Lambda(g) f(\omega)=f\left(g^{-1} \omega\right)$.\\
+Define the rotation operator $\Lambda(g), g\in SO(3)$: $\Lambda(g) f(\omega) = f\left(g^{-1} \omega\right)$.
 
 We now want to understand how to set the edges and the weights of $G$ such that
-\begin{equation}\label{eq:equivariance}
-T \Lambda(g) T^{-1} \Omega_k T f = \Omega_k T \Lambda(g) f
+\begin{equation} \label{eq:equivariance}
+	T \Lambda(g) T^{-1} \Omega_k T f = \Omega_k T \Lambda(g) f,
 \end{equation}
@@
 Thanks to this we are able, for a given sampling, a given function $f$, a given rotation $g$, and a given kernel $k$, to compute the \textit{normalized equivariance error}
-\begin{equation}\label{eq:equivariance error}
-E_{G}(f, g) = \left(\frac{ \norm {T \Lambda(g) T^{-1} \Omega_k Tf - \Omega_k T \Lambda(g) f}_{L^2(\mathbb R^2)}}{\norm {Tf}_{L^2(\mathbb R^2)}}\right)^2
+\begin{equation} \label{eq:equivariance error}
+	E_{G}(f, g) = \left(\frac{ \norm {T \Lambda(g) T^{-1} \Omega_k Tf - \Omega_k T \Lambda(g) f}_{L^2(\mathbb R^2)}}{\norm {Tf}_{L^2(\mathbb R^2)}}\right)^2,
 \end{equation}
@@
 A measure of how equivariant a graph is with respect to rotations will then be given by the \textit{mean equivariance error}
-\begin{equation}\label{eq:mean equivariance error}
-\overline E_G = \mathbb E_{f, g}\ 	E_G(f, g) 
+\begin{equation} \label{eq:mean equivariance error}
+	\overline E_G = \mathbb E_{f, g} \ E_G(f, g).
 \end{equation}
@@
 The mean equivariance error $\overline E_G$ gives us an indication of how close the graph $G$ is from being equivariant to rotations.
-Now we state an intuitive concept that explains how to construct rotation invariant graphs, i.e.
-graphs such that $\overline{E_G}$ is small.\\
-The mean equivariance error $\overline{E_G}$ will be small if the scalar product $\mathbf f^T \mathbf v_{i(\ell, m)}$ well approximates $\hat {f}(\ell,m)$ i.e., the $L^2$ scalar product of the continuous signal $\hat {f}(\ell,m)= \int_{\eta \in \mathbb S^2}f(\eta)Y_\ell^m(\eta)d\mu(\eta)$.
+Now we state an intuitive concept that explains how to construct rotation invariant graphs, i.e., graphs such that $\overline{E_G}$ is small.
+The mean equivariance error $\overline{E_G}$ will be small if the scalar product $\mathbf f^T \mathbf v_{i(\ell, m)}$ well approximates $\hat {f}(\ell,m)$, i.e., the $L^2$ scalar product of the continuous signal $\hat {f}(\ell,m)= \int_{\eta \in \mathbb S^2}f(\eta)Y_\ell^m(\eta)d\mu(\eta)$.
 
-	\textit{If $V$ is an equal area sampling scheme}, i.e.
-the area around each pixel $v_i$ is the same, $\overline{E_G}$ will be small if the graph Laplacian $\mathbf L$ is such that its eigenvectors $\mathbf v_i$ well approximate the eigenfunctions of the Laplace-Beltrami operator $\Delta_{\mathbb S^2}$ evaluated in the points of the sampling scheme, i.e.,
-	$$
-	\mathbf v_{i(\ell, m)} \approx Y_\ell^m(x_i)
-	$$
+\textit{If $V$ is an equal area sampling scheme}, i.e., the area around each pixel $v_i$ is the same, $\overline{E_G}$ will be small if the graph Laplacian $\mathbf L$ is such that its eigenvectors $\mathbf v_i$ well approximate the eigenfunctions of the Laplace-Beltrami operator $\Delta_{\mathbb S^2}$ evaluated in the points of the sampling scheme, i.e., $\mathbf v_{i(\ell, m)} \approx Y_\ell^m(x_i)$.
 
@@
 
-* show convergence empirically (for Nside up to 1024) \\
-* improved upon V1\\
-
-\begin{figure}[h]
+\begin{figure}
 	\centering
@@
 
-* no difference in practice (see experiment xx) => NNs are resilient to equiv error\\
-
 \section{Experiments [2 pages]}
 
+\todo{
 Show: \\
 * meet the desiderata \\
-* DeepSphere V1 and V2 are equivalent in practice \\
+* DeepSphere V1 and V2 are equivalent in practice, wait on SHREC and cosmo exp \\
 * anisotropy doesn't help \\
+}
 
-\subsection{3D object recognition}
+\subsection{3D objects recognition}
 
+\todo{
 * same perf as other spherical CNNs, but 40 times faster \\
-* compare the two samplings => not much difference \\
+* compare samplings (equi, HEALPix) $\Rightarrow$ not much difference \\
+* compare with improved graph (Nside=32) $\Rightarrow$ no improvement if information in low frequencies, do an SHT \\
+* ModelNet 40: same conclusions $\Rightarrow$ appendix \\
+}
 
-\subsubsection*{SHREC17}
-
-\begin{table}[ht]
+\begin{table}
     \centering
@@
         \cmidrule(lr){2-3} \cmidrule(lr){4-4} \cmidrule(lr){5-6}
-        \multicolumn{1}{l}{Method} & F1-score & mAP & params & inference [ms] & training \\ \hline
+        \multicolumn{1}{l}{Method} & F1 & mAP & params & inference [ms] & training \\ \hline
         \cite{cohen_spherical_2018} & 78.85 & 67.6 & 1.4M & 38 & 50h\\
@@
 
-* add improved graph results too? ==> improved graph unnecessary (main information in low frequency) \\
-* diminish resolution ==> no change in result until nside=8, no change for high resolution => info in the low freq\\
+* diminish resolution $\Rightarrow$ no change in result until nside=8, no change for high resolution $\Rightarrow$ info in the low freq\\
 * same conclusion, anisotropy unnecessary cost to pay\\
-* Limited by representation of data?\\
+* Limited by representation of data? yep, treat them as point clouds \\
 
-\subsubsection*{ModelNet 40}
-* in appendix now\\
+\subsection{Cosmological model discrimination}
 
-\subsection{cosmo}
-
+\todo{
 * other sphercial CNNs cannot scale to 10M pixels (tested on 10k at most) \\
-* redo the experiment with the optimal graph (cannot just copy the old results) and compare \\
+* redo the experiment with the optimal graph \\
+}
 
@@
 * cannot compare with Mudigonda (16 vs 1 input channel)\\
-* full: we scale (50B pixels, 20TB) => lead to better perf?\\
+* (full: we scale (50B pixels, 20TB) $\Rightarrow$ lead to better perf?) \\
 
-\begin{table}[!ht]
+\begin{table}
 	\begin{tabular}{l|c c c c}
@@
 * days represented by a sine to represent the periodic nature of the year.\\
-* task too easy, temperature feature already periodic ==> second experiment with only precipitation feature\\
+* task too easy, temperature feature already periodic $\Rightarrow$ second experiment with only precipitation feature\\
 * structure is still helping\\
 
-\begin{table}[!ht]
+\begin{table}
     \centering
@@
 * DeepSphere seems to be in the sweet spot of tradeoffs. Recall the desiderata.\\
-  * respect geometry: No need for a very precise equivariance, i.e. a very good graph...\\
+  * respect geometry: No need for a very precise equivariance, i.e., a very good graph...\\
   * Not the most general (restricted to isotropic filters), but didn't hurt perf in any experiment\\
-  * scales linearly => cannot do better ($n^{1.25}$ for best HEALPix, linear for not optimal)\\
-  * flexible => independent of the sampling\\
+  * scales linearly $\Rightarrow$ cannot do better ($n^{1.25}$ for best HEALPix, linear for not optimal)\\
+  * flexible $\Rightarrow$ independent of the sampling\\
 
@@
 \newpage
-
-{\LARGE \sc {Title of the paper: Supplementary Material}}
+{\LARGE \sc {Supplementary Material}}
 \appendix
@@
 \begin{prop} 	Let $\mathcal M$ be a $k$-dimensional compact smooth manifold embedded in some euclidean space $\mathbb R^N$, and fix $p\in\mathcal M$.
-Let the data points $x_1, ...
-x_n$ be sampled form a uniform distribution on the manifold $\mathcal M$.
+Let the data points $x_1, \dots, x_n$ be sampled form a uniform distribution on the manifold $\mathcal M$.
 Set $t_n=n^{-\frac{1}{k+2+\alpha}}$, for any $\alpha>0$ and let $f\in\mathcal C_\infty(\mathcal M)$.
@@
 \begin{prop}\label{prop:2}
-	Given a sampling regular enough i.e., for which we assume $A_i=A_j \ \forall i,j\text{ and }d^{(n)}\leq \frac{C}{\sqrt{n}}$, for a fixed $t>0$, a fixed Lipschitz function $f$ and a fixed point $y\in\mathbb S^2$ there exists a sequence $t_n = n^\beta, \beta<0$ such that
+	Given a sampling regular enough, i.e., for which we assume $A_i=A_j \ \forall i,j\text{ and }d^{(n)}\leq \frac{C}{\sqrt{n}}$, for a fixed $t>0$, a fixed Lipschitz function $f$ and a fixed point $y\in\mathbb S^2$ there exists a sequence $t_n = n^\beta, \beta<0$ such that
 $$
@@
 If the sampling is equal area as HEALPix, meaning that all the patches $\sigma_i$ have the same area, then we need to impose that $ d^{(n)}\leq \frac{1}{\sqrt{n}}$.
-If the sampling is not equal area, meaning that in general $A_i\neq A_j$, it can be shown that we need a slightly more complex condition: $\max_{i=0,...,n-1}d_iA_i\leq Cn^{-\frac{3}{2}}$.\\
+If the sampling is not equal area, meaning that in general $A_i\neq A_j$, it can be shown that we need a slightly more complex condition: $\max_{i=0,\dots,n-1}d_iA_i\leq Cn^{-\frac{3}{2}}$.\\
 In the work of Belkin et al.
@@
 
-\section{Experiments details}
+\section{Experimental details}
+
 * Network architecture and details
+
 \subsection{3D object Recognition}
@@
 \paragraph*{SHREC17}
-\begin{table}[!ht]
+
+\begin{table}
     \centering
@@
 
-\begin{table}[!ht]
+\begin{table}
     \centering
@@
 \paragraph*{ModelNet 40}
-\begin{table}[!ht]
+
+\begin{table}
     \centering
@@
 \end{table}
+
 \subsubsection*{HEALPix}
@@
 \subsubsection*{Results}
-\begin{table}[!ht]
+
+\begin{table}
+
 \begin{tabular}{l|c c c c}
@@
 
-\begin{table}[!ht]
+\begin{table}
 \begin{tabular}{l|c c c c c}
@@
 \end{table}
+
 \subsubsection*{Icosahedron}
+
 icosahedron sampling, level-5 resolution
@@
 250 epochs with no augmentation
+
 \subsubsection*{Results}
-\begin{table}[!ht]
+
+\begin{table}
     \centering

### 2019-09-10 main.tex
Updates from Overleaf

--- 2019-09-04 main.tex
@@
 
-%\title{Which spherical CNN should you use?\\ DeepSphere V2}
-\title{DeepSphere: an efficient graph-based spherical CNN}
-%\title{DeepSphere, an efficient (& equivariant) graph-based spherical CNN}
+\title{Which spherical CNN should you use?\\ DeepSphere V2}
 
@@
         \cite{jiang_spherical_2019} & 94.67 & - & - & -\\
-        \cite{jiang_spherical_2019} \emph{rerun} & 94.95 & 38.41 & 10.2 & 10h14m\\
+        \cite{jiang_spherical_2019} \emph{rerun} & 94.95 & 38.41 & 10 & 10h14m\\
         % 328'339
@@
         % unknown
-        DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 25 ms & 25h \\
-        DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 30 ms & 13h\\
+        DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 25 & 25h \\
+        DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 30 & 13h\\
         % 12'926'432
@@
 batch size 32, adam optimizer, constant learning rate of $5 \cdot 10^{-2}$
-cross-entropy loss, and add triplet loss from ``Esteves et al.''
+cross-entropy loss, and add triplet loss from ``Esteves et al.´´
 
@@
 
-concat the results of the corresponding encoder layer after the graph convolution. Similar to ``Jiang et al.''
+concat the results of the corresponding encoder layer after the graph convolution. Similar to ``Jiang et al.´´
 \subsubsection*{Equiangular}
@@
 \end{dmath}
-
 \end{document}

### 2019-09-10 main.tex
time table shrec17

--- 2019-09-05 main.tex
@@
         \cite{esteves_learning_2017} & 79.36 & 68.5 & 500k & 10 & 2h52\\ \hline
-        DeepSphere \emph{Equiangular} & 79.36 & 66.5 & 190k & 1 & 2h33m \\
-        DeepSphere \emph{HEALPix} & 80.65 & 68.6 & 190k & 1 & 48m\\
+        DeepSphere \emph{Equiangular} & 79.36 & 66.5 & 190k & 1 & 50m \\
+        DeepSphere \emph{HEALPix} & 80.65 & 68.6 & 190k & 1 & 50m\\
         DeepSphere \emph{Improved HEALPix} & ? & ? & 190k & ? & ?
@@
 	\cite{jiang_spherical_2019} & 94.67 & - & - & -\\
-	\cite{jiang_spherical_2019} \emph{rerun} & 94.95 & 38.41 & 10.2 & 10h14m\\
+	\cite{jiang_spherical_2019} \emph{rerun} & 94.95 & 38.41 & 10 & 10h14m\\
 	% 328'339
@@
 	% unknown
-	DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 25 ms & 25h \\
-	DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 30 ms & 13h\\
+	DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 25 & 25h \\
+	DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 33 & 13h35\\
 	% 12'926'432
@@
         Esteves \emph{sphericalcnn} & 79.18 & 79.36 & 9.8ms & 2h52\\ \hline
-        DeepSphere \emph{Equiangular} & 79.25 & 79.36 & 0.98ms & 2h33m \\
-        DeepSphere \emph{HEALPix} & 80.42 & 80.65 & 1.0ms & 48m\\
+        DeepSphere \emph{Equiangular} & 79.25 & 79.36 & 0.9ms & 47m \\
+        DeepSphere \emph{HEALPix} & 80.42 & 80.65 & 0.9ms & 46m\\
         DeepSphere \emph{Improved HEALPix} & 80.76 & & &

### 2019-09-11 main.tex
intro and some figures

@@
 \usepackage{booktabs}
-
-% ------ Martino's usepackage ------
-\usepackage{graphicx}
+\usepackage{graphicx} \graphicspath{{figures/}}
 \usepackage{amsthm}
@@
 \newcommand{\norm}[1]{\left\lVert#1\right\rVert}
-% ----------------------------------
 
@@
 
+Experiments on xxx show
+Comparison with previous work on shape classification and climate event detection suggests that anisotropic filters are an unnecessary price to pay.
+% memory, computations, implementation complexity
+
 \end{abstract}
@@
 	* adjacency matrix: $A$ instead of $W$? \\
+	* anonymize DeepSphere citation
 }
@@
 \section{Introduction [2 pages]}
-Get inspiration from DeepSphere V1\\
 
-Why are spherical CNNs important? What are the application?\\
-See DeepSphere workshop paper\\
+Spherical data is common, and comes in two favors: (i) intrinsically spherical, and (ii) projection due to observation.
+% spherical data f: S^2 -> R, projection from R^3
+Examples of (i) are planetary data (such as temperature, wind, geological) and brain activity.
+An example of (ii) is cosmological observations.
 
-Desiderata:\\
+Learning is desirable for...
+Problems to be tackled by machine learning might be local or global regression or classification.
+
+\begin{figure}[h]
+	\includegraphics[height=0.25\linewidth]{example_cosmo_cmb}
+	\hfill
+	\includegraphics[height=0.25\linewidth]{example_brain_meg}
+	\hfill
+	\includegraphics[height=0.25\linewidth]{example_ghcn_daily_tmax}
+	\hfill
+	\includegraphics[height=0.25\linewidth]{example_ghcn_graph}
+	\caption{
+		Examples of intrinsically spherical data: (left) the cosmic microwave background (CMB) temperature from \citet{planck2015overview},
+		%with galactic plane masked
+		(middle) daily maximum temperature from the Global Historical Climatology Network (GHCN),\protect\footnotemark (right) brain activity recorded through magnetoencephalography (MEG).\protect\footnotemark
+		For those examples, a rigid full-sphere pixelization is not ideal: the Milky Way's galactic plane masks observations, brain activity is measured on the scalp only, and the position and density of weather stations is arbitrary and changes over time.
+		Graphs can faithfully and efficiently represent sampled spherical data by placing vertices where data has been measured.
+		%\todo{something from climate, weather?}
+		%\todo{compare ideal full-spheres (like SHREC-17 projection from Esteves, 360 from Coors) to real-world measurements?}
+		%\todo{horizontal colorbar for brain}
+	}
+	\label{fig:examples}
+\end{figure}
+\footnotetext[1]{\scriptsize\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
+\footnotetext[2]{\scriptsize\url{https://martinos.org/mne/stable/auto_tutorials/plot_visualize_evoked.html}}
+
+Exploit the geometrical properties of the domain, symmetries.
+
+We identify the following desiderata for spherical CNNs:\\
 * respect the domain\\
@@
 
+Multiple methods have been developed to handle spherical data, each with their strengths and weaknesses.
+
+On the one side, we have Cohen which is computationally very expensive but perfectly equivariant most general, on the other we have cube sphere which computationl very good but not equivariant at all.
+Other methods are tradedoff between these two.
+What is a good tradeoff?
+We think that DeepSphere is
+
+Present the different spherical CNNs with pro and cons $\Rightarrow$ mostly scale vs generality\\
+* 2D CNN $\Rightarrow$ doesn't respect geometry and equivariance\\
+* Cohen spherical CNN $\Rightarrow$ most general, but doesn't scale\\
+* Cohen gauge $\Rightarrow$ fixes scale, at the price of deformation (sphere $\Rightarrow$ icosahedron)\\
+* Esteves $\Rightarrow$ ? \\
+* Jiang $\Rightarrow$ need a global coordinate system (ok for planets, not projections like cosmo)\\
+
 \begin{table}[b]
@@
     \begin{tabular}{l|c|c|c|c}
-         & Scale & Generality& equivariance & Flexibility \\
+         method & equivariance & generality & scalability & flexibility \\
          \hline
@@
 
-On the one side, we have Cohen which is computationally very expensive but perfectly equivariant most general, on the other we have cube sphere which computationl very good but not equivariant at all.
-Other methods are tradedoff between these two.
-What is a good tradeoff?
-We think that DeepSphere is
-
-Present the different spherical CNNs with pro and cons $\Rightarrow$ mostly scale vs generality\\
-* 2D CNN $\Rightarrow$ doesn't respect geometry and equivariance\\
-* Cohen spherical CNN $\Rightarrow$ most general, but doesn't scale\\
-* Cohen gauge $\Rightarrow$ fixes scale, at the price of deformation (sphere $\Rightarrow$ icosahedron)\\
-* Esteves $\Rightarrow$ ? \\
-* Jiang $\Rightarrow$ need a global coordinate system (ok for planets, not projections like cosmo)\\
+This paper focuses on improving the equivariance of \cite{perraudin2019deepsphere}, a scalable graph-based method designed for cosmological applications.
+\todo{cite RLGM paper}
+Experiments on multiple problems of practical interest shows the competitiveness and flexibility of our method.
+Furthermore, those experiments show, contrarily to previously published results \cite{cohen_gauge_2019}, that anisotropic filters may be an unnecessary price to pay.
 
@@
 * HEALPix: improvement from DeepSphere v1 \cite{perraudin2019deepsphere} \\
-* equiangular: Renata \& Pascal
+* equiangular: Renata \& Pascal \\
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.9\linewidth]{figure_architecture_v3}
+	\caption{Example architecture from \cite{perraudin2019deepsphere}.
+		Global tasks need a spatial summarization: the FCN variant is rotation invariant (and accepts inputs of varying sizes), while the CNN variant is not.
+		Dense tasks (when the output lives on the sphere, like segmentation) are rotation equivariant.
+	}
+	\label{fig:architecture}
+\end{figure}
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{figures/KhasanovaFrossardgraphonequiangularsampling.png}
+	\includegraphics[width=\textwidth]{KhasanovaFrossardgraphonequiangularsampling.png}
 	\caption{Equivariance error of the Khasanova-Frossard graph on the equiangular sampling with bandwidth $b=8$ by spherical harmonic degree $\ell$.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figures/DeepSphereonHEALPix.png}
-	\includegraphics[width=\textwidth]{figures/OptimalHKGLonHEALPix.png}
+	\includegraphics[width=\textwidth]{DeepSphereonHEALPix.png}
+	\includegraphics[width=\textwidth]{OptimalHKGLonHEALPix.png}
 	\caption{\label{fig:DeepSphere equivariance error}Mean equivariance error of the diffusion filter $\exp(-\Lambda)$ for $G$, $G'$ and the full HKGL, by spherical harmonic degree.
@@
 * compare samplings (equi, HEALPix) $\Rightarrow$ not much difference \\
-* compare with improved graph (Nside=32) $\Rightarrow$ no improvement if information in low frequencies, do an SHT \\
+* compare with improved graph (Nside=32) $\Rightarrow$ no improvement as information in the low frequencies (PSD, and works down to nside=8) \\
 * ModelNet 40: same conclusions $\Rightarrow$ appendix \\

### 2019-09-11 figures/example_brain_meg.py

@@ -1,0 +1,28 @@
+#!/usr/bin/env python3
+
+"""
+From https://martinos.org/mne/dev/auto_tutorials/plot_visualize_evoked.html
+"""
+
+import os
+
+import matplotlib.pyplot as plt
+import mne
+
+# plt.rc('font', family='Latin Modern Roman')
+plt.rc('text', usetex=True)
+plt.rc('text.latex', preamble=r'\usepackage{lmodern}')
+
+data_path = mne.datasets.sample.data_path()
+fname = os.path.join(data_path, 'MEG', 'sample', 'sample_audvis-ave.fif')
+evoked = mne.read_evokeds(fname, baseline=(None, 0), proj=True)
+
+fig = plt.figure(figsize=(4, 4))
+ax = fig.add_subplot(1, 1, 1)
+evoked[0].plot_topomap(times=0.1, show=False, colorbar=False, axes=ax)#, contours=False)
+ax.set_title('MEG evoked potential, $0.1s$')
+#cb = fig.colorbar(ax.collections[-1], ax=ax, orientation='horizontal', fraction=0.02, aspect=40, pad=0.03)#, ticks=ticks)
+
+fig.tight_layout()
+filename = os.path.splitext(os.path.basename(__file__))[0] + '.pdf'
+fig.savefig(filename)

### 2019-09-11 figures/example_ghcn_daily_tmax.py

@@ -1,0 +1,107 @@
+#!/usr/bin/env python3
+# coding: utf-8
+
+# # DAILY GLOBAL HISTORICAL CLIMATOLOGY NETWORK (GHCN-DAILY)
+#
+# Version 3.24
+#
+# [Andreas Loukas](https://andreasloukas.wordpress.com/), [EPFL LTS2](https://lts2.epfl.ch/), [Michaël Defferrard](http://deff.ch)
+#
+# Menne, M.J., I. Durre, B. Korzeniewski, S. McNeal, K. Thomas, X. Yin, S. Anthony, R. Ray,
+# R.S. Vose, B.E.Gleason, and T.G. Houston, 2012: Global Historical Climatology Network -
+# Daily (GHCN-Daily), Version 3.
+#
+# The five core features are:
+#
+# * PRCP = Precipitation (tenths of mm)
+# * SNOW = Snowfall (mm)
+# * SNWD = Snow depth (mm)
+# * TMAX = Maximum temperature (tenths of degrees C)
+# * TMIN = Minimum temperature (tenths of degrees C)
+#
+# [FTP link](ftp://ftp.ncdc.noaa.gov/pub/data/ghcn/daily/)
+
+
+import os
+
+import numpy as np
+import pandas as pd
+from matplotlib import pyplot as plt
+import cartopy.crs as ccrs
+
+
+# plt.rc('font', family='Latin Modern Roman')
+plt.rc('text', usetex=True)
+plt.rc('text.latex', preamble=r'\usepackage{lmodern}')
+
+years = np.arange(2010, 2015)
+n_years = len(years)
+
+# Load station data
+
+stations = np.load('ghcn_stations_{:4d}-{:4d}.npz'.format(years[0], years[-1]))
+n_stations = len(stations['id_ghcn'])
+print('{} weather stations identified.'.format(n_stations))
+
+# Load station measurements
+
+feature_name = 'TMAX'
+filename = 'ghcn_data_{:4d}-{:4d}_{}.npz'.format(years[0], years[-1], feature_name)
+data_file = np.load(filename)
+data, valid_days = data_file['data'], data_file['valid_days']
+n_stations = data.shape[0]
+print(f'{n_stations} stations loaded.')
+
+# Data inspection
+
+# Reshape our data array from (years, months, days) into a timeseries
+data = data.reshape((n_stations, n_years*12*31))
+
+# change to Celsius
+if feature_name in ['TMIN', 'TMAX']:
[…]

### 2019-09-11 figures/example_ghcn_graph.py

@@ -1,0 +1,76 @@
+#!/usr/bin/env python3
+# coding: utf-8
+
+
+import os
+
+import numpy as np
+from matplotlib import pyplot as plt
+import pygsp as pg
+
+
+# plt.rc('font', family='Latin Modern Roman')
+plt.rc('text', usetex=True)
+plt.rc('text.latex', preamble=r'\usepackage{lmodern}')
+
+stations = np.load('ghcn_stations_2010-2014.npz')
+data = np.load('ghcn_data_2010-2014_TMAX.npz')
+
+keep = data['valid_days'].flatten()
+data = data['data'].reshape(len(stations['id_ghcn']), -1)
+data = data[:, keep]
+data = data / 10
+
+# Show the same stations as for the temperature plot.
+year, month, day = 2014, 1, 1
+t = (year-2010)*365 + (month-1)*30 + (day-1)
+keep = ~np.isnan(data[:, t])
+
+data = data[keep]
+lon = stations['lon'][keep]
+lat = stations['lat'][keep]
+
+print('n_stations: {}, n_days: {}'.format(*data.shape))
+
+# Rotate the view.
+lon -= 50
+lat -= 20
+
+lon *= np.pi / 180
+lat *= np.pi / 180
+
+x = np.cos(lat) * np.cos(lon)
+y = np.cos(lat) * np.sin(lon)
+z = np.sin(lat)
+
+positions = np.stack([x, y, z], axis=1)
+graph = pg.graphs.NNGraph(positions, k=20)
+print(graph)
+
+graph.set_signal(np.clip(data[:, t], -20, 40), 'temperature')
+
+graph = graph.subgraph(x > 0)
+print(graph)
+
+graph.plotting.update({
+    'elevation': 0,
+    'azimuth': 0,
+    'distance': 8,
+    'vertex_size': 10,
+    'vertex_color': (0, 0, 0, 1),
+    'edge_color': (0.5, 0.5, 0.5, 0.2),
+})
+
+graph.coords = graph.coords[:, 1:]
+
+fig = plt.figure(figsize=(4, 4))
+ax = fig.add_subplot(1, 1, 1)
+graph.plot(edges=True, title='graph of GHCN stations', ax=ax)
+#fig, ax = graph.plot(graph.signals['temperature'], edges=True, title='')
+#ax.scatter(graph.coords[:, 0], graph.coords[:, 1], 10, graph.signals['temperature'], cmap='RdYlBu_r')
[…]

### 2019-09-11 main.tex
Updates from Overleaf

--- 2019-09-10 main.tex
@@
 	\cite{jiang_spherical_2019} & 94.67 & - & - & -\\
-	\cite{jiang_spherical_2019} \emph{rerun} & 94.95 & 38.41 & 10 & 10h14m\\
+	\cite{jiang_spherical_2019} \emph{rerun} & 94.95 & 38.41 & 10 & 10h\\
 	% 328'339
@@
 	% unknown
-	DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 25 & 25h \\
-	DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 33 & 13h35\\
+	DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 33 & 13h \\
+	DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 33 & 13h\\
 	% 12'926'432
@@
         \cite{cohen_gauge_2019} (R2R) & - & -& 75.9 & - & -\\ \hline
-        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 25 & 25h \\
-        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 30 & 13h \\ \hline
+        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 33 & 13h \\
+        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 33 & 13h \\ \hline
         % 12'926'432

### 2019-09-11 main.tex
add size and optimal in climate exp

@@
 
-\begin{tabular}{l|c c c c}
-        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy}\\
-        \cmidrule(lr){2-5}
-        \multicolumn{1}{l}{Method} & TC & AR & BG & mean \\ \hline
+\begin{tabular}{l|c c c c c}
+        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy} & Size\\
+        \cmidrule(lr){2-5} \cmidrule(lr){6-6}
+        \multicolumn{1}{l}{Method} & TC & AR & BG & mean & params \\ \hline
         %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
-        \cite{jiang_spherical_2019} & 94 & 93 & 97 & 94.67\\
-        \cite{jiang_spherical_2019} \emph{rerun} & 93.9 & 95.7 & 95.2 & 94.95\\
+        \cite{jiang_spherical_2019} & 94 & 93 & 97 & 94.67 & 330k\\
+        \cite{jiang_spherical_2019} \emph{rerun} & 93.9 & 95.7 & 95.2 & 94.95 & 330k\\
         % 328'339
-        \cite{cohen_gauge_2019} (S2R) & 97.3 & 97.3 & 97.8 & 97.5\\
-        \cite{cohen_gauge_2019} (R2R) & 97.8 & 97.4 & 97.9 & 97.7\\ \hline
-        DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ \\
-        DS (non-weighted) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ \\ \hline
+        \cite{cohen_gauge_2019} (S2R) & 97.3 & 97.3 & 97.8 & 97.5 & -\\
+        \cite{cohen_gauge_2019} (R2R) & 97.8 & 97.4 & 97.9 & 97.7 & -\\ \hline
+        DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ & 13M\\
+        DS (non-weighted) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ & 13M\\ \hline
         % 12'926'432
-        DS-Jiang (weighted) & 97.1 & 97.6 & 96.5 & 97.1\\
-        DS-Jiang (non-weighted) & 33.6 & 93.6 & 99.3 & 75.5
+        DS-Jiang (weighted) & 97.1 & 97.6 & 96.5 & 97.1 & 590k\\
+        DS-Jiang (non-weighted) & 33.6 & 93.6 & 99.3 & 75.5 & 590k\\ \hline
         % 590k
+        DS-optimal (non-weighted) & 99.8 & 73.4 & 92.7 & 88.7 & \\ \hline
+        %DS-Cohen (weighted) &
         % DeepSphere (equi non-weighted) & 99.9 & 31.3 & 75.2 & 68.80
@@
 * DS-jiang is the similar architecture as \cite{jiang_spherical_2019}.\\
+* DS-optimal has 2 times the number of feature maps of DS.\\
 
@@
         DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 & 5 & 3h06m\\
-        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 & 5 & 3h04m
+        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 & 5 & 3h04m \\ \hline
         % 590k
+        DS-optimal (non-weighted) & 84.71 & 98.05 & 91.38 & 55 & 22h \\
         % DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h

### 2019-09-17 main.tex
Updates from Overleaf

@@
 \usepackage{booktabs}
+\usepackage{bbm}        % for mathbbm
 \usepackage{graphicx} \graphicspath{{figures/}}
@@
 
+\renewcommand{\b}[1]{{\bm{#1}}}   % bold symbol
+
 \newcommand{\fix}{\marginpar{FIX}}
@@
 \newcommand{\todo}[1]{{\color[rgb]{.6,.1,.6}{#1}}}
+\newcommand{\nati}[1]{{\color[rgb]{.3,.5,.9}{#1}}}
 
@@
 
-\section{Rotation equivariance [2.5 pages]}
+\section{Is graph convolution equivariant to rotation? [2 pages]}
 
-\subsection{Link with the Laplace-Beltrami Operator}
+% The plan for this section
+% 0) Explain why the Laplacian is so important...
+By definition, the graph convolution (on the sphere) is rotation equivariant to rotation, if and only if, it commutes with the rotation operator. 
+As, in the context of this work, graph convolution can be performed is performed by successive application of the graph Laplacian, i.e: $g(\b{L}) \b{f} = \left(\sum_{i=0}^K \alpha_i \b{L}^i\right) \b{f}$, if the graph Laplacian $\b{L}$ commutes with the rotation operator, then, by recursion, it will also commute with the convolution $g(\b{L})$.
+Hence to simplify our analysis, we concentrate on the graph Laplacian.
 
-\subsection{HEALPix: convergence theorem}
+% 0.5) Explain the sampling and metric
+We first need to deal with the sampling problem. The rotation operator $R_{b}$ \nati{define rotation} act on the continuous signal $R(b), b\in SO(3): R(b)f(\omega) = f(g^{-1}\omega)$
+graph laplacian on a discrete graph that is build from a sampling.
+So we need a sampling operator, ideally invertible. \nati{Define sampling}
+Eventually, we formulate the commute error of the graph Laplacian and the rotation operator as: 
+equ...
+Of course result will depend on the sampling and on the graph construction
 
-Given a sampling $x_0, \dots, x_{n-1}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to the $i$-th point of the sampling, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing the $i$-th patch.
-Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
+% !) summary the work of Khasanova
 
-\begin{theorem}
-	For a sampling $\mathcal P = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian operator $\frac{|\mathbb S^2|}{4\pi t_n}L^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\triangle_{\mathbb S^2}$  for $n\to\infty$:
-	$$ \lim_{n\to\infty}\frac{|\mathbb S^2|}{4\pi t_n} L_n^{t_n}f(y) =  \triangle_{\mathbb S^2}f(y).$$
-	\label{theo:pointwise convergence in the healpix case}
-\end{theorem}
+% 2) explain our approach
+Our approach is different as we do not miminize eq...
+Instead we inspire ourselves with Belkin, which says that for \emph{uniform sampling} the graph Laplacian converges toward the Laplace-Beltrami.
+b) The Laplace Beltrami commute with rotation.
+The following theorem extend the work of Belkin and Niogi to fixed sampling \nati{(Including Healpix or not?)}
+THEOREM HERE
+This is \emph{not} a proof of equivariance of the graph convolution for a specific sampling.
+We simply observe that the graph Laplacian converges pointwisely toward an operator that commutes with rotation.
+To have the desired equality in eq..., we would need to prove a stronger result, for example uniform convergence (in the space of the operators).
+\nati{Should we put this here?: }This does not hold in general \cite{belkin-spectral}. However, we believe that this is achievable for a bandlimited signals.
+More importantly, the proof of ... in Appendix ... inspires us in the construction of our graph Laplacian. a) use gaussian kernel b) we need to adjust t with respect of n such that ...
 
-\subsection{Equiangular}
+% 3) Show experimental results
+Define the error, show results and comments
+
+Explain the difference of errors... Uniform sampling is better
+
+\subsection{Theoretical evidence of equivariance}
+
+% \subsection{Equiangular}
 
@@
 \end{figure}
+
+\paragraph{Link with the Laplace-Beltrami Operator}
+
+Given a sampling $x_0, \dots, x_{n-1}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to the $i$-th point of the sampling, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing the $i$-th patch.
+Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
+
+\begin{theorem}
+	For a sampling $\mathcal P = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian operator $\frac{|\mathbb S^2|}{4\pi t_n}L^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\triangle_{\mathbb S^2}$  for $n\to\infty$:
+	$$ \lim_{n\to\infty}\frac{|\mathbb S^2|}{4\pi t_n} L_n^{t_n}f(y) =  \triangle_{\mathbb S^2}f(y).$$
+	\label{theo:pointwise convergence in the healpix case}
+\end{theorem}
 
@@
         % 590k
-        DS-optimal (non-weighted) & 99.8 & 73.4 & 92.7 & 88.7 & \\ \hline
-        %DS-Cohen (weighted) &
-        % DeepSphere (equi non-weighted) & 99.9 & 31.3 & 75.2 & 68.80
+        DS-optimal (weighted) & 91.5 & 93.4 & 99.0 & 94.6 & 52M\\
+        DS-optimal (non-weighted) & 73.4 & 92.7 & 99.8 & 88.7 & 52M\\ \hline
+        %DS-Cohen (weighted) & 95.5 & 96.9 & 93.9 & 95.4 & 2M \\
+        %DS-Cohen (non-weighted) & 95.5 & 96.9 & 93.9 & 95.4 & 2M \\
+        % DeepSphere (equi non-weighted) & 31.3 & 75.2 & 99.9 & 68.80
     \end{tabular}
@@
         % 590k
-        DS-optimal (non-weighted) & 84.71 & 98.05 & 91.38 & 55 & 22h \\
+        DS-optimal (weighted) & 52.80 & 94.78 & 73.79 & 50 & 20h \\
+        DS-optimal (non-weighted) & 84.71 & 98.05 & 91.38 & 50 & 20h \\ \hline
+        %DS-Cohen (weighted) & 13.1 & 80.3 & 46.7 & 11 & 4h \\
         % DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h

### 2019-09-18 main.tex
fixed third section

@@
 By definition, the graph convolution (on the sphere) is rotation equivariant to rotation, if and only if, it commutes with the rotation operator. 
-As, in the context of this work, graph convolution can be performed is performed by successive application of the graph Laplacian, i.e: $g(\b{L}) \b{f} = \left(\sum_{i=0}^K \alpha_i \b{L}^i\right) \b{f}$, if the graph Laplacian $\b{L}$ commutes with the rotation operator, then, by recursion, it will also commute with the convolution $g(\b{L})$.
+As, in the context of this work, graph convolution can be performed by successive application of the graph Laplacian, i.e: $g(\b{L}) \b{f} = \left(\sum_{i=0}^K \alpha_i \b{L}^i\right) \b{f}$, if the graph Laplacian $\b{L}$ commutes with the rotation operator, then, by recursion, it will also commute with the convolution $g(\b{L})$.
 Hence to simplify our analysis, we concentrate on the graph Laplacian.
@@
 % 0.5) Explain the sampling and metric
-We first need to deal with the sampling problem. The rotation operator $R_{b}$ \nati{define rotation} act on the continuous signal $R(b), b\in SO(3): R(b)f(\omega) = f(g^{-1}\omega)$
-graph laplacian on a discrete graph that is build from a sampling.
-So we need a sampling operator, ideally invertible. \nati{Define sampling}
-Eventually, we formulate the commute error of the graph Laplacian and the rotation operator as: 
-equ...
-Of course result will depend on the sampling and on the graph construction
+We first need to deal with the sampling problem. 
+Take a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere, a weighted undirected graph $G(V, E, \mathbf W)$, a signal $f: \mathbb S^2\to\mathbb R$ and its sampled representation $\mathbf f:\ f_i=f(v_i)$.
+Suppose that there exists a sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \mathbf f$ defined on a suitable subspace $F$ of $L^2(\mathbb S^2)$ such that it is invertible, i.e., we can unambiguously reconstruct the function $f\in F$ from its sampled values $\mathbf f$.
+The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing \cite{Driscoll:1994:CFT:184069.184073}.
+Define the rotation operator $R(g), g\in SO(3)$: $R(g) f(\omega) = f\left(g^{-1} \omega\right)$.
+
+We now want to understand how to set the edges and the weights of $G$ such that
+\begin{equation} \label{eq:equivariance}
+	T \R(g) T^{-1} \Omega_k T f = \Omega_k T R(g) f,
+\end{equation}
+i.e., the graph convolution $\Omega_k$ and any rotation $R(g)$ commute.
+
+Verifying equation (\ref{eq:equivariance}) is really hard in practice, due to the fact that for almost all sampling schemes $V$ it is not known if there exists a space $F$ in which $T$ is invertible.
+A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds \cite{Driscoll:1994:CFT:184069.184073}, and thus we have a closed form of $T^{-1}$.
+For sampling schemes where no such sampling theorem is available, there are implementations of discrete SHT to reconstruct a sampled signal $\mathbf f$, thus providing a way to approximate $T^{-1}$.
+Thanks to this we are able, for a given sampling, a given function $f$, a given rotation $g$, and a given kernel $k$, to compute the \textit{normalized equivariance error}
+\begin{equation} \label{eq:equivariance error}
+	E_{G}(f, g) = \left(\frac{ \norm {T R(g) T^{-1} \Omega_k Tf - \Omega_k T R(g) f}_{L^2(\mathbb R^2)}}{\norm {Tf}_{L^2(\mathbb R^2)}}\right)^2,
+\end{equation}
+where $T^{-1}$ is substituted with a discrete SHT in case $T$ is not invertible.
+A measure of how equivariant a graph is with respect to rotations will then be given by the \textit{mean equivariance error}
+\begin{equation} \label{eq:mean equivariance error}
+	\overline E_G = \mathbb E_{f, g} \ E_G(f, g).
+\end{equation}
+In practice the expected value is obtained by averaging over a finite number of random functions and random rotations.
+The mean equivariance error $\overline E_G$ gives us an indication of how close the graph $G$ is from being equivariant to rotations.
+Of course result will depend on the sampling and on the graph construction.
 
 % !) summary the work of Khasanova
-
-% 2) explain our approach
-Our approach is different as we do not miminize eq...
-Instead we inspire ourselves with Belkin, which says that for \emph{uniform sampling} the graph Laplacian converges toward the Laplace-Beltrami.
-b) The Laplace Beltrami commute with rotation.
-The following theorem extend the work of Belkin and Niogi to fixed sampling \nati{(Including Healpix or not?)}
-THEOREM HERE
-This is \emph{not} a proof of equivariance of the graph convolution for a specific sampling.
-We simply observe that the graph Laplacian converges pointwisely toward an operator that commutes with rotation.
-To have the desired equality in eq..., we would need to prove a stronger result, for example uniform convergence (in the space of the operators).
-\nati{Should we put this here?: }This does not hold in general \cite{belkin-spectral}. However, we believe that this is achievable for a bandlimited signals.
-More importantly, the proof of ... in Appendix ... inspires us in the construction of our graph Laplacian. a) use gaussian kernel b) we need to adjust t with respect of n such that ...
-
-% 3) Show experimental results
-Define the error, show results and comments
-
-Explain the difference of errors... Uniform sampling is better
-
-\subsection{Theoretical evidence of equivariance}
-
-% \subsection{Equiangular}
-
 \cite{khasanova2017graphomni} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling.
@@
 \end{equation}
-This construction is interesting since it is adapted to the equiangular sampling, and leads to a very sparse graph with only 4 neighbors per vertex.
-Furthermore, to obtain the weights (\ref{eq:frossard weights}) every calculation was done in the \textit{spatial domain}, without any consideration about the spectral interpretation of the filter.
-In order to compare it to the HKGL we show the equivariance error by spherical harmonic degree in figure \ref{fig:Equivariance error of the Frossard-Khasanove graph}.
-It can be appreciated how this construction performs a little worse that the full HKGL for low bandwidth samplings, but converges faster than the \textit{full} HKGL, and its spectrum looks much more similar to the one of $\Delta_{\mathbb S^2}$.
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{KhasanovaFrossardgraphonequiangularsampling.png}
-	\caption{Equivariance error of the Khasanova-Frossard graph on the equiangular sampling with bandwidth $b=8$ by spherical harmonic degree $\ell$.}
-	\label{fig:Equivariance error of the Frossard-Khasanove graph}
-\end{figure}
-
-\paragraph{Link with the Laplace-Beltrami Operator}
-
-Given a sampling $x_0, \dots, x_{n-1}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to the $i$-th point of the sampling, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing the $i$-th patch.
+% 2) explain our approach
+Our approach is different as we do not miminize eq \ref{eq:minimization frossard}.
+Instead we inspire ourselves with Belkin, which says that for \emph{uniform sampling} the graph Laplacian converges toward the Laplace-Beltrami.
+b) The Laplace Beltrami commute with rotation.
+The following theorem extend the work of Belkin and Nyiogi to fixed sampling \nati{(Including Healpix or not?)}.
+Given a sampling $V = \{x_0, \dots, x_{n-1}\}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$.
 Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
@@
 	$$ \lim_{n\to\infty}\frac{|\mathbb S^2|}{4\pi t_n} L_n^{t_n}f(y) =  \triangle_{\mathbb S^2}f(y).$$
-	\label{theo:pointwise convergence in the healpix case}
+	\label{theo:pointwise convergence for a regular sampling}
 \end{theorem}
 
-\subsection{Equivariance error}
+This is \emph{not} a proof of equivariance of the graph convolution for a specific sampling.
+We simply observe that the graph Laplacian converges pointwisely toward an operator that commutes with rotation.
+To have the desired equality in eq..., we would need to prove a stronger result, for example uniform convergence (in the space of the operators).
+\nati{Should we put this here?: }This does not hold in general \cite{belkin-spectral}. However, we believe that this is achievable for a bandlimited signals.
+More importantly, the proof of theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix ...
+inspires us in the construction of our graph Laplacian.
+a) use gaussian kernel b) we need to adjust t with respect of n such that ...
 
-\todo{
-* define a measure of equiv error \\
-* show convergence empirically (for Nside up to 1024) \\
-* improved upon V1 \\
-* no difference in practice (see experiment xx) $\Rightarrow$ NNs are resilient to equiv error \\
-}
+% 3) Show experimental results
+Define the error, show results and comments
 
-Take a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere, a weighted undirected graph $G(V, E, \mathbf W)$, a signal $f: \mathbb S^2\to\mathbb R$ and its sampled representation $\mathbf f:\ f_i=f(v_i)$.
-Suppose that there exists a sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \mathbf f$ defined on a suitable subspace $F$ of $L^2(\mathbb S^2)$ such that it is invertible, i.e., we can unambiguously reconstruct the function $f\in F$ from its sampled values $\mathbf f$.
-The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing \cite{Driscoll:1994:CFT:184069.184073}.
-Define the rotation operator $\Lambda(g), g\in SO(3)$: $\Lambda(g) f(\omega) = f\left(g^{-1} \omega\right)$.
-
-We now want to understand how to set the edges and the weights of $G$ such that
-\begin{equation} \label{eq:equivariance}
-	T \Lambda(g) T^{-1} \Omega_k T f = \Omega_k T \Lambda(g) f,
-\end{equation}
-i.e., the graph convolution $\Omega_k$ and any rotation $\Lambda(g)$ commute.
-
-Verifying equation (\ref{eq:equivariance}) is really hard in practice, due to the fact that for almost all sampling schemes $V$ it is not known if there exists a space $F$ in which $T$ is invertible.
-A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds \cite{Driscoll:1994:CFT:184069.184073}, and thus we have a closed form of $T^{-1}$.
-For sampling schemes where no such sampling theorem is available, there are implementations of discrete SHT to reconstruct a sampled signal $\mathbf f$, thus providing a way to approximate $T^{-1}$.
-Thanks to this we are able, for a given sampling, a given function $f$, a given rotation $g$, and a given kernel $k$, to compute the \textit{normalized equivariance error}
-\begin{equation} \label{eq:equivariance error}
-	E_{G}(f, g) = \left(\frac{ \norm {T \Lambda(g) T^{-1} \Omega_k Tf - \Omega_k T \Lambda(g) f}_{L^2(\mathbb R^2)}}{\norm {Tf}_{L^2(\mathbb R^2)}}\right)^2,
-\end{equation}
-where $T^{-1}$ is substituted with a discrete SHT in case $T$ is not invertible.
-A measure of how equivariant a graph is with respect to rotations will then be given by the \textit{mean equivariance error}
-\begin{equation} \label{eq:mean equivariance error}
-	\overline E_G = \mathbb E_{f, g} \ E_G(f, g).
-\end{equation}
-In practice the expected value is obtained by averaging over a finite number of random functions and random rotations.
-The mean equivariance error $\overline E_G$ gives us an indication of how close the graph $G$ is from being equivariant to rotations.
-Now we state an intuitive concept that explains how to construct rotation invariant graphs, i.e., graphs such that $\overline{E_G}$ is small.
-The mean equivariance error $\overline{E_G}$ will be small if the scalar product $\mathbf f^T \mathbf v_{i(\ell, m)}$ well approximates $\hat {f}(\ell,m)$, i.e., the $L^2$ scalar product of the continuous signal $\hat {f}(\ell,m)= \int_{\eta \in \mathbb S^2}f(\eta)Y_\ell^m(\eta)d\mu(\eta)$.
-
-\textit{If $V$ is an equal area sampling scheme}, i.e., the area around each pixel $v_i$ is the same, $\overline{E_G}$ will be small if the graph Laplacian $\mathbf L$ is such that its eigenvectors $\mathbf v_i$ well approximate the eigenfunctions of the Laplace-Beltrami operator $\Delta_{\mathbb S^2}$ evaluated in the points of the sampling scheme, i.e., $\mathbf v_{i(\ell, m)} \approx Y_\ell^m(x_i)$.
-
-In this way we framed the problem of constructing a rotation invariant graph with the more general problem of coming up with a matrix $\mathbf L$ with some specific spectral properties.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{DeepSphereonHEALPix.png}
-	\includegraphics[width=\textwidth]{OptimalHKGLonHEALPix.png}
-	\caption{\label{fig:DeepSphere equivariance error}Mean equivariance error of the diffusion filter $\exp(-\Lambda)$ for $G$, $G'$ and the full HKGL, by spherical harmonic degree.
-Notice the difference in the scale of the y axis for DeepSphere, that reaches errors up to 30\%.}
-\end{figure}
+Explain the difference of errors... Uniform sampling is better
 
@@
 \end{definition}
-\begin{definition}{}(from \cite[Belkin et al.
-]{Belkin:2005:TTF:2138147.2138189}Functional approximation to the Laplace-Beltrami operator)\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, where $\text{vol}(\mathcal M)$ is the volume of $\mathcal M$.
+\begin{definition}{} \cite{Belkin:2005:TTF:2138147.2138189}\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, and let $\text{vol}(\mathcal M)$ be the volume of $\mathcal M$.
 We define the functional approximation to the Laplace-Beltrami operator to be the operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
@@
 
-\begin{prop} 	Let $\mathcal M$ be a $k$-dimensional compact smooth manifold embedded in some euclidean space $\mathbb R^N$, and fix $p\in\mathcal M$.
+\begin{prop} \cite{Belkin:2005:TTF:2138147.2138189} \\
+Let $\mathcal M$ be a $k$-dimensional compact smooth manifold embedded in some euclidean space $\mathbb R^N$, and fix $p\in\mathcal M$.
 Let the data points $x_1, \dots, x_n$ be sampled form a uniform distribution on the manifold $\mathcal M$.
@@
 
+\subsection{MATERIAL FROM MARTINO'S MASTER PROJECT}
+
+% \subsection{Equiangular}
+
+\cite{khasanova2017graphomni} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling.
+They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes.
+In other words, they solve the minimization problem
+\begin{equation} \label{eq:minimization frossard}
+	\min_{W\in\mathcal G} \left|\mathcal{F}\left(\mathbf{y}\left(v_{ e}\right)\right)-\mathcal{F}\left(\mathbf{y}\left(v_{ i}\right)\right)\right|
+\end{equation}
+for the adjacency matrix $W$, where $\mathbf y(v_i)$ is the image of the object on the sphere centered on the vertex $v_i$, and $\mathcal F (\mathbf y(v_e))$ is the response of the filter at the vertex $v_e$ that lies at the same longitude of the vertex $v_i$ but on the equator.
+In their work they prove that the optimal weights solving the minimization problem (\ref{eq:minimization frossard}) are given by weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
+\begin{equation} \label{eq:frossard weights}
+	w_{ij} = \frac{1}{\norm{x_i-x_j}}
+\end{equation}
+This construction is interesting since it is adapted to the equiangular sampling, and leads to a very sparse graph with only 4 neighbors per vertex.
+Furthermore, to obtain the weights (\ref{eq:frossard weights}) every calculation was done in the \textit{spatial domain}, without any consideration about the spectral interpretation of the filter.
+In order to compare it to the HKGL we show the equivariance error by spherical harmonic degree in figure \ref{fig:Equivariance error of the Frossard-Khasanove graph}.
+It can be appreciated how this construction performs a little worse that the full HKGL for low bandwidth samplings, but converges faster than the \textit{full} HKGL, and its spectrum looks much more similar to the one of $\Delta_{\mathbb S^2}$.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{KhasanovaFrossardgraphonequiangularsampling.png}
+	\caption{Equivariance error of the Khasanova-Frossard graph on the equiangular sampling with bandwidth $b=8$ by spherical harmonic degree $\ell$.}
+	\label{fig:Equivariance error of the Frossard-Khasanove graph}
+\end{figure}
+
+\paragraph{Link with the Laplace-Beltrami Operator}
+
+Given a sampling $x_0, \dots, x_{n-1}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to the $i$th point of the sampling, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing the $i$-th patch.
+Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
+
+\begin{theorem}
+	For a sampling $\mathcal P = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian operator $\frac{|\mathbb S^2|}{4\pi t_n}L^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\triangle_{\mathbb S^2}$  for $n\to\infty$:
+	$$ \lim_{n\to\infty}\frac{|\mathbb S^2|}{4\pi t_n} L_n^{t_n}f(y) =  \triangle_{\mathbb S^2}f(y).$$
+	\label{theo:pointwise convergence in the healpix case}
+\end{theorem}
+
+\subsection{MATERIAL FROM MARTINO'S MASTER PROJECT}
+
+\todo{
+* define a measure of equiv error \\
+* show convergence empirically (for Nside up to 1024) \\
+* improved upon V1 \\
+* no difference in practice (see experiment xx) $\Rightarrow$ NNs are resilient to equiv error \\
+}
+
+Take a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere, a weighted undirected graph $G(V, E, \mathbf W)$, a signal $f: \mathbb S^2\to\mathbb R$ and its sampled representation $\mathbf f:\ f_i=f(v_i)$.
+Suppose that there exists a sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \mathbf f$ defined on a suitable subspace $F$ of $L^2(\mathbb S^2)$ such that it is invertible, i.e., we can unambiguously reconstruct the function $f\in F$ from its sampled values $\mathbf f$.
+The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing \cite{Driscoll:1994:CFT:184069.184073}.
+Define the rotation operator $\Lambda(g), g\in SO(3)$: $\Lambda(g) f(\omega) = f\left(g^{-1} \omega\right)$.
+
+We now want to understand how to set the edges and the weights of $G$ such that
+\begin{equation} \label{eq:equivariance}
+	T \Lambda(g) T^{-1} \Omega_k T f = \Omega_k T \Lambda(g) f,
+\end{equation}
+i.e., the graph convolution $\Omega_k$ and any rotation $\Lambda(g)$ commute.
+
+Verifying equation (\ref{eq:equivariance}) is really hard in practice, due to the fact that for almost all sampling schemes $V$ it is not known if there exists a space $F$ in which $T$ is invertible.
+A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds \cite{Driscoll:1994:CFT:184069.184073}, and thus we have a closed form of $T^{-1}$.
+For sampling schemes where no such sampling theorem is available, there are implementations of discrete SHT to reconstruct a sampled signal $\mathbf f$, thus providing a way to approximate $T^{-1}$.
+Thanks to this we are able, for a given sampling, a given function $f$, a given rotation $g$, and a given kernel $k$, to compute the \textit{normalized equivariance error}
+\begin{equation} \label{eq:equivariance error}
+	E_{G}(f, g) = \left(\frac{ \norm {T \Lambda(g) T^{-1} \Omega_k Tf - \Omega_k T \Lambda(g) f}_{L^2(\mathbb R^2)}}{\norm {Tf}_{L^2(\mathbb R^2)}}\right)^2,
+\end{equation}
+where $T^{-1}$ is substituted with a discrete SHT in case $T$ is not invertible.
+A measure of how equivariant a graph is with respect to rotations will then be given by the \textit{mean equivariance error}
+\begin{equation} \label{eq:mean equivariance error}
+	\overline E_G = \mathbb E_{f, g} \ E_G(f, g).
+\end{equation}
+In practice the expected value is obtained by averaging over a finite number of random functions and random rotations.
+The mean equivariance error $\overline E_G$ gives us an indication of how close the graph $G$ is from being equivariant to rotations.
+Now we state an intuitive concept that explains how to construct rotation invariant graphs, i.e., graphs such that $\overline{E_G}$ is small.
+The mean equivariance error $\overline{E_G}$ will be small if the scalar product $\mathbf f^T \mathbf v_{i(\ell, m)}$ well approximates $\hat {f}(\ell,m)$, i.e., the $L^2$ scalar product of the continuous signal $\hat {f}(\ell,m)= \int_{\eta \in \mathbb S^2}f(\eta)Y_\ell^m(\eta)d\mu(\eta)$.
+
+\textit{If $V$ is an equal area sampling scheme}, i.e., the area around each pixel $v_i$ is the same, $\overline{E_G}$ will be small if the graph Laplacian $\mathbf L$ is such that its eigenvectors $\mathbf v_i$ well approximate the eigenfunctions of the Laplace-Beltrami operator $\Delta_{\mathbb S^2}$ evaluated in the points of the sampling scheme, i.e., $\mathbf v_{i(\ell, m)} \approx Y_\ell^m(x_i)$.
+
+In this way we framed the problem of constructing a rotation invariant graph with the more general problem of coming up with a matrix $\mathbf L$ with some specific spectral properties.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{DeepSphereonHEALPix.png}
+	\includegraphics[width=\textwidth]{OptimalHKGLonHEALPix.png}
+	\caption{\label{fig:DeepSphere equivariance error}Mean equivariance error of the diffusion filter $\exp(-\Lambda)$ for $G$, $G'$ and the full HKGL, by spherical harmonic degree.
+Notice the difference in the scale of the y axis for DeepSphere, that reaches errors up to 30\%.}
+\end{figure}
+
 \end{document}

### 2019-09-18 main.tex
Updates from Overleaf

@@
 
+\cite{khasanova2017graphomni} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling.
+They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes.
+In other words, they solve the minimization problem
+\begin{equation} \label{eq:minimization frossard}
+	\min_{W\in\mathcal G} \left|\mathcal{F}\left(\mathbf{y}\left(v_{ e}\right)\right)-\mathcal{F}\left(\mathbf{y}\left(v_{ i}\right)\right)\right|
+\end{equation}
+for the adjacency matrix $W$, where $\mathbf y(v_i)$ is the image of the object on the sphere centered on the vertex $v_i$, and $\mathcal F (\mathbf y(v_e))$ is the response of the filter at the vertex $v_e$ that lies at the same longitude of the vertex $v_i$ but on the equator.
+In their work they prove that the optimal weights solving the minimization problem (\ref{eq:minimization frossard}) are given by weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
+\begin{equation} \label{eq:frossard weights}
+	w_{ij} = \frac{1}{\norm{x_i-x_j}}
+\end{equation}
+
 \begin{figure}
@@
 
-% !) summary the work of Khasanova
-\cite{khasanova2017graphomni} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling.
-They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes.
-In other words, they solve the minimization problem
-\begin{equation} \label{eq:minimization frossard}
-	\min_{W\in\mathcal G} \left|\mathcal{F}\left(\mathbf{y}\left(v_{ e}\right)\right)-\mathcal{F}\left(\mathbf{y}\left(v_{ i}\right)\right)\right|
-\end{equation}
-for the adjacency matrix $W$, where $\mathbf y(v_i)$ is the image of the object on the sphere centered on the vertex $v_i$, and $\mathcal F (\mathbf y(v_e))$ is the response of the filter at the vertex $v_e$ that lies at the same longitude of the vertex $v_i$ but on the equator.
-In their work they prove that the optimal weights solving the minimization problem (\ref{eq:minimization frossard}) are given by weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
-\begin{equation} \label{eq:frossard weights}
-	w_{ij} = \frac{1}{\norm{x_i-x_j}}
-\end{equation}
+% !) summary the work of Khasanova -> No! to be put in section 2) Method
 
 % 2) explain our approach
-Our approach is different as we do not miminize eq \ref{eq:minimization frossard}.
-Instead we inspire ourselves with Belkin, which says that for \emph{uniform sampling} the graph Laplacian converges toward the Laplace-Beltrami.
+We inspire ourselves with Belkin, which says that for \emph{uniform sampling} the graph Laplacian converges toward the Laplace-Beltrami.
 b) The Laplace Beltrami commute with rotation.
@@
 Define the error, show results and comments
+\begin{figure}
+	\centering
+	\includegraphics[width=0.9\linewidth]{figure_architecture_v3}
+	\caption{Example architecture from \cite{perraudin2019deepsphere}.
+		Global tasks need a spatial summarization: the FCN variant is rotation invariant (and accepts inputs of varying sizes), while the CNN variant is not.
+		Dense tasks (when the output lives on the sphere, like segmentation) are rotation equivariant.
+	}
+	\label{fig:architecture}
+\end{figure}
 

### 2019-09-19 main.tex
update intro & results

@@
 
+\renewcommand{\figref}[1]{figure~\ref{fig:#1}}
+\renewcommand{\Figref}[1]{Figure~\ref{fig:#1}}
+\newcommand{\tabref}[1]{table~\ref{tab:#1}}
+\newcommand{\Tabref}[1]{Table~\ref{tab:#1}}
+\renewcommand{\secref}[1]{section~\ref{sec:#1}}
+\renewcommand{\Secref}[1]{Section~\ref{sec:#1}}
+%\newcommand{\secref}[1]{\S\ref{sec:#1}}
+\newcommand{\eqnref}[1]{equation~(\ref{eqn:#1})}
+\newcommand{\Eqnref}[1]{Equation~(\ref{eqn:#1})}
+
 %\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
@@
 	* adjacency matrix: $A$ instead of $W$? \\
-	* anonymize DeepSphere citation
+	* anonymize DeepSphere citation \\
+	* climate spherical figure: inputs with TC and AR labels superimposed \\
+	* citet for inline, citep for parenthesis \\
 }
@@
 % spherical data f: S^2 -> R, projection from R^3
-Examples of (i) are planetary data (such as temperature, wind, geological) and brain activity.
-An example of (ii) is cosmological observations.
-
-Learning is desirable for...
-Problems to be tackled by machine learning might be local or global regression or classification.
+Examples of (i) are planetary data (such as meteorological or geological measurements) and brain activity.
+Examples of (ii) is the observation of the universe, LIDAR scans, and the digitalization of 3D objects. % through which apparatus?
+See \figref{examples}.
+In many applications, labels or variables are to be inferred from spherical data.
+Examples are the inference of cosmological parameters from the distribution of mass in the universe \citep{perraudin2019deepsphere}, and the segmentation of cyclones from Earth observation \citep{mudigonda2017climateevents}.
 
@@
 
-Exploit the geometrical properties of the domain, symmetries.
-
-We identify the following desiderata for spherical CNNs:\\
-* respect the domain\\
-  * rotational equivariance\\
-  * deformation (e.g., on the icosahedron for gauge)\\
+Neural networks (NNs) have proved to be great tools to solve inference problems. % when a huge amount of data is available.
+As such, multiple kinds of NNs have been developed to handle spherical data, each with their strengths and weaknesses.
+% balance of ??
+% Exploit the geometrical properties of the domain, symmetries.
+% desiderata or tradeoff
+We identified the following desiderata for a spherical NN.
+\begin{enumerate}
+	\item \textbf{Respect the domain.}
+		By respecting the domain, a spherical NN should respect the symmetries of the sphere, i.e., be equivariant to rotation, and not deform the sphere, e.g., by a projection on the icosahedron.
+	\item \textbf{Be powerful.}
+	\item \textbf{Scale.}
+	\item \textbf{Be flexible.}
+\begin{enumerate}
 * powerful / generality $\Rightarrow$ isotropic vs anisotropic\\
@@
 * flexible (samplings, irregular), simplicity (implementation)\\
-
-Multiple methods have been developed to handle spherical data, each with their strengths and weaknesses.
 
@@
 * 5 runs for each loss to obtain mean and std\\
+* same architecture as gauge, more feature maps than Jiang\\
+* perf with same arch as Jiang in appendix => not enough channels!\\
+* even more feature maps give us one more point in perf\\
+* cannot compare with Mudigonda: not the same input data\\
+* why: icosahedron, can do anisotropy with isotropy + non-linearity + pooling
 
@@
   * Not the most general (restricted to isotropic filters), but didn't hurt perf in any experiment\\
+  * Similar as in GNN: most general might not be the best [Andreas paper?] \\
   * scales linearly $\Rightarrow$ cannot do better ($n^{1.25}$ for best HEALPix, linear for not optimal)\\
@@
 Left blank for anonymity reason
-% Use unnumbered third level headings for the acknowledgments. All
-% acknowledgments, including those to funding agencies, go at the end of the paper.
+
+%We thank Taco Cohen for his inputs on the intriguing results of our comparisons with their gauge CNN \citep{}.
 

### 2019-09-19 main.tex
Updates from Overleaf

--- 2019-09-18 main.tex
@@
 
-\cite{khasanova2017graphomni} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling.
+% \cite{khasanova2017graphomni} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling.
 They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes.
 In other words, they solve the minimization problem
-\begin{equation} \label{eq:minimization frossard}
-	\min_{W\in\mathcal G} \left|\mathcal{F}\left(\mathbf{y}\left(v_{ e}\right)\right)-\mathcal{F}\left(\mathbf{y}\left(v_{ i}\right)\right)\right|
-\end{equation}
-for the adjacency matrix $W$, where $\mathbf y(v_i)$ is the image of the object on the sphere centered on the vertex $v_i$, and $\mathcal F (\mathbf y(v_e))$ is the response of the filter at the vertex $v_e$ that lies at the same longitude of the vertex $v_i$ but on the equator.
+% \begin{equation} \label{eq:minimization frossard}
+% 	\min_{W\in\mathcal G} \left|\mathcal{F}\left(\mathbf{y}\left(v_{ e}\right)\right)-\mathcal{F}\left(\mathbf{y}\left(v_{ i}\right)\right)\right|
+% \end{equation}
+% for the adjacency matrix $W$, where $\mathbf y(v_i)$ is the image of the object on the sphere centered on the vertex $v_i$, and $\mathcal F (\mathbf y(v_e))$ is the response of the filter at the vertex $v_e$ that lies at the same longitude of the vertex $v_i$ but on the equator.
 In their work they prove that the optimal weights solving the minimization problem (\ref{eq:minimization frossard}) are given by weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
-\begin{equation} \label{eq:frossard weights}
-	w_{ij} = \frac{1}{\norm{x_i-x_j}}
-\end{equation}
+% \begin{equation} \label{eq:frossard weights}
+% 	w_{ij} = \frac{1}{\norm{x_i-x_j}}
+% \end{equation}
 
@@
 
+% \section{Notation}
+% Throughout this contribution, we denote with bold font all vectors and matrices such as $\b{L}$ the graph Laplacian and $\b{f}$ the vector of the sampled function $f$.
+% \nati{Right now, it is not True}
+% % , a weighted undirected graph $G(V, E, \mathbf W)$,
+% \nati{I do not think we should have a notation section, but should somehow write this somewhere...}
+
 \section{Is graph convolution equivariant to rotation? [2 pages]}
@@
 % The plan for this section
-% 0) Explain why the Laplacian is so important...
-By definition, the graph convolution (on the sphere) is rotation equivariant to rotation, if and only if, it commutes with the rotation operator. 
-As, in the context of this work, graph convolution can be performed by successive application of the graph Laplacian, i.e: $g(\b{L}) \b{f} = \left(\sum_{i=0}^K \alpha_i \b{L}^i\right) \b{f}$, if the graph Laplacian $\b{L}$ commutes with the rotation operator, then, by recursion, it will also commute with the convolution $g(\b{L})$.
-Hence to simplify our analysis, we concentrate on the graph Laplacian.
+% 0.1 Explain the sampling problem
+\paragraph{Sampling} 
+As the graph convolution act on a sampled version of the signal $\b{f}$ and the rotation on its continuous counterpart $f$, we first need to define a sampling operator.
+Given a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere and a function $f : \mathbb S^2 \supset F_V \to \mathbb R$, the sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \b{f}$ is defined as $\b{f}:\ f_i=f(v_i)$, where $F_V$ suitable subspace of $L^2(\mathbb S^2)$ such that $T_V$ is invertible, i.e., we can unambiguously reconstruct the function $f\in F_V$ from its sampled values $\b{f}$.
+The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing \cite{Driscoll:1994:CFT:184069.184073}. 
+For most samplings, it is not known if $F_V$ exist and hence if $T_V$ is invertible.
+A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds, and thus we have a closed form of $T_V^{-1}$ is known.
+% \cite{Driscoll:1994:CFT:184069.184073}
+For sampling schemes where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\bf{f}$, thus approximating $T_V^{-1}$. 
+For all theoretical consideration, we assume that $F_V$ exists and $f \in F_V$.
 
-% 0.5) Explain the sampling and metric
-We first need to deal with the sampling problem. 
-Take a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere, a weighted undirected graph $G(V, E, \mathbf W)$, a signal $f: \mathbb S^2\to\mathbb R$ and its sampled representation $\mathbf f:\ f_i=f(v_i)$.
-Suppose that there exists a sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \mathbf f$ defined on a suitable subspace $F$ of $L^2(\mathbb S^2)$ such that it is invertible, i.e., we can unambiguously reconstruct the function $f\in F$ from its sampled values $\mathbf f$.
-The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing \cite{Driscoll:1994:CFT:184069.184073}.
-Define the rotation operator $R(g), g\in SO(3)$: $R(g) f(\omega) = f\left(g^{-1} \omega\right)$.
+% 0.2 Explain why the Laplacian is so important...
+\paragraph{Problem formulation} 
+By definition, our (spherical) graph convolution is rotation equivariant, if and only if, it commutes with the rotation operator defined as $R(g), g\in SO(3)$: $R(g) f(x) = f\left(g^{-1} x \right)$. 
+In the context of this work, graph convolution is performed by recursive applications of the graph Laplacian, i.e: $h(\b{L}) \b{f} = \left(\sum_{i=0}^K \alpha_i \b{L}^i\right) \b{f}$\nati{Put this equation somewhere else?}.
+Hence, if $\b{L}$ commutes with the rotation operator, then, by recursion, it will also commute with the convolution $h(\b{L})$.
+As a result, to simplify our analysis, we concentrate on the graph Laplacian and $h(\b{L})$ is rotational invariant if and only if 
+% 0.3 Formulate the problem
+\begin{equation} \label{eq:equivariance}
+	\b{R}_V(g) \b{L} \b{f} = \b{L} \b{R}_V(g) \b{f} \hspace{1cm} \forall f\in F_V \text{ and } \forall g\in SO(3), 
+\end{equation}
+where $\b{R}_V(g) = T_V R(g) T_V^{-1}$. For practical application, we define the \textit{normalized equivariance error} for a signal $\b{f}$, and a  rotation $g$ as:
+\begin{equation} \label{eq:equivariance error}
+	E_{\b{L}}(\b{f}, g) = \left(\frac{ \norm {\b{R}_V(g) \b{L} \b{f} - \b{L} \b{R}_V(g) \b{f}} }{\norm {\b{f}}}\right)^2,
+\end{equation}
+More generally for a class of signal $f \in C \subset F_V$, the \textit{mean equivariance error}
+\begin{equation} \label{eq:mean equivariance error}
+	\overline E_{\b{L}, C} = \mathbb E_{\b{f}\in C, g\in SO(3)} \ E_{\b{L}}(\b{f}, g).
+\end{equation}
+In practice, to anlyse the equivariance error frequency,  the set $C$ we used is composed of functions $f$ with made of spherical harmonic of a single degree $\ell$.
+The expected value is obtained by averaging over a finite number of random functions and random rotations.
 
-We now want to understand how to set the edges and the weights of $G$ such that
-\begin{equation} \label{eq:equivariance}
-	T \R(g) T^{-1} \Omega_k T f = \Omega_k T R(g) f,
+\subsection{Finding a the optimal set of weights}
+% !) summary the work of Khasanova -> No! to be put in section 2) Method
+\cite{khasanova2017graphomni} designed a Laplacian $\b{L}$ explicitly intended to work with the equiangular sampling. 
+They consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude latitude axis.
+Their approach leads to weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
+\begin{equation} \label{eq:frossard weights}
+	w_{ij} = \frac{1}{\norm{x_i-x_j}}
 \end{equation}
-i.e., the graph convolution $\Omega_k$ and any rotation $R(g)$ commute.
-
-Verifying equation (\ref{eq:equivariance}) is really hard in practice, due to the fact that for almost all sampling schemes $V$ it is not known if there exists a space $F$ in which $T$ is invertible.
-A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds \cite{Driscoll:1994:CFT:184069.184073}, and thus we have a closed form of $T^{-1}$.
-For sampling schemes where no such sampling theorem is available, there are implementations of discrete SHT to reconstruct a sampled signal $\mathbf f$, thus providing a way to approximate $T^{-1}$.
-Thanks to this we are able, for a given sampling, a given function $f$, a given rotation $g$, and a given kernel $k$, to compute the \textit{normalized equivariance error}
-\begin{equation} \label{eq:equivariance error}
-	E_{G}(f, g) = \left(\frac{ \norm {T R(g) T^{-1} \Omega_k Tf - \Omega_k T R(g) f}_{L^2(\mathbb R^2)}}{\norm {Tf}_{L^2(\mathbb R^2)}}\right)^2,
-\end{equation}
-where $T^{-1}$ is substituted with a discrete SHT in case $T$ is not invertible.
-A measure of how equivariant a graph is with respect to rotations will then be given by the \textit{mean equivariance error}
-\begin{equation} \label{eq:mean equivariance error}
-	\overline E_G = \mathbb E_{f, g} \ E_G(f, g).
-\end{equation}
-In practice the expected value is obtained by averaging over a finite number of random functions and random rotations.
-The mean equivariance error $\overline E_G$ gives us an indication of how close the graph $G$ is from being equivariant to rotations.
-Of course result will depend on the sampling and on the graph construction.
-
-% !) summary the work of Khasanova -> No! to be put in section 2) Method
 
 % 2) explain our approach
-We inspire ourselves with Belkin, which says that for \emph{uniform sampling} the graph Laplacian converges toward the Laplace-Beltrami.
-b) The Laplace Beltrami commute with rotation.
+We chose a different approach and take inspiration from \cite{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta$ as the number of sampling point goes to infinity.
+This convergence result is important as a) $\Delta$ commutes with rotation and b) is diagonalized by the spherical harmonics. 
+In this case the weighting scheme is full (every node is connected to every node) and is based the exponential kernel: 
+\nati{@martino, please check this equation... Do you use 4t?}
+\begin{equation} \label{eq:belkin_weights}
+w_{ij} = e^{-\frac{1}{t} \norm{x_i-x_j}^2}
+\end{equation}
+In practice
 The following theorem extend the work of Belkin and Nyiogi to fixed sampling \nati{(Including Healpix or not?)}. 
@@
 To have the desired equality in eq..., we would need to prove a stronger result, for example uniform convergence (in the space of the operators).
-\nati{Should we put this here?: }This does not hold in general \cite{belkin-spectral}. However, we believe that this is achievable for a bandlimited signals.
+\nati{Should we put this here?: }
+This does not hold in general \cite{belkin2007convergence}. However, we believe that this is achievable for a bandlimited signals.
 More importantly, the proof of theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix ...
@@
 Define the error, show results and comments
-\begin{figure}
-	\centering
-	\includegraphics[width=0.9\linewidth]{figure_architecture_v3}
-	\caption{Example architecture from \cite{perraudin2019deepsphere}.
-		Global tasks need a spatial summarization: the FCN variant is rotation invariant (and accepts inputs of varying sizes), while the CNN variant is not.
-		Dense tasks (when the output lives on the sphere, like segmentation) are rotation equivariant.
-	}
-	\label{fig:architecture}
-\end{figure}
 
@@
 }
+
+% \begin{table}[]
+%     \centering
+%     \begin{tabular}{c|c}
+%          &  \\
+%          & 
+%     \end{tabular}
+%     \caption{Caption}
+%     \label{tab:cosmo_newgraph}
+% \end{table}
 

### 2019-09-19 main.tex
Updates from Overleaf

--- 2019-09-19 main.tex
@@
 \paragraph{Sampling} 
-As the graph convolution act on a sampled version of the signal $\b{f}$ and the rotation on its continuous counterpart $f$, we first need to define a sampling operator.
+As the graph convolution acts on a sampled version of the signal $\b{f}$ and the rotation on its continuous counterpart $f$, we first need to define a sampling operator.
 Given a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere and a function $f : \mathbb S^2 \supset F_V \to \mathbb R$, the sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \b{f}$ is defined as $\b{f}:\ f_i=f(v_i)$, where $F_V$ suitable subspace of $L^2(\mathbb S^2)$ such that $T_V$ is invertible, i.e., we can unambiguously reconstruct the function $f\in F_V$ from its sampled values $\b{f}$.

### 2019-09-19 main.tex
fix latex

--- 2019-09-19 main.tex
@@
 	\item \textbf{Be flexible.}
-\begin{enumerate}
+\end{enumerate}
 * powerful / generality $\Rightarrow$ isotropic vs anisotropic\\

### 2019-09-19 main.tex
update references

@@
 In many applications, labels or variables are to be inferred from spherical data.
-Examples are the inference of cosmological parameters from the distribution of mass in the universe \citep{perraudin2019deepsphere}, and the segmentation of cyclones from Earth observation \citep{mudigonda2017climateevents}.
+Examples are the inference of cosmological parameters from the distribution of mass in the universe \citep{perraudin2019deepspherecosmo}, and the segmentation of cyclones from Earth observation \citep{mudigonda2017climateevents}.
 
@@
 
-This paper focuses on improving the equivariance of \cite{perraudin2019deepsphere}, a scalable graph-based method designed for cosmological applications.
+This paper focuses on improving the equivariance of \cite{perraudin2019deepspherecosmo}, a scalable graph-based method designed for cosmological applications.
 \todo{cite RLGM paper}
 Experiments on multiple problems of practical interest shows the competitiveness and flexibility of our method.
-Furthermore, those experiments show, contrarily to previously published results \cite{cohen_gauge_2019}, that anisotropic filters may be an unnecessary price to pay.
+Furthermore, those experiments show, contrarily to previously published results \cite{cohen2019gauge}, that anisotropic filters may be an unnecessary price to pay.
 
@@
 
-* HEALPix: improvement from DeepSphere v1 \cite{perraudin2019deepsphere} \\
+* HEALPix: improvement from DeepSphere v1 \cite{perraudin2019deepspherecosmo} \\
 * equiangular: Renata \& Pascal \\
 
-% \cite{khasanova2017graphomni} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling.
+% \cite{khasanova2017sphericalcnn} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling.
 They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes.
@@
 	\includegraphics[width=0.9\linewidth]{figure_architecture_v3}
-	\caption{Example architecture from \cite{perraudin2019deepsphere}.
+	\caption{Example architecture from \cite{perraudin2019deepspherecosmo}.
 		Global tasks need a spatial summarization: the FCN variant is rotation invariant (and accepts inputs of varying sizes), while the CNN variant is not.
@@
 Given a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere and a function $f : \mathbb S^2 \supset F_V \to \mathbb R$, the sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \b{f}$ is defined as $\b{f}:\ f_i=f(v_i)$, where $F_V$ suitable subspace of $L^2(\mathbb S^2)$ such that $T_V$ is invertible, i.e., we can unambiguously reconstruct the function $f\in F_V$ from its sampled values $\b{f}$.
-The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing \cite{Driscoll:1994:CFT:184069.184073}. 
+The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing \cite{driscoll1994Fouriersphere}.
 For most samplings, it is not known if $F_V$ exist and hence if $T_V$ is invertible.
 A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds, and thus we have a closed form of $T_V^{-1}$ is known.
-% \cite{Driscoll:1994:CFT:184069.184073}
+% \cite{driscoll1994Fouriersphere}
 For sampling schemes where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\bf{f}$, thus approximating $T_V^{-1}$.
@@
 % !) summary the work of Khasanova -> No! to be put in section 2) Method
-\cite{khasanova2017graphomni} designed a Laplacian $\b{L}$ explicitly intended to work with the equiangular sampling. 
+\cite{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ explicitly intended to work with the equiangular sampling.
 They consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude latitude axis.
@@
         \multicolumn{1}{l}{Method} & F1 & mAP & params & inference [ms] & training \\ \hline
-        \cite{cohen_spherical_2018} & 78.85 & 67.6 & 1.4M & 38 & 50h\\
+        \cite{cohen2018sphericalcnn} & 78.85 & 67.6 & 1.4M & 38 & 50h\\
         % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
-        \cite{esteves_learning_2017} & 79.36 & 68.5 & 500k & 10 & 2h52\\ \hline
+        \cite{esteves2018sphericalcnn} & 79.36 & 68.5 & 500k & 10 & 2h52\\ \hline
         DeepSphere \emph{Equiangular} & 79.36 & 66.5 & 190k & 1 & 50m \\
@@
 	%Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
-	\cite{jiang_spherical_2019} & 94.67 & - & - & -\\
-	\cite{jiang_spherical_2019} \emph{rerun} & 94.95 & 38.41 & 10 & 10h\\
+	\cite{jiang2019sphericalcnn} & 94.67 & - & - & -\\
+	\cite{jiang2019sphericalcnn} \emph{rerun} & 94.95 & 38.41 & 10 & 10h\\
 	% 328'339
-	\cite{cohen_gauge_2019} (S2R) & 97.5 & 68.6 & - & -\\
-	\cite{cohen_gauge_2019} (R2R) & 97.7 & 75.9 & - & -\\ \hline
+	\cite{cohen2019gauge} (S2R) & 97.5 & 68.6 & - & -\\
+	\cite{cohen2019gauge} (R2R) & 97.7 & 75.9 & - & -\\ \hline
 	% unknown
@@
 	\end{tabular}
-	\caption{Climate pattern segmentation mean accuracy (\%), mean Average Precision (\%) and speed for different models run on the icosahedron dataset from \cite{jiang_spherical_2019}}
+	\caption{Climate pattern segmentation mean accuracy (\%), mean Average Precision (\%) and speed for different models run on the icosahedron dataset from \cite{jiang2019sphericalcnn}}
 \end{table}
@@
 \end{definition}
-\begin{definition}{} \cite{Belkin:2005:TTF:2138147.2138189}\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, and let $\text{vol}(\mathcal M)$ be the volume of $\mathcal M$.
+\begin{definition}{} \cite{belkin2005towards}\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, and let $\text{vol}(\mathcal M)$ be the volume of $\mathcal M$.
 We define the functional approximation to the Laplace-Beltrami operator to be the operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
@@
 
-\begin{prop} \cite{Belkin:2005:TTF:2138147.2138189} \\
+\begin{prop} \cite{belkin2005towards} \\
 Let $\mathcal M$ be a $k$-dimensional compact smooth manifold embedded in some euclidean space $\mathbb R^N$, and fix $p\in\mathcal M$.
@@
 In the work of Belkin et al.
-\cite{Belkin:2005:TTF:2138147.2138189} the sampling is drawn form a uniform random distribution on the sphere, and their proof heavily relies on the uniformity properties of the distribution from which the sampling is drawn.
+\cite{belkin2005towards} the sampling is drawn form a uniform random distribution on the sphere, and their proof heavily relies on the uniformity properties of the distribution from which the sampling is drawn.
 In our case the sampling is deterministic, and the fact that for a sphere there doesn't exist a regular sampling with more than 12 points (the vertices of a icosahedron) is indeed a problem that we need to overcome by imposing the regularity conditions above.
 
-To conclude, we can see that the result obtained has the same form than the result obtained in \cite{Belkin:2005:TTF:2138147.2138189}.
+To conclude, we can see that the result obtained has the same form than the result obtained in \cite{belkin2005towards}.
 Given the kernel density $t(n)=n^\beta$, if Belkin et al.
@@
         %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
-        \cite{jiang_spherical_2019} & 94 & 93 & 97 & 94.67 & 330k\\
-        \cite{jiang_spherical_2019} \emph{rerun} & 93.9 & 95.7 & 95.2 & 94.95 & 330k\\
+        \cite{jiang2019sphericalcnn} & 94 & 93 & 97 & 94.67 & 330k\\
+        \cite{jiang2019sphericalcnn} \emph{rerun} & 93.9 & 95.7 & 95.2 & 94.95 & 330k\\
         % 328'339
-        \cite{cohen_gauge_2019} (S2R) & 97.3 & 97.3 & 97.8 & 97.5 & -\\
-        \cite{cohen_gauge_2019} (R2R) & 97.8 & 97.4 & 97.9 & 97.7 & -\\ \hline
+        \cite{cohen2019gauge} (S2R) & 97.3 & 97.3 & 97.8 & 97.5 & -\\
+        \cite{cohen2019gauge} (R2R) & 97.8 & 97.4 & 97.9 & 97.7 & -\\ \hline
         DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ & 13M\\
@@
 
-* DS-jiang is the similar architecture as \cite{jiang_spherical_2019}.\\
+* DS-jiang is the similar architecture as \cite{jiang2019sphericalcnn}.\\
 * DS-optimal has 2 times the number of feature maps of DS.\\
@@
         %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
-        \cite{jiang_spherical_2019} \emph{rerun} & 11.08 & 65.21 & 38.41 & 10.2 & 10h14m\\
+        \cite{jiang2019sphericalcnn} \emph{rerun} & 11.08 & 65.21 & 38.41 & 10.2 & 10h14m\\
         % 328'339
-        \cite{cohen_gauge_2019} (S2R) & - & -& 68.6 & - & - \\
-        \cite{cohen_gauge_2019} (R2R) & - & -& 75.9 & - & -\\ \hline
+        \cite{cohen2019gauge} (S2R) & - & -& 68.6 & - & - \\
+        \cite{cohen2019gauge} (R2R) & - & -& 75.9 & - & -\\ \hline
         DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 33 & 13h \\
@@
 
-\cite{khasanova2017graphomni} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling.
+\cite{khasanova2017sphericalcnn} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling.
 They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes.
@@
 Suppose that there exists a sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \mathbf f$ defined on a suitable subspace $F$ of $L^2(\mathbb S^2)$ such that it is invertible, i.e., we can unambiguously reconstruct the function $f\in F$ from its sampled values $\mathbf f$.
-The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing \cite{Driscoll:1994:CFT:184069.184073}.
+The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing \cite{driscoll1994Fouriersphere}.
 Define the rotation operator $\Lambda(g), g\in SO(3)$: $\Lambda(g) f(\omega) = f\left(g^{-1} \omega\right)$.
@@
 Verifying equation (\ref{eq:equivariance}) is really hard in practice, due to the fact that for almost all sampling schemes $V$ it is not known if there exists a space $F$ in which $T$ is invertible.
-A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds \cite{Driscoll:1994:CFT:184069.184073}, and thus we have a closed form of $T^{-1}$.
+A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds \cite{driscoll1994Fouriersphere}, and thus we have a closed form of $T^{-1}$.
 For sampling schemes where no such sampling theorem is available, there are implementations of discrete SHT to reconstruct a sampled signal $\mathbf f$, thus providing a way to approximate $T^{-1}$.

### 2019-09-19 main.tex
Updates from Overleaf

--- 2019-09-19 main.tex
@@
 
+\subsection{Problem formulation} 
 % The plan for this section
 % 0.1 Explain the sampling problem
-\paragraph{Sampling} 
-As the graph convolution act on a sampled version of the signal $\b{f}$ and the rotation on its continuous counterpart $f$, we first need to define a sampling operator.
+As the graph convolution acts on a sampled version of the signal $\b{f}$ and the rotation on its continuous counterpart $f$, we first need to define a sampling operator.
 Given a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere and a function $f : \mathbb S^2 \supset F_V \to \mathbb R$, the sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \b{f}$ is defined as $\b{f}:\ f_i=f(v_i)$, where $F_V$ suitable subspace of $L^2(\mathbb S^2)$ such that $T_V$ is invertible, i.e., we can unambiguously reconstruct the function $f\in F_V$ from its sampled values $\b{f}$.
@@
 % 0.2 Explain why the Laplacian is so important...
-\paragraph{Problem formulation} 
 By definition, our (spherical) graph convolution is rotation equivariant, if and only if, it commutes with the rotation operator defined as $R(g), g\in SO(3)$: $R(g) f(x) = f\left(g^{-1} x \right)$. 
@@
 % 2) explain our approach
-We chose a different approach and take inspiration from \cite{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta$ as the number of sampling point goes to infinity.
-This convergence result is important as a) $\Delta$ commutes with rotation and b) is diagonalized by the spherical harmonics. 
+We chose a different approach and take inspiration from \cite{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling point goes to infinity.
+This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics. 
 In this case the weighting scheme is full (every node is connected to every node) and is based the exponential kernel: 
@@
 \end{equation}
-In practice
-The following theorem extend the work of Belkin and Nyiogi to fixed sampling \nati{(Including Healpix or not?)}. 
+In practice most of the weights are very close to $0$ and hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
+Given $k$, we find the optimal $t$, a grid search is performed using \eqref{eq:mean equivariance error}.
+
+\subsection{Analysis of the proposed weighting scheme}
+We analyse our proposed weighting scheme both theoretically and empirically
+
+\paragraph{Theoretical convergence.}
+We extend the work Belkin and Nyiogi to a fixed sampling. 
 Given a sampling $V = \{x_0, \dots, x_{n-1}\}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$.
 Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
-
 \begin{theorem}
 	For a sampling $\mathcal P = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian operator $\frac{|\mathbb S^2|}{4\pi t_n}L^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\triangle_{\mathbb S^2}$  for $n\to\infty$:
-	$$ \lim_{n\to\infty}\frac{|\mathbb S^2|}{4\pi t_n} L_n^{t_n}f(y) =  \triangle_{\mathbb S^2}f(y).$$
+	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n} \b{L}_n^{t_n} T_{V_n} f(y) =  \Delta_{\mathbb{S}^2}f(y).$$
 	\label{theo:pointwise convergence for a regular sampling}
 \end{theorem}
-
-This is \emph{not} a proof of equivariance of the graph convolution for a specific sampling.
-We simply observe that the graph Laplacian converges pointwisely toward an operator that commutes with rotation.
+While this is \emph{not} a proof of equivariance of the graph convolution for a specific sampling, we observe that the $\b{L}$ converges pointwisely toward an operator ($\Delta_{\mathbb S^2}$) commuting with rotation.
 To have the desired equality in eq..., we would need to prove a stronger result, for example uniform convergence (in the space of the operators).
@@
 a) use gaussian kernel b) we need to adjust t with respect of n such that ...
+\nati{While do not have a proof for it, we srongly believe that the HEALpix sampling do satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}.
+This is discussed in Appendix~\ref{...}}
 
 % 3) Show experimental results
-Define the error, show results and comments
-
+\paragraph{Empirical convergence.}
+\nati{@martino, please put some stuff here...}
 Explain the difference of errors... Uniform sampling is better

### 2019-09-19 main.tex

--- 2019-09-19 main.tex
@@
 
+\subsection{Problem formulation} 
 % The plan for this section
 % 0.1 Explain the sampling problem
-\paragraph{Sampling}
 As the graph convolution acts on a sampled version of the signal $\b{f}$ and the rotation on its continuous counterpart $f$, we first need to define a sampling operator.
@@
 % 0.2 Explain why the Laplacian is so important...
-\paragraph{Problem formulation}
 By definition, our (spherical) graph convolution is rotation equivariant, if and only if, it commutes with the rotation operator defined as $R(g), g\in SO(3)$: $R(g) f(x) = f\left(g^{-1} x \right)$. 
@@
 % 2) explain our approach
-We chose a different approach and take inspiration from \cite{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta$ as the number of sampling point goes to infinity.
-This convergence result is important as a) $\Delta$ commutes with rotation and b) is diagonalized by the spherical harmonics.
+We chose a different approach and take inspiration from \cite{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling point goes to infinity.
+This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics. 
 In this case the weighting scheme is full (every node is connected to every node) and is based the exponential kernel: 
@@
 \end{equation}
-In practice
-The following theorem extend the work of Belkin and Nyiogi to fixed sampling \nati{(Including Healpix or not?)}.
+In practice most of the weights are very close to $0$ and hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
+Given $k$, we find the optimal $t$, a grid search is performed using \eqref{eq:mean equivariance error}.
+
+\subsection{Analysis of the proposed weighting scheme}
+We analyse our proposed weighting scheme both theoretically and empirically.
+
+\paragraph{Theoretical convergence.}
+We extend the work Belkin and Nyiogi to a fixed sampling. 
 Given a sampling $V = \{x_0, \dots, x_{n-1}\}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$.
 Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
-
 \begin{theorem}
 	For a sampling $\mathcal P = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian operator $\frac{|\mathbb S^2|}{4\pi t_n}L^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\triangle_{\mathbb S^2}$  for $n\to\infty$:
-	$$ \lim_{n\to\infty}\frac{|\mathbb S^2|}{4\pi t_n} L_n^{t_n}f(y) =  \triangle_{\mathbb S^2}f(y).$$
+	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n} \b{L}_n^{t_n} T_{V_n} f(y) =  \Delta_{\mathbb{S}^2}f(y).$$
 	\label{theo:pointwise convergence for a regular sampling}
 \end{theorem}
-
-This is \emph{not} a proof of equivariance of the graph convolution for a specific sampling.
-We simply observe that the graph Laplacian converges pointwisely toward an operator that commutes with rotation.
+While this is \emph{not} a proof of equivariance of the graph convolution for a specific sampling, we observe that the $\b{L}$ converges pointwisely toward an operator ($\Delta_{\mathbb S^2}$) commuting with rotation.
 To have the desired equality in eq..., we would need to prove a stronger result, for example uniform convergence (in the space of the operators).

### 2019-09-19 main.tex
Updates from Overleaf

@@
 \end{theorem}
-While this is \emph{not} a proof of equivariance of the graph convolution for a specific sampling, we observe that the $\b{L}$ converges pointwisely toward an operator ($\Delta_{\mathbb S^2}$) commuting with rotation.
-To have the desired equality in eq..., we would need to prove a stronger result, for example uniform convergence (in the space of the operators).
-\nati{Should we put this here?: }
-This does not hold in general \cite{belkin2007convergence}. However, we believe that this is achievable for a bandlimited signals.
-More importantly, the proof of theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix ...
-inspires us in the construction of our graph Laplacian.
-a) use gaussian kernel b) we need to adjust t with respect of n such that ...
-\nati{While do not have a proof for it, we srongly believe that the HEALpix sampling do satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}.
-This is discussed in Appendix~\ref{...}}
+This theorem show that the $\b{L}$ converges pointwisely toward an operator ($\Delta_{\mathbb S^2}$) commuting with rotation and hence is a strong hints for equivariance.
+Importantly, the proof of Theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix \ref{...} inspires us in the construction of our graph Laplacian.
+It gives us a strong hint how the parameter $t$ needs to adjusted with respect of the number of point $n$.
+
+It is important to keep in mind the limits of Theorem \ref{theo:pointwise convergence for a regular sampling}.
+First, it is \emph{not} a proof of equivariance of the graph convolution for a specific sampling.
+To construct such a proof, a stronger convergence result is needed, for example uniform convergence (instead of pointwise).
+Unfortunately, the graph laplacian does \emph{not} converges uniformly in general \cite{belkin2007convergence}.
+This can probably be overcomed by considering a specific class of functions, such as bandlimited function.
+Second, while do not have a proof for it, we strongly believe that the HEALpix sampling do satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}.
+This is discussed in Appendix~\ref{...}
 
@@
 \paragraph{Empirical convergence.}
-\nati{@martino, please put some stuff here...}
+From 20\% error on V1, we got to less than 2\% error on v2.
+More neighbors, more precision, plus a better kernel width obtained "minimizing" the equivariance error.
+How to explain how we found the kernel width?
+Because minimizing the kernel width would lead to a completely disconnected graph.
+What we did was finding a heuristic law (fix neighbors, set the kernel width by imposing the minimum weight to be equal to $0.1$) and then optimizing
+\begin{figure}
+	\centering
+	\includegraphics[width=0.9\linewidth]{DeepSphereV1}
+	\caption{Shall we put it here or in Appendix?
+	}
+	\label{fig:deepsphereV1}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.9\linewidth]{DeepSphereV2_50neighbors.pdf}
+	\caption{}
+	\label{fig:deepsphereV2}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.9\linewidth]{khasanova_frossard.pdf}
+	\caption{}
+	\label{fig:khasanova_frossard}
+\end{figure}
 Explain the difference of errors... Uniform sampling is better

### 2019-09-19 main.tex
introduction & conclusion

@@
 
+\todo{
+\begin{itemize}
+	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN.
+	\item adjacency matrix: $A$ instead of $W$?
+	\item anonymize DeepSphere citation
+	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
+	\item citet for inline, citep for parenthesis
+	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
+	\item PSD of climate data: how does it compare to cosmo and 3D objects?
+	\item align the spheres in figure 1
+\end{itemize}
+}
+\newpage
+
 \maketitle
@@
 
-story: there are tradeoffs when designing a spherical CNN
+story: there are tradeoffs when designing a spherical CNN -> DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
+% DSv2 has a clear tradeoff between equivariance and computational cost
 
@@
 
-\todo{
-	* adjacency matrix: $A$ instead of $W$? \\
-	* anonymize DeepSphere citation \\
-	* climate spherical figure: inputs with TC and AR labels superimposed \\
-	* citet for inline, citep for parenthesis \\
-}
-
 \section{Introduction [2 pages]}
 
-Spherical data is common, and comes in two favors: (i) intrinsically spherical, and (ii) projection due to observation.
+Spherical data is found in many applications.
 % spherical data f: S^2 -> R, projection from R^3
-Examples of (i) are planetary data (such as meteorological or geological measurements) and brain activity.
-Examples of (ii) is the observation of the universe, LIDAR scans, and the digitalization of 3D objects. % through which apparatus?
+Planetary data (such as meteorological or geological measurements) and brain activity are example of intrinsically spherical data.
+The observation of the universe, LIDAR scans, and the digitalization of 3D objects are examples of projections due to observation.
 See \figref{examples}.
 In many applications, labels or variables are to be inferred from spherical data.
-Examples are the inference of cosmological parameters from the distribution of mass in the universe \citep{perraudin2019deepspherecosmo}, and the segmentation of cyclones from Earth observation \citep{mudigonda2017climateevents}.
+Examples are the inference of cosmological parameters from the distribution of mass in the universe \citep{perraudin2019deepspherecosmo}, the segmentation of omnidirectional images \citep{khasanova2017sphericalcnn}, and the segmentation of cyclones from Earth observation \citep{mudigonda2017climateevents}.
 
@@
 	\caption{
-		Examples of intrinsically spherical data: (left) the cosmic microwave background (CMB) temperature from \citet{planck2015overview},
-		%with galactic plane masked
-		(middle) daily maximum temperature from the Global Historical Climatology Network (GHCN),\protect\footnotemark (right) brain activity recorded through magnetoencephalography (MEG).\protect\footnotemark
-		For those examples, a rigid full-sphere pixelization is not ideal: the Milky Way's galactic plane masks observations, brain activity is measured on the scalp only, and the position and density of weather stations is arbitrary and changes over time.
+		Examples of intrinsically spherical data:
+		(left) the cosmic microwave background (CMB) temperature from \citet{planck2015overview},
+		(middle) brain activity recorded through magnetoencephalography (MEG),\protect\footnotemark
+		(right) daily maximum temperature from the Global Historical Climatology Network (GHCN).\protect\footnotemark
+		A rigid full-sphere pixelization is not ideal: the Milky Way's galactic plane masks observations, brain activity is only measured on the scalp, and the position of weather stations is arbitrary and changes over time.
 		Graphs can faithfully and efficiently represent sampled spherical data by placing vertices where data has been measured.
@@
 
-Neural networks (NNs) have proved to be great tools to solve inference problems. % when a huge amount of data is available.
-As such, multiple kinds of NNs have been developed to handle spherical data, each with their strengths and weaknesses.
 % balance of ??
@@
 % desiderata or tradeoff
-We identified the following desiderata for a spherical NN.
-\begin{enumerate}
-	\item \textbf{Respect the domain.}
-		By respecting the domain, a spherical NN should respect the symmetries of the sphere, i.e., be equivariant to rotation, and not deform the sphere, e.g., by a projection on the icosahedron.
-	\item \textbf{Be powerful.}
-	\item \textbf{Scale.}
-	\item \textbf{Be flexible.}
-\end{enumerate}
-* powerful / generality $\Rightarrow$ isotropic vs anisotropic\\
-* scale: computational cost \& memory usage (feature maps)\\
-* flexible (samplings, irregular), simplicity (implementation)\\
-
-On the one side, we have Cohen which is computationally very expensive but perfectly equivariant most general, on the other we have cube sphere which computationl very good but not equivariant at all.
+% We identified the following desiderata for a spherical NN.
+%Those take different tradeoffs among the following desiderata.
+%\begin{enumerate}
+%	\item \textbf{Respect the geometry.}  % geometry, domain
+%		By respecting the domain, a spherical NN should respect the symmetries of the sphere, i.e., be equivariant to rotation, and not deform the sphere, e.g., by a projection on the icosahedron.
+%	\item \textbf{Generality.} % powerful
+%		How general the NN is as a function approximator.
+%		For example, isotropic filters are less general than anisotropic filters.
+%	\item \textbf{Scalability.}
+%		How a spherical CNN scales w.r.t.\ the number of pixels in terms of computational cost and memory usage.
+%		% memory: feature maps and parameters
+%	\item \textbf{Flexibility.}
+%		Whether the NN is constrained to work on specific samplings, part of the sphere (useful when data is masked), and irregular samplings.
+%	\item \textbf{Simplicity.}
+%		Simplicity of its derivation and implementation.
+%\end{enumerate}
+
+% keep the story simple and focus on the tradeoff between cost (time / computational and storage / memory) and exactitude
+As neural networks (NNs) have proved to be great tools for inference, variants have been developed to handle spherical data.
+Exploiting the locally Euclidean property of the sphere, early attempts used standard 2D convolutions on a grid discretization of the sphere \citep{boomsma2017sphericalcnn, su2017sphericalcnn, coors2018sphericalcnn}.
+While simple and efficient, those convolutions are not equivariant to rotations.
+On the other side of this tradeoff, \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn} proposed to perform proper spherical convolutions through the spherical harmonic transform.
+While equivariant to rotations, those convolutions are expensive.
+
+% On the one side, we have Cohen which is computationally very expensive but perfectly equivariant most general, on the other we have cube sphere which computationl very good but not equivariant at all.
 Other methods are tradedoff between these two.
 What is a good tradeoff?
-We think that DeepSphere is
-
-Present the different spherical CNNs with pro and cons $\Rightarrow$ mostly scale vs generality\\
-* 2D CNN $\Rightarrow$ doesn't respect geometry and equivariance\\
-* Cohen spherical CNN $\Rightarrow$ most general, but doesn't scale\\
-* Cohen gauge $\Rightarrow$ fixes scale, at the price of deformation (sphere $\Rightarrow$ icosahedron)\\
-* Esteves $\Rightarrow$ ? \\
-* Jiang $\Rightarrow$ need a global coordinate system (ok for planets, not projections like cosmo)\\
-
-\begin{table}[b]
-    \centering
-    \begin{tabular}{l|c|c|c|c}
-         method & equivariance & generality & scalability & flexibility \\
-         \hline
-        Cohen & & & &  \\
-         \hline
-        Gauge & & & &  \\
-         \hline
-        Esteves & & & &  \\
-         \hline
-        Jiang & & & &  \\
-         \hline
-        2D CNN (cubed sphere) & & & &  \\
-         \hline
-        Ours & & & &  \\
-    \end{tabular}
-    \caption{Caption}
-    \label{tab:my_label}
-\end{table}
-
-This paper focuses on improving the equivariance of \cite{perraudin2019deepspherecosmo}, a scalable graph-based method designed for cosmological applications.
-\todo{cite RLGM paper}
-Experiments on multiple problems of practical interest shows the competitiveness and flexibility of our method.
-Furthermore, those experiments show, contrarily to previously published results \cite{cohen2019gauge}, that anisotropic filters may be an unnecessary price to pay.
+We think that DeepSphere is.
+
+As the lack of equivariance penalizes performance (\secref{exp:cosmo}) and expensive convolutions prohibit their application to some real-world problems, methods standing between those two extremes are desired.
+\citet{cohen2019gauge} proposed to reduce costs by limiting the size of the representation of the symmetry group.
+% (from the continuous rotation group SO(3) to a discrete rotation group)
+% the dimensionality of feature maps is equal to the size of the irreducible representation of the symmetry group
+%As a platonic solid, it \todo{exhibits discrete rotations}.
+% the representation of its symmetry group is much smaller than SO(3)
+\todo{not all rotations, subset of SO(3)?}
+The projection of the data from the sphere to the icosahedron however introduces distortions that might hinder performance (see the experiments in \secref{exp:climate}).
+\todo{Where does Jiang fit? Need a global coordinate system (ok for planets, not projections like cosmo)}
+
+Another approach represents the discretized sphere as a graph connecting pixels according to the distance between them \citep{khasanova2017sphericalcnn, perraudin2019deepspherecosmo}.
+While Laplacian-based graph convolutions are more efficient than spherical convolutions, they are not exactly equivariant \citep{defferrard2019deepsphereequiv}.
+In this work, we argue that graph-based spherical CNNs strike an interesting balance, with a controllable tradeoff between cost and equivariance.
+Experiments on multiple problems of practical interest show the competitiveness and flexibility of this approach.
+% Furthermore, experiments show that, perhaps surprisingly and contrarily to previously published results \citep{cohen2019gauge} \todo{[Bronstein?]}, anisotropic filters might be an unnecessary price to pay.
+% This paper focuses on improving the rotation equivariance of \citet{perraudin2019deepspherecosmo}, a scalable graph-based method designed for cosmological applications.
 
 \section{Method [1 pages]}
+
+The gist of the method is to define the spherical convolution using a graph, and the down-sampling operation using a hierarchical pixelisation of the sphere.
 
@@
 
-\section{Is graph convolution equivariant to rotation? [2 pages]}
+\section{Is graph convolution equivariant to rotation? [2 pages]} \label{sec:equivariance}
 
@@
 
-\subsection{3D objects recognition}
+\subsection{3D objects recognition} \label{sec:exp:objects}
 
@@
 
-\subsection{Cosmological model discrimination}
+\subsection{Cosmological model discrimination} \label{sec:exp:cosmo}
 
@@
 * redo the experiment with the optimal graph \\
+* DSv2 better than v1 -> equivariance has practical implications \\
+* clear cost-accuracy tradeoff with n_neighbors \\
+* show the baselines? (at least the 2D CNN?) \\
 }
@@
 
-\subsection{Climate event detection}
+\subsection{Climate event detection} \label{sec:exp:climate}
 
@@
 
-\subsection{GHCN}
+\subsection{GHCN} \label{sec:exp:ghcn}
 
@@
 * structure (looking around) help for prediction\\
+* equivariance to be verified in this case (next paper)\\
 
@@
 
-* DeepSphere seems to be in the sweet spot of tradeoffs. Recall the desiderata.\\
-  * respect geometry: No need for a very precise equivariance, i.e., a very good graph...\\
-  * Not the most general (restricted to isotropic filters), but didn't hurt perf in any experiment\\
-  * Similar as in GNN: most general might not be the best [Andreas paper?] \\
-  * scales linearly $\Rightarrow$ cannot do better ($n^{1.25}$ for best HEALPix, linear for not optimal)\\
-  * flexible $\Rightarrow$ independent of the sampling\\
-
-future work:\\
-* when anisotropy useful? (research question)\\
-* irregular sampling while respecting the geometry\\
-* beyond the sphere, any manifold\\
+This work showed that DeepSphere strikes an interesting balance between desiderata for a spherical CNN.
+A single parameter, the number of neighbors a pixel is connected to in the graph, controls the tradeoff between \todo{performance and efficiency}.
+% vague words
+As computational cost and memory consumption scales linearly with the number of pixels, DeepSphere easily deals with spherical maps made of millions of pixels.
+Such high resolutions are not necessary to represent thethe  depth maps of 3D objects, but are required to faithfully represent cosmological and climate data.
+% That has to do with the frequency content of the signals (see fig xx)
+% cannot do better
+Also relevant in scientific applications is the flexibility offered by a graph representation to deal with partial coverage and non-uniform samplings.
+% partial coverage / missing data
+Finally, the implementation of Laplacian-based graph convolutions is straightforward.
+The ubiquity of graph neural networks, pushing for a first-class support in Deep Learning frameworks, will make implementations even easier and more efficient.
+
+A potential drawback of graph Laplacian-based approaches is that graph filters are isotropic, reducing the expressive power of the NN.
+% in principle -> may in fact not
+% Our experiments showed that DeepSphere nonetheless achieved state-of-the-art performance, on par with methods featuring anisotropic filters.
+% didn't hurt perf in any experiment
+% expressive power / generality / powerful / function approximator
+%Why anisotropic filters?
+Experiments from \citet{cohen2019gauge} suggest that more general convolutions achieve better performance.
+Our climate experiments (\secref{exp:climate}) however show that DeepSphere achieves similar performance than their most general convolution.
+Works on shape alignment indicates that anisotropic filters achieve better performance \todo{[Bronstein]}.
+Possible explanations for this discrepancy are that NNs somehow compensate for the lack of anisotropic filters, or that some tasks can be solved with isotropic filters.
+The distortions induced by the icosahedral projection in \citep{cohen2019gauge} or the leakage of curvature information in \todo{[Bronstein]} might also be explanations.
+Further research is needed to determine if anisotropic filters are an unnecessary price to pay or if they are needed for some applications.
+% As was recently shown for graph NNs used for graph classification, most general might not be the best, when the ultimate goal is generalization [Andreas paper? + previous by xx]
+
+Developing graph convolutions on irregular samplings that still respect the geometry of the sphere is another research direction of importance.
+% known underlying manifold
+Practitioners currently interpolate their measurements (coming from arbitrarily positioned weather stations, satellites or telescopes) to regular samplings.
+This practice either results in a waste of precision or computational and storage resources.
+Our ultimate goal is for practitioners to be able to work directly on their measurement, however distributed.
+
+% beyond the sphere => any manifold
+% what are other manifolds of interest?
+% done by monet & co on shapes
+
+% beyond scalar fields => simplicial complexes
 

### 2019-09-20 main.tex
Updates from Overleaf

--- 2019-09-19 main.tex
@@
 \newcommand{\nati}[1]{{\color[rgb]{.3,.5,.9}{#1}}}
+\newcommand{\mart}[1]{{\color[rgb]{.9,.5,.3}{#1}}}
 
@@
 \paragraph{Theoretical convergence.}
-We extend the work Belkin and Nyiogi to a fixed sampling. 
+We extend the work of Belkin and Nyiogi to a fixed sampling. 
 Given a sampling $V = \{x_0, \dots, x_{n-1}\}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$.
 Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
+
 \begin{theorem}
-	For a sampling $\mathcal P = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian operator $\frac{|\mathbb S^2|}{4\pi t_n}L^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\triangle_{\mathbb S^2}$  for $n\to\infty$:
-	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n} \b{L}_n^{t_n} T_{V_n} f(y) =  \Delta_{\mathbb{S}^2}f(y).$$
+	For a sampling $V = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian $\frac{|\mathbb S^2|}{4\pi t_n}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\mathbb S^2}$  for $n\to\infty$:
+	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n} \b{L}_n^{t_n} T_V f(x_i) =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.$$
 	\label{theo:pointwise convergence for a regular sampling}
 \end{theorem}
-This theorem show that the $\b{L}$ converges pointwisely toward an operator ($\Delta_{\mathbb S^2}$) commuting with rotation and hence is a strong hints for equivariance.
+This theorem implies immediately that $\b{L}$ converges pointwisely toward an operator ($\Delta_{\mathbb S^2}$) commuting with rotation and hence is a strong hints for equivariance.
 Importantly, the proof of Theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix \ref{...} inspires us in the construction of our graph Laplacian.
@@
 Unfortunately, the graph laplacian does \emph{not} converges uniformly in general \cite{belkin2007convergence}.
-This can probably be overcomed by considering a specific class of functions, such as bandlimited function.
+This can probably be overcome by considering a specific class of functions, such as bandlimited function.
 Second, while do not have a proof for it, we strongly believe that the HEALpix sampling do satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}.
@@
 \paragraph{Empirical convergence.}
-From 20\% error on V1, we got to less than 2\% error on v2.
-More neighbors, more precision, plus a better kernel width obtained "minimizing" the equivariance error.
-How to explain how we found the kernel width?
-Because minimizing the kernel width would lead to a completely disconnected graph.
-What we did was finding a heuristic law (fix neighbors, set the kernel width by imposing the minimum weight to be equal to $0.1$) and then optimizing
+
+% 3.0) explain how we obtained the figures
+We calculated numerically the equivariance error (\ref{eq:mean equivariance error}) by generating $N$ monochromatic signals and $M$ random rotations for each signal.
+The colors that were used were chosen in the range $(0,\  3N_{side}-1)$ to allow for an almost perfect synthesis of the rotated signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_V$ (\cite{healpix_primer})
+
+% 3.1) explain what the figures tell us
+From 20\% error on V1, we got to less than 2\% error on V2.
+The number of neighbors used for V2 is $50$.
+More neighbors implies naturally more precision, plus a better kernel width obtained by "minimizing" the equivariance error.
+\mart{How to explain how we found the kernel width?
+Micha\"el I need your help here!!} Literally, minimizing the kernel width would lead to a completely disconnected graph.
+What we did was finding a heuristic law (fix neighbors, set the kernel width $\hat t$ by imposing the minimum weight to be equal to $0.1$) and then minimizing the equivariance error in the range $(\hat t / 10, \hat t\cdot 10) $.
+We got better that Khasanova-Frossard \mart{(check the code)} that however uses only 4 neighbors.
+However, it is built to explicitely minimize the equivariance error, so we expect it to be a good benchmark against which to test our construction.
 \begin{figure}
@@
 \end{figure}
-Explain the difference of errors... Uniform sampling is better
 
@@
 \section{Proof of theorem}
-
+Since it is known that to prove the pointwise convergence of $\b{L}_n^t$ it is sufficient to prove the convergence of its continuous counterpart $L_n^t$ to $\Delta_{\mathbb S^2}$ (\cite{belkin2005towards}), we will prove here that
+\begin{equation}\label{eq:continuous convergence}
+ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n} {L}_n^{t_n} f(y) =  \Delta_{\mathbb{S}^2}f(y)
+\end{equation}
+where $L_n^t$ is defined as follows:
 \begin{definition}{}(Heat Kernel Graph Laplacian operator)\\
@@
 \end{definition}
+For the sake of the proof we will need also the following facts:
 \begin{definition}{} \cite{belkin2005towards}\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, and let $\text{vol}(\mathcal M)$ be the volume of $\mathcal M$.
@@
 \end{definition}
-
-The core of the work of Belkin et al. is the proof, that we will not discuss, of the following proposition.
 
@@
 
-Our first goal is to prove the following Proposition:
+% brief introduction:
+This proof consists in two steps: first, we prove that $\b L_n^t \rightarrow L^t$, and second we use proposition \ref{prop:3} from Belkin et al.
+to prove equation \ref{eq:continuous convergence}.
+This equation, as already explained in \cite{belkin2007convergence}, directly implies theorem \ref{theo:pointwise convergence for a regular sampling}.
+
+Our first goal is thus to prove the following Proposition:
 \vspace{0.5cm}
@@
 \vspace{0.5cm}
-
-The main result of this section, theorem  \ref{theo:pointwise convergence in the healpix case}, is then an immediate consequence of Proposition \ref{prop:2} and Proposition \ref{prop:3}.
 
@@
 
-The proof of theorem \ref{theo:pointwise convergence in the healpix case} is now trivial:
-\begin{proof}[Proof of Theorem \ref{theo:pointwise convergence in the healpix case}]
+Theorem  \ref{theo:pointwise convergence for a regular sampling}, is then an immediate consequence of Proposition \ref{prop:2} and Proposition \ref{prop:3}.
+\begin{proof}[Proof of Theorem \ref{theo:pointwise convergence for a regular sampling}]
 	Thanks to Proposition \ref{prop:2} and Proposition \ref{prop:3}	we conclude that $\forall y\in\mathbb S^2 $
@@
 
-\subsection{MATERIAL FROM MARTINO'S MASTER PROJECT}
-
-% \subsection{Equiangular}
-
-\cite{khasanova2017sphericalcnn} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling.
-They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes.
-In other words, they solve the minimization problem
-\begin{equation} \label{eq:minimization frossard}
-	\min_{W\in\mathcal G} \left|\mathcal{F}\left(\mathbf{y}\left(v_{ e}\right)\right)-\mathcal{F}\left(\mathbf{y}\left(v_{ i}\right)\right)\right|
-\end{equation}
-for the adjacency matrix $W$, where $\mathbf y(v_i)$ is the image of the object on the sphere centered on the vertex $v_i$, and $\mathcal F (\mathbf y(v_e))$ is the response of the filter at the vertex $v_e$ that lies at the same longitude of the vertex $v_i$ but on the equator.
-In their work they prove that the optimal weights solving the minimization problem (\ref{eq:minimization frossard}) are given by weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
-\begin{equation} \label{eq:frossard weights}
-	w_{ij} = \frac{1}{\norm{x_i-x_j}}
-\end{equation}
-This construction is interesting since it is adapted to the equiangular sampling, and leads to a very sparse graph with only 4 neighbors per vertex.
-Furthermore, to obtain the weights (\ref{eq:frossard weights}) every calculation was done in the \textit{spatial domain}, without any consideration about the spectral interpretation of the filter.
-In order to compare it to the HKGL we show the equivariance error by spherical harmonic degree in figure \ref{fig:Equivariance error of the Frossard-Khasanove graph}.
-It can be appreciated how this construction performs a little worse that the full HKGL for low bandwidth samplings, but converges faster than the \textit{full} HKGL, and its spectrum looks much more similar to the one of $\Delta_{\mathbb S^2}$.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{KhasanovaFrossardgraphonequiangularsampling.png}
-	\caption{Equivariance error of the Khasanova-Frossard graph on the equiangular sampling with bandwidth $b=8$ by spherical harmonic degree $\ell$.}
-	\label{fig:Equivariance error of the Frossard-Khasanove graph}
-\end{figure}
-
-\paragraph{Link with the Laplace-Beltrami Operator}
-
-Given a sampling $x_0, \dots, x_{n-1}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to the $i$th point of the sampling, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing the $i$-th patch.
-Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
-
-\begin{theorem}
-	For a sampling $\mathcal P = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian operator $\frac{|\mathbb S^2|}{4\pi t_n}L^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\triangle_{\mathbb S^2}$  for $n\to\infty$:
-	$$ \lim_{n\to\infty}\frac{|\mathbb S^2|}{4\pi t_n} L_n^{t_n}f(y) =  \triangle_{\mathbb S^2}f(y).$$
-	\label{theo:pointwise convergence in the healpix case}
-\end{theorem}
-
-\subsection{MATERIAL FROM MARTINO'S MASTER PROJECT}
-
-\todo{
-* define a measure of equiv error \\
-* show convergence empirically (for Nside up to 1024) \\
-* improved upon V1 \\
-* no difference in practice (see experiment xx) $\Rightarrow$ NNs are resilient to equiv error \\
-}
-
-Take a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere, a weighted undirected graph $G(V, E, \mathbf W)$, a signal $f: \mathbb S^2\to\mathbb R$ and its sampled representation $\mathbf f:\ f_i=f(v_i)$.
-Suppose that there exists a sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \mathbf f$ defined on a suitable subspace $F$ of $L^2(\mathbb S^2)$ such that it is invertible, i.e., we can unambiguously reconstruct the function $f\in F$ from its sampled values $\mathbf f$.
-The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing \cite{driscoll1994Fouriersphere}.
-Define the rotation operator $\Lambda(g), g\in SO(3)$: $\Lambda(g) f(\omega) = f\left(g^{-1} \omega\right)$.
-
-We now want to understand how to set the edges and the weights of $G$ such that
-\begin{equation} \label{eq:equivariance}
-	T \Lambda(g) T^{-1} \Omega_k T f = \Omega_k T \Lambda(g) f,
-\end{equation}
-i.e., the graph convolution $\Omega_k$ and any rotation $\Lambda(g)$ commute.
-
-Verifying equation (\ref{eq:equivariance}) is really hard in practice, due to the fact that for almost all sampling schemes $V$ it is not known if there exists a space $F$ in which $T$ is invertible.
-A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds \cite{driscoll1994Fouriersphere}, and thus we have a closed form of $T^{-1}$.
-For sampling schemes where no such sampling theorem is available, there are implementations of discrete SHT to reconstruct a sampled signal $\mathbf f$, thus providing a way to approximate $T^{-1}$.
-Thanks to this we are able, for a given sampling, a given function $f$, a given rotation $g$, and a given kernel $k$, to compute the \textit{normalized equivariance error}
-\begin{equation} \label{eq:equivariance error}
-	E_{G}(f, g) = \left(\frac{ \norm {T \Lambda(g) T^{-1} \Omega_k Tf - \Omega_k T \Lambda(g) f}_{L^2(\mathbb R^2)}}{\norm {Tf}_{L^2(\mathbb R^2)}}\right)^2,
-\end{equation}
-where $T^{-1}$ is substituted with a discrete SHT in case $T$ is not invertible.
-A measure of how equivariant a graph is with respect to rotations will then be given by the \textit{mean equivariance error}
-\begin{equation} \label{eq:mean equivariance error}
-	\overline E_G = \mathbb E_{f, g} \ E_G(f, g).
-\end{equation}
-In practice the expected value is obtained by averaging over a finite number of random functions and random rotations.
-The mean equivariance error $\overline E_G$ gives us an indication of how close the graph $G$ is from being equivariant to rotations.
-Now we state an intuitive concept that explains how to construct rotation invariant graphs, i.e., graphs such that $\overline{E_G}$ is small.
-The mean equivariance error $\overline{E_G}$ will be small if the scalar product $\mathbf f^T \mathbf v_{i(\ell, m)}$ well approximates $\hat {f}(\ell,m)$, i.e., the $L^2$ scalar product of the continuous signal $\hat {f}(\ell,m)= \int_{\eta \in \mathbb S^2}f(\eta)Y_\ell^m(\eta)d\mu(\eta)$.
-
-\textit{If $V$ is an equal area sampling scheme}, i.e., the area around each pixel $v_i$ is the same, $\overline{E_G}$ will be small if the graph Laplacian $\mathbf L$ is such that its eigenvectors $\mathbf v_i$ well approximate the eigenfunctions of the Laplace-Beltrami operator $\Delta_{\mathbb S^2}$ evaluated in the points of the sampling scheme, i.e., $\mathbf v_{i(\ell, m)} \approx Y_\ell^m(x_i)$.
-
-In this way we framed the problem of constructing a rotation invariant graph with the more general problem of coming up with a matrix $\mathbf L$ with some specific spectral properties.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{DeepSphereonHEALPix.png}
-	\includegraphics[width=\textwidth]{OptimalHKGLonHEALPix.png}
-	\caption{\label{fig:DeepSphere equivariance error}Mean equivariance error of the diffusion filter $\exp(-\Lambda)$ for $G$, $G'$ and the full HKGL, by spherical harmonic degree.
-Notice the difference in the scale of the y axis for DeepSphere, that reaches errors up to 30\%.}
-\end{figure}
-
 \end{document}

### 2019-09-20 main.tex

@@
 % 0.1 Explain the sampling problem
-As the graph convolution acts on a sampled version of the signal $\b{f}$ and the rotation on its continuous counterpart $f$, we first need to define a sampling operator.
+As the graph convolution acts on a sampled version of the function $\b{f}$ and the rotation on its continuous counterpart $f$, a sampling operator is needed.
 Given a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere and a function $f : \mathbb S^2 \supset F_V \to \mathbb R$, the sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \b{f}$ is defined as $\b{f}:\ f_i=f(v_i)$, where $F_V$ suitable subspace of $L^2(\mathbb S^2)$ such that $T_V$ is invertible, i.e., we can unambiguously reconstruct the function $f\in F_V$ from its sampled values $\b{f}$.
@@
 \end{equation}
-where $\b{R}_V(g) = T_V R(g) T_V^{-1}$. For practical application, we define the \textit{normalized equivariance error} for a signal $\b{f}$, and a  rotation $g$ as:
+where $\b{R}_V(g) = T_V R(g) T_V^{-1}$. For practical a evaluation of the equivariance, we define the \textit{normalized equivariance error} for a signal $\b{f}$, and a  rotation $g$ as:
 \begin{equation} \label{eq:equivariance error}
@@
 \end{equation}
-In practice, to anlyse the equivariance error frequency,  the set $C$ we used is composed of functions $f$ with made of spherical harmonic of a single degree $\ell$.
+In practice, to analyze the equivariance error frequency,  the set $C$ we used is composed of functions $f$ made of spherical harmonic of a single degree $\ell$.
 The expected value is obtained by averaging over a finite number of random functions and random rotations.
 
-\subsection{Finding a the optimal set of weights}
+\subsection{Finding the optimal set of weights}
 % !) summary the work of Khasanova -> No! to be put in section 2) Method
@@
 % 2) explain our approach
-We chose a different approach and take inspiration from \cite{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling point goes to infinity.
+We chose a different approach and take inspiration from \cite{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling points goes to infinity.
 This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics. 
-In this case the weighting scheme is full (every node is connected to every node) and is based the exponential kernel: 
+In this case the weighting scheme is full (every node is connected to every node) and is based on the exponential kernel: 
 \nati{@martino, please check this equation... Do you use 4t?}
@@
 We extend the work of Belkin and Nyiogi to a fixed sampling. 
-Given a sampling $V = \{x_0, \dots, x_{n-1}\}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$.
+Given a sampling $V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$.
 Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
@@
 \begin{theorem}
-	For a sampling $V = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian $\frac{|\mathbb S^2|}{4\pi t_n}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\mathbb S^2}$  for $n\to\infty$:
+	For a sampling $V = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian $\frac{|\mathbb S^2|}{4\pi t_n}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\mathbb S^2}$  for $n\to\infty$:
 	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n} \b{L}_n^{t_n} T_V f(x_i) =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.$$
@@
 \end{theorem}
-This theorem implies immediately that $\b{L}$ converges pointwisely toward an operator ($\Delta_{\mathbb S^2}$) commuting with rotation and hence is a strong hints for equivariance.
+This theorem implies immediately that $\b{L}$ converges pointwisely toward an operator ($\Delta_{\mathbb S^2}$) commuting with rotation and hence is a strong hint for equivariance.
 Importantly, the proof of Theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix \ref{...} inspires us in the construction of our graph Laplacian.
-It gives us a strong hint how the parameter $t$ needs to adjusted with respect of the number of point $n$.
+It gives us a strong hint how the parameter $t$ needs to be adjusted with respect to the number of points $n$.
 
@@
 This can probably be overcome by considering a specific class of functions, such as bandlimited function.
-Second, while do not have a proof for it, we strongly believe that the HEALpix sampling do satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}.
+Second, while do not have a proof for it, we strongly believe that the HEALpix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}.
 This is discussed in Appendix~\ref{...}
@@
 \begin{prop} \cite{belkin2005towards} \\
-Let $\mathcal M$ be a $k$-dimensional compact smooth manifold embedded in some euclidean space $\mathbb R^N$, and fix $p\in\mathcal M$.
+Let $\mathcal M$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb R^N$, and fix $p\in\mathcal M$.
 Let the data points $x_1, \dots, x_n$ be sampled form a uniform distribution on the manifold $\mathcal M$.
@@
 \begin{prop}\label{prop:1}
-	For an equal area sampling $\{x_i\in\mathbb S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the euclidean distance $||\cdot||$ with Lipschitz constant $\mathcal L_f$
+	For an equal area sampling $\{x_i\in\mathbb S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance $||\cdot||$ with Lipschitz constant $\mathcal L_f$
 	$$

### 2019-09-23 figures/example_climate_TMQ.py
Updates from Overleaf

@@ -1,0 +1,84 @@
+#!/usr/bin/env python3
+# coding: utf-8
+
+# # Climate event detection
+#
+# https://portal.nersc.gov/project/dasrepo/deepcam/segm_h5_v3_reformat/gb_data_readme
+#
+# The 16 features are:
+#
+# * TMQ: Total (vertically integrated) precipitatable water
+# * U850: Zonal wind at 850 mbar pressure surface
+# * V850: Meridional wind at 850 mbar pressure surface
+# * UBOT: Lowest model level zonal wind
+# * VBOT: Lowest model level meridional wind
+# * QREFHT: Reference height humidity
+# * PS: Surface pressure
+# * PSL: sea level pressure
+# * T200: temp at 200 mbar pressure surface
+# * T500: temp at 500 mbar pressure surface
+# * PRECT: Total (convective and large-scale) precipitation rate (liq + ice)
+# * TS: Surface temperature (radiative)
+# * Z100: Geopotential Z at 100 mbar pressure surface
+# * Z200: Geopotential Z at 200 mbar pressure surface
+# * ZBOT: Lowest model level height
+#
+# resolution of 768 x 1152 equirectangular grid (25-km at equator)
+
+# The labels are 0 for background class, 1 for tropical cyclone (TC), and 2 for atmoshperic river (AR)
+
+
+import os
+
+import numpy as np
+import pandas as pd
+from matplotlib import pyplot as plt
+plt.switch_backend('agg')
+import cartopy.crs as ccrs
+
+import h5py
+
+
+# plt.rc('text', usetex=True)
+# plt.rc('text.latex', preamble=r'\usepackage{lmodern}')
+
+# Load simulation data
+
+year, month, day, hour, run = 2106, 1, 1, 0, 1
+datapath = '../../data/Climate/data-{}-{:0>2d}-{:0>2d}-{:0>2d}-{}.h5'.format(year, month, day, hour, run)
+
+h5f = h5py.File(datapath)
+data = h5f['climate']["data"] # (16,768,1152) numpy array
+labels = h5f['climate']["labels"] # (768,1152) numpy array
+
+lon_ = np.arange(1152)/1152*360
+lat_ = np.arange(768)/768*180-90
+lon, lat = np.meshgrid(lon_, lat_)
+
+# Figure
+
[…]

### 2019-09-23 main.tex

@@
 	\item anonymize DeepSphere citation
-	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
+% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
 	\item citet for inline, citep for parenthesis
@@
 	\includegraphics[height=0.25\linewidth]{example_brain_meg}
+% 	\hfill
+% 	\includegraphics[height=0.25\linewidth]{example_climate_TMQ}
 	\hfill
@@
 Given a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere and a function $f : \mathbb S^2 \supset F_V \to \mathbb R$, the sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \b{f}$ is defined as $\b{f}:\ f_i=f(v_i)$, where $F_V$ suitable subspace of $L^2(\mathbb S^2)$ such that $T_V$ is invertible, i.e., we can unambiguously reconstruct the function $f\in F_V$ from its sampled values $\b{f}$.
-The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing \cite{driscoll1994Fouriersphere}.
-For most samplings, it is not known if $F_V$ exist and hence if $T_V$ is invertible.
+The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing (\cite{driscoll1994Fouriersphere}).
+For most sampling schemes, it is not known if $F_V$ exist and hence if $T_V$ is invertible.
 A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds, and thus we have a closed form of $T_V^{-1}$ is known.
@@
 \end{equation}
+\mart{Talk about the probability measure used on C, SO(3)?}
 In practice, to analyze the equivariance error frequency,  the set $C$ we used is composed of functions $f$ made of spherical harmonic of a single degree $\ell$.
@@
 In this case the weighting scheme is full (every node is connected to every node) and is based on the exponential kernel: 
-\nati{@martino, please check this equation... Do you use 4t?}
 \begin{equation} \label{eq:belkin_weights}
-w_{ij} = e^{-\frac{1}{t} \norm{x_i-x_j}^2}
+w_{ij} = e^{-\frac{1}{4t} \norm{x_i-x_j}^2}
 \end{equation}
@@
 
+\begin{dmath}
+    [GC_{16}\, +\, BN\, +\, ReLU]_{nside1024}\, +\, \textrm{Pool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{nside512}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{nside256}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{nside128}\, +\,\textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{nside64}\, +\, \textrm{Pool}\, +\, [GC_{2}]_{nside32}\, +\, GAP\, +\, \textrm{softmax}
+\end{dmath}
+
+The order of the Chebyshev polynomial is 5 for each layer, the number of feature maps are [16, 32, 64, 64, 64, 3] respectively and down-sampling to the immediate smaller resolution for each layer.
+
+batch size = 8, 80 epochs, adam optimizer, cross-entropy loss, learning rate $2\cdot10^{-4}\cdot0.999^{\textrm{step}}$
+
 \subsection{climate event detection}
@@
 \end{dmath}
-number of parameters: 2,2M
+% number of parameters: 2,2M
 
@@
 \end{dmath}
-number of parameters: 590'976  % more feat is 16 times more
+% number of parameters: 590'976  % more feat is 16 times more
 

### 2019-09-23 main.tex
SHREC17 experiment

@@
 \usepackage{graphicx} \graphicspath{{figures/}}
+%\usepackage{wrapfig}
+\usepackage{floatflt}
 \usepackage{amsthm}
@@
 	\item align the spheres in figure 1
+	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
+	\item check footnotes
 \end{itemize}
@@
 
+\todo{
+	* discuss discretizations (equiangular, HEALPix) -> more uniform is better \\
+	* no uniform sampling: tradeoffs have to be made \\
+	* CNN vs FCN discussion (GAP for invariance) \\
+}
+
 * HEALPix: improvement from DeepSphere v1 \cite{perraudin2019deepspherecosmo} \\
@@
 This can probably be overcome by considering a specific class of functions, such as bandlimited function.
-Second, while do not have a proof for it, we strongly believe that the HEALpix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}.
+Second, while do not have a proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}.
 This is discussed in Appendix~\ref{...}
@@
 
-\todo{
-* same perf as other spherical CNNs, but 40 times faster \\
-* compare samplings (equi, HEALPix) $\Rightarrow$ not much difference \\
-* compare with improved graph (Nside=32) $\Rightarrow$ no improvement as information in the low frequencies (PSD, and works down to nside=8) \\
-* ModelNet 40: same conclusions $\Rightarrow$ appendix \\
+\begin{floatingfigure}[r]{0.5\linewidth}
+%\begin{wrapfigure}{r}{0.5\linewidth}
+	\centering
+	\includegraphics[height=6em]{lamp_000018}
+	\includegraphics[height=6em]{lamp_000018_sphere_nobar}
+	\caption{Example of a 3D object represented as a spherical depth map. T}
+	\label{fig:depthmap}
+%\end{wrapfigure}
+\end{floatingfigure}
+
+The recognition of 3D shapes is a rotation invariant task: rotating an object doesn't change its nature.
+While 3D shapes are usually represented as meshes or point clouds, representing them as spherical maps (\figref{depthmap}) naturally allows a rotation invariant treatment.
+LIDAR actually acquires depth maps, which are a posteriori represented as point clouds.
+
+The SHREC'17 shape retrieval contest \citep{shrec17} contains 51,300 randomly oriented 3D models from ShapeNet \citep{shapenet}, to be classified in 55 categories (tables, lamps, airplanes, etc.).
+As in \citet{cohen2018sphericalcnn}, objects are represented by 6 spherical maps.
+At each pixel, a ray is traced towards the center of the sphere.
+The distance from the sphere to the object forms a depth map.
+The $\cos$ / $\sin$ of the surface angle forms two normal maps.
+The same is done for the object's convex hull.
+The maps are discretized using either an equiangular grid \citep{driscoll1994Fouriersphere} with bandwidth $b = 64$ ($N_{pix} = 4 b^2 = 16,384$), or an HEALPix \citep{healpix} grid with $N_{side} = 32$ ($N_{pix} = 12 N_{side}^2 = 12,288$).
+
+\todo{Graph, network architecture (info in the appendix, set the notation in the method section) and hyper-parameters. Or leave in appendix.}
+
+\begin{table}%[ht]
+    \centering
+	\begin{tabular}{l cc r rS[table-format=2.0]}
+		\toprule
+		& \multicolumn{2}{c}{performance} & \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed} \\
+		\cmidrule(lr){2-3} \cmidrule(lr){4-4} \cmidrule(lr){5-6}
+		& F1 & mAP & params & \multicolumn{1}{c}{inference} & \multicolumn{1}{c}{training} \\
+		\midrule
+		% $SO(3)$ vs $S^2$ vs graph
+		\citet{cohen2018sphericalcnn} ($b=128$) & 78.9 & 67.6 & 1400\,k & 38.0\,ms & 50\,h \\
+		\citet{cohen2018sphericalcnn} (simplified,\protect\footnotemark $b=64$) & 78.6 & 66.5 & 400\,k & 12.0\,ms & 32\,h \\
+		\citet{esteves2018sphericalcnn} ($b=64$) & 79.4 & 68.5 & 500\,k & 9.8\,ms & 3\,h \\
+		DeepSphere (equiangular $b=64$) & 79.4 & 66.5 & 190\,k & 0.9\,ms & 50\,m \\
+		DeepSphere (HEALPix $N_{side}=32$) & 80.7 & 68.6 & 190\,k & 0.9\,ms & 50\,m \\
+		\bottomrule
+	\end{tabular}
+    \caption{
+		Results on SHREC'17 (3D shapes): DeepSphere achieves similar performance at a much lower cost, suggesting that anisotropic filters are an unnecessary price to pay.
+		% F1-score computed with sklearn, mAP from the official script of the competition.
+		% inference speed = time for a single instance to do a single training pass
+		% training speed = time for the neural net to train to peak performance
 	}
+    \label{tab:shrec17}
+\end{table}
+\footnotetext[5]{As implemented in \url{https://github.com/jonas-koehler/s2cnn}.}
 
-\begin{table}
-    \centering
-    \begin{tabular}{l|c c c c c}
-        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed}\\
-        \cmidrule(lr){2-3} \cmidrule(lr){4-4} \cmidrule(lr){5-6}
-        \multicolumn{1}{l}{Method} & F1 & mAP & params & inference [ms] & training \\ \hline
-        \cite{cohen2018sphericalcnn} & 78.85 & 67.6 & 1.4M & 38 & 50h\\
-        % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
-        \cite{esteves2018sphericalcnn} & 79.36 & 68.5 & 500k & 10 & 2h52\\ \hline
-        DeepSphere \emph{Equiangular} & 79.36 & 66.5 & 190k & 1 & 50m \\
-        DeepSphere \emph{HEALPix} & 80.65 & 68.6 & 190k & 1 & 50m\\
-        DeepSphere \emph{Improved HEALPix} & ? & ? & 190k & ? & ?
-    \end{tabular}
-    \caption{Performance of different models for SHREC'17 task. F1-score computed with sklearn, mAP from the official script of the competition.}
-    \label{tab:SHREC17_class}
-\end{table}
+Results are shown in \tabref{shrec17}.
+DeepSphere achieves the same performance as \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn} while being much more efficient, suggesting that anisotropic filters are an unnecessary price to pay.
+% x times faster
+As the information in those spherical maps resides in the low frequencies (\todo{figure}), reducing the equivariance error didn't translate into improved performance.
+For the same reason, using the more uniform HEALPix discretization or lowering the resolution down to $N_{side} = 8$ didn't impact performance.
+\todo{The same conclusions are drawn from ModelNet 40 (see appendix ??).}
 
-* inference speed = time for a single instance to do a single training pass\\
-* training speed = time for the neural net to train to peak performance\\
-
-* diminish resolution $\Rightarrow$ no change in result until nside=8, no change for high resolution $\Rightarrow$ info in the low freq\\
-* same conclusion, anisotropy unnecessary cost to pay\\
-* Limited by representation of data? yep, treat them as point clouds \\
+% Limited by representation of data? yep, treat them as point clouds
 

### 2019-09-23 main.tex
spectrum (SHREC17 and cosmo)

@@
 %\usepackage{wrapfig}
-\usepackage{floatflt}
+%\usepackage{floatflt}
 \usepackage{amsthm}
@@
 
-\begin{floatingfigure}[r]{0.5\linewidth}
+\begin{figure}
+%\begin{floatingfigure}[r]{0.5\linewidth}
 %\begin{wrapfigure}{r}{0.5\linewidth}
-	\centering
-	\includegraphics[height=6em]{lamp_000018}
-	\includegraphics[height=6em]{lamp_000018_sphere_nobar}
-	\caption{Example of a 3D object represented as a spherical depth map. T}
+	\begin{minipage}[t]{0.57\linewidth}
+		\centering
+		\includegraphics[height=7em]{lamp_000018}
+		\hfill
+		\includegraphics[height=7em]{lamp_000018_sphere_nobar}
+		\caption{Example of a 3D object represented as a spherical depth map.}
 		\label{fig:depthmap}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.35\linewidth}
+		\centering
+		\includegraphics[height=7em]{spectrum}
+		\caption{Power spectral densities.}
+		\label{fig:spectrum}
+	\end{minipage}
 %\end{wrapfigure}
-\end{floatingfigure}
+%\end{floatingfigure}
+\end{figure}
 
@@
 % x times faster
-As the information in those spherical maps resides in the low frequencies (\todo{figure}), reducing the equivariance error didn't translate into improved performance.
+As the information in those spherical maps resides in the low frequencies (\figref{spectrum}), reducing the equivariance error didn't translate into improved performance.
 For the same reason, using the more uniform HEALPix discretization or lowering the resolution down to $N_{side} = 8$ didn't impact performance.

### 2019-09-23 figures/spectrum.py

@@ -1,0 +1,69 @@
+#!/usr/bin/env python3
+
+from os import path
+import pickle
+
+import numpy as np
+from matplotlib import pyplot as plt
+
+#plt.rc('font', family='Latin Modern Roman')
+#plt.rc('text', usetex=True)
+#plt.rc('text.latex', preamble=r'\usepackage{lmodern}')
+
+def plot_with_std(x, y, color=None, alpha=0.2, ax=None, **kwargs):
+    ystd = np.std(y, axis=0)
+    ymean = np.mean(y, axis=0)
+    if ax is None:
+        ax = plt.gca()
+    lines = ax.plot(x, ymean, color=color, **kwargs)
+    color = lines[0].get_color()
+    ax.fill_between(x, ymean - ystd, ymean + ystd, alpha=alpha, color=color)
+    return ax
+
+# 1000 objects out of 30k were randomly sampled to be analyzed.
+# The mean was subtracted from each signal in a preprocessing step.
+# The spectrum was computed by healpy.anafast up to lmax=nside (since there's nothing beyond).
+# cl is a dictionary with keys = {0, 1, 2}. cl[feature] is a matrix of shape [1000, 33] where each row is the spectrum of one signal.
+spectrum_shrec17 = pickle.load(open('../figures/spectrum_shrec17.pickle', 'rb'))
+spectrum_shrec17 = np.vstack([
+    spectrum_shrec17[0],
+    spectrum_shrec17[1],
+    spectrum_shrec17[2],
+])
+
+spectrum_cosmo = np.load('../figures/spectrum_cosmo.npz')
+spectrum_cosmo = np.vstack([
+    spectrum_cosmo['psd_class1'],
+    spectrum_cosmo['psd_class2'],
+])
+
+print("SHREC'17: {} maps with degree at most {}".format(*spectrum_shrec17.shape))
+print("cosmo: {} maps with degree at most {}".format(*spectrum_cosmo.shape))
+
+fig, ax = plt.subplots(figsize=(5, 2.5))
+
+l = np.arange(spectrum_shrec17.shape[1])
+y = np.mean(spectrum_shrec17, axis=0) # *l*(l+1)
+scale = np.mean(y[:33])  # or y[1]
+ax.plot(l, y / scale, label="SHREC'17 (depth and normal maps)")
[…]

### 2019-09-23 main.tex
Updates from Overleaf

--- 2019-09-23 main.tex
@@
 \section{Proof of theorem}
-Since it is known that to prove the pointwise convergence of $\b{L}_n^t$ it is sufficient to prove the convergence of its continuous counterpart $L_n^t$ to $\Delta_{\mathbb S^2}$ (\cite{belkin2005towards}), we will prove here that
+Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a close, compact and infinitely differentiable manifold $\mathcal M$, a smooth function $f:\mathcal M \rightarrow \mathbb R$, and defined the vector $\b f$ of samples of $f$ as follows: $\b f\in \mathbb R^n,\ \b f_i = f(x_i)$, it is known that  (\cite{belkin2005towards}) to prove the convergence of $\b{L}_n^t \b f _i$ to $\Delta_{\mathbb S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\mathbb S^2}f(x)$
+where $L_n^t$ is defined as follows:
+\begin{definition}{}\\
+	\label{def:Heat Kernel Graph Laplacian operator}
+	\text{Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of the manifold we define the \textbf{operator} }$L_n^t$ such that
+	$$L_n^tf(y) := \frac{1}{n}\left[ \sum_{i=0}^{n-1} \exp \left\{ {-\frac{||x_i-y||^2}{4t}}\right\}\left(f(y)-f(x_i)\right)\right]$$
+\end{definition}
+Thus, it will be sufficient to prove that 
 \begin{equation}\label{eq:continuous convergence}
@@
 \end{equation}
-where $L_n^t$ is defined as follows:
-\begin{definition}{}(Heat Kernel Graph Laplacian operator)\\
-	\label{def:Heat Kernel Graph Laplacian operator}
-	\text{Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of the manifold we define the \textbf{operator} }$L_n^t$ such that
-	$$L_n^tf(y) := \frac{1}{n}\left[ \sum_{i=0}^{n-1} \exp{-\frac{||x_i-y||^2}{4t}}\left(f(y)-f(x_i)\right)\right]$$
-\end{definition}
 For the sake of the proof we will need also the following facts:
-\begin{definition}{} \cite{belkin2005towards}\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, and let $\text{vol}(\mathcal M)$ be the volume of $\mathcal M$.
+\begin{definition}{} (\cite{belkin2005towards})\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, and let $\text{vol}(\mathcal M)$ be the volume of $\mathcal M$.
 We define the functional approximation to the Laplace-Beltrami operator to be the operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
 	\label{def:Functional approximation to the Laplace-Beltrami operator}
-	$$ L^tf(y) = \int_{\mathcal M}e^{-\frac{||y-x||^2}{4t}}\left(f(y)-f(x)\right)d\mu(x)$$
+	$$ L^tf(y) = \int_{\mathcal M}\exp\left\{-\frac{||y-x||^2}{4t}\right\}\left(f(y)-f(x)\right)d\mu(x)$$
 \end{definition}
 
-\begin{prop} \cite{belkin2005towards} \\
-Let $\mathcal M$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb R^N$, and fix $p\in\mathcal M$.
+\begin{prop} (\cite{belkin2005towards}) \\
+Let $\mathcal M$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb R^N$, and fix $y\in\mathcal M$.
 Let the data points $x_1, \dots, x_n$ be sampled form a uniform distribution on the manifold $\mathcal M$.
@@
 Then
-	$$\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(p) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\triangle_{\mathcal M}f(p).$$
+	$$\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(y) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\triangle_{\mathcal M}f(y).$$
 	\label{prop:3}
@@
 % brief introduction:
-This proof consists in two steps: first, we prove that $\b L_n^t \rightarrow L^t$, and second we use proposition \ref{prop:3} from Belkin et al.
-to prove equation \ref{eq:continuous convergence}.
+This proof consists in two steps: first, we prove that $\b L_n^t \rightarrow L^t$, and second, we use proposition \ref{prop:3} to prove equation \eqref{eq:continuous convergence}.
 This equation, as already explained in \cite{belkin2007convergence}, directly implies theorem \ref{theo:pointwise convergence for a regular sampling}.

### 2019-09-23 main.tex
climate result tables

@@
 \usepackage{booktabs}
+\usepackage{siunitx} % used in SHREC table
 \usepackage{bbm}        % for mathbbm
@@
 	\item check footnotes
+	\item climate data on spectrum plot
+	\item result tables: only what supports the main message in the text, everything we have in the appendix
 \end{itemize}
@@
 
-\todo{Graph, network architecture (info in the appendix, set the notation in the method section) and hyper-parameters. Or leave in appendix.}
+\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section) and hyper-parameters. Or leave in appendix.}
 
@@
     \centering
+	%\begin{tabular}{l cc r rr}
 	\begin{tabular}{l cc r rS[table-format=2.0]}
@@
 
-\subsection{Climate event detection} \label{sec:exp:climate}
+\subsection{Climate event segmentation} \label{sec:exp:climate}
 
@@
 \begin{table}
-	\begin{tabular}{l|c c c c}
-	\multicolumn{1}{l}{} & Accuracy & Average Precision & \multicolumn{2}{c}{Speed}\\
-	\cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-5}
-	\multicolumn{1}{l}{Method} & mean & mean & inference [ms] & training \\ \hline
-	%Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
-	\cite{jiang2019sphericalcnn} & 94.67 & - & - & -\\
-	\cite{jiang2019sphericalcnn} \emph{rerun} & 94.95 & 38.41 & 10 & 10h\\
-	% 328'339
-	\cite{cohen2019gauge} (S2R) & 97.5 & 68.6 & - & -\\
-	\cite{cohen2019gauge} (R2R) & 97.7 & 75.9 & - & -\\ \hline
-	% unknown
-	DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 33 & 13h \\
-	DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 33 & 13h\\
-	% 12'926'432
-	\end{tabular}
-	\caption{Climate pattern segmentation mean accuracy (\%), mean Average Precision (\%) and speed for different models run on the icosahedron dataset from \cite{jiang2019sphericalcnn}}
+	\centering
+	\begin{tabular}{l l l}
+	\toprule
+	& accuracy & mAP \\
+	\midrule
+	\cite{jiang2019sphericalcnn} (paper) & 94.67 & - \\
+	\cite{jiang2019sphericalcnn} (rerun) & 94.95 & 38.41 \\
+	\cite{cohen2019gauge} (S2R) & 97.5 & 68.6 \\
+	\cite{cohen2019gauge} (R2R) & 97.7 & 75.9 \\
+	DeepSphere (weighted loss) & $97.8\pm 0.3$ & $77.15\pm 1.94$ \\
+	DeepSphere (non-weighted loss) & $87.8\pm 0.5$ & $89.16\pm 1.37$ \\
+	\bottomrule
+	\end{tabular}
+	\caption{
+		Climate event segmentation results: mean accuracy and mean average precision (mAP).
+DeepSphere achieves state-of-the-art performance while using isotropic filters (S2S in \citet{cohen2019gauge}'s language), suggesting again that anisotropic filters are an unnecessary price to pay.
+		Note that \citet{jiang2019sphericalcnn} and \citet{cohen2019gauge} use a weighted cross-entropy loss, which is good for the accuracy metric (as it corrects for class imbalance) but bad for the mAP metric.
+	}
 \end{table}
 
+* icosahedron dataset from \cite{jiang2019sphericalcnn} \\
 * Jiang rerun with a batch size of 64 instead of 256 due to memory limit.\\
@@
 
+* DS-jiang is the similar architecture as \cite{jiang2019sphericalcnn}. \\
+* DS-optimal has 2 times the number of feature maps of DS. \\
+* \todo{What is DS and DS-Cohen?} \\
+* \todo{Is (equi non-weighted) the full resolution?} \\
+* \todo{check column order for DS} \\
+
 \begin{table}
-
-\begin{tabular}{l|c c c c c}
-        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy} & Size\\
-        \cmidrule(lr){2-5} \cmidrule(lr){6-6}
-        \multicolumn{1}{l}{Method} & TC & AR & BG & mean & params \\ \hline
+    \centering
+	\begin{tabular}{l l l l l}
+		\toprule
+        & TC & AR & BG & mean \\
+		\midrule
+		\cite{mudigonda2017climateevents} & 74 & 65 & 97 & 78.67 \\
+		\cite{jiang2019sphericalcnn} (paper) & 94 & 93 & 97 & 94.67 \\
+		\cite{jiang2019sphericalcnn} (rerun) & 93.9 & 95.7 & 95.2 & 94.95 \\
+        \cite{cohen2019gauge} (S2R) & 97.8 & 97.3 & 97.3 & 97.5 \\
+        \cite{cohen2019gauge} (R2R) & 97.9 & 97.8 & 97.4 & 97.7 \\
+		\midrule
+        DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ \\
+        DS-Jiang (weighted) & 97.1 & 97.6 & 96.5 & 97.1 \\
+        DS-optimal (weighted) & 91.5 & 93.4 & 99.0 & 94.6 \\
+		\midrule
+        DS (non-weighted) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ \\
+        DS-Jiang (non-weighted) & 33.6 & 93.6 & 99.3 & 75.5 \\
+        DS-optimal (non-weighted) & 73.4 & 92.7 & 99.8 & 88.7 \\
+		\midrule
+		\todo{DS-Cohen (weighted)} & 95.5 & 96.9 & 93.9 & 95.4 \\
+		\todo{DS-Cohen (non-weighted)} & 95.5 & 96.9 & 93.9 & 95.4 \\
+		\todo{DeepSphere (equi non-weighted)} & 31.3 & 75.2 & 99.9 & 68.80 \\
+		\bottomrule
+    \end{tabular}
+    \caption{
+		Results on climate event segmentation: accuracy.
+		Tropical cyclones (TC) and atmospheric rivers (AR) are the two positive classes, against the background (BG).
+		\todo{\citet{mudigonda2017climateevents} is not directly comparable as they don't use the same input feature maps.}
+		Note that a non-weighted cross-entropy loss is not optimal for the accuracy metric.
+	}
+\end{table}
+
+\begin{table}
+	\centering
+	\begin{tabular}{l l l l}
+		\toprule
+        & TC & AR & mean \\
+		\midrule
+		\cite{jiang2019sphericalcnn} (rerun) & 11.08 & 65.21 & 38.41 \\
+        \cite{cohen2019gauge} (S2R) & - & -& 68.6 \\
+        \cite{cohen2019gauge} (R2R) & - & -& 75.9 \\
+		\midrule
+        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ \\
+        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 \\
+        DS-optimal (non-weighted) & 84.71 & 98.05 & 91.38 \\
+		\midrule
+        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ \\
+        DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 \\
+        DS-optimal (weighted) & 52.80 & 94.78 & 73.79 \\
+		\midrule
+		\todo{DS-Cohen (weighted)} & 13.1 & 80.3 & 46.7 \\
+		\todo{DeepSphere (equi non-weighted)} & 55.53 & 94.85 & 75.19 \\
+		\bottomrule
+    \end{tabular}
+    \caption{
+		Results on climate event segmentation: average precision.
+		Tropical cyclones (TC) and atmospheric rivers (AR) are the two positive classes.
+		Note that a weighted cross-entropy loss is not optimal for the average precision metric.
+	}
+\end{table}
+
+\begin{table}
+	\centering
+	\begin{tabular}{l r r r}
+		\toprule
+		& \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed} \\
+        \cmidrule(lr){2-2} \cmidrule(lr){3-4}
+		& params & inference & training \\
+		\midrule
         %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
-        \cite{jiang2019sphericalcnn} & 94 & 93 & 97 & 94.67 & 330k\\
-        \cite{jiang2019sphericalcnn} \emph{rerun} & 93.9 & 95.7 & 95.2 & 94.95 & 330k\\
-        % 328'339
-        \cite{cohen2019gauge} (S2R) & 97.3 & 97.3 & 97.8 & 97.5 & -\\
-        \cite{cohen2019gauge} (R2R) & 97.8 & 97.4 & 97.9 & 97.7 & -\\ \hline
-        DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ & 13M\\
-        DS (non-weighted) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ & 13M\\ \hline
-        % 12'926'432
-        DS-Jiang (weighted) & 97.1 & 97.6 & 96.5 & 97.1 & 590k\\
-        DS-Jiang (non-weighted) & 33.6 & 93.6 & 99.3 & 75.5 & 590k\\ \hline
-        % 590k
-        DS-optimal (weighted) & 91.5 & 93.4 & 99.0 & 94.6 & 52M\\
-        DS-optimal (non-weighted) & 73.4 & 92.7 & 99.8 & 88.7 & 52M\\ \hline
-        %DS-Cohen (weighted) & 95.5 & 96.9 & 93.9 & 95.4 & 2M \\
-        %DS-Cohen (non-weighted) & 95.5 & 96.9 & 93.9 & 95.4 & 2M \\
-        % DeepSphere (equi non-weighted) & 31.3 & 75.2 & 99.9 & 68.80
-    \end{tabular}
-    \caption{Climate pattern segmentation accuracy (\%) for BG, TC
-and AR classes plus mean accuracy.}
-\end{table}
-
-* DS-jiang is the similar architecture as \cite{jiang2019sphericalcnn}.\\
-* DS-optimal has 2 times the number of feature maps of DS.\\
-
-\begin{table}
-\begin{tabular}{l|c c c c c}
-        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
-        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
-        \multicolumn{1}{l}{Method} & TC & AR & mean & inference [ms] & training \\ \hline
-        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
-        \cite{jiang2019sphericalcnn} \emph{rerun} & 11.08 & 65.21 & 38.41 & 10.2 & 10h14m\\
-        % 328'339
-        \cite{cohen2019gauge} (S2R) & - & -& 68.6 & - & - \\
-        \cite{cohen2019gauge} (R2R) & - & -& 75.9 & - & -\\ \hline
-        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 33 & 13h \\
-        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 33 & 13h \\ \hline
-        % 12'926'432
-        DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 & 5 & 3h06m\\
-        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 & 5 & 3h04m \\ \hline
-        % 590k
-        DS-optimal (weighted) & 52.80 & 94.78 & 73.79 & 50 & 20h \\
-        DS-optimal (non-weighted) & 84.71 & 98.05 & 91.38 & 50 & 20h \\ \hline
-        %DS-Cohen (weighted) & 13.1 & 80.3 & 46.7 & 11 & 4h \\
-        % DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
-    \end{tabular}
-    \caption{Climate pattern segmentation average precision for positive classes and mean as well, plus speed performance for inference (one training pass for one instance)  and training time.}
+		\cite{jiang2019sphericalcnn} & 330\,k & 10\,ms & 10\,h \\ % 328'339
+		% \cite{cohen2019gauge} (S2R) & - & - & - \\
+        % \cite{cohen2019gauge} (R2R) & - & - & - \\
+		DeepSphere (Jiang) & 590\,k & 5\,ms & 3\,h \\ % 590k
+        DeepSphere & 13\,M & 33\,ms & 13\,h \\ % 12'926'432
+		DeepSphere (optimal) & 52\,M & 50\,ms & 20\,h \\
+		\todo{DS-Cohen (weighted)} & 2\,M & 11\,ms & 4\,h \\
+		\todo{DeepSphere (equi non-weighted)} & - & 567\,ms & 48\,h \\
+		\bottomrule
+    \end{tabular}
+    \caption{
+		Results on climate event segmentation: size and speed.
+	}
 \end{table}

### 2019-09-23 main.tex
Updates from Overleaf

--- 2019-09-23 main.tex
@@
 As the graph convolution acts on a sampled version of the function $\b{f}$ and the rotation on its continuous counterpart $f$, a sampling operator is needed.
-Given a sampling scheme $V=\{v_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere and a function $f : \mathbb S^2 \supset F_V \to \mathbb R$, the sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \b{f}$ is defined as $\b{f}:\ f_i=f(v_i)$, where $F_V$ suitable subspace of $L^2(\mathbb S^2)$ such that $T_V$ is invertible, i.e., we can unambiguously reconstruct the function $f\in F_V$ from its sampled values $\b{f}$.
+Given a sampling scheme $V=\{x_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere and a function $f : \mathbb S^2 \supset F_V \to \mathbb R$, the sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \b{f}$ is defined as $\b{f}:\ f_i=f(x_i)$, where $F_V$ suitable subspace of $L^2(\mathbb S^2)$ such that $T_V$ is invertible, i.e., we can unambiguously reconstruct the function $f\in F_V$ from its sampled values $\b{f}$.
 The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing (\cite{driscoll1994Fouriersphere}).
@@
 % 0.3 Formulate the problem
+\mart{Correct formula for equivariance error and the corresponding plots as soon as you changed it!}
 \begin{equation} \label{eq:equivariance}
@@
 \paragraph{Theoretical convergence.}
-We extend the work of Belkin and Nyiogi to a fixed sampling. 
-Given a sampling $V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$.
+We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme. 
+Given a sampling scheme $V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$.
 Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
@@
 \begin{theorem}
-	For a sampling $V = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian $\frac{|\mathbb S^2|}{4\pi t_n}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\mathbb S^2}$  for $n\to\infty$:
-	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n} \b{L}_n^{t_n} T_V f(x_i) =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.$$
+	For a sampling $V = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian $\frac{|\mathbb S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\mathbb S^2}$  for $n\to\infty$:
+	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} f(x_i) =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.$$
 	\label{theo:pointwise convergence for a regular sampling}
@@
 This theorem implies immediately that $\b{L}$ converges pointwisely toward an operator ($\Delta_{\mathbb S^2}$) commuting with rotation and hence is a strong hint for equivariance.
-Importantly, the proof of Theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix \ref{...} inspires us in the construction of our graph Laplacian.
+Importantly, the proof of Theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix \ref{sec: appendix: proof of theorem} inspires us in the construction of our graph Laplacian.
 It gives us a strong hint how the parameter $t$ needs to be adjusted with respect to the number of points $n$.
@@
 Second, while do not have a proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}.
-This is discussed in Appendix~\ref{...}
+This is discussed in Appendix \ref{sec: appendix: proof of theorem}.
 
@@
 
-\section{Proof of theorem}
-Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a close, compact and infinitely differentiable manifold $\mathcal M$, a smooth function $f:\mathcal M \rightarrow \mathbb R$, and defined the vector $\b f$ of samples of $f$ as follows: $\b f\in \mathbb R^n,\ \b f_i = f(x_i)$, it is known that  (\cite{belkin2005towards}) to prove the convergence of $\b{L}_n^t \b f _i$ to $\Delta_{\mathbb S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\mathbb S^2}f(x)$
+\section{Proof of theorem}\label{sec: appendix: proof of theorem}
+Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal M$, a smooth function $f:\mathcal M \rightarrow \mathbb R$, and defined the vector $\b f$ of samples of $f$ as follows: $\b f\in \mathbb R^n,\ \b f_i = f(x_i)$, it is known that  (\cite{belkin2005towards}) to prove the convergence of $(\b {L}_n^t \b f) _i$ to $\Delta_{\mathbb S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\mathbb S^2}f(x)$
 where $L_n^t$ is defined as follows:
@@
 \end{definition}
-Thus, it will be sufficient to prove that 
+Thus, to prove theorem \ref{theo:pointwise convergence for a regular sampling} it will be sufficient to prove that 
 \begin{equation}\label{eq:continuous convergence}
- \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n} {L}_n^{t_n} f(y) =  \Delta_{\mathbb{S}^2}f(y)
+ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} {L}_n^{t_n} f(y) =  \Delta_{\mathbb{S}^2}f(y)
 \end{equation}
@@
 % brief introduction:
-This proof consists in two steps: first, we prove that $\b L_n^t \rightarrow L^t$, and second, we use proposition \ref{prop:3} to prove equation \eqref{eq:continuous convergence}.
+This proof consists in two steps: first, we prove that $L_n^t \rightarrow L^t$, and second, we use proposition \ref{prop:3} to prove \eqref{eq:continuous convergence}.
 This equation, as already explained in \cite{belkin2007convergence}, directly implies theorem \ref{theo:pointwise convergence for a regular sampling}.

### 2019-09-23 main.tex

--- 2019-09-23 main.tex
@@
 \paragraph{Theoretical convergence.}
-We extend the work of Belkin and Nyiogi to a fixed sampling.
-Given a sampling $V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$.
+We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme. 
+Given a sampling scheme $V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$.
 Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
-
 \begin{theorem}
-	For a sampling $V = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian $\frac{|\mathbb S^2|}{4\pi t_n}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\mathbb S^2}$  for $n\to\infty$:
-	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n} \b{L}_n^{t_n} T_V f(x_i) =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.$$
+	For a sampling $V = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian $\frac{|\mathbb S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\mathbb S^2}$  for $n\to\infty$:
+	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} f(x_i) =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.$$
 	\label{theo:pointwise convergence for a regular sampling}

### 2019-09-23 main.tex
precisions in climate tables

@@
 * even more feature maps give us one more point in perf\\
+* need more feature maps and layers to compensate for isotropy \\
 * cannot compare with Mudigonda: not the same input data\\
@@
 If the sampling is equal area as HEALPix, meaning that all the patches $\sigma_i$ have the same area, then we need to impose that $ d^{(n)}\leq \frac{1}{\sqrt{n}}$.
-If the sampling is not equal area, meaning that in general $A_i\neq A_j$, it can be shown that we need a slightly more complex condition: $\max_{i=0,\dots,n-1}d_iA_i\leq Cn^{-\frac{3}{2}}$.\\
-In the work of Belkin et al.
-\cite{belkin2005towards} the sampling is drawn form a uniform random distribution on the sphere, and their proof heavily relies on the uniformity properties of the distribution from which the sampling is drawn.
+\\
+In the work of \cite{belkin2005towards} the sampling is drawn form a uniform random distribution on the sphere, and their proof heavily relies on the uniformity properties of the distribution from which the sampling is drawn.
 In our case the sampling is deterministic, and the fact that for a sphere there doesn't exist a regular sampling with more than 12 points (the vertices of a icosahedron) is indeed a problem that we need to overcome by imposing the regularity conditions above.
@@
 Given the kernel density $t(n)=n^\beta$, if Belkin et al.
-proved convergence in the random case for $\beta \in (-\frac{1}{4}, 0)$, we proved convergence in the HEALPix case for $\beta \in (-\frac{1}{5}, 0)$.
+proved convergence in the random case for $\beta \in (-\frac{1}{4}, 0)$, we proved convergence in the deterministic case for $\beta \in (-\frac{1}{5}, 0)$.
 This kind of result can be interpreted in the following way.
-In order to have this pointwise convergence, we need to reduce the kernel width but \textit{not so fast} compared to the resolution of the graph.
+In order to have this pointwise convergence, we need to reduce the kernel width but \emph{not so fast} compared to the resolution of the graph.
 In other words, the kernel width has to be reduced but is somewhat limited by the resolution of the graph.
-In the next section we'll see how to set in practice a good kernel width $t$ given a graph resolution $n$.
-\begin{remark}
-	Pointwise convergence is just a necessary condition for spectral convergence.  Theorem \ref{theo:pointwise convergence in the healpix case} does not imply convergence of eigenvalues and eigenvectors.
-\end{remark}
 
@@
 * DS-optimal has 2 times the number of feature maps of DS. \\
-* \todo{What is DS and DS-Cohen?} \\
-* \todo{Is (equi non-weighted) the full resolution?} \\
+* \todo{What is DS and DS-Cohen?} DS has 4 times more feature maps and one more layer than DS-Jiang.
+DS-optimal has still 2 times more feature maps.
+DS-Cohen should be mostly gauge (based on paper, no code): 4 times more feature maps, but 2 layers less than DS-Jiang.
+\\
+* \todo{Is (equi non-weighted) the full resolution?} Yes, but less feature maps and layers. Can run, but not enough GPU memory for an optimal architecture. \\
 * \todo{check column order for DS} \\
@@
 		\midrule
-        DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ \\
-        DS-Jiang (weighted) & 97.1 & 97.6 & 96.5 & 97.1 \\
-        DS-optimal (weighted) & 91.5 & 93.4 & 99.0 & 94.6 \\
+		DS (Jiang architecture, weighted loss) & 97.1 & 97.6 & 96.5 & 97.1 \\
+        DS (weighted loss) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ \\
+		DS (wider architecture, weighted loss) & 91.5 & 93.4 & 99.0 & 94.6 \\
 		\midrule
-        DS (non-weighted) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ \\
-        DS-Jiang (non-weighted) & 33.6 & 93.6 & 99.3 & 75.5 \\
-        DS-optimal (non-weighted) & 73.4 & 92.7 & 99.8 & 88.7 \\
+        DS (Jiang architecture, non-weighted loss) & 33.6 & 93.6 & 99.3 & 75.5 \\
+        DS (non-weighted loss) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ \\
+        DS (wider architecture, non-weighted loss) & 73.4 & 92.7 & 99.8 & 88.7 \\
 		\midrule
-		\todo{DS-Cohen (weighted)} & 95.5 & 96.9 & 93.9 & 95.4 \\
-		\todo{DS-Cohen (non-weighted)} & 95.5 & 96.9 & 93.9 & 95.4 \\
-		\todo{DeepSphere (equi non-weighted)} & 31.3 & 75.2 & 99.9 & 68.80 \\
+		\todo{DS (Cohen architecture, weighted loss)} & 95.5 & 96.9 & 93.9 & 95.4 \\
+		\todo{DS (Cohen architecture, non-weighted loss)} & 95.5 & 96.9 & 93.9 & 95.4 \\
+		\todo{DS (full dataset, non-weighted loss)} & 31.3 & 75.2 & 99.9 & 68.80 \\
 		\bottomrule
@@
 		\midrule
-        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ \\
-        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 \\
-        DS-optimal (non-weighted) & 84.71 & 98.05 & 91.38 \\
+        DS (Jiang architecture, non-weighted loss) & 46.2 & 93.9 & 70.0 \\
+        DS (non-weighted loss) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ \\
+        DS (wider architecture, non-weighted loss) & 84.71 & 98.05 & 91.38 \\
 		\midrule
-        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ \\
-        DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 \\
-        DS-optimal (weighted) & 52.80 & 94.78 & 73.79 \\
+        DS (Jiang architecture, weighted loss) & 49.7 & 89.2 & 69.5 \\
+        DS (weighted loss) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ \\
+        DS (wider architecture, weighted loss) & 52.80 & 94.78 & 73.79 \\
 		\midrule
-		\todo{DS-Cohen (weighted)} & 13.1 & 80.3 & 46.7 \\
-		\todo{DeepSphere (equi non-weighted)} & 55.53 & 94.85 & 75.19 \\
+		\todo{DS (Cohen architecture, weighted loss)} & 13.1 & 80.3 & 46.7 \\
+		\todo{DS (full dataset, non-weighted loss)} & 55.53 & 94.85 & 75.19 \\
 		\bottomrule
@@
         % \cite{cohen2019gauge} (R2R) & - & - & - \\
-		DeepSphere (Jiang) & 590\,k & 5\,ms & 3\,h \\ % 590k
+		DeepSphere (Jiang architecture) & 590\,k & 5\,ms & 3\,h \\ % 590k
         DeepSphere & 13\,M & 33\,ms & 13\,h \\ % 12'926'432
-		DeepSphere (optimal) & 52\,M & 50\,ms & 20\,h \\
-		\todo{DS-Cohen (weighted)} & 2\,M & 11\,ms & 4\,h \\
-		\todo{DeepSphere (equi non-weighted)} & - & 567\,ms & 48\,h \\
+		DeepSphere (wider architecture) & 52\,M & 50\,ms & 20\,h \\
+		\todo{DS (Cohen architecture)} & 2\,M & 11\,ms & 4\,h \\
+		\todo{DS (full dataset)} & - & 567\,ms & 48\,h \\
 		\bottomrule

### 2019-09-23 main.tex
Updates from Overleaf
add climate figure

--- 2019-09-23 main.tex
@@
 \usepackage{graphicx} \graphicspath{{figures/}}
+\usepackage[export]{adjustbox} % figure vertical alignment
+\usepackage{subfig}
 %\usepackage{wrapfig}
@@
 \begin{figure}[h]
-	\includegraphics[height=0.25\linewidth]{example_cosmo_cmb}
-	\hfill
-	\includegraphics[height=0.25\linewidth]{example_brain_meg}
-% 	\hfill
-% 	\includegraphics[height=0.25\linewidth]{example_climate_TMQ}
-	\hfill
-	\includegraphics[height=0.25\linewidth]{example_ghcn_daily_tmax}
-	\hfill
-	\includegraphics[height=0.25\linewidth]{example_ghcn_graph}
+	\centering
+	\subfloat[]{
+		\includegraphics[height=0.20\linewidth,valign=t]{example_cosmo_cmb}
+	} \hfill
+	\subfloat[]{
+		\includegraphics[height=0.20\linewidth,valign=t]{example_brain_meg}
+	} \hspace{0.1em}
+	\subfloat[]{
+		\includegraphics[height=0.20\linewidth,valign=t]{example_climate_TMQ}
+		\label{fig:examples:climate}
+	} \hfill
+	\subfloat[]{
+		\includegraphics[height=0.20\linewidth,valign=t]{example_ghcn_daily_tmax}
+	} \hfill
+	\subfloat[]{
+		\includegraphics[height=0.20\linewidth,valign=t]{example_ghcn_graph}
+	}
 	\caption{
 		Examples of intrinsically spherical data:
-		(left) the cosmic microwave background (CMB) temperature from \citet{planck2015overview},
-		(middle) brain activity recorded through magnetoencephalography (MEG),\protect\footnotemark
-		(right) daily maximum temperature from the Global Historical Climatology Network (GHCN).\protect\footnotemark
-		A rigid full-sphere pixelization is not ideal: the Milky Way's galactic plane masks observations, brain activity is only measured on the scalp, and the position of weather stations is arbitrary and changes over time.
-		Graphs can faithfully and efficiently represent sampled spherical data by placing vertices where data has been measured.
+		(a) the cosmic microwave background (CMB) temperature from \citet{planck2015overview},
+		(b) brain activity recorded through magnetoencephalography (MEG),\protect\footnotemark
+		(c) hourly precipitation from a climate simulation \citep{mudigonda2017climateevents},
+		(d) daily maximum temperature from the Global Historical Climatology Network (GHCN).\protect\footnotemark
+		A rigid full-sphere pixelization is not ideal: the Milky Way's galactic plane masks observations, brain activity is only measured on the scalp, climate scientists desire a variable resolution, and the position of weather stations is arbitrary and changes over time.
+		(e) Graphs can faithfully and efficiently represent sampled spherical data by placing vertices where data has been measured.
 		%\todo{something from climate, weather?}
@@
 \begin{equation} \label{eq:equivariance error}
-	E_{\b{L}}(\b{f}, g) = \left(\frac{ \norm {\b{R}_V(g) \b{L} \b{f} - \b{L} \b{R}_V(g) \b{f}} }{\norm {\b{f}}}\right)^2,
+	E_{\b{L}}(\b{f}, g) = \left(\frac{ \norm {\b{R}_V(g) \b{L} \b{f} - \b{L} \b{R}_V(g) \b{f}} }{\norm {\b{L} \b{f}}}\right)^2,
 \end{equation}

### 2019-09-24 main.tex
climate experiment

@@
 		(b) brain activity recorded through magnetoencephalography (MEG),\protect\footnotemark
-		(c) hourly precipitation from a climate simulation \citep{mudigonda2017climateevents},
+		(c) hourly precipitation from a climate simulation \citep{jiang2019sphericalcnn}, %\citep{mudigonda2017climateevents},
 		(d) daily maximum temperature from the Global Historical Climatology Network (GHCN).\protect\footnotemark
@@
 \todo{
-	* discuss discretizations (equiangular, HEALPix) -> more uniform is better \\
+	* discuss discretizations (equiangular, HEALPix, icosahedral sphere) -> more uniform is better \\
 	* no uniform sampling: tradeoffs have to be made \\
@@
 The distance from the sphere to the object forms a depth map.
-The $\cos$ / $\sin$ of the surface angle forms two normal maps.
+The $\cos$ and $\sin$ of the surface angle forms two normal maps.
 The same is done for the object's convex hull.
@@
 
-\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section) and hyper-parameters. Or leave in appendix.}
-
-\begin{table}%[ht]
+\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section), loss, hyper-parameters. Or leave in appendix.}
+
+\begin{table}
     \centering
@@
 Results are shown in \tabref{shrec17}.
-DeepSphere achieves the same performance as \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn} while being much more efficient, suggesting that anisotropic filters are an unnecessary price to pay.
+DeepSphere achieves the same performance as \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn} at a much lower cost, suggesting that anisotropic filters are an unnecessary price to pay.
 % x times faster
@@
 
-* small: better perf than gauge and Jiang. due to icosahedron distortion? to be confirmed\\
-* cannot compare with Mudigonda (16 vs 1 input channel)\\
-* (full: we scale (50B pixels, 20TB) $\Rightarrow$ lead to better perf?) \\
+We evaluate our method on a task proposed by \citep{mudigonda2017climateevents}: the segmentation of extreme climate events, Tropical Cyclones (TC) and Atmospheric Rivers (AR), in global climate simulations (\figref{examples:climate}).
+The data was produced by a 20-year run of the Community Atmospheric Model v5 (CAM5) and consists of 16 channels such as temperature, wind, humidity, and pressure at multiple altitudes.
+We used the pre-processed dataset from \citep{jiang2019sphericalcnn}.\footnote{Available at \url{http://island.me.berkeley.edu/ugscnn/data}.}
+%\url{https://github.com/maxjiang93/ugscnn}
+%\url{https://github.com/maxjiang93/ugscnn/blob/master/experiments/exp4_sphere_climate/run.sh}
+%\url{http://island.me.berkeley.edu/ugscnn/data/climate_sphere_l5.zip}
+There is 1,072,805 spherical maps, down-sampled to a level-5 icosahedral grid ($N_{pix} = 10 \cdot 4^l + 2 = 10,242$).
+The labels are heavily unbalanced with 0.1\% TC, 2.2\% AR, and 97.7\% background (BG) pixels.
+
+\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section), loss, hyper-parameters. Or leave in appendix.}
 
@@
 	\midrule
-	\cite{jiang2019sphericalcnn} (paper) & 94.67 & - \\
+	%\cite{jiang2019sphericalcnn} (paper) & 94.67 & - \\
 	\cite{jiang2019sphericalcnn} (rerun) & 94.95 & 38.41 \\
@@
 	\caption{
-		Climate event segmentation results: mean accuracy and mean average precision (mAP).
-DeepSphere achieves state-of-the-art performance while using isotropic filters (S2S in \citet{cohen2019gauge}'s language), suggesting again that anisotropic filters are an unnecessary price to pay.
-		Note that \citet{jiang2019sphericalcnn} and \citet{cohen2019gauge} use a weighted cross-entropy loss, which is good for the accuracy metric (as it corrects for class imbalance) but bad for the mAP metric.
-	}
+		Climate event segmentation results: mean accuracy (over TC, AR, BG) and mean average precision (over TC and AR).
+		DeepSphere achieves state-of-the-art performance. %, suggesting again that anisotropic filters are an unnecessary price to pay.
+	}
+	\label{tab:climate}
 \end{table}
 
-* icosahedron dataset from \cite{jiang2019sphericalcnn} \\
-* Jiang rerun with a batch size of 64 instead of 256 due to memory limit.\\
-* cross entropy loss between parenthesis\\
-* 5 runs for each loss to obtain mean and std\\
-* same architecture as gauge, more feature maps than Jiang\\
-* perf with same arch as Jiang in appendix => not enough channels!\\
-* even more feature maps give us one more point in perf\\
-* need more feature maps and layers to compensate for isotropy \\
-* cannot compare with Mudigonda: not the same input data\\
-* why: icosahedron, can do anisotropy with isotropy + non-linearity + pooling
-
-* trade off between AP and accuracy in the case of TC class, it seems.\\
-* change base, influence?\\
-
-* full dataset not enough memory to run a correct model
-
-% jiang like correct: 99.81631631, 13.18655162, 52.62412867, 55.20899887;  0.3990812 , 0.80056251, 0.59982186; 4 ms; 2h40
-% more feat: 99.67871329, 38.78607557, 66.37910064, 68.2812965: 0.99981102, 0.60714174, 0.83236147, 0.71975161; 12ms; 6h20
+Results are shown in \tabref{climate} (details in tables~\ref{tab:climate:accuracy}, \ref{tab:climate:map} and~\ref{tab:climate:speed}).
+The mean and standard deviation are computed over 5 runs.
+Note that while \citet{jiang2019sphericalcnn} and \citet{cohen2019gauge} use a weighted cross-entropy loss, it is not ideal for the mAP metric.
+Results from \citet{mudigonda2017climateevents} cannot be directly compared as they don't use the same input channels.
+DeepSphere achieves state-of-the-art performance, suggesting again that anisotropic filters are not necessary.
+
+Compared to \citet{cohen2019gauge}'s conclusion, it is surprising that S2R does worse than DeepSphere (which is limited to S2S).
+Potential explanations are (i) that their icosahedral projection introduces harmful distortions, or (ii) that a larger architecture can compensate for the lack of generality. % powerfulness?
+We indeed observed that more feature maps and depth led to higher performance (\ref{sec:climate:appendix}).
 
@@
 As computational cost and memory consumption scales linearly with the number of pixels, DeepSphere easily deals with spherical maps made of millions of pixels.
-Such high resolutions are not necessary to represent thethe  depth maps of 3D objects, but are required to faithfully represent cosmological and climate data.
+Such high resolutions are not necessary to represent the depth maps of 3D objects, but are required to faithfully represent cosmological and climate data.
 % That has to do with the frequency content of the signals (see fig xx)
@@
 Our climate experiments (\secref{exp:climate}) however show that DeepSphere achieves similar performance than their most general convolution.
+% the SHREC17 experiment too shows that isotropic filters are sufficient
 Works on shape alignment indicates that anisotropic filters achieve better performance \todo{[Bronstein]}.
 Possible explanations for this discrepancy are that NNs somehow compensate for the lack of anisotropic filters, or that some tasks can be solved with isotropic filters.
+% why: icosahedron, can do anisotropy with isotropy + non-linearity + pooling
 The distortions induced by the icosahedral projection in \citep{cohen2019gauge} or the leakage of curvature information in \todo{[Bronstein]} might also be explanations.
@@
 
-\subsection{climate event detection}
-\subsubsection*{Results}
-
+\subsection{Climate event segmentation} \label{sec:climate:appendix}
+
+* Jiang rerun with a batch size of 64 instead of 256 due to memory limit.\\
 * DS-jiang is the similar architecture as \cite{jiang2019sphericalcnn}. \\
@@
 * \todo{check column order for DS} \\
+* perf with same arch as Jiang in appendix => not enough channels!\\
+* even more feature maps give us one more point in perf\\
+
+% trade off between AP and accuracy in the case of TC class, it seems.\\
+% (full: we scale (50B pixels, 20TB) $\Rightarrow$ lead to better perf?)
+% full dataset not enough memory to run a correct model
 
@@
 		Note that a non-weighted cross-entropy loss is not optimal for the accuracy metric.
+		\label{tab:climate:accuracy}
 	}
@@
 	}
+		\label{tab:climate:map}
 \end{table}
@@
 	}
+		\label{tab:climate:speed}
 \end{table}

### 2019-09-24 main.tex
uneven sampling experiment

@@
 	\item result tables: only what supports the main message in the text, everything we have in the appendix
+	\item Sampling, discretization, or pixelization of the sphere? Be consistent.
 \end{itemize}
@@
 		\includegraphics[height=0.20\linewidth,valign=t]{example_ghcn_daily_tmax}
+		\label{fig:examples:ghcn:tmax}
 	} \hfill
@@
 		\includegraphics[height=0.20\linewidth,valign=t]{example_ghcn_graph}
+		\label{fig:examples:ghcn:graph}
 	}
@@
 \end{figure}
-\footnotetext[1]{\scriptsize\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
-\footnotetext[2]{\scriptsize\url{https://martinos.org/mne/stable/auto_tutorials/plot_visualize_evoked.html}}
+\footnotetext[1]{\scriptsize\url{https://martinos.org/mne/stable/auto_tutorials/plot_visualize_evoked.html}}
+\footnotetext[2]{\scriptsize\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
 
@@
 
-\subsection{GHCN} \label{sec:exp:ghcn}
-
-* task is artificial, but it shows DeepSphere's flexibility\\
-* structure (looking around) help for prediction\\
-* equivariance to be verified in this case (next paper)\\
-
-* non-regular sampling with different density over the globe (continent vs ocean)\\
-* resulting graph is not rotation equivariant\\
-* Two different tasks: a dense regression and a global regression\\
-
-\paragraph*{dense regression - future temperature estimation}~\\
-* Task is to find the temperature at day T, knowing the temperature of the 5 previous days.\\
-* Goal is to change the order of the chebyshev filter to find the influence of the structure.\\
-* order 0 is the same as time series, as the pixel have no information of its neighborhood.\\
-* increasing order is good until threshold.\\
-* The NN indeed predicts the correct temperature at day T, and not day T-1 (baseline) even though there is small difference.\\
-
-\paragraph*{global regression - day in year estimation}~\\
-* days represented by a sine to represent the periodic nature of the year.\\
-* task too easy, temperature feature already periodic $\Rightarrow$ second experiment with only precipitation feature\\
-* structure is still helping\\
+\subsection{Uneven sampling} \label{sec:exp:ghcn}
+
+To demonstrate the flexibility of modeling the discretized sphere by a graph, we collected historical measurements from weather stations scattered across the Earth.\footnote{\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
+The spherical data is heavily non-uniformly sampled, with a much higher density of weather stations over North America than the Pacific (\figref{examples:ghcn:tmax}).
+There are \todo{xx} stations in total.
+For illustration, we devised two artificial tasks.
+A dense regression that consists of predicting the temperature on a given day knowing the temperature on the 5 previous days.
+A global regression that consists of predicting the day (represented as one period of a sine over the year) from temperature or precipitations.
 
@@
     \centering
-    \begin{tabular}{c|ccc}
-        order & future temp & day (temperature) & day (precipitations) \\ \hline
-        0 & 0.896 & 0.881 & - 0.920\\
-        4 & 0.919 & 0.969 & 0.597\\
+    \begin{tabular}{
+			c
+			S[table-format=2.2]
+			S[table-format=1.2]
+			S[table-format=1.3]
+			S[table-format=1.2]
+			S[table-format=1.2]
+			S[table-format=1.3]
+			S[table-format=1.2]
+			S[table-format=1.2]
+			S[table-format=-1.3]
+		}
+		\toprule
+		& \multicolumn{3}{c}{temp. (from past temp.)} & \multicolumn{3}{c}{day (from temperature)} & \multicolumn{3}{c}{day (from precipitations)} \\
+		\cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10}
+		order $K$ & {MSE} & {MAE} & {R2} & {MSE} & {MAE} & {R2} & {MSE} & {MAE} & {R2} \\
+		\midrule
+		$0$ & 10.88 & 2.42 & 0.896 & 0.10 & 0.10 & 0.881 & 0.58 & 0.42 & -0.920 \\
+		%%$1$ &  8.91 & 2.20 & 0.906 & - & - & - & - & - & - \\
+		$4$ &  8.20 & 2.11 & 0.919 & 0.05 & 0.06 & 0.969 & 0.50 & 0.18 &  0.597 \\
+		%$9$ &  8.38 & 2.12 & 0.915 & - & - & - & - & - & - \\
+		\bottomrule
     \end{tabular}
-    \caption{R2 coefficient for different tasks on the GHCN dataset}
-    \label{tab:GHCN_results}
+    \caption{
+		Prediction results on data from weather stations.
+		Structure always helps.
+	}
+    \label{tab:ghcn}
 \end{table}
+
+Results from \tabref{ghcn} show that treating the times series as a time-varying spherical signal (with filters of polynomial order $K>0$) yields higher performance than treating each time series independently ($K=0$).
+Note that predicting the day from temperature is much easier as temperature has a yearly pattern.
+Still, structure helps.
+
+% * increasing order is good until threshold \\
+% * equivariance to be verified in this case (next paper) -> in conclusion \\
+% * The NN indeed predicts the correct temperature at day T, and not day T-1 (baseline) even though there is small difference. \\
+% * \todo{performance of baseline} \\
 
@@
 
-%We thank Taco Cohen for his inputs on the intriguing results of our comparisons with their gauge CNN \citep{}.
+%We thank Pierre Vandergheynst for advices, and Andreas Loukas for having processed the GHCN data.
+%We thank Taco Cohen for his inputs on the intriguing results of our comparison with \citet{cohen2019gauge}.
+%We used the Python Graph Signal Processing package (PyGSP) \citep{pygsp} for computations and plots.
+%The Python Graph Signal Processing package (PyGSP) \citep{pygsp} was used to build graphs, compute the Laplacian and Fourier basis, and perform graph convolutions.
 
@@
 where $L_n^t$ is defined as follows:
-\begin{definition}{}\\
+\begin{definition}{}
 	\label{def:Heat Kernel Graph Laplacian operator}
@@
 
-\begin{table}
-    \centering
-    \begin{tabular}{c|ccc}
-        order & MSE & MAE & R2 \\ \hline
-        0 & 10.88 & 2.42 & 0.896\\
-        1 & 8.91 & 2.20 & 0.906\\
-        4 & 8.20 & 2.11 & 0.919\\
-        9 & 8.38 & 2.12 & 0.915\\
-    \end{tabular}
-    \caption{Future temperature estimation task. Evolution of performance in respect of the order of the graph filter}
-    \label{tab:future_results}
-    \hfill
-    %~\\[1cm]
-    % \begin{minipage}{0.48\linewidth}
-    % \begin{tabular}{c|ccc}
-    %     order & MSE & MAE & R2 \\ \hline
-    %     1 & 134.01 & 10.51 & -0.319\\
-    %     4 & 129.48 & 10.31 & -0.274\\
-    %     9 & 141.68 & 10.82 & -0.389\\
-    % \end{tabular}
-    % \caption{Baseline: testing with the present day (T-1) instead of the future day T}
-    % \label{tab:present_results}
-    % \end{minipage}
-\end{table}
-
-\begin{table}
-    \centering
-    \begin{minipage}{0.48\linewidth}
-    \begin{tabular}{c|ccc}
-        order & MSE & MAE & R2 \\ \hline
-        0 & 0.58 & 0.42 & -0.92\\
-        4 & 0.50 & 0.18 & 0.597\\
-    \end{tabular}
-    \caption{Find day in year using precipitation}
-    \label{tab:glob_prec}
-    \end{minipage}
-    \hfill
-    %~\\[1cm]
-    \begin{minipage}{0.48\linewidth}
-    \begin{tabular}{c|ccc}
-        order & MSE & MAE & R2 \\ \hline
-        0 & 0.10 & 0.10 & 0.881\\
-        4 & 0.05 & 0.05 & 0.969\\
-    \end{tabular}
-    \caption{Using temperature feature that is already periodical}
-    \label{tab:glob_all}
-    \end{minipage}
-\end{table}
-
 \subsubsection*{Dense}

### 2019-09-24 main.tex
cosmo experiment

@@
 	\item result tables: only what supports the main message in the text, everything we have in the appendix
-	\item Sampling, discretization, or pixelization of the sphere? Be consistent.
+	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions.
 \end{itemize}
@@
 
-Another approach represents the discretized sphere as a graph connecting pixels according to the distance between them \citep{khasanova2017sphericalcnn, perraudin2019deepspherecosmo}.
+Another approach represents the discretized sphere as a graph connecting pixels according to the distance between them \citep{bruna2013gnn, khasanova2017sphericalcnn, perraudin2019deepspherecosmo}.
 While Laplacian-based graph convolutions are more efficient than spherical convolutions, they are not exactly equivariant \citep{defferrard2019deepsphereequiv}.
@@
 
-\section{Is graph convolution equivariant to rotation? [2 pages]} \label{sec:equivariance}
+\section{Graph convolution and equivariance [2 pages]} \label{sec:equivariance}
+%\section{Is graph convolution equivariant to rotation? [2 pages]} \label{sec:equivariance}
 
@@
 
-\todo{
-Show: \\
-* meet the desiderata \\
-* DeepSphere V1 and V2 are equivalent in practice, wait on SHREC and cosmo exp \\
-* anisotropy doesn't help \\
-}
+% Show:
+% * meet the desiderata: scale
+% * DeepSphere V1 and V2 are equivalent in practice: better equivariance doesn't translate to better performance
+% * anisotropy doesn't help
 
@@
 LIDAR actually acquires depth maps, which are a posteriori represented as point clouds.
+\todo{move to intro?}
 
@@
 
-\subsection{Cosmological model discrimination} \label{sec:exp:cosmo}
+\subsection{Cosmological model classification} \label{sec:exp:cosmo}
+
+Given observations, cosmologists estimate the posterior probability of cosmological parameters, such as the matter density $\Omega_m$ and the normalization of the matter power spectrum $\sigma_8$.
+Those parameters are typically estimated by likelihood-free inference, which requires a function to predict the parameters from simulations.
+% such as Approximate Bayesian computation (ABC)
+As that is complicated to setup, prediction methods are typically benchmarked on the classification of spherical maps into cosmological model classes \citep{schmelze2017cosmologicalmodel}.
+We used the same task, data, and setup as \citet{perraudin2019deepspherecosmo}: the classification of $720$ partial convergence maps ($1/12 \approx 8\%$ of the sphere) made of $10^6$ pixels from two $\Lambda$CDM cosmological models, ($\Omega_m = 0.31$, $\sigma_8 = 0.82)$ and ($\Omega_m = 0.26$, $\sigma_8 = 0.91)$, at a relative noise level of $4$.
+% 60 maps * 12 parts = 720 parts
+Convergence maps represent the distribution of over- and under-densities of mass in the universe \citep[see][for a review of gravitational lensing]{bartelman2010gravitationallensing}.
+
+\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section), loss, hyper-parameters. Or leave in appendix.}
+
+\begin{table}
+    \centering
+    \begin{tabular}{l c c c}
+		\toprule
+		& accuracy & conv. equiv. error & NN inv. error \\
+		\midrule
+		2D CNN baseline \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{can we?} \\
+		8 neighbors, $\hat{t} = ??$, CNN variant, \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{??} \\
+		8 neighbors, $\hat{t} = ??$, FCN variant, \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{??} \\
+		8 neighbors, optimal kernel width $\hat{t} = ??$ & \todo{??} & \todo{??} \\
+		20 neighbors, optimal kernel width $\hat{t} = ??$ & \todo{??} & \todo{??} \\
+		40 neighbors, optimal kernel width $\hat{t} = ??$ & \todo{??} & \todo{??} \\
+		\bottomrule
+    \end{tabular}
+	\caption{
+		Results on the classification of partial convergence maps.
+		\todo{While extreme non-equivariance (the 2D CNN baseline) penalizes performance, improving equivariance doesn't improve performance.}
+	}
+    \label{tab:cosmo}
+\end{table}
 
 \todo{
-* other sphercial CNNs cannot scale to 10M pixels (tested on 10k at most) \\
-* redo the experiment with the optimal graph \\
-* DSv2 better than v1 -> equivariance has practical implications \\
-* clear cost-accuracy tradeoff with n_neighbors \\
-* show the baselines? (at least the 2D CNN?) \\
-}
-
-% \begin{table}[]
-%     \centering
-%     \begin{tabular}{c|c}
-%          &  \\
-%          &
-%     \end{tabular}
-%     \caption{Caption}
-%     \label{tab:cosmo_newgraph}
-% \end{table}
+}
+
+Results are shown in \tabref{cosmo}.
+\todo{
+	While extreme non-equivariance (the 2D CNN baseline) penalizes performance, better equivariance doesn't improve performance.
+	It might be that the lack of built-in equivariance is compensated by learned equivariance (as done when augmenting data during training).}
+\todo{
+	Alternative: DSv2 better than v1 -> equivariance has practical implications.
+	Clear cost-accuracy tradeoff with the number of neighbors.
+}
+This experiment moreover demonstrates DeepSphere's flexibility (using partial spherical maps) and scalability (competing spherical CNNs were tested on maps of at most $10,000$ pixels).
 
@@
 
-To demonstrate the flexibility of modeling the discretized sphere by a graph, we collected historical measurements from weather stations scattered across the Earth.\footnote{\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
+To demonstrate the flexibility of modeling the discretized sphere by a graph, we collected historical measurements from about 10,000 weather stations scattered across the Earth.\footnote{\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
 The spherical data is heavily non-uniformly sampled, with a much higher density of weather stations over North America than the Pacific (\figref{examples:ghcn:tmax}).
-There are \todo{xx} stations in total.
 For illustration, we devised two artificial tasks.
@@
 A global regression that consists of predicting the day (represented as one period of a sine over the year) from temperature or precipitations.
+
+\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section), loss, hyper-parameters. Or leave in appendix.}
 

### 2019-09-24 main.tex
Updates from Overleaf

--- 2019-09-24 main.tex
@@
 \usepackage{graphicx} \graphicspath{{figures/}}
-\usepackage[export]{adjustbox} % figure vertical alignment
-\usepackage{subfig}
 %\usepackage{wrapfig}
@@
 \begin{figure}[h]
-	\centering
-	\subfloat[]{
-		\includegraphics[height=0.20\linewidth,valign=t]{example_cosmo_cmb}
-	} \hfill
-	\subfloat[]{
-		\includegraphics[height=0.20\linewidth,valign=t]{example_brain_meg}
-	} \hspace{0.1em}
-	\subfloat[]{
-		\includegraphics[height=0.20\linewidth,valign=t]{example_climate_TMQ}
-		\label{fig:examples:climate}
-	} \hfill
-	\subfloat[]{
-		\includegraphics[height=0.20\linewidth,valign=t]{example_ghcn_daily_tmax}
-	} \hfill
-	\subfloat[]{
-		\includegraphics[height=0.20\linewidth,valign=t]{example_ghcn_graph}
-	}
+	\includegraphics[height=0.25\linewidth]{example_cosmo_cmb}
+	\hfill
+	\includegraphics[height=0.25\linewidth]{example_brain_meg}
+% 	\hfill
+% 	\includegraphics[height=0.25\linewidth]{example_climate_TMQ}
+	\hfill
+	\includegraphics[height=0.25\linewidth]{example_ghcn_daily_tmax}
+	\hfill
+	\includegraphics[height=0.25\linewidth]{example_ghcn_graph}
 	\caption{
 		Examples of intrinsically spherical data:
-		(a) the cosmic microwave background (CMB) temperature from \citet{planck2015overview},
-		(b) brain activity recorded through magnetoencephalography (MEG),\protect\footnotemark
-		(c) hourly precipitation from a climate simulation \citep{jiang2019sphericalcnn}, %\citep{mudigonda2017climateevents},
-		(d) daily maximum temperature from the Global Historical Climatology Network (GHCN).\protect\footnotemark
-		A rigid full-sphere pixelization is not ideal: the Milky Way's galactic plane masks observations, brain activity is only measured on the scalp, climate scientists desire a variable resolution, and the position of weather stations is arbitrary and changes over time.
-		(e) Graphs can faithfully and efficiently represent sampled spherical data by placing vertices where data has been measured.
+		(left) the cosmic microwave background (CMB) temperature from \citet{planck2015overview},
+		(middle) brain activity recorded through magnetoencephalography (MEG),\protect\footnotemark
+		(right) daily maximum temperature from the Global Historical Climatology Network (GHCN).\protect\footnotemark
+		A rigid full-sphere pixelization is not ideal: the Milky Way's galactic plane masks observations, brain activity is only measured on the scalp, and the position of weather stations is arbitrary and changes over time.
+		Graphs can faithfully and efficiently represent sampled spherical data by placing vertices where data has been measured.
 		%\todo{something from climate, weather?}
@@
 \todo{
-	* discuss discretizations (equiangular, HEALPix, icosahedral sphere) -> more uniform is better \\
+	* discuss discretizations (equiangular, HEALPix) -> more uniform is better \\
 	* no uniform sampling: tradeoffs have to be made \\
@@
 The distance from the sphere to the object forms a depth map.
-The $\cos$ and $\sin$ of the surface angle forms two normal maps.
+The $\cos$ / $\sin$ of the surface angle forms two normal maps.
 The same is done for the object's convex hull.
@@
 
-\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section), loss, hyper-parameters. Or leave in appendix.}
-
-\begin{table}
+\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section) and hyper-parameters. Or leave in appendix.}
+
+\begin{table}%[ht]
     \centering
@@
 Results are shown in \tabref{shrec17}.
-DeepSphere achieves the same performance as \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn} at a much lower cost, suggesting that anisotropic filters are an unnecessary price to pay.
+DeepSphere achieves the same performance as \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn} while being much more efficient, suggesting that anisotropic filters are an unnecessary price to pay.
 % x times faster
@@
 
-We evaluate our method on a task proposed by \citep{mudigonda2017climateevents}: the segmentation of extreme climate events, Tropical Cyclones (TC) and Atmospheric Rivers (AR), in global climate simulations (\figref{examples:climate}).
-The data was produced by a 20-year run of the Community Atmospheric Model v5 (CAM5) and consists of 16 channels such as temperature, wind, humidity, and pressure at multiple altitudes.
-We used the pre-processed dataset from \citep{jiang2019sphericalcnn}.\footnote{Available at \url{http://island.me.berkeley.edu/ugscnn/data}.}
-%\url{https://github.com/maxjiang93/ugscnn}
-%\url{https://github.com/maxjiang93/ugscnn/blob/master/experiments/exp4_sphere_climate/run.sh}
-%\url{http://island.me.berkeley.edu/ugscnn/data/climate_sphere_l5.zip}
-There is 1,072,805 spherical maps, down-sampled to a level-5 icosahedral grid ($N_{pix} = 10 \cdot 4^l + 2 = 10,242$).
-The labels are heavily unbalanced with 0.1\% TC, 2.2\% AR, and 97.7\% background (BG) pixels.
-
-\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section), loss, hyper-parameters. Or leave in appendix.}
+* small: better perf than gauge and Jiang. due to icosahedron distortion? to be confirmed\\
+* cannot compare with Mudigonda (16 vs 1 input channel)\\
+* (full: we scale (50B pixels, 20TB) $\Rightarrow$ lead to better perf?) \\
 
@@
 	\midrule
-	%\cite{jiang2019sphericalcnn} (paper) & 94.67 & - \\
+	\cite{jiang2019sphericalcnn} (paper) & 94.67 & - \\
 	\cite{jiang2019sphericalcnn} (rerun) & 94.95 & 38.41 \\
@@
 	\caption{
-		Climate event segmentation results: mean accuracy (over TC, AR, BG) and mean average precision (over TC and AR).
-		DeepSphere achieves state-of-the-art performance. %, suggesting again that anisotropic filters are an unnecessary price to pay.
-	}
-	\label{tab:climate}
+		Climate event segmentation results: mean accuracy and mean average precision (mAP).
+DeepSphere achieves state-of-the-art performance while using isotropic filters (S2S in \citet{cohen2019gauge}'s language), suggesting again that anisotropic filters are an unnecessary price to pay.
+		Note that \citet{jiang2019sphericalcnn} and \citet{cohen2019gauge} use a weighted cross-entropy loss, which is good for the accuracy metric (as it corrects for class imbalance) but bad for the mAP metric.
+	}
 \end{table}
 
-Results are shown in \tabref{climate} (details in tables~\ref{tab:climate:accuracy}, \ref{tab:climate:map} and~\ref{tab:climate:speed}).
-The mean and standard deviation are computed over 5 runs.
-Note that while \citet{jiang2019sphericalcnn} and \citet{cohen2019gauge} use a weighted cross-entropy loss, it is not ideal for the mAP metric.
-Results from \citet{mudigonda2017climateevents} cannot be directly compared as they don't use the same input channels.
-DeepSphere achieves state-of-the-art performance, suggesting again that anisotropic filters are not necessary.
-
-Compared to \citet{cohen2019gauge}'s conclusion, it is surprising that S2R does worse than DeepSphere (which is limited to S2S).
-Potential explanations are (i) that their icosahedral projection introduces harmful distortions, or (ii) that a larger architecture can compensate for the lack of generality. % powerfulness?
-We indeed observed that more feature maps and depth led to higher performance (\ref{sec:climate:appendix}).
+* icosahedron dataset from \cite{jiang2019sphericalcnn} \\
+* Jiang rerun with a batch size of 64 instead of 256 due to memory limit.\\
+* cross entropy loss between parenthesis\\
+* 5 runs for each loss to obtain mean and std\\
+* same architecture as gauge, more feature maps than Jiang\\
+* perf with same arch as Jiang in appendix => not enough channels!\\
+* even more feature maps give us one more point in perf\\
+* need more feature maps and layers to compensate for isotropy \\
+* cannot compare with Mudigonda: not the same input data\\
+* why: icosahedron, can do anisotropy with isotropy + non-linearity + pooling
+
+* trade off between AP and accuracy in the case of TC class, it seems.\\
+* change base, influence?\\
+
+* full dataset not enough memory to run a correct model
+
+% jiang like correct: 99.81631631, 13.18655162, 52.62412867, 55.20899887;  0.3990812 , 0.80056251, 0.59982186; 4 ms; 2h40
+% more feat: 99.67871329, 38.78607557, 66.37910064, 68.2812965: 0.99981102, 0.60714174, 0.83236147, 0.71975161; 12ms; 6h20
 
@@
 As computational cost and memory consumption scales linearly with the number of pixels, DeepSphere easily deals with spherical maps made of millions of pixels.
-Such high resolutions are not necessary to represent the depth maps of 3D objects, but are required to faithfully represent cosmological and climate data.
+Such high resolutions are not necessary to represent thethe  depth maps of 3D objects, but are required to faithfully represent cosmological and climate data.
 % That has to do with the frequency content of the signals (see fig xx)
@@
 Our climate experiments (\secref{exp:climate}) however show that DeepSphere achieves similar performance than their most general convolution.
-% the SHREC17 experiment too shows that isotropic filters are sufficient
 Works on shape alignment indicates that anisotropic filters achieve better performance \todo{[Bronstein]}.
 Possible explanations for this discrepancy are that NNs somehow compensate for the lack of anisotropic filters, or that some tasks can be solved with isotropic filters.
-% why: icosahedron, can do anisotropy with isotropy + non-linearity + pooling
 The distortions induced by the icosahedral projection in \citep{cohen2019gauge} or the leakage of curvature information in \todo{[Bronstein]} might also be explanations.
@@
 
-\section{Proof of theorem}\label{sec: appendix: proof of theorem}
-Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal M$, a smooth function $f:\mathcal M \rightarrow \mathbb R$, and defined the vector $\b f$ of samples of $f$ as follows: $\b f\in \mathbb R^n,\ \b f_i = f(x_i)$, it is known that  (\cite{belkin2005towards}) to prove the convergence of $(\b {L}_n^t \b f) _i$ to $\Delta_{\mathbb S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\mathbb S^2}f(x)$
-where $L_n^t$ is defined as follows:
-\begin{definition}{}\\
-	\label{def:Heat Kernel Graph Laplacian operator}
-	\text{Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of the manifold we define the \textbf{operator} }$L_n^t$ such that
-	$$L_n^tf(y) := \frac{1}{n}\left[ \sum_{i=0}^{n-1} \exp \left\{ {-\frac{||x_i-y||^2}{4t}}\right\}\left(f(y)-f(x_i)\right)\right]$$
-\end{definition}
-Thus, to prove theorem \ref{theo:pointwise convergence for a regular sampling} it will be sufficient to prove that 
-\begin{equation}\label{eq:continuous convergence}
- \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} {L}_n^{t_n} f(y) =  \Delta_{\mathbb{S}^2}f(y)
+\section{Proof of theorem \ref{theo:pointwise convergence for a regular sampling}}\label{sec: appendix: proof of theorem}
+
+\paragraph{Preliminaries.}
+The proof of theorem \ref{theo:pointwise convergence for a regular sampling} is inspired from the work of \cite{belkin2005towards}. As a result, we start by restating some of their results.
+Given a sampling $V = \{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_Vf=\b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
+The proof is constructed by leveraging 3 different operators:
+\begin{itemize}
+    \item The extended graph Laplacian operator is a functional $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$  is defined given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ and $y\in \mathcal{M}$  as
+	\begin{equation}
+	\label{eq:Heat Kernel Graph Laplacian operator}
+	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
 	\end{equation}
-For the sake of the proof we will need also the following facts:
-\begin{definition}{} (\cite{belkin2005towards})\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, and let $\text{vol}(\mathcal M)$ be the volume of $\mathcal M$.
-We define the functional approximation to the Laplace-Beltrami operator to be the operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
-	\label{def:Functional approximation to the Laplace-Beltrami operator}
-	$$ L^tf(y) = \int_{\mathcal M}\exp\left\{-\frac{||y-x||^2}{4t}\right\}\left(f(y)-f(x)\right)d\mu(x)$$
-\end{definition}
-
-\begin{prop} (\cite{belkin2005towards}) \\
-Let $\mathcal M$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb R^N$, and fix $y\in\mathcal M$.
-Let the data points $x_1, \dots, x_n$ be sampled form a uniform distribution on the manifold $\mathcal M$.
-Set $t_n=n^{-\frac{1}{k+2+\alpha}}$, for any $\alpha>0$ and let $f\in\mathcal C_\infty(\mathcal M)$.
-Then
-	$$\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(y) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\triangle_{\mathcal M}f(y).$$
+	Note that we have the following relation $\b{L}_n^t \b{f} = T_V L_n^t f$.
+	\item The functional approximation to the Laplace-Beltrami operator is a functional $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined  as
+	\begin{equation}
+    \label{eq:Functional approximation to the Laplace-Beltrami operator}
+	L^tf(y) = \int_{\mathcal{M}} \exp^{-\frac{\|y-x\|^2}{4t}}\left(f(y)-f(x)\right)d\mu(x),
+	\end{equation}
+	where given $\mu$ be the uniform probability measure on the manifold $\mathcal{M}$, and let $\text{vol}(\mathcal{M})$ be the volume of $\mathcal{M}$.
+	\item 
+	The Laplace-Beltrami operator $\Delta_{\mathcal{M}}$ is defined as the divergence of the gradient
+	\begin{equation}
+        \label{eq:laplace-beltrami}
+        \Delta_{\mathcal M}f(y):= -\text{div}(\nabla_{\mathcal M}f)
+    \end{equation}
+    of a differentiable function $f: \mathcal M\rightarrow \mathbb R$.
+The gradient $\nabla f: \mathcal M \rightarrow T_p\mathcal M$ is a vector field defined on the manifold pointing towards the direction of steepest ascent of $f$, where $T_p\mathcal M$ is the affine space of all vectors tangent to $\mathcal M$ at $p$
+
+\end{itemize}
+
+Leaveraging these three operators \cite{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian toward the Laplace-Beltrami operator.
+The proofs consists in establishing that \eqref{eq:Heat Kernel Graph Laplacian operator} converges toward \eqref{eq:Functional approximation to the Laplace-Beltrami operator} as $n\rightarrow \infty$ and \eqref{eq:Functional approximation to the Laplace-Beltrami operator} converges toward \eqref{eq:laplace-beltrami} as $t\rightarrow 0$.
+In particular, this second step is given by the following:
+\begin{prop}
+[\cite{belkin2005towards}, Proposition 4.4]
+Let $\mathcal{M}$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb{R}^N$, and fix $y\in\mathcal{M}$. Let $f\in\mathcal{C}_\infty(\mathcal{M)}$. Then
+\begin{equation}
+\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(y) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\Delta_{\mathcal M}f(y).    
+\end{equation}
 \label{prop:3}
@@
 
+\paragraph{Building the proof.}
+As the sphere is a compact smooth manifold embedded in $\mathbb{R}^3$, we can reuse the second part or their proofs where \eqref{eq:Functional approximation to the Laplace-Beltrami operator} $\rightarrow$ \eqref{eq:laplace-beltrami}.
+Thus, our strategy to prove Theorem \ref{theo:pointwise convergence for a regular sampling} is to a) show that 
+\begin{equation}\label{eq:continuous convergence}
+ \lim_{n\to\infty}L_n^{t} f(y) =  L^t(y)
+\end{equation}
+for a particular class of sampling and b) apply Proposition \ref{prop:3}.
+
+%  \frac{|\mathbb{S}^2|}{4\pi t} 
+% \begin{definition}{}\\
+% 	\label{def:Heat Kernel Graph Laplacian operator}
+% 	\text{Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of the manifold we define the \textbf{operator} }$L_n^t$ such that
+% 	$$L_n^tf(y) := \frac{1}{n}\left[ \sum_{i=0}^{n-1} \exp \left\{ {-\frac{||x_i-y||^2}{4t}}\right\}\left(f(y)-f(x_i)\right)\right]$$
+% \end{definition}
+
+% it is known that  (\cite{belkin2005towards}) to prove the convergence of $(\b {L}_n^t \b f) _i$ to $\Delta_{\mathbb S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\mathbb S^2}f(x)$
+% where $L_n^t$ is defined as follows:
+
+% For the sake of the proof we will need also the following facts:
+% \begin{definition}{} (\cite{belkin2005towards})\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, and let $\text{vol}(\mathcal M)$ be the volume of $\mathcal M$.
+We define the functional approximation to the Laplace-Beltrami operator to be the operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
+% 	\label{def:Functional approximation to the Laplace-Beltrami operator}
+% 	$$ L^tf(y) = \int_{\mathcal M}\exp\left\{-\frac{||y-x||^2}{4t}\right\}\left(f(y)-f(x)\right)d\mu(x)$$
+% \end{definition}
+
 % brief introduction:
-This proof consists in two steps: first, we prove that $L_n^t \rightarrow L^t$, and second, we use proposition \ref{prop:3} to prove \eqref{eq:continuous convergence}.
+% This proof consists in two steps: first, we prove that $L_n^t \rightarrow L^t$, and second, we use proposition \ref{prop:3} to prove \eqref{eq:continuous convergence}.
 This equation, as already explained in \cite{belkin2007convergence}, directly implies theorem \ref{theo:pointwise convergence for a regular sampling}.
 
-Our first goal is thus to prove the following Proposition:
+We start by proving the following Proposition:
 \vspace{0.5cm}
 \begin{prop}\label{prop:1}
-	For an equal area sampling $\{x_i\in\mathbb S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance $||\cdot||$ with Lipschitz constant $\mathcal L_f$
+	For an equal area sampling $\{x_i\in\mathbb S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance $\|\cdot\|$ with Lipschitz constant $\mathcal L_f$
 	$$
@@
         DeepSphere \emph{HEALPix} & 80.42 & 80.65 & 0.9ms & 46m\\
-        DeepSphere \emph{Improved HEALPix} & 80.76 & & &
+        % DeepSphere \emph{Improved HEALPix} & 80.76 & & &
     \end{tabular}
@@
     DeepSphere \emph{HEALPix} & 0.725 & 0.717 & 0.715 & 0.686 & 0.475 & 0.508 & 0.468 & 0.428\\
-    DeepSphere \emph{Improved HEALPix} & & & & &
+    % DeepSphere \emph{Improved HEALPix} & & & & &
     \end{tabular}
@@
 
-\subsubsection*{HEALPix}
+\subsubsection*{HEALPix architecure}
 
@@
 
-30 epochs with augmented dataset, 3 random translation perturbation, or 90 epochs over dataset that can be augmented
-\subsubsection*{Equiangular}
+30 epochs with augmented dataset, 3 random translation perturbation (same as 90 epochs over dataset with 3 possible random rotation)
+\subsubsection*{Equiangular architecture}
 Equiangular sampling with bandwidth of 64 in longitude and latitude.
@@
 
-\subsection{Climate event segmentation} \label{sec:climate:appendix}
-
-* Jiang rerun with a batch size of 64 instead of 256 due to memory limit.\\
+\subsection{climate event detection}
+\subsubsection*{Detailled results}
+
 * DS-jiang is the similar architecture as \cite{jiang2019sphericalcnn}. \\
@@
 * \todo{check column order for DS} \\
-* perf with same arch as Jiang in appendix => not enough channels!\\
-* even more feature maps give us one more point in perf\\
-
-% trade off between AP and accuracy in the case of TC class, it seems.\\
-% (full: we scale (50B pixels, 20TB) $\Rightarrow$ lead to better perf?)
-% full dataset not enough memory to run a correct model
 
@@
 		\todo{DS (Cohen architecture, weighted loss)} & 95.5 & 96.9 & 93.9 & 95.4 \\
-		\todo{DS (Cohen architecture, non-weighted loss)} & 95.5 & 96.9 & 93.9 & 95.4 \\
+		\todo{DS (Cohen architecture, non-weighted loss)} & 56.4 & 90.0 & 98.9 & 81.8 \\
 		\todo{DS (full dataset, non-weighted loss)} & 31.3 & 75.2 & 99.9 & 68.80 \\
@@
 		Note that a non-weighted cross-entropy loss is not optimal for the accuracy metric.
-		\label{tab:climate:accuracy}
 	}
@@
 		\todo{DS (Cohen architecture, weighted loss)} & 13.1 & 80.3 & 46.7 \\
+		\todo{DS (Cohen architecture, non-weighted loss)} & 59.8 & 85.0 & 72.4 \\
 		\todo{DS (full dataset, non-weighted loss)} & 55.53 & 94.85 & 75.19 \\
@@
 	}
-		\label{tab:climate:map}
 \end{table}
@@
 	}
-		\label{tab:climate:speed}
 \end{table}
 
-\subsubsection*{Icosahedron}
+\subsubsection*{DS Icosahedron architecture}
 
@@
 30 epochs
-\subsubsection*{DS-jiang}
+
+wider architecture is the same, but with 2 time the feature maps.
+\subsubsection*{DS (Jiang architecture)}
 encoder:\\
@@
 concat the results of the corresponding encoder layer after the graph convolution. Similar to ``Jiang et al.''
-\subsubsection*{Equiangular}
+\subsubsection*{Full dataset - Equiangular architecture}
 Equiangular sampling, with a latitude bandwidth 384 and longitude bandwidth 576.
@@
 
-\subsubsection*{Results}
+\subsubsection*{Deatilled results}
 
@@
 
-\subsubsection*{Dense}
+\subsubsection*{Dense task architecture}
 
@@
 
-\subsubsection*{Global}
+\subsubsection*{Global task architecture}
 

### 2019-09-24 main.tex

--- 2019-09-24 main.tex
@@
 
-\section{Proof of theorem}\label{sec: appendix: proof of theorem}
-Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal M$, a smooth function $f:\mathcal M \rightarrow \mathbb R$, and defined the vector $\b f$ of samples of $f$ as follows: $\b f\in \mathbb R^n,\ \b f_i = f(x_i)$, it is known that  (\cite{belkin2005towards}) to prove the convergence of $(\b {L}_n^t \b f) _i$ to $\Delta_{\mathbb S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\mathbb S^2}f(x)$
-where $L_n^t$ is defined as follows:
-\begin{definition}{}
-	\label{def:Heat Kernel Graph Laplacian operator}
-	\text{Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of the manifold we define the \textbf{operator} }$L_n^t$ such that
-	$$L_n^tf(y) := \frac{1}{n}\left[ \sum_{i=0}^{n-1} \exp \left\{ {-\frac{||x_i-y||^2}{4t}}\right\}\left(f(y)-f(x_i)\right)\right]$$
-\end{definition}
-Thus, to prove theorem \ref{theo:pointwise convergence for a regular sampling} it will be sufficient to prove that 
-\begin{equation}\label{eq:continuous convergence}
- \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} {L}_n^{t_n} f(y) =  \Delta_{\mathbb{S}^2}f(y)
+\section{Proof of theorem \ref{theo:pointwise convergence for a regular sampling}}\label{sec: appendix: proof of theorem}
+
+\paragraph{Preliminaries.}
+The proof of theorem \ref{theo:pointwise convergence for a regular sampling} is inspired from the work of \cite{belkin2005towards}. As a result, we start by restating some of their results.
+Given a sampling $V = \{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_Vf=\b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
+The proof is constructed by leveraging 3 different operators:
+\begin{itemize}
+    \item The extended graph Laplacian operator is a functional $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$  is defined given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ and $y\in \mathcal{M}$  as
+	\begin{equation}
+	\label{eq:Heat Kernel Graph Laplacian operator}
+	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
 	\end{equation}
-For the sake of the proof we will need also the following facts:
-\begin{definition}{} (\cite{belkin2005towards})\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, and let $\text{vol}(\mathcal M)$ be the volume of $\mathcal M$.
-We define the functional approximation to the Laplace-Beltrami operator to be the operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
-	\label{def:Functional approximation to the Laplace-Beltrami operator}
-	$$ L^tf(y) = \int_{\mathcal M}\exp\left\{-\frac{||y-x||^2}{4t}\right\}\left(f(y)-f(x)\right)d\mu(x)$$
-\end{definition}
-
-\begin{prop} (\cite{belkin2005towards}) \\
-Let $\mathcal M$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb R^N$, and fix $y\in\mathcal M$.
-Let the data points $x_1, \dots, x_n$ be sampled form a uniform distribution on the manifold $\mathcal M$.
-Set $t_n=n^{-\frac{1}{k+2+\alpha}}$, for any $\alpha>0$ and let $f\in\mathcal C_\infty(\mathcal M)$.
-Then
-	$$\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(y) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\triangle_{\mathcal M}f(y).$$
+	Note that we have the following relation $\b{L}_n^t \b{f} = T_V L_n^t f$.
+	\item The functional approximation to the Laplace-Beltrami operator is a functional $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined  as
+	\begin{equation}
+    \label{eq:Functional approximation to the Laplace-Beltrami operator}
+	L^tf(y) = \int_{\mathcal{M}} \exp^{-\frac{\|y-x\|^2}{4t}}\left(f(y)-f(x)\right)d\mu(x),
+	\end{equation}
+	where given $\mu$ be the uniform probability measure on the manifold $\mathcal{M}$, and let $\text{vol}(\mathcal{M})$ be the volume of $\mathcal{M}$.
+	\item 
+	The Laplace-Beltrami operator $\Delta_{\mathcal{M}}$ is defined as the divergence of the gradient
+	\begin{equation}
+        \label{eq:laplace-beltrami}
+        \Delta_{\mathcal M}f(y):= -\text{div}(\nabla_{\mathcal M}f)
+    \end{equation}
+    of a differentiable function $f: \mathcal M\rightarrow \mathbb R$.
+The gradient $\nabla f: \mathcal M \rightarrow T_p\mathcal M$ is a vector field defined on the manifold pointing towards the direction of steepest ascent of $f$, where $T_p\mathcal M$ is the affine space of all vectors tangent to $\mathcal M$ at $p$
+
+\end{itemize}
+
+Leaveraging these three operators \cite{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian toward the Laplace-Beltrami operator.
+The proofs consists in establishing that \eqref{eq:Heat Kernel Graph Laplacian operator} converges toward \eqref{eq:Functional approximation to the Laplace-Beltrami operator} as $n\rightarrow \infty$ and \eqref{eq:Functional approximation to the Laplace-Beltrami operator} converges toward \eqref{eq:laplace-beltrami} as $t\rightarrow 0$.
+In particular, this second step is given by the following:
+\begin{prop}
+[\cite{belkin2005towards}, Proposition 4.4]
+Let $\mathcal{M}$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb{R}^N$, and fix $y\in\mathcal{M}$. Let $f\in\mathcal{C}_\infty(\mathcal{M)}$. Then
+\begin{equation}
+\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(y) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\Delta_{\mathcal M}f(y).    
+\end{equation}
 \label{prop:3}
@@
 
-\subsubsection*{Icosahedron}
+\subsubsection*{DS Icosahedron architecture}
 
@@
 
-\subsubsection*{Results}
-
-\subsubsection*{Dense}
+\subsubsection*{Deatilled results}
+
+\subsubsection*{Dense task architecture}
 

### 2019-09-24 main.tex
small edits

@@
 The $\cos$ and $\sin$ of the surface angle forms two normal maps.
-The same is done for the object's convex hull.
+The same is done for the object's convex hull.\footnote{Albeit we didn't observe much improvement by using the convex hull.}
 The maps are discretized using either an equiangular grid \citep{driscoll1994Fouriersphere} with bandwidth $b = 64$ ($N_{pix} = 4 b^2 = 16,384$), or an HEALPix \citep{healpix} grid with $N_{side} = 32$ ($N_{pix} = 12 N_{side}^2 = 12,288$).
@@
 For the same reason, using the more uniform HEALPix discretization or lowering the resolution down to $N_{side} = 8$ didn't impact performance.
+\todo{be sure that it fits with the cosmo conclusion}
 \todo{The same conclusions are drawn from ModelNet 40 (see appendix ??).}
@@
 \subsection{Uneven sampling} \label{sec:exp:ghcn}
+% Weather prediction? But it's not a real task. Rather a demo.
 
@@
 \subsubsection*{Author Contributions}
-Left blank for anonymity reason
+Left blank for anonymity reason.
 % If you'd like to, you may include a section for author contributions as is done
@@
 \subsubsection*{Acknowledgments}
-Left blank for anonymity reason
+Left blank for anonymity reason.
 
@@
 
-* Network architecture and details
+* Network architecture and training details
 

### 2019-09-24 main.tex
unify notation: n for number of pixels

@@
 	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions.
+	\item unify enumerations. I like (i), (ii), etc.
 \end{itemize}
@@
 We calculated numerically the equivariance error (\ref{eq:mean equivariance error}) by generating $N$ monochromatic signals and $M$ random rotations for each signal.
-The colors that were used were chosen in the range $(0,\  3N_{side}-1)$ to allow for an almost perfect synthesis of the rotated signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_V$ (\cite{healpix_primer})
+The colors that were used were chosen in the range $(0,\  3N_{side}-1)$ to allow for an almost perfect synthesis of the rotated signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_V$ \citep{healpix_primer}.
 
@@
 The same is done for the object's convex hull.\footnote{Albeit we didn't observe much improvement by using the convex hull.}
-The maps are discretized using either an equiangular grid \citep{driscoll1994Fouriersphere} with bandwidth $b = 64$ ($N_{pix} = 4 b^2 = 16,384$), or an HEALPix \citep{healpix} grid with $N_{side} = 32$ ($N_{pix} = 12 N_{side}^2 = 12,288$).
+The maps are discretized using either an equiangular grid \citep{driscoll1994Fouriersphere} with bandwidth $b = 64$ ($n = 4 b^2 = 16,384$ pixels), or an HEALPix \citep{healpix} grid with $N_{side} = 32$ ($n = 12 N_{side}^2 = 12,288$ pixels).
 
@@
 As that is complicated to setup, prediction methods are typically benchmarked on the classification of spherical maps into cosmological model classes \citep{schmelze2017cosmologicalmodel}.
-We used the same task, data, and setup as \citet{perraudin2019deepspherecosmo}: the classification of $720$ partial convergence maps ($1/12 \approx 8\%$ of the sphere) made of $10^6$ pixels from two $\Lambda$CDM cosmological models, ($\Omega_m = 0.31$, $\sigma_8 = 0.82)$ and ($\Omega_m = 0.26$, $\sigma_8 = 0.91)$, at a relative noise level of $4$.
+We used the same task, data, and setup as \citet{perraudin2019deepspherecosmo}: the classification of $720$ partial convergence maps ($1/12 \approx 8\%$ of the sphere) made of $n \approx 10^6$ pixels from two $\Lambda$CDM cosmological models, ($\Omega_m = 0.31$, $\sigma_8 = 0.82)$ and ($\Omega_m = 0.26$, $\sigma_8 = 0.91)$, at a relative noise level of $4$.
 % 60 maps * 12 parts = 720 parts
@@
 %\url{http://island.me.berkeley.edu/ugscnn/data/climate_sphere_l5.zip}
-There is 1,072,805 spherical maps, down-sampled to a level-5 icosahedral grid ($N_{pix} = 10 \cdot 4^l + 2 = 10,242$).
+There is 1,072,805 spherical maps, down-sampled to a level-5 icosahedral grid ($n = 10 \cdot 4^l + 2 = 10,242$ pixels).
 The labels are heavily unbalanced with 0.1\% TC, 2.2\% AR, and 97.7\% background (BG) pixels.
@@
 
-To demonstrate the flexibility of modeling the discretized sphere by a graph, we collected historical measurements from about 10,000 weather stations scattered across the Earth.\footnote{\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
+To demonstrate the flexibility of modeling the discretized sphere by a graph, we collected historical measurements from about $n = 10,000$ weather stations scattered across the Earth.\footnote{\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
 The spherical data is heavily non-uniformly sampled, with a much higher density of weather stations over North America than the Pacific (\figref{examples:ghcn:tmax}).

### 2019-09-24 main.tex
todos

@@
 	\item unify enumerations. I like (i), (ii), etc.
+	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness?
+	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere.
 \end{itemize}
@@
 To construct such a proof, a stronger convergence result is needed, for example uniform convergence (instead of pointwise).
+\todo{Can we intuitively write what pointwise convergence means, and how it is more limited than spectral or uniform convergence?}
 Unfortunately, the graph laplacian does \emph{not} converges uniformly in general \cite{belkin2007convergence}.

### 2019-09-24 main.tex
Updates from Overleaf

--- 2019-09-24 main.tex
@@
 The $\cos$ and $\sin$ of the surface angle forms two normal maps.
-The same is done for the object's convex hull.\footnote{Albeit we didn't observe much improvement by using the convex hull.}
+The same is done for the object's convex hull.
 The maps are discretized using either an equiangular grid \citep{driscoll1994Fouriersphere} with bandwidth $b = 64$ ($N_{pix} = 4 b^2 = 16,384$), or an HEALPix \citep{healpix} grid with $N_{side} = 32$ ($N_{pix} = 12 N_{side}^2 = 12,288$).
@@
 For the same reason, using the more uniform HEALPix discretization or lowering the resolution down to $N_{side} = 8$ didn't impact performance.
-\todo{be sure that it fits with the cosmo conclusion}
 \todo{The same conclusions are drawn from ModelNet 40 (see appendix ??).}
@@
 \subsection{Uneven sampling} \label{sec:exp:ghcn}
-% Weather prediction? But it's not a real task. Rather a demo.
 
@@
 \subsubsection*{Author Contributions}
-Left blank for anonymity reason.
+Left blank for anonymity reason
 % If you'd like to, you may include a section for author contributions as is done
@@
 \subsubsection*{Acknowledgments}
-Left blank for anonymity reason.
+Left blank for anonymity reason
 
@@
 \paragraph{Building the proof.}
-As the sphere is a compact smooth manifold embedded in $\mathbb{R}^3$, we can reuse the second part or their proofs where \eqref{eq:Functional approximation to the Laplace-Beltrami operator} $\rightarrow$ \eqref{eq:laplace-beltrami}.
+As the sphere is a compact smooth manifold embedded in $\mathbb{R}^3$, we can reuse proposition \ref{prop:3}.
 Thus, our strategy to prove Theorem \ref{theo:pointwise convergence for a regular sampling} is to a) show that
@@
 
-	Definitions \ref{def:Heat Kernel Graph Laplacian operator} and \ref{def:Functional approximation to the Laplace-Beltrami operator} end the proof.
+	Definitions \ref{eq:Heat Kernel Graph Laplacian operator} and \ref{eq:Functional approximation to the Laplace-Beltrami operator} end the proof.
 \end{proof}
@@
 
-* Network architecture and training details
+* Network architecture and details
 

### 2019-09-24 main.tex
add links to git and overleaf
brain figure first for better alignment

@@
 
+\begin{description}
+	\item[git] \url{https://github.com/nperraud/deepsphere_v2_paper}
+	\item[overleaf] \url{https://www.overleaf.com/project/5d31d2fbd6859d54cb707212}
+\end{description}
+
 \todo{
@@
 	\subfloat[]{
+		\includegraphics[height=0.20\linewidth,valign=t]{example_brain_meg}
+	} \hspace{0.1em}
+	\subfloat[]{
 		\includegraphics[height=0.20\linewidth,valign=t]{example_cosmo_cmb}
 	} \hfill
-	\subfloat[]{
-		\includegraphics[height=0.20\linewidth,valign=t]{example_brain_meg}
-	} \hspace{0.1em}
 	\subfloat[]{
@@
 		Examples of intrinsically spherical data:
-		(a) the cosmic microwave background (CMB) temperature from \citet{planck2015overview},
-		(b) brain activity recorded through magnetoencephalography (MEG),\protect\footnotemark
+		(a) brain activity recorded through magnetoencephalography (MEG),\protect\footnotemark
+		(b) the cosmic microwave background (CMB) temperature from \citet{planck2015overview},
 		(c) hourly precipitation from a climate simulation \citep{jiang2019sphericalcnn}, %\citep{mudigonda2017climateevents},
 		(d) daily maximum temperature from the Global Historical Climatology Network (GHCN).\protect\footnotemark
-		A rigid full-sphere pixelization is not ideal: the Milky Way's galactic plane masks observations, brain activity is only measured on the scalp, climate scientists desire a variable resolution, and the position of weather stations is arbitrary and changes over time.
+		A rigid full-sphere pixelization is not ideal: brain activity is only measured on the scalp, the Milky Way's galactic plane masks observations, climate scientists desire a variable resolution, and the position of weather stations is arbitrary and changes over time.
 		(e) Graphs can faithfully and efficiently represent sampled spherical data by placing vertices where data has been measured.

### 2019-09-24 main.tex
shortcut macros for S and R

@@
 % Optional math commands from https://github.com/goodfeli/dlbook_notation.
-\input{math_commands.tex}
+%\input{math_commands.tex}
+\usepackage{amsmath,amsfonts,bm}
 
@@
 \usepackage{amssymb}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{prop}{Proposition}
-\newtheorem*{remark}{Remark}
-\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
 
@@
 
+\newtheorem{definition}{Definition}[section]
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{prop}{Proposition}
+\newtheorem*{remark}{Remark}
+\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
 \renewcommand{\b}[1]{{\bm{#1}}}   % bold symbol
+\newcommand{\bO}{\mathcal{O}}
+\newcommand{\R}{\mathbb{R}}
+\renewcommand{\S}{\mathbb{S}}
 
@@
 
-\renewcommand{\figref}[1]{figure~\ref{fig:#1}}
-\renewcommand{\Figref}[1]{Figure~\ref{fig:#1}}
+\newcommand{\figref}[1]{figure~\ref{fig:#1}}
+\newcommand{\Figref}[1]{Figure~\ref{fig:#1}}
 \newcommand{\tabref}[1]{table~\ref{tab:#1}}
 \newcommand{\Tabref}[1]{Table~\ref{tab:#1}}
-\renewcommand{\secref}[1]{section~\ref{sec:#1}}
-\renewcommand{\Secref}[1]{Section~\ref{sec:#1}}
+\newcommand{\secref}[1]{section~\ref{sec:#1}}
+\newcommand{\Secref}[1]{Section~\ref{sec:#1}}
 %\newcommand{\secref}[1]{\S\ref{sec:#1}}
@@
 As the graph convolution acts on a sampled version of the function $\b{f}$ and the rotation on its continuous counterpart $f$, a sampling operator is needed.
-Given a sampling scheme $V=\{x_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere and a function $f : \mathbb S^2 \supset F_V \to \mathbb R$, the sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \b{f}$ is defined as $\b{f}:\ f_i=f(x_i)$, where $F_V$ suitable subspace of $L^2(\mathbb S^2)$ such that $T_V$ is invertible, i.e., we can unambiguously reconstruct the function $f\in F_V$ from its sampled values $\b{f}$.
+Given a sampling scheme $V=\{x_i\in\S^2, i=0, \dots, n\}$ of the sphere and a function $f : \S^2 \supset F_V \to \R$, the sampling operator $T_V: L^2(\S^2) \supset F\to \R^n,\  T_V(f) = \b{f}$ is defined as $\b{f}:\ f_i=f(x_i)$, where $F_V$ suitable subspace of $L^2(\S^2)$ such that $T_V$ is invertible, i.e., we can unambiguously reconstruct the function $f\in F_V$ from its sampled values $\b{f}$.
 The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing (\cite{driscoll1994Fouriersphere}).
@@
 We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme. 
-Given a sampling scheme $V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$.
+Given a sampling scheme $V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\R^3$ containing $\sigma_i$.
 Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
 \begin{theorem}
-	For a sampling $V = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian $\frac{|\mathbb S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\mathbb S^2}$  for $n\to\infty$:
+	For a sampling $V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$  for $n\to\infty$:
 	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} f(x_i) =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.$$
@@
 \end{theorem}
-This theorem implies immediately that $\b{L}$ converges pointwisely toward an operator ($\Delta_{\mathbb S^2}$) commuting with rotation and hence is a strong hint for equivariance.
+This theorem implies immediately that $\b{L}$ converges pointwisely toward an operator ($\Delta_{\S^2}$) commuting with rotation and hence is a strong hint for equivariance.
 Importantly, the proof of Theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix \ref{sec: appendix: proof of theorem} inspires us in the construction of our graph Laplacian.
@@
     \end{equation}
-    of a differentiable function $f: \mathcal M\rightarrow \mathbb R$.
+    of a differentiable function $f: \mathcal M\rightarrow \R$.
 The gradient $\nabla f: \mathcal M \rightarrow T_p\mathcal M$ is a vector field defined on the manifold pointing towards the direction of steepest ascent of $f$, where $T_p\mathcal M$ is the affine space of all vectors tangent to $\mathcal M$ at $p$
@@
 
-% it is known that  (\cite{belkin2005towards}) to prove the convergence of $(\b {L}_n^t \b f) _i$ to $\Delta_{\mathbb S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\mathbb S^2}f(x)$
+% it is known that  (\cite{belkin2005towards}) to prove the convergence of $(\b {L}_n^t \b f) _i$ to $\Delta_{\S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\S^2}f(x)$
 % where $L_n^t$ is defined as follows:
@@
 \begin{prop}\label{prop:1}
-	For an equal area sampling $\{x_i\in\mathbb S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance $\|\cdot\|$ with Lipschitz constant $\mathcal L_f$
+	For an equal area sampling $\{x_i\in\S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance $\|\cdot\|$ with Lipschitz constant $\mathcal L_f$
 	$$
-	\left| \int_{\mathbb S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right|\leq \mathcal L_fd^{(n)}.
+	\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right|\leq \mathcal L_fd^{(n)}.
 	$$
-	Furthermore, for all $y\in\mathbb S^2$ the Heat Kernel Graph Laplacian operator $L^t_n$ converges pointwise to the functional approximation of the Laplace Beltrami operator $L^t$
+	Furthermore, for all $y\in\S^2$ the Heat Kernel Graph Laplacian operator $L^t_n$ converges pointwise to the functional approximation of the Laplace Beltrami operator $L^t$
 	$$ L_n^tf(y)\xrightarrow{n\to\infty} L^tf(y).$$
@@
 
-	Let us assume that the function $f:\mathbb R^3\rightarrow \mathbb R$ is Lipschitz with Lipschitz constant $\mathcal L_f$, we have
+	Let us assume that the function $f:\R^3\rightarrow \R$ is Lipschitz with Lipschitz constant $\mathcal L_f$, we have
 
@@
 	So, by triangular inequality and by summing all the contributions of all the $n$ patches
-	$$\left| \int_{\mathbb S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right| \leq \sum_i \left| \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right|\leq n  \mathcal L_fd^{(n)}\frac{1}{n} = \mathcal L_fd^{(n)}$$
+	$$\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right| \leq \sum_i \left| \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right|\leq n  \mathcal L_fd^{(n)}\frac{1}{n} = \mathcal L_fd^{(n)}$$
 	Thanks to this result, we have the following two pointwise convergences
 
-	$$\forall f \text{ Lipschiz,}\quad \forall y\in\mathbb S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}\rightarrow \int e^{-\frac{||x-y||^2}{4t}}d\mu(x)$$
-	$$\forall f \text{ Lipschiz,}\quad \forall y\in\mathbb S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}f(x_i)\rightarrow \int e^{-\frac{||x-y||^2}{4t}}f(x)d\mu(x)$$
+	$$\forall f \text{ Lipschiz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}\rightarrow \int e^{-\frac{||x-y||^2}{4t}}d\mu(x)$$
+	$$\forall f \text{ Lipschiz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}f(x_i)\rightarrow \int e^{-\frac{||x-y||^2}{4t}}f(x)d\mu(x)$$
 
@@
 \begin{prop}\label{prop:2}
-	Given a sampling regular enough, i.e., for which we assume $A_i=A_j \ \forall i,j\text{ and }d^{(n)}\leq \frac{C}{\sqrt{n}}$, for a fixed $t>0$, a fixed Lipschitz function $f$ and a fixed point $y\in\mathbb S^2$ there exists a sequence $t_n = n^\beta, \beta<0$ such that
+	Given a sampling regular enough, i.e., for which we assume $A_i=A_j \ \forall i,j\text{ and }d^{(n)}\leq \frac{C}{\sqrt{n}}$, for a fixed $t>0$, a fixed Lipschitz function $f$ and a fixed point $y\in\S^2$ there exists a sequence $t_n = n^\beta, \beta<0$ such that
 $$
-\forall f \text{ Lipschitz, } \forall x\in\mathbb S^2 \quad \left|\frac{1}{4\pi t_n^2}\left(L_n^{t_n}f(x) - L^{t_n}f(x)\right)\right|\xrightarrow{n\to \infty}0.
+\forall f \text{ Lipschitz, } \forall x\in\S^2 \quad \left|\frac{1}{4\pi t_n^2}\left(L_n^{t_n}f(x) - L^{t_n}f(x)\right)\right|\xrightarrow{n\to \infty}0.
 $$
@@
 \begin{align*}
-	||L_n^tf-L^tf||_\infty &= \max _{y\in \mathbb S^2} \left|L_n^tf(y)-L^tf(y)\right|\\
-	&= \max _{y\in \mathbb S^2} \left| \frac{1}{n} \sum_{i=1}^n \phi^t(x_i; y)- \int_{\mathbb S^2} \phi^t(x;y)d\mu(x) \right|\\
-	&\leq \max _{y\in \mathbb S^2}  \sum_{i=1}^n   \left| \frac{1}{n}  \phi^t(x_i; y)- \int_{\sigma_i} \phi^t(x;y)d\mu(x) \right|\\
-	&\leq  \max _{y\in \mathbb S^2} \left[\mathcal L_{\phi^t_y}d^{(n)} \right]\\
+	||L_n^tf-L^tf||_\infty &= \max _{y\in \S^2} \left|L_n^tf(y)-L^tf(y)\right|\\
+	&= \max _{y\in \S^2} \left| \frac{1}{n} \sum_{i=1}^n \phi^t(x_i; y)- \int_{\S^2} \phi^t(x;y)d\mu(x) \right|\\
+	&\leq \max _{y\in \S^2}  \sum_{i=1}^n   \left| \frac{1}{n}  \phi^t(x_i; y)- \int_{\sigma_i} \phi^t(x;y)d\mu(x) \right|\\
+	&\leq  \max _{y\in \S^2} \left[\mathcal L_{\phi^t_y}d^{(n)} \right]\\
 \end{align*}
@@
 
-$$||L_n^tf-L^tf||_\infty  \leq  \max _{y\in \mathbb S^2} \left[ \mathcal L_{\phi^t_y} \frac{C}{\sqrt{n}} \right]$$
+$$||L_n^tf-L^tf||_\infty  \leq  \max _{y\in \S^2} \left[ \mathcal L_{\phi^t_y} \frac{C}{\sqrt{n}} \right]$$
 
@@
 $$\begin{aligned}
-	\max _{y\in \mathbb S^2} \left[  \mathcal L_{\phi^t_y} \frac{C}{\sqrt{n}} \right]
+	\max _{y\in \S^2} \left[  \mathcal L_{\phi^t_y} \frac{C}{\sqrt{n}} \right]
 	&\leq  \frac{C}{\sqrt{n}} \left( (2et)^{-\frac{1}{2}} \norm{f}_\infty + \mathcal L_f \right)\\
@@
 \begin{proof}[Proof of Theorem \ref{theo:pointwise convergence for a regular sampling}]
-	Thanks to Proposition \ref{prop:2} and Proposition \ref{prop:3}	we conclude that $\forall y\in\mathbb S^2 $
-	$$\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) =  \lim_{n\to\infty}\frac{1}{4\pi t_n^2} L^{t_n}f(y) = \frac{1}{|\mathbb S^2|}\triangle_{\mathbb S^2}f(y) $$
+	Thanks to Proposition \ref{prop:2} and Proposition \ref{prop:3}	we conclude that $\forall y\in\S^2 $
+	$$\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) =  \lim_{n\to\infty}\frac{1}{4\pi t_n^2} L^{t_n}f(y) = \frac{1}{|\S^2|}\triangle_{\S^2}f(y) $$
 \end{proof}

### 2019-09-25 main.tex
method

@@
 \renewcommand{\S}{\mathbb{S}}
+\newcommand{\G}{\mathcal{G}}  % graph
+\newcommand{\V}{\mathcal{V}}  % vertex set
+\newcommand{\E}{\mathcal{E}}  % edge set
+\DeclareMathOperator*{\diag}{diag}
 
@@
 	\item result tables: only what supports the main message in the text, everything we have in the appendix
-	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions.
+	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
+	\item check English vs American English
 	\item unify enumerations. I like (i), (ii), etc.
@@
 	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere.
+	\item figure placements
+	\item add figure with optimal kernel widths
+	\item do the experiments on the icosahedral grid with the pooling as defined in the paper
+	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
+	\item check that NN architectures and hyper-params are correctly reported
 \end{itemize}
@@
 
-The gist of the method is to define the spherical convolution using a graph, and the down-sampling operation using a hierarchical pixelisation of the sphere.
-
-\todo{
-	* discuss discretizations (equiangular, HEALPix, icosahedral sphere) -> more uniform is better \\
-	* no uniform sampling: tradeoffs have to be made \\
-	* CNN vs FCN discussion (GAP for invariance) \\
-}
-
-* HEALPix: improvement from DeepSphere v1 \cite{perraudin2019deepspherecosmo} \\
-* equiangular: Renata \& Pascal \\
-
-% \cite{khasanova2017sphericalcnn} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling.
-They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes.
-In other words, they solve the minimization problem
-% \begin{equation} \label{eq:minimization frossard}
-% 	\min_{W\in\mathcal G} \left|\mathcal{F}\left(\mathbf{y}\left(v_{ e}\right)\right)-\mathcal{F}\left(\mathbf{y}\left(v_{ i}\right)\right)\right|
-% \end{equation}
-% for the adjacency matrix $W$, where $\mathbf y(v_i)$ is the image of the object on the sphere centered on the vertex $v_i$, and $\mathcal F (\mathbf y(v_e))$ is the response of the filter at the vertex $v_e$ that lies at the same longitude of the vertex $v_i$ but on the equator.
-In their work they prove that the optimal weights solving the minimization problem (\ref{eq:minimization frossard}) are given by weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
-% \begin{equation} \label{eq:frossard weights}
-% 	w_{ij} = \frac{1}{\norm{x_i-x_j}}
-% \end{equation}
-
 \begin{figure}
@@
 		Dense tasks (when the output lives on the sphere, like segmentation) are rotation equivariant.
+		\todo{Shall we keep this figure? It's very nice, but we could save space. ML people probably have this in mind.}
 	}
@@
 \end{figure}
+
+DeepSphere leverages graph convolutions to achieve the following properties: (i) computational efficiency, (ii) sampling flexibility, and (iii) rotation equivariance (\secref{equivariance}).
+An example architecture is shown in \figref{architecture}.
+The main idea is to model the discretized sphere as a graph of connected pixels: the length of the shortest path between two pixels is an approximation of the geodesic distance between them.
+We use the graph CNN formulation introduced in \citep{defferrard2016graphnn}, and a pooling strategy that exploits hierarchical pixelizations of the sphere.
+
+\paragraph{Sampling.}
+Given a sampling scheme $\V = \{x_i \in \S^2\}_{i=1}^n$, a function $f : \S^2 \supset F_\V \to \R$ is sampled as $T_\V(f) = \b{f}$ by the sampling operator $T_\V: L^2(\S^2) \supset F_\V \to \R^n$ defined as $\b{f}: f_i=f(x_i)$, where $F_\V$ will be specified in \secref{equivariance}.
+As there is no analogue of uniform sampling on the sphere, many schemes have been proposed with different tradeoffs.
+In this work, depending on the considered application, we will use the equiangular \citep{driscoll1994Fouriersphere}, HEALPix \citep{gorski2005healpix}, and icosahedral \citep{baumgardner1985icosahedral} grids.
+
+\paragraph{Graph.}
+From $\V$, we construct a weighted undirected graph $\G = (\V, w)$, where the elements of $\V$ are the vertices and the weight $w_{ij} = w_{ji}$ is a similarity measure between vertices $x_i$ and $x_j$.
+The combinatorial graph Laplacian $\b{L} \in \R^{n \times n}$ is defined as $\b{L} = \b{D} - \b{A}$, where $\b{A} = (w_{ij})$ is the weighted adjacency matrix, $\b{D} = (d_{ii})$ is the diagonal degree matrix, and $d_{ii} = \sum_j w_{ij}$ is the weighted degree of vertex $x_i$.
+%$\b{D} = \diag(\b{A} \b{1})$
+Given a sampling scheme $\V$, usually fixed by the application or the available measurements, the only freedom in constructing $\G$ is in setting $w$.
+\Secref{equivariance} shows how to set $w$ to minimize the equivariance error.
+%building a good graph amounts to set a good $w$.
+
+\paragraph{Convolution.}
+On Euclidean domains, convolutions are efficiently implemented by sliding a window in the signal domain.
+On the sphere however, there is no straightforward way to implement a convolution in the signal domain due to non-uniform samplings.
+Convolutions are most often performed in the spectral domain through a spherical harmonic transform (SHT).
+That is the approach taken by \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn}, which has a computational cost of $\bO(n^{3/2})$ on isolatitude pixelizations (such as the HEALPix and equiangular grids) and $\bO(n^2)$ in general.
+On the other hand, following \citet{defferrard2016graphnn}, graph convolutions can be defined as
+\begin{equation} \label{eqn:graph_conv}
+	h(\b{L}) \b{f} = \left(\sum_{i=0}^K \alpha_i \b{L}^i\right) \b{f},
+\end{equation}
+where $K$ is the polynomial order (which corresponds to the filter's size) and $\alpha_i$ are the coefficients to be optimized during training.
+Those convolutions are used by \citet{khasanova2017sphericalcnn} and \citet{perraudin2019deepspherecosmo} and cost $\bO(n)$ operations through a recursive application of $\b{L}$.\footnote{As long as the graph is sparsified such that the number of edges, i.e., the number of non-zeros in $\b{A}$, is proportional to the number of vertices $n$.
+This can always be done as most weights are very small.}
+
+\paragraph{Pooling.}
+Down- and up-sampling is natural for hierarchical pixelizations,\footnote{The equiangular, HEALPix, and icosahedral schemes are of this kind.} where each subdivision divides a pixel in (an equal number of) child sub-pixels.
+To pool (down-sample), the data supported on the sub-pixels is summarized by a permutation invariant function such as the maximum or the average.
+To unpool (up-sample), the data supported on a pixel is copied to all its sub-pixels.
+% Frédérick: Dans le cas de l'icosahedron, le pooling n'est pas invariant à la permutation (on prend la valeur du 1er pixel, sans regarder les autres)
+% Frédérick: Et le unpooling est correct uniquement dans le cas de l'average pooling (mais on fait pas de max pooling dans ce cas).
+Encore une fois, l'icosahedron est inspiré de Jiang, où 1 seul sub-pixel prend la valeur du pixel, le reste est rempli avec des '1'
+
+\paragraph{Architecture.}
+All our NNs are fully convolutional, and employ a global average pooling (GAP) for rotation invariant tasks.
+Graph convolutional layers are always followed by batch normalization and ReLU activation, except in the last layer.
+Note that batch normalization and activation act on the elements of $\b{f}$ independently, and hence don't depend on the domain of $f$.
+%We denote graph convolutional layers with $C$ output channels as $GC_C$ and fully connected layers with $C$ output neurons as $FC_C$.
+%Those linear layers are always followed by batch normalization and ReLU activation, except in the last layer.
+%softmax normalization as $SM$
+%Pooling and unpooling by a factor $F$ are denoted as $P_F$ and $P^{-1}_F$, global average pooling as $GAP$.
 
@@
 % \nati{I do not think we should have a notation section, but should somehow write this somewhere...}
+% mdeff: I think this convention is clear enough when reading.
 
@@
 
+While the graph framework offers great flexibility, its ability to faithfully represent the underlying sphere --- for graph convolutions to be rotation equivariant --- highly depends on the sampling locations and the graph construction.
+
 \subsection{Problem formulation}
-% The plan for this section
 % 0.1 Explain the sampling problem
-As the graph convolution acts on a sampled version of the function $\b{f}$ and the rotation on its continuous counterpart $f$, a sampling operator is needed.
-Given a sampling scheme $V=\{x_i\in\S^2, i=0, \dots, n\}$ of the sphere and a function $f : \S^2 \supset F_V \to \R$, the sampling operator $T_V: L^2(\S^2) \supset F\to \R^n,\  T_V(f) = \b{f}$ is defined as $\b{f}:\ f_i=f(x_i)$, where $F_V$ suitable subspace of $L^2(\S^2)$ such that $T_V$ is invertible, i.e., we can unambiguously reconstruct the function $f\in F_V$ from its sampled values $\b{f}$.
-The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing (\cite{driscoll1994Fouriersphere}).
-For most sampling schemes, it is not known if $F_V$ exist and hence if $T_V$ is invertible.
-A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds, and thus we have a closed form of $T_V^{-1}$ is known.
-% \cite{driscoll1994Fouriersphere}
-For sampling schemes where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\bf{f}$, thus approximating $T_V^{-1}$.
-For all theoretical consideration, we assume that $F_V$ exists and $f \in F_V$.
+%As the graph convolution acts on a sampled version of the function $\b{f}$ and the rotation on its continuous counterpart $f$, a sampling operator is needed.
+
+We require $F_\V$ to be a suitable subspace of $L^2(\S^2)$ such that $T_\V$ is invertible, i.e., the function $f \in F_\V$ can be unambiguously reconstructed from its sampled values $\b{f}$.
+The existence of such a subspace depends on the sampling scheme $\V$, and its characterization is a common problem in signal processing \citep{driscoll1994Fouriersphere}.
+For most sampling schemes, it is not known if $F_\V$ exists and hence if $T_\V$ is invertible.
+A special case is the equiangular sampling scheme where a sampling theorem holds, and thus a closed form of $T_\V^{-1}$ is known. % \cite{driscoll1994Fouriersphere}
+For sampling schemes where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\b{f}$, thus approximating $T_\V^{-1}$.
+For all theoretical considerations, we assume that $F_\V$ exists and $f \in F_\V$.
 
@@
 By definition, our (spherical) graph convolution is rotation equivariant, if and only if, it commutes with the rotation operator defined as $R(g), g\in SO(3)$: $R(g) f(x) = f\left(g^{-1} x \right)$.
-In the context of this work, graph convolution is performed by recursive applications of the graph Laplacian, i.e: $h(\b{L}) \b{f} = \left(\sum_{i=0}^K \alpha_i \b{L}^i\right) \b{f}$\nati{Put this equation somewhere else?}.
+In the context of this work, graph convolution is performed by recursive applications of the graph Laplacian (\eqnref{graph_conv}).
 Hence, if $\b{L}$ commutes with the rotation operator, then, by recursion, it will also commute with the convolution $h(\b{L})$.
@@
 \begin{equation} \label{eq:equivariance}
-	\b{R}_V(g) \b{L} \b{f} = \b{L} \b{R}_V(g) \b{f} \hspace{1cm} \forall f\in F_V \text{ and } \forall g\in SO(3),
+	\b{R}_\V(g) \b{L} \b{f} = \b{L} \b{R}_\V(g) \b{f} \hspace{1cm} \forall f\in F_\V \text{ and } \forall g\in SO(3),
 \end{equation}
-where $\b{R}_V(g) = T_V R(g) T_V^{-1}$. For practical a evaluation of the equivariance, we define the \textit{normalized equivariance error} for a signal $\b{f}$, and a  rotation $g$ as:
+where $\b{R}_\V(g) = T_\V R(g) T_\V^{-1}$. For practical a evaluation of the equivariance, we define the \textit{normalized equivariance error} for a signal $\b{f}$, and a  rotation $g$ as:
 \begin{equation} \label{eq:equivariance error}
-	E_{\b{L}}(\b{f}, g) = \left(\frac{ \norm {\b{R}_V(g) \b{L} \b{f} - \b{L} \b{R}_V(g) \b{f}} }{\norm {\b{L} \b{f}}}\right)^2,
+	E_{\b{L}}(\b{f}, g) = \left(\frac{ \norm {\b{R}_\V(g) \b{L} \b{f} - \b{L} \b{R}_\V(g) \b{f}} }{\norm {\b{L} \b{f}}}\right)^2,
 \end{equation}
-More generally for a class of signal $f \in C \subset F_V$, the \textit{mean equivariance error}
+More generally for a class of signal $f \in C \subset F_\V$, the \textit{mean equivariance error}
 \begin{equation} \label{eq:mean equivariance error}
@@
 We calculated numerically the equivariance error (\ref{eq:mean equivariance error}) by generating $N$ monochromatic signals and $M$ random rotations for each signal.
-The colors that were used were chosen in the range $(0,\  3N_{side}-1)$ to allow for an almost perfect synthesis of the rotated signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_V$ \citep{healpix_primer}.
+The colors that were used were chosen in the range $(0,\  3N_{side}-1)$ to allow for an almost perfect synthesis of the rotated signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ \citep{gorski1999healpixprimer}.
 
@@
 		\includegraphics[height=7em]{lamp_000018_sphere_nobar}
-		\caption{Example of a 3D object represented as a spherical depth map.}
+		\caption{Example of a 3D object from SHREC'17 represented as a spherical depth map.}
 		\label{fig:depthmap}
@@
 The same is done for the object's convex hull.\footnote{Albeit we didn't observe much improvement by using the convex hull.}
-The maps are discretized using either an equiangular grid \citep{driscoll1994Fouriersphere} with bandwidth $b = 64$ ($n = 4 b^2 = 16,384$ pixels), or an HEALPix \citep{healpix} grid with $N_{side} = 32$ ($n = 12 N_{side}^2 = 12,288$ pixels).
+The maps are discretized using either an equiangular grid with bandwidth $b = 64$ ($n = 4 b^2 = 16,384$ pixels) or an HEALPix grid with $N_{side} = 32$ ($n = 12 N_{side}^2 = 12,288$ pixels).
 
@@
 Results from \citet{mudigonda2017climateevents} cannot be directly compared as they don't use the same input channels.
-DeepSphere achieves state-of-the-art performance, suggesting again that anisotropic filters are not necessary.
+DeepSphere achieves state-of-the-art performance, suggesting again that anisotropic filters are unnecessary.
 
@@
 The proof of theorem \ref{theo:pointwise convergence for a regular sampling} is inspired from the work of \cite{belkin2005towards}. As a result, we start by restating some of their results.
-Given a sampling $V = \{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_Vf=\b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
+Given a sampling $V = \{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_\V f = \b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
 The proof is constructed by leveraging 3 different operators:
@@
 	\end{equation}
-	Note that we have the following relation $\b{L}_n^t \b{f} = T_V L_n^t f$.
+	Note that we have the following relation $\b{L}_n^t \b{f} = T_\V L_n^t f$.
 	\item The functional approximation to the Laplace-Beltrami operator is a functional $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined  as
@@
 
-\subsubsection*{HEALPix architecure}
+\subsubsection*{HEALPix architecture}
 
@@
 \begin{dmath}
-    [GC_{50}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{1}\, +\, BN\, +\, ReLU]
+    [GC_{50}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{1}]
 \end{dmath}

### 2019-09-25 main.tex
trim whitespace
add optimal kernel width figure

@@
 	\item figure placements
-	\item add figure with optimal kernel widths
 	\item do the experiments on the icosahedral grid with the pooling as defined in the paper
 	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
+	\item update pygsp and merge sphere branch
 	\item check that NN architectures and hyper-params are correctly reported
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{figure_architecture_v3}
+	\includegraphics[width=\linewidth]{figure_architecture_v3}
 	\caption{Example architecture from \cite{perraudin2019deepspherecosmo}.
@@
 \subsection{Finding the optimal set of weights}
-% !) summary the work of Khasanova -> No! to be put in section 2) Method
+
+% 1) summary the work of Khasanova
 \cite{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ explicitly intended to work with the equiangular sampling.
@@
 \end{equation}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.4\linewidth]{kernel_widths}
+	\caption{
+		Optimal kernel widths for various resolutions of the HEALPix grid.
+	}
+	\label{fig:kernel_widths}
+\end{figure}
 
@@
 In practice most of the weights are very close to $0$ and hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
-Given $k$, we find the optimal $t$, a grid search is performed using \eqref{eq:mean equivariance error}.
+Given $k$, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
+\Figref{kernel_widths} shows the optimal kernel widths found for various resolutions of the HEALPix grid.
 

### 2019-09-25 figures/kernel_widths.py

@@ -1,0 +1,60 @@
+#!/usr/bin/env python3
+
+from os import path
+
+from matplotlib import pyplot as plt
+
+#plt.rc('font', family='Latin Modern Roman')
+#plt.rc('text', usetex=True)
+#plt.rc('text.latex', preamble=r'\usepackage{lmodern}')
+
+kernel_width_optimal = {
+    8: {
+        32:   0.02500,
+        64:   0.01228,
+        128:  0.00614,
+        256:  0.00307,
+        512:  0.00154,
+        1024: 0.00077,
+    },
+    20: {
+        32:   0.03185,
+        64:   0.01564,
+        128:  0.00782,
+        256:  0.00391,
+        512:  0.00196,
+        1024: 0.00098,
+    },
+    40: {
+        32:   0.042432,
+        64:   0.021354,
+        128:  0.010595,
+        256:  0.005551,  # seems a bit off
+        #512:  0.003028,  # seems buggy
+        512:  0.005551 / 2,  # extrapolated
+        1024: 0.005551 / 4,  # extrapolated
+    },
+    60: {
+        32:   0.051720,
+        64:   0.025403,
+        128:  0.012695,
+        256:  0.006351,
+        #512:  0.002493,  # seems buggy
+        512:  0.006351 / 2,  # extrapolated
+        1024: 0.006351 / 4,  # extrapolated
+    },
+}
+
+fig, ax = plt.subplots(figsize=(5, 3))
+for neighbors, optimums in sorted(kernel_width_optimal.items(), reverse=True):
+    nside = list(optimums.keys())
+    width = list(optimums.values())
+    ax.loglog(nside, width, '.-', label=f'$k={neighbors}$ neighbors')
+ax.legend(loc='upper right')
+ax.set_xlabel('$N_{side}$ ($n = 12 N_{side}^2$ pixels)')
+ax.set_ylabel('kernel width $t$')
+#ax.set_title('optimal kernel widths')
+
+fig.tight_layout()
+filename = path.splitext(path.basename(__file__))[0] + '.pdf'
+fig.savefig(filename)

### 2019-09-25 main.tex
experiments: graphs, NN architectures, hyper-params, and cleanup of SHREC'17 and ModelNet40 appendix

@@
 	\item check that NN architectures and hyper-params are correctly reported
+	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space.
+	\item shall we still site adam and batch norm?
+	\item check results on ModelNet40
 \end{itemize}
@@
 \end{equation}
-where $K$ is the polynomial order (which corresponds to the filter's size) and $\alpha_i$ are the coefficients to be optimized during training.
+where $K$ is the polynomial order (which corresponds to the filter's size) and $\alpha_i$ are the coefficients to be optimized during training.\footnote{In practice, training with Chebyshev polynomials (instead of monomials) is slightly more stable.
+We believe it to be due to their orthogonality and uniformity.}
 Those convolutions are used by \citet{khasanova2017sphericalcnn} and \citet{perraudin2019deepspherecosmo} and cost $\bO(n)$ operations through a recursive application of $\b{L}$.\footnote{As long as the graph is sparsified such that the number of edges, i.e., the number of non-zeros in $\b{A}$, is proportional to the number of vertices $n$.
@@
 All our NNs are fully convolutional, and employ a global average pooling (GAP) for rotation invariant tasks.
-Graph convolutional layers are always followed by batch normalization and ReLU activation, except in the last layer.
+Graph convolutional layers are always followed by batch normalization \citep{ioffe2015batchnorm} and ReLU activation, except in the last layer.
 Note that batch normalization and activation act on the elements of $\b{f}$ independently, and hence don't depend on the domain of $f$.
@@
 
-\subsection{Finding the optimal set of weights}
+\subsection{Finding the optimal set of weights}  \label{sec:optimal}
 
@@
 Their approach leads to weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
-\begin{equation} \label{eq:frossard weights}
+\begin{equation} \label{eqn:weights:khasanova}
 	w_{ij} = \frac{1}{\norm{x_i-x_j}}
@@
 In this case the weighting scheme is full (every node is connected to every node) and is based on the exponential kernel:
-\begin{equation} \label{eq:belkin_weights}
+\begin{equation} \label{eqn:weights:belkin}
 w_{ij} = e^{-\frac{1}{4t} \norm{x_i-x_j}^2}
@@
 
-\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section), loss, hyper-parameters. Or leave in appendix.}
+The equiangular graph is built with \eqnref{weights:khasanova} and $k = 4$ neighbors \citep[following][]{khasanova2017sphericalcnn}.
+\todo{The HEALPix graph is built with \eqnref{weights:belkin}, $k = ?$ and the corresponding optimal kernel width $t = ?$.}
+\todo{Following Esteves or Cohen?}
+The NN is made of $5$ graph convolutional layers, each followed by a \todo{max?} pooling layer down-sampling by $4$.
+A GAP and a fully connected layer with softmax follow.
+The Chebyshev polynomials are all of order $K=4$ and the number of channels per layer is $16, 32, 64, 128, 256$, respectively.
+Following \citet{esteves2018sphericalcnn}, the cross-entropy plus a triplet loss is optimized with Adam \citep{kingma2014adam} for 30 epochs on the dataset augmented by 3 random translations.
+The learning rate is $5 \cdot 10^{-2}$ and the batch size is 32.
 
@@
 		% $SO(3)$ vs $S^2$ vs graph
-		\citet{cohen2018sphericalcnn} ($b=128$) & 78.9 & 67.6 & 1400\,k & 38.0\,ms & 50\,h \\
-		\citet{cohen2018sphericalcnn} (simplified,\protect\footnotemark $b=64$) & 78.6 & 66.5 & 400\,k & 12.0\,ms & 32\,h \\
+		\citet{cohen2018sphericalcnn} ($b=128$) & - & 67.6 & 1400\,k & 38.0\,ms & 50\,h \\
+		\citet{cohen2018sphericalcnn} (simplified,\protect\footnotemark $b=64$) & 78.9 & 66.5 & 400\,k & 12.0\,ms & 32\,h \\
 		\citet{esteves2018sphericalcnn} ($b=64$) & 79.4 & 68.5 & 500\,k & 9.8\,ms & 3\,h \\
@@
 As that is complicated to setup, prediction methods are typically benchmarked on the classification of spherical maps into cosmological model classes \citep{schmelze2017cosmologicalmodel}.
-We used the same task, data, and setup as \citet{perraudin2019deepspherecosmo}: the classification of $720$ partial convergence maps ($1/12 \approx 8\%$ of the sphere) made of $n \approx 10^6$ pixels from two $\Lambda$CDM cosmological models, ($\Omega_m = 0.31$, $\sigma_8 = 0.82)$ and ($\Omega_m = 0.26$, $\sigma_8 = 0.91)$, at a relative noise level of $4$.
+We used the same task, data, and setup as \citet{perraudin2019deepspherecosmo}: the classification of $720$ partial convergence maps made of $n \approx 10^6$ pixels ($1/12 \approx 8\%$ of a sphere at $N_{side} = 1024$) from two $\Lambda$CDM cosmological models, ($\Omega_m = 0.31$, $\sigma_8 = 0.82)$ and ($\Omega_m = 0.26$, $\sigma_8 = 0.91)$, at a relative noise level of $4$.
 % 60 maps * 12 parts = 720 parts
@@
 
-\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section), loss, hyper-parameters. Or leave in appendix.}
+Graphs are built with \eqnref{weights:belkin}, $k = 8, 20, 40$ and the corresponding optimal kernel widths $t = ?, ?, ?$.
+Following \citet{perraudin2019deepspherecosmo}, the NN is made of $5$ graph convolutional layers, each followed by a \todo{max?} pooling layer down-sampling by $4$.
+A GAP and a fully connected layer with softmax follow.
+The Chebyshev polynomials are all of order $K=5$ and the number of channels per layer is $16, 32, 64, 64, 64$, respectively.
+The cross-entropy loss is optimized with Adam for 80 epochs.
+The learning rate is $2 \cdot 10^{-4} \cdot 0.999^{\textrm{step}}$ and the batch size is 8.
 
@@
 
-\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section), loss, hyper-parameters. Or leave in appendix.}
+The graph is built with \eqnref{weights:belkin}, \todo{$k = ?$} and the \todo{corresponding optimal kernel widths $t = ?, ?, ?$}.
+Following \citet{jiang2019sphericalcnn}, the NN is an encoder-decoder with skip connections.
+Details in \secref{climate:appendix}.
+%The encoder is made of $5$ graph convolutional layers, each followed by a \todo{pick-one?} pooling layer down-sampling by $4$.
+%the number of channels per layer is $16, 32, 64, 64, 64$, respectively.
+%The decoder is made of
+The Chebyshev polynomials are all of \todo{order $K=5$}.
+The cross-entropy loss (weighted or non-weighted) is optimized with Adam for 30 epochs.
+The learning rate is $1 \cdot 10{-3}$ and the batch size is 64.
 
@@
 Potential explanations are (i) that their icosahedral projection introduces harmful distortions, or (ii) that a larger architecture can compensate for the lack of generality. % powerfulness?
-We indeed observed that more feature maps and depth led to higher performance (\ref{sec:climate:appendix}).
+We indeed observed that more feature maps and depth led to higher performance (\secref{climate:appendix}).
 
@@
 
-\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section), loss, hyper-parameters. Or leave in appendix.}
+The graph is built with \eqnref{weights:khasanova} and \todo{$k = ?$} neighbors.
+The kernel width $t$ is set as the average of the distances.
+The equivariance property of the resulting graph has not been tested, and we don't expect it to be good due to the heavily non-uniform sampling.
+The NN is made of $3$ graph convolutional layers.
+The Chebyshev polynomials are all of order $K=0$ or $4$ and the number of channels per layer is $50, 100, 100$, respectively.
+For the global regression, a GAP and a fully connected layer follow.
+For the dense regression, a graph convolutional layer follows instead.
+The MSE loss is optimized with RMSprop for 250 epochs.
+The learning rate is $1 \cdot 10^{-3}$ and the batch size is 64.
 
@@
 
-* Network architecture and training details
-
-\subsection{3D object Recognition}
-\subsubsection*{Detailed results}
-\paragraph*{SHREC17}
+\subsection{3D objects recognition}
+
+\Tabref{shrec17_retrieval} shows the results obtained from the competition's official evaluation script.
+\Tabref{modelnet40} shows results on ModelNet40.
 
@@
     \centering
-    \begin{tabular}{l|c c r r}
-        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{2}{c}{speed}\\
-        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
-        \multicolumn{1}{l}{Method} & Accuracy & F1-score & inference & training \\ \hline
-        Cohen \emph{s2cnn} & - & - & 38ms & 50h\\
-        % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
-        Esteves \emph{sphericalcnn} & 79.18 & 79.36 & 9.8ms & 2h52\\ \hline
-        DeepSphere \emph{Equiangular} & 79.25 & 79.36 & 0.9ms & 47m \\
-        DeepSphere \emph{HEALPix} & 80.42 & 80.65 & 0.9ms & 46m\\
-        % DeepSphere \emph{Improved HEALPix} & 80.76 & & &
+	\scriptsize
+    \begin{tabular}{l cccc cccc}
+    & \multicolumn{4}{c}{micro (label average)} & \multicolumn{4}{c}{macro (instance average)} \\
+	\cmidrule(lr){2-5} \cmidrule(lr){6-9}
+    & P@N & R@N & F1@N & mAP & P@N & R@N & F1@N & mAP \\
+	\toprule
+    \citet{cohen2018sphericalcnn} ($b=128$) & 0.701 & 0.711 & 0.699 & 0.676 & - & - & - & - \\
+    \citet{cohen2018sphericalcnn} (simplified, $b=64$) & 0.704 & 0.701 & 0.696 & 0.665 & 0.430 & 0.480 & 0.429 & 0.385 \\
+    \citet{esteves2018sphericalcnn} ($b=64$) & 0.717 & 0.737 & - & 0.685 & 0.450 & 0.550 & - & 0.444 \\
+    DeepSphere (equiangular $b=64$) & 0.709 & 0.700 & 0.698 & 0.665 & 0.439 & 0.489 & 0.439 & 0.403 \\
+    DeepSphere (HEALPix $N_{side}=32$) & 0.725 & 0.717 & 0.715 & 0.686 & 0.475 & 0.508 & 0.468 & 0.428\\
+	\bottomrule
     \end{tabular}
-    \caption{Performance of different models}
-    \label{tab:SHREC17_class}
+    \caption{Official metrics from the SHREC'17 object retrieval competition.}
+    \label{tab:shrec17_retrieval}
 \end{table}
@@
     \centering
-    \begin{tabular}{l|c c c c|c c c c}
-     & \multicolumn{4}{c|}{micro (label average)} & \multicolumn{4}{c}{macro (instance average)} \\
-    Method & P@N & R@N & F1@N & mAP & P@N & R@N & F1@N & mAP \\ \hline
-    Cohen \emph{s2cnn} & 0.701 & 0.711 & 0.699 & 0.676 & - & - & - & - \\
-    % Cohen \emph{s2cnn\_simple} & 0.704 & 0.701 & 0.696 & 0.665 & 0.430 & 0.480 & 0.429 & 0.385\\
-    Esteves \emph{sphericalcnn} & 0.717 & 0.737 & - & 0.685 & 0.450 & 0.550 & - & 0.444\\ \hline
-    DeepSphere \emph{Equiangular} & 0.709 & 0.700 & 0.698 & 0.665 & 0.439 & 0.489 & 0.439 & 0.403 \\
-    DeepSphere \emph{HEALPix} & 0.725 & 0.717 & 0.715 & 0.686 & 0.475 & 0.508 & 0.468 & 0.428\\
-    % DeepSphere \emph{Improved HEALPix} & & & & &
+    \begin{tabular}{l cccc}
+	\toprule
+    & no/no & z/z & SO3/SO3 & z/SO3 \\
+	\midrule
+	\citet{cohen2018sphericalcnn} & 85.0 & - & - & - \\
+	\citet{jiang2019sphericalcnn} & 90.5 & - & - & - \\
+	\citet{esteves2018sphericalcnn} & - & 88.9 & 86.9 & 76.7 \\
+	%Esteves \emph{MVCNN} & 94.69 & - & - & - \\
+	DeepSphere & 87.8 & 86.8 & 86.7 & 76.9 \\
+	\bottomrule
     \end{tabular}
-    \caption{Performance of different models over SHREC17 perturbed dataset as a retrieval task, using the official script of the competition.}
-    \label{tab:SHREC17_retriev}
+    \caption{
+		Accuracy results on ModelNet40.
+		``no'' denotes no augmentation, ``z'' is augmented with rotations around the Z-axis, and ``SO3'' with ZYZ rotations.
+		\todo{The first is training time augmentation, the second test time augmentation.}
+	}
+    \label{tab:modelnet40}
 \end{table}
 
-\paragraph*{ModelNet 40}
-
-\begin{table}
-    \centering
-    \begin{tabular}{c|cccc}
-         &  x/x & z/z & SO3/SO3 & z/SO3 \\ \hline
-Cohen & 85.0 & - & - & - \\
-Jiang & 90.5 & - & - & - \\
-Esteves \emph{scnn} & - & 88.9 & 86.9 & 78.6 \\
-%Esteves \emph{MVCNN} & 94.69 & - & - & - \\
-DeepSphere & 87.8 & 86.8 & 86.7 & 76.9
-    \end{tabular}
-    \caption{Accuracy (in percent) on test set, for different models. The x dataset has no augmentation, the z dataset is augmented with rotation around Z-axis, and SO3 with ZYZ rotations.}
-    \label{tab:mn40_results}
-\end{table}
-
-\subsubsection*{HEALPix architecture}
-
-HEALPix sampling, input signal at Nside = 32
-
-CNN having 5 convolutional layers, a global average pooling layer and a fully-connected layer at the end, such as this:
 \begin{dmath}
@@
 \end{dmath}
-Each convolutional layer has a graph convolution using Chebyshev polynomial approximation, batch normalization and ReLU activation.
-The order of the Chebyshev polynomial is 4 for each layer, the number of feature maps are [16, 32, 64, 128, 256] respectively and down-sampling to the immediate smaller resolution for each layer.
-
-number of parameter: 190k TODO exact number?
-
-batch size 32, adam optimizer, constant learning rate of $5 \cdot 10^{-2}$
-cross-entropy loss, and add triplet loss from ``Esteves et al.''
-
-30 epochs with augmented dataset, 3 random translation perturbation (same as 90 epochs over dataset with 3 possible random rotation)
-\subsubsection*{Equiangular architecture}
-Equiangular sampling with bandwidth of 64 in longitude and latitude.
-The architecture of the Neural Network is exactly the same, with a stride of [2, 2] for each pooling layer
-\subsection{cosmo}
-HEALPix sampling, Nside = 1024, with improved graph
+
+\subsection{Cosmological model classification}
 
@@
 
-The order of the Chebyshev polynomial is 5 for each layer, the number of feature maps are [16, 32, 64, 64, 64, 3] respectively and down-sampling to the immediate smaller resolution for each layer.
-
-batch size = 8, 80 epochs, adam optimizer, cross-entropy loss, learning rate $2\cdot10^{-4}\cdot0.999^{\textrm{step}}$
-
 \subsection{Climate event segmentation} \label{sec:climate:appendix}
+
+\Tabref{climate:accuracy}, \ref{tab:climate:map}, and \ref{tab:climate:speed} show the accuracy, mAP, and efficiency of all the NNs we ran.
 
@@
 batch size 1
-\subsection{GHCN}
-non-regular sampling, thus no pooling was used
-
-batch size 64, RMSprop optimizer, constant learning rate of $1 \cdot 10{-3}$, MSE loss, order of 5 for all layers
-
-250 epochs with no augmentation
-
-\subsubsection*{Deatilled results}
-
-\subsubsection*{Dense task architecture}
-
+
+\subsection{Uneven sampling}
+
+Architecture for dense regression:
 \begin{dmath}
@@
 
-\subsubsection*{Global task architecture}
-
+Architecture for global regression:
 \begin{dmath}

### 2019-09-25 main.tex
morning 8am

@@
 \newcommand{\Eqnref}[1]{Equation~(\ref{eqn:#1})}
+
+\newcommand{\linefrac}[2]{
+    {#1/#2}
+}
 
@@
 
-We start by proving the following Proposition:
-\vspace{0.5cm}
+We start by proving that for smooth functions, the sum converges toward an integral as the sampling increase in size.
 \begin{prop}\label{prop:1}
-	For an equal area sampling $\{x_i\in\S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance $\|\cdot\|$ with Lipschitz constant $\mathcal L_f$
-	$$
+	For an equal area sampling $\{x_i\in\S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance $\|\cdot\|$ with Lipschitz constant $C_f$
+	\begin{equation*}
 	\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right|\leq \mathcal L_fd^{(n)}.	    
-	$$
+	\end{equation*}
 	Furthermore, for all $y\in\S^2$ the Heat Kernel Graph Laplacian operator $L^t_n$ converges pointwise to the functional approximation of the Laplace Beltrami operator $L^t$
-	$$ L_n^tf(y)\xrightarrow{n\to\infty} L^tf(y).$$
+	\begin{equation*}
+	 L_n^tf(y)\xrightarrow{n\to\infty} L^tf(y).
+	\end{equation*}
 \end{prop}
-\vspace{0.5cm}
-
 \begin{proof}
-
-	Let us assume that the function $f:\R^3\rightarrow \R$ is Lipschitz with Lipschitz constant $\mathcal L_f$, we have
-
-	$$\left| \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right| \leq \mathcal L_fd^{(n)}\frac{1}{n} $$
-
-	So, by triangular inequality and by summing all the contributions of all the $n$ patches
-	$$\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right| \leq \sum_i \left| \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right|\leq n  \mathcal L_fd^{(n)}\frac{1}{n} = \mathcal L_fd^{(n)}$$
-	Thanks to this result, we have the following two pointwise convergences
-
-	$$\forall f \text{ Lipschiz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}\rightarrow \int e^{-\frac{||x-y||^2}{4t}}d\mu(x)$$
-	$$\forall f \text{ Lipschiz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}f(x_i)\rightarrow \int e^{-\frac{||x-y||^2}{4t}}f(x)d\mu(x)$$
-
+\nati{@martino, the function should be from $\S^2$ instead of $\R^3$ here right? }
+	Assuming $f:\R^3\rightarrow \R$ is Lipschitz with Lipschitz constant $C_f$, we have
+	\begin{equation*}
+	\left| \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right| \leq C_fd^{(n)}\frac{1}{n},	    
+	\end{equation*}
+	where $\sigma_i\in \S^2$ is the subset of the sphere corresponding to the patch arround $x_i$. Remember that the sampling is equal area.
+	Hence, using the triangular inequality and summing all the contributions of the $n$ patches, we obtain
+	\begin{equation*}
+	\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right| \leq \sum_i \left| \frac{1}{4\pi^2} \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right|\leq n  C_fd^{(n)}\frac{1}{n} = C_fd^{(n)}
+	\end{equation*}
+	A direct application of this result leads to the following pointwise convergences
+	\begin{equation*}
+	\forall f \text{ Lipschiz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{\|x_i-y\|^2}{4t}}\rightarrow   \int e^{-\frac{\|x-y\|^2}{4t}}d\mu(x) 
+	\end{equation*}
+    \begin{equation*}
+    \forall f \text{ Lipschiz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}f(x_i)\rightarrow   \int e^{-\frac{\|x-y\|^2}{4t}}f(x)d\mu(x)        
+    \end{equation*}
 	Definitions \ref{eq:Heat Kernel Graph Laplacian operator} and \ref{eq:Functional approximation to the Laplace-Beltrami operator} end the proof.
 \end{proof}
-\vspace{0.5cm}
-
-Now, we just proved that \textit{keeping t fixed} $L_n^tf(x)\rightarrow L^tf(x)$. Now our goal is to prove that:
-
-\vspace{0.5cm}
+
+The last proposition show that for a \emph{fixed} $t$, $L_n^tf(x)\rightarrow \linefrac{1}{4\pi^2} L^tf(x)$.
+To utilize Proposition \ref{prop:3} and complete the proof, we need to find a sequence of $t_n$ for which this holds as $t_n \rightarrow 0$.
+Furthermore this should hold with a faster decay than $\frac{1}{4\pi t_n^2}$.
 \begin{prop}\label{prop:2}
-	Given a sampling regular enough, i.e., for which we assume $A_i=A_j \ \forall i,j\text{ and }d^{(n)}\leq \frac{C}{\sqrt{n}}$, for a fixed $t>0$, a fixed Lipschitz function $f$ and a fixed point $y\in\S^2$ there exists a sequence $t_n = n^\beta, \beta<0$ such that
-$$
+	Given a sampling regular enough, i.e., for which we assume $A_i=A_j \ \forall i,j\text{ and }d^{(n)}\leq \frac{C}{\sqrt{n}}$, a Lipschitz function $f$ and a point $y\in\S^2$ there exists a sequence $t_n = n^\beta, \beta<0$ such that
+\begin{equation*}
     \forall f \text{ Lipschitz, } \forall x\in\S^2 \quad \left|\frac{1}{4\pi t_n^2}\left(L_n^{t_n}f(x) -  L^{t_n}f(x)\right)\right|\xrightarrow{n\to \infty}0.
-$$
+\end{equation*}
 \end{prop}
-\vspace{0.5cm}
-
-\begin{proof}[Proof of Proposition \ref{prop:2}]
-
-We define for simplicity of notation
+\begin{proof}
+% [Proof of Proposition \ref{prop:2}]
+To ease the notation, we define
 \begin{align}
-	\phi^t(x;y) &:= e^{-\frac{||x-y||^2}{4t}}\left(f(y)-f(x)\right)\\
-	K^t(x,y) &:=  e^{-\frac{||x-y||^2}{4t}}
+	K^t(x,y) &:=  e^{-\frac{\|x-y\|^2}{4t}}\\
+	\phi^t(x;y) &:= e^{-\frac{\|x-y\|^2}{4t}}\left(f(y)-f(x)\right).
 \end{align}
-We start by writing the following chain of inequalities
+We start with the following inequality
 \begin{align*}
-	||L_n^tf-L^tf||_\infty &= \max _{y\in \S^2} \left|L_n^tf(y)-L^tf(y)\right|\\
+	\|L_n^tf-L^tf\|_\infty &= \max _{y\in \S^2} \left|L_n^tf(y)-L^tf(y)\right|\\
 	&= \max _{y\in \S^2} \left| \frac{1}{n} \sum_{i=1}^n \phi^t(x_i; y)- \int_{\S^2} \phi^t(x;y)d\mu(x) \right|\\
 	&\leq \max _{y\in \S^2}  \sum_{i=1}^n   \left| \frac{1}{n}  \phi^t(x_i; y)- \int_{\sigma_i} \phi^t(x;y)d\mu(x) \right|\\
-	&\leq  \max _{y\in \S^2} \left[\mathcal L_{\phi^t_y}d^{(n)} \right]\\
+	&\leq  d^{(n)} \max _{y\in \S^2} C_{\phi^t_y} ,\\
 \end{align*}
-where $\mathcal L_{\phi^t_y}$ is the Lipschitz constant of $x \rightarrow \phi^t(x, y)$ and where we used for the last inequality Proposition \ref{prop:1}.
-If we assume $d^{(n)}\leq \frac{C}{\sqrt{n}}$ we have that
-
-$$||L_n^tf-L^tf||_\infty  \leq  \max _{y\in \S^2} \left[ \mathcal L_{\phi^t_y} \frac{C}{\sqrt{n}} \right]$$
-
-Let's now find the explicit dependence $t\rightarrow \mathcal L_{\phi^t_y}$
+where $C_{\phi^t_y}$ is the Lipschitz constant of $x \rightarrow \phi^t(x, y)$ and the last inequality follows from Proposition \ref{prop:1}. 
+Using the assumption $d^{(n)}\leq \frac{C}{\sqrt{n}}$ we find
+\begin{equation*}
+\|L_n^tf-L^tf\|_\infty  \leq  \frac{C}{\sqrt{n}} \max _{y\in \S^2}  C_{\phi^t_y}  
+\end{equation*}
+We now find the explicit dependence between $t$ and $C_{\phi^t_y}$
 \begin{align*}
-	\mathcal L_{\phi^t_y} &= ||\partial_x\phi^t(\cdot;y)||_\infty\\&
-	= ||\partial_x\left(K^t(\cdot;y)f\right)||_\infty\\&
-	= ||\partial_x K^t(\cdot;y)f + K^t(\cdot;y)\partial_x f||_\infty\\&
-	\leq ||\partial_x K^t(\cdot;y)f||_\infty + ||K^t(\cdot;y)\partial_x f||_\infty\\&
-	\leq  ||\partial_x K^t(\cdot;y)||_\infty||f||_\infty + ||K^t(\cdot;y)||_\infty||\partial_x f||_\infty\\&
-	= ||\partial_x K^t(\cdot;y)||_\infty||f||_\infty + ||\partial_x f||_\infty\\&
-	= \mathcal L_{K^t_y} ||f||_\infty + ||\partial_xf||_\infty\\&
-	= \mathcal L_{K^t_y} ||f||_\infty + \mathcal L_f
+	C_{\phi^t_y} &= \|\partial_x\phi^t(\cdot;y)|\_\infty\\&
+	= \|\partial_x\left(K^t(\cdot;y)f\right)\|_\infty\\&
+	= \|\partial_x K^t(\cdot;y)f + K^t(\cdot;y)\partial_x f||_\infty\\&
+	\leq \|\partial_x K^t(\cdot;y)f\|_\infty + \|K^t(\cdot;y)\partial_x f\|_\infty\\&
+	\leq  \|\partial_x K^t(\cdot;y)\|_\infty\|f\|_\infty + \|K^t(\cdot;y)\|_\infty\|\partial_x f\|_\infty\\&
+	= \|\partial_x K^t(\cdot;y)\|_\infty\|f\|_\infty + \|\partial_x f\|_\infty\\&
+	= C_{K^t_y} \|f\|_\infty + \|\partial_xf\|_\infty\\&
+	= C_{K^t_y} \|f\|_\infty + C_f
 \end{align*}
-where $\mathcal L_{K^t_y}$ is the Lipschitz constant of $x\rightarrow K^t(x;y)$. We can observe that such constant does not depend on $y$:
+where $C_{K^t_y}$ is the Lipschitz constant of $x\rightarrow K^t(x;y)$. We can observe that such constant does not depend on $y$:
 

### 2019-09-25 main.tex
finish the proof

@@
 	For a sampling $V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$  for $n\to\infty$:
-	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} f(x_i) =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.$$
+	\begin{equation*}
+	 \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} f(x_i) =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.
+	\end{equation*}
 	\label{theo:pointwise convergence for a regular sampling}
@@
 We start with the following inequality
-\begin{align*}
-	\|L_n^tf-L^tf\|_\infty &= \max _{y\in \S^2} \left|L_n^tf(y)-L^tf(y)\right|\\
-	&= \max _{y\in \S^2} \left| \frac{1}{n} \sum_{i=1}^n \phi^t(x_i; y)- \int_{\S^2} \phi^t(x;y)d\mu(x) \right|\\
-	&\leq \max _{y\in \S^2}  \sum_{i=1}^n   \left| \frac{1}{n}  \phi^t(x_i; y)- \int_{\sigma_i} \phi^t(x;y)d\mu(x) \right|\\
-	&\leq  d^{(n)} \max _{y\in \S^2} C_{\phi^t_y} ,\\
-\end{align*}
+\begin{align}
+	\|L_n^tf-L^tf\|_\infty &= \max _{y\in \S^2} \left|L_n^tf(y)-L^tf(y)\right| \nonumber\\
+	&= \max _{y\in \S^2} \left| \frac{1}{n} \sum_{i=1}^n \phi^t(x_i; y)- \int_{\S^2} \phi^t(x;y)d\mu(x) \right| \nonumber\\
+	&\leq \max _{y\in \S^2}  \sum_{i=1}^n   \left| \frac{1}{n}  \phi^t(x_i; y)- \int_{\sigma_i} \phi^t(x;y)d\mu(x) \right| \nonumber\\
+	&\leq  d^{(n)} \max _{y\in \S^2} C_{\phi^t_y} , \label{eq:prop3-base-ineq}
+\end{align}
 where $C_{\phi^t_y}$ is the Lipschitz constant of $x \rightarrow \phi^t(x, y)$ and the last inequality follows from Proposition \ref{prop:1}. 
@@
 \end{align*}
-where $C_{K^t_y}$ is the Lipschitz constant of $x\rightarrow K^t(x;y)$. We can observe that such constant does not depend on $y$:
-
-$\mathcal L_{K^t_y} = \norm{\partial_x e^{-\frac{x^2}{4t}}}_\infty = \norm{\frac{x}{2t}e^{-\frac{x^2}{4t}}}_\infty = \left.
-\frac{x}{2t}e^{-\frac{x^2}{4t}}\right|_{x=\sqrt{2t}}=(2et)^{-\frac{1}{2}}\propto t ^ {-\frac{1}{2}}$
-
-So we can continue
-$$\begin{aligned}
-	\max _{y\in \S^2} \left[  \mathcal L_{\phi^t_y} \frac{C}{\sqrt{n}} \right]
-	&\leq  \frac{C}{\sqrt{n}} \left( (2et)^{-\frac{1}{2}} \norm{f}_\infty + \mathcal L_f \right)\\
-	&\leq \frac{C\norm{f}_\infty}{\sqrt{n}(2et)^{1/2}} +   \frac{C}{\sqrt{n}}\mathcal L_f\\
-\end{aligned}$$
-So we have that, rescaling by a factor $\frac{1}{4\pi t^2}$
+where $C_{K^t_y}$ is the Lipschitz constant of the function $x\rightarrow K^t(x;y)$. We note that this constant does not depend on $y$:
+\begin{equation*}
+C_{K^t_y} = \norm{\partial_x e^{-\frac{x^2}{4t}}}_\infty = \norm{\frac{x}{2t}e^{-\frac{x^2}{4t}}}_\infty = \left.
+\frac{x}{2t}e^{-\frac{x^2}{4t}}\right|_{x=\sqrt{2t}}=(2et)^{-\frac{1}{2}}\propto t ^ {-\frac{1}{2}}.
+\end{equation*}
+Hence we have
+\begin{align*}
+	\frac{C}{\sqrt{n}}  \max _{y\in \S^2} C_{\phi^t_y} 
+	&\leq  \frac{C}{\sqrt{n}} \left( (2et)^{-\frac{1}{2}} \norm{f}_\infty + C_f \right)\\
+	&\leq \frac{C \norm{f}_\infty}{\sqrt{n}(2et)^{1/2}} +   \frac{C}{\sqrt{n}} C_f.
+\end{align*}
+Inculding this result in \eqref{eq:prop3-base-ineq} and rescaling by $\linefrac{1}{4\pi t^2}$, we obtain
 \begin{align*}
 	\norm{\frac{1}{4\pi t^2}\left(L_n^tf-L^tf\right)}_\infty&\leq \frac{1}{4\pi t^2}\norm{\left(L_n^tf-L^tf\right)}_\infty \\
-	&\leq \frac{C}{4\pi}\left[\frac{\norm{f}_\infty}{\sqrt{2e}}\frac{1}{\sqrt{n}t^{5/2}} + \frac{\mathcal L_f}{\sqrt{n}t^2}\right]
+	&\leq \frac{C}{4\pi}\left[\frac{\norm{f}_\infty}{\sqrt{2e}}\frac{1}{\sqrt{n}t^{5/2}} + \frac{C_f}{\sqrt{n}t^2}\right].
 \end{align*}
-
-we want $\begin{cases}
-t \rightarrow 0\\
-n \rightarrow \infty\\
+In order for $ \frac{C}{4\pi}\left[\frac{\norm{f}_\infty}{\sqrt{2e}}\frac{1}{\sqrt{n}t^{5/2}} + \frac{C_f}{\sqrt{n}t^2}\right] \xrightarrow[t\to 0 ]{n\to\infty}0$, 
+we need $\begin{cases}
+% t \rightarrow 0\\
+% n \rightarrow \infty\\
 \sqrt{n}t^{5/2} \rightarrow \infty\\
 \sqrt{n}t^2 \rightarrow \infty
-\end{cases}$ in order for $ \frac{C}{4\pi}\left[\frac{\norm{f}_\infty}{\sqrt{2e}}\frac{1}{\sqrt{n}t^{5/2}} + \frac{\mathcal L_f}{\sqrt{n}t^2}\right] \xrightarrow[t\to 0 ]{n\to\infty}0$
-
-This is true if $\begin{cases}
+\end{cases}$ \\
+It happens if $\begin{cases}
 t(n) = n^\beta, &\beta\in(-\frac{1}{5}, 0) \\
 t(n) = n^\beta, &\beta\in(-\frac{1}{4}, 0)
-\end{cases} \implies t(n) = n^\beta, \quad \beta\in(-\frac{1}{5}, 0)$
-
-Indeed
-
-$\sqrt{n}t^{5/2}=n^{5/2\beta+1/2}\xrightarrow{n \to \infty} \infty$ since $\frac{5}{2}\beta+1/2>0 \iff \beta>-\frac{1}{5}$
-
-$\sqrt{n}t^2=n^{2\beta+1/2}\xrightarrow {N \to \infty} \infty$ since $2\beta+1/2>0 \iff \beta>-\frac{1}{4}$
-
-So, for $t=n^\beta$ with $\beta\in(-\frac{1}{5}, 0)$ we have that
-
-$$\begin{cases}
+\end{cases} \implies t(n) = n^\beta, \quad \beta\in(-\frac{1}{5}, 0)$.\\
+Indeed, we have\\
+$\sqrt{n}t^{5/2}=n^{5/2\beta+1/2}\xrightarrow{n \to \infty} \infty$ since $\frac{5}{2}\beta+1/2>0 \iff \beta>-\frac{1}{5}$\\
+and $\sqrt{n}t^2=n^{2\beta+1/2}\xrightarrow {N \to \infty} \infty$ since $2\beta+1/2>0 \iff \beta>-\frac{1}{4}$.\\
+As a result, for $t=n^\beta$ with $\beta\in(-\frac{1}{5}, 0)$ we have
+$\begin{cases}
 (t_n)\xrightarrow{n\to\infty}0\\
-\norm{\frac{1}{4\pi t_n^2}L_n^{t_n}f-\frac{1}{4\pi t_n^2}L^{t_n}f}_\infty  \xrightarrow{n\to\infty}0
-\end{cases}$$
-
+\norm{\frac{1}{4\pi t_n^2}L_n^{t_n}f-\frac{1}{4\pi t_n^2}L^{t_n}f}_\infty  \xrightarrow{n\to\infty}0,
+\end{cases}$\\
+which concludes the proof.
 \end{proof}
@@
 	Thanks to Proposition \ref{prop:2} and Proposition \ref{prop:3}	we conclude that $\forall y\in\S^2 $
-	$$\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) =  \lim_{n\to\infty}\frac{1}{4\pi t_n^2} L^{t_n}f(y) = \frac{1}{|\S^2|}\triangle_{\S^2}f(y) $$
+	\begin{equation*}
+	\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) =  \lim_{n\to\infty}\frac{1}{4\pi t_n^2} L^{t_n}f(y) = \frac{1}{|\S^2|}\triangle_{\S^2}f(y)
+	\end{equation*}
+	Eventually selecting $y$ as a point of the sampling, we obtain
+	\begin{equation*}
+	 \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} f(x_i) =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.
+	\end{equation*} 
 \end{proof}

### 2019-09-25 main.tex
Done with the proof

@@
 	\begin{equation*}
-	 \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} f(x_i) =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.
+	 \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} T_V f [i] =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.
 	\end{equation*} 
@@
 $\sqrt{n}t^{5/2}=n^{5/2\beta+1/2}\xrightarrow{n \to \infty} \infty$ since $\frac{5}{2}\beta+1/2>0 \iff \beta>-\frac{1}{5}$\\
-and $\sqrt{n}t^2=n^{2\beta+1/2}\xrightarrow {N \to \infty} \infty$ since $2\beta+1/2>0 \iff \beta>-\frac{1}{4}$.\\
+and $\sqrt{n}t^2=n^{2\beta+1/2}\xrightarrow {n \to \infty} \infty$ since $2\beta+1/2>0 \iff \beta>-\frac{1}{4}$.\\
 As a result, for $t=n^\beta$ with $\beta\in(-\frac{1}{5}, 0)$ we have
@@
 
-Theorem  \ref{theo:pointwise convergence for a regular sampling}, is then an immediate consequence of Proposition \ref{prop:2} and Proposition \ref{prop:3}.
+Theorem  \ref{theo:pointwise convergence for a regular sampling}, is then an immediate consequence of Proposition \ref{prop:2} and \ref{prop:3}.
 \begin{proof}[Proof of Theorem \ref{theo:pointwise convergence for a regular sampling}]
@@
 
-The proof of this result is instructive since it shows that we need to impose some regularity conditions on the sampling.
+\nati{@martino, actually we do not need $ d^{(n)}\leq \frac{1}{\sqrt{n}}$, we only need $ d^{(n)}\leq \frac{1}{n^\alpha}$, where $\alpha>0$.
+As the $\S^2$ is of dimension $2$, $\alpha$ cannot be larger than $\linefrac{1}{2}$.
+If we put that into the theorem, we obtain that $\frac{5}{2}\beta+\alpha>0 \iff \beta>-\frac{2\alpha}{5}$.
+I think this is important, because we can still have convergence even if we do not have perfect patches...
+Please confirm ASAP, so we can update the Proposition and the text bellow.
+For HealPix sampling, we could say that while we have not proof, it make sense that it statisfies the hypothesis probably with $\alpha=\linefrac{1}{2}$.}
+
+The proof of Proposition \ref{prop:2} is instructive.
+First, we note that some regularity conditions on the sampling are needed.
 If the sampling is equal area as HEALPix, meaning that all the patches $\sigma_i$ have the same area, then we need to impose that $ d^{(n)}\leq \frac{1}{\sqrt{n}}$.

### 2019-09-25 main.tex
small edits

@@
 
-\section{Introduction [2 pages]}
+\section{Introduction}
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{figure_architecture_v3}
-	\caption{Example architecture from \cite{perraudin2019deepspherecosmo}.
-		Global tasks need a spatial summarization: the FCN variant is rotation invariant (and accepts inputs of varying sizes), while the CNN variant is not.
-		Dense tasks (when the output lives on the sphere, like segmentation) are rotation equivariant.
-		\todo{Shall we keep this figure? It's very nice, but we could save space. ML people probably have this in mind.}
-	}
-	\label{fig:architecture}
-\end{figure}
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=\linewidth]{figure_architecture_v3}
+% 	\caption{Example architecture from \cite{perraudin2019deepspherecosmo}.
+% 		Global tasks need a spatial summarization: the FCN variant is rotation invariant (and accepts inputs of varying sizes), while the CNN variant is not.
+% 		Dense tasks (when the output lives on the sphere, like segmentation) are rotation equivariant.
+% 		\todo{Shall we keep this figure? It's very nice, but we could save space. ML people probably have this in mind.}
+% 	}
+% 	\label{fig:architecture}
+% \end{figure}
 
 DeepSphere leverages graph convolutions to achieve the following properties: (i) computational efficiency, (ii) sampling flexibility, and (iii) rotation equivariance (\secref{equivariance}).
-An example architecture is shown in \figref{architecture}.
+% An example architecture is shown in \figref{architecture}.
 The main idea is to model the discretized sphere as a graph of connected pixels: the length of the shortest path between two pixels is an approximation of the geodesic distance between them.

### 2019-09-25 main.tex
Updates from Overleaf

--- 2019-09-25 main.tex
@@
 	\begin{equation*}
-	\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right|\leq \mathcal L_fd^{(n)}.	    
+	\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right|\leq C_f d^{(n)}.	    
 	\end{equation*}
@@
 \begin{proof}
-\nati{@martino, the function should be from $\S^2$ instead of $\R^3$ here right? }
-	Assuming $f:\R^3\rightarrow \R$ is Lipschitz with Lipschitz constant $C_f$, we have
+
+	Assuming $f:\mathbb S^2 \rightarrow \R$ is Lipschitz with Lipschitz constant $C_f$, we have
 	\begin{equation*}
@@
 	\end{equation*}
-	where $\sigma_i\in \S^2$ is the subset of the sphere corresponding to the patch arround $x_i$. Remember that the sampling is equal area.
+	where $\sigma_i\subset \S^2$ is the subset of the sphere corresponding to the patch arround $x_i$. Remember that the sampling is equal area.
 	Hence, using the triangular inequality and summing all the contributions of the $n$ patches, we obtain

### 2019-09-25 main.tex
Updates from Overleaf

@@
 \usepackage{amssymb}
+\usepackage{wrapfig}
 
@@
 	\item check results on ModelNet40
+	\item Check that HEALPix is introduced in the introduction
 \end{itemize}
@@
 
-\section{Method [1 pages]}
+\section{Method}
 
@@
 
-\section{Graph convolution and equivariance [2 pages]} \label{sec:equivariance}
+\section{Graph convolution and equivariance} \label{sec:equivariance}
 %\section{Is graph convolution equivariant to rotation? [2 pages]} \label{sec:equivariance}
@@
 A special case is the equiangular sampling scheme where a sampling theorem holds, and thus a closed form of $T_\V^{-1}$ is known. % \cite{driscoll1994Fouriersphere}
-For sampling schemes where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\b{f}$, thus approximating $T_\V^{-1}$.
+For sampling schemes where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\b{f}=T_\V f$, thus approximating $T_\V^{-1}$.
 For all theoretical considerations, we assume that $F_\V$ exists and $f \in F_\V$.
@@
 % 0.2 Explain why the Laplacian is so important...
-By definition, our (spherical) graph convolution is rotation equivariant, if and only if, it commutes with the rotation operator defined as $R(g), g\in SO(3)$: $R(g) f(x) = f\left(g^{-1} x \right)$.
+By definition, the (spherical) graph convolution is rotation equivariant, if and only if, it commutes with the rotation operator defined as $R(g), g\in SO(3)$: $R(g) f(x) = f\left(g^{-1} x \right)$.
 In the context of this work, graph convolution is performed by recursive applications of the graph Laplacian (\eqnref{graph_conv}).
@@
 % 0.3 Formulate the problem
-\mart{Correct formula for equivariance error and the corresponding plots as soon as you changed it!}
 \begin{equation} \label{eq:equivariance}
@@
 \end{equation}
-More generally for a class of signal $f \in C \subset F_\V$, the \textit{mean equivariance error}
+More generally for a class of signal $f \in C \subset F_\V$, the \textit{mean equivariance error} defined as
 \begin{equation} \label{eq:mean equivariance error}
-	\overline E_{\b{L}, C} = \mathbb E_{\b{f}\in C, g\in SO(3)} \ E_{\b{L}}(\b{f}, g).
+	\overline E_{\b{L}, C} = \mathbb E_{\b{f}\in C, g\in SO(3)} \ E_{\b{L}}(\b{f}, g),
 \end{equation}
-\mart{Talk about the probability measure used on C, SO(3)?}
-In practice, to analyze the equivariance error frequency,  the set $C$ we used is composed of functions $f$ made of spherical harmonic of a single degree $\ell$.
+represents well the overall equivariance error.
+In practice, we analyse this error with respect of the frequency by setting the set $C$ to functions $f$ made of single degree spherical harmonic.
 The expected value is obtained by averaging over a finite number of random functions and random rotations.
@@
 \subsection{Finding the optimal set of weights}  \label{sec:optimal}
-
 % 1) summary the work of Khasanova
-\cite{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ explicitly intended to work with the equiangular sampling.
-They consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude latitude axis.
+Naturally, \cite{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude and latitude axis. 
+Working specifically with the equiangular sampling, they consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East).
+% and propose a weighting scheme $w_{ij}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude latitude axis.
 Their approach leads to weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.4\linewidth]{kernel_widths}
+\begin{wrapfigure}{r}{5.5cm}
+	\centering
+	\vspace{-0.3cm}
+	\includegraphics[width=5cm]{kernel_widths}
 	\caption{
-		Optimal kernel widths for various resolutions of the HEALPix grid.
+		Optimal kernel widths for various resolutions of the HEALPix grid and numbers of neighbors.
 	}
 	\label{fig:kernel_widths}
-\end{figure}
-
+\end{wrapfigure}
 % 2) explain our approach
@@
 \end{equation}
-In practice most of the weights are very close to $0$ and hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
+In practice, because of the exponential, most of the weights are very close to $0$. Hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
 Given $k$, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{DeepSphereV1}
-	\caption{Shall we put it here or in Appendix?
-	}
+	\includegraphics[width=0.9\linewidth]{V1.pdf}
+	\caption{V1}
 	\label{fig:deepsphereV1}
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{DeepSphereV2_50neighbors.pdf}
-	\caption{}
+	\includegraphics[width=0.9\linewidth]{V2.pdf}
+	\caption{V2, 20 neighbors}
 	\label{fig:deepsphereV2}
-\end{figure}
-\begin{figure}
-	\centering
-	\includegraphics[width=0.9\linewidth]{khasanova_frossard.pdf}
-	\caption{}
-	\label{fig:khasanova_frossard}
 \end{figure}
@@
 		8 neighbors, $\hat{t} = ??$, CNN variant, \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{??} \\
-		8 neighbors, $\hat{t} = ??$, FCN variant, \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{??} \\
-		8 neighbors, optimal kernel width $\hat{t} = ??$ & \todo{??} & \todo{??} \\
-		20 neighbors, optimal kernel width $\hat{t} = ??$ & \todo{??} & \todo{??} \\
+		8 neighbors, $\hat{t} = ??$, FCN variant, \citep{perraudin2019deepspherecosmo} & 83.8 & \todo{??} \\
+		8 neighbors, optimal kernel width $\hat{t} = ??$ & 87.1 & \todo{??} \\
+		20 neighbors, optimal kernel width $\hat{t} = ??$ & 91.25 & \todo{??} \\
 		40 neighbors, optimal kernel width $\hat{t} = ??$ & \todo{??} & \todo{??} \\
@@
 \begin{itemize}
-    \item The extended graph Laplacian operator is a functional $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$  is defined given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ and $y\in \mathcal{M}$  as
+    \item The extended graph Laplacian operator is a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$  is defined given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ and $y\in \mathcal{M}$  as
 	\begin{equation}
@@
 	Note that we have the following relation $\b{L}_n^t \b{f} = T_\V L_n^t f$.
-	\item The functional approximation to the Laplace-Beltrami operator is a functional $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined  as
+	\item The functional approximation to the Laplace-Beltrami operator is a linear operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined  as
 	\begin{equation}
     \label{eq:Functional approximation to the Laplace-Beltrami operator}
-	L^tf(y) = \int_{\mathcal{M}} \exp^{-\frac{\|y-x\|^2}{4t}}\left(f(y)-f(x)\right)d\mu(x),
+	L^tf(y) = \int_{\mathcal{M}} e^{-\frac{\|x-y\|^2}{4t}}\left(f(y)-f(x)\right)d\mu(x),
 	\end{equation}
@@
     of a differentiable function $f: \mathcal M\rightarrow \R$.
-The gradient $\nabla f: \mathcal M \rightarrow T_p\mathcal M$ is a vector field defined on the manifold pointing towards the direction of steepest ascent of $f$, where $T_p\mathcal M$ is the affine space of all vectors tangent to $\mathcal M$ at $p$
+The gradient $\nabla f: \mathcal M \rightarrow T_p\mathcal M$ is a vector field defined on the manifold pointing towards the direction of steepest ascent of $f$, where $T_p\mathcal M$ is the affine space of all vectors tangent to $\mathcal M$ at $p$.
 
@@
 
-Leaveraging these three operators \cite{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian toward the Laplace-Beltrami operator.
+Leveraging these three operators \cite{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian toward the Laplace-Beltrami operator.
 The proofs consists in establishing that \eqref{eq:Heat Kernel Graph Laplacian operator} converges toward \eqref{eq:Functional approximation to the Laplace-Beltrami operator} as $n\rightarrow \infty$ and \eqref{eq:Functional approximation to the Laplace-Beltrami operator} converges toward \eqref{eq:laplace-beltrami} as $t\rightarrow 0$.

### 2019-09-25 main.tex
many small edits to experiments

@@
 	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space.
-	\item shall we still site adam and batch norm?
-	\item check results on ModelNet40
+	%\item shall we still site adam and batch norm? no, mainstream enough
+	\item check results for ModelNet40 and integrate in text
 	\item Check that HEALPix is introduced in the introduction
+	\item heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison.
+	\item check experiments section [Frédérick]: all the results numbers and NN + training details
 \end{itemize}
@@
 All our NNs are fully convolutional, and employ a global average pooling (GAP) for rotation invariant tasks.
-Graph convolutional layers are always followed by batch normalization \citep{ioffe2015batchnorm} and ReLU activation, except in the last layer.
+Graph convolutional layers are always followed by batch normalization and ReLU activation, except in the last layer.
 Note that batch normalization and activation act on the elements of $\b{f}$ independently, and hence don't depend on the domain of $f$.
@@
 While 3D shapes are usually represented as meshes or point clouds, representing them as spherical maps (\figref{depthmap}) naturally allows a rotation invariant treatment.
-LIDAR actually acquires depth maps, which are a posteriori represented as point clouds.
-\todo{move to intro?}
+%LIDAR is an example of a physical sensor that acquires spherical depth maps
+%, which are a posteriori represented as point clouds.
+% but there is gravity, might not really be SO(3) invariant
+%\todo{move to intro?} no, good to motivate each task
 
@@
 The equiangular graph is built with \eqnref{weights:khasanova} and $k = 4$ neighbors \citep[following][]{khasanova2017sphericalcnn}.
-\todo{The HEALPix graph is built with \eqnref{weights:belkin}, $k = ?$ and the corresponding optimal kernel width $t = ?$.}
+The HEALPix graph is built with \eqnref{weights:belkin}, $k = 8$, and a kernel width $t$ set to the average of the distances \citep[following][]{perraudin2019deepspherecosmo}.
 \todo{Following Esteves or Cohen?}
-The NN is made of $5$ graph convolutional layers, each followed by a \todo{max?} pooling layer down-sampling by $4$.
+The NN is made of $5$ graph convolutional layers, each followed by a max pooling layer down-sampling by $4$.
 A GAP and a fully connected layer with softmax follow.
 The Chebyshev polynomials are all of order $K=4$ and the number of channels per layer is $16, 32, 64, 128, 256$, respectively.
-Following \citet{esteves2018sphericalcnn}, the cross-entropy plus a triplet loss is optimized with Adam \citep{kingma2014adam} for 30 epochs on the dataset augmented by 3 random translations.
+Following \citet{esteves2018sphericalcnn}, the cross-entropy plus a triplet loss is optimized with Adam for 30 epochs on the dataset augmented by 3 random translations.
 The learning rate is $5 \cdot 10^{-2}$ and the batch size is 32.
@@
 Results are shown in \tabref{shrec17}.
+As the network is trained for shape classification rather than retrieval, we report the classification F1 score alongside the mAP used in the retrieval contest.\footnote{We omit the F1 for \citet{cohen2018sphericalcnn} as we didn't get the mAP reported in the paper when running it.}
 DeepSphere achieves the same performance as \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn} at a much lower cost, suggesting that anisotropic filters are an unnecessary price to pay.
@@
 \todo{be sure that it fits with the cosmo conclusion}
-\todo{The same conclusions are drawn from ModelNet 40 (see appendix ??).}
+%\todo{The same conclusions are drawn from ModelNet40 (\tabref{modelnet40}).}
 
@@
 
-Graphs are built with \eqnref{weights:belkin}, $k = 8, 20, 40$ and the corresponding optimal kernel widths $t = ?, ?, ?$.
-Following \citet{perraudin2019deepspherecosmo}, the NN is made of $5$ graph convolutional layers, each followed by a \todo{max?} pooling layer down-sampling by $4$.
+Graphs are built with \eqnref{weights:belkin}, $k = 8, 20, 40$ neighbors, and the corresponding optimal kernel widths $t$ given by the procedure in \secref{optimal}.
+Following \citet{perraudin2019deepspherecosmo}, the NN is made of $5$ graph convolutional layers, each followed by a max pooling layer down-sampling by $4$.
 A GAP and a fully connected layer with softmax follow.
@@
 		\todo{While extreme non-equivariance (the 2D CNN baseline) penalizes performance, improving equivariance doesn't improve performance.}
+		\todo{add speed to show trade-off}
 	}
@@
 
-The graph is built with \eqnref{weights:belkin}, \todo{$k = ?$} and the \todo{corresponding optimal kernel widths $t = ?, ?, ?$}.
+The graph is built with \eqnref{weights:belkin}, $k = 6$ neighbors, and a kernel width $t$ set to the average of the distances.
 Following \citet{jiang2019sphericalcnn}, the NN is an encoder-decoder with skip connections.
@@
 %The decoder is made of
-The Chebyshev polynomials are all of \todo{order $K=5$}.
+The Chebyshev polynomials are all of order $K=4$.
 The cross-entropy loss (weighted or non-weighted) is optimized with Adam for 30 epochs.
@@
 The mean and standard deviation are computed over 5 runs.
-Note that while \citet{jiang2019sphericalcnn} and \citet{cohen2019gauge} use a weighted cross-entropy loss, it is not ideal for the mAP metric.
-Results from \citet{mudigonda2017climateevents} cannot be directly compared as they don't use the same input channels.
+Note that while \citet{jiang2019sphericalcnn} and \citet{cohen2019gauge} use a weighted cross-entropy loss, that is a suboptimal proxy for the mAP metric.
 DeepSphere achieves state-of-the-art performance, suggesting again that anisotropic filters are unnecessary.
+Note that results from \citet{mudigonda2017climateevents} cannot be directly compared as they don't use the same input channels.
 
@@
 \subsection{Uneven sampling} \label{sec:exp:ghcn}
+% time series modeling? GHCN?
 % Weather prediction? But it's not a real task. Rather a demo.
 
-To demonstrate the flexibility of modeling the discretized sphere by a graph, we collected historical measurements from about $n = 10,000$ weather stations scattered across the Earth.\footnote{\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
+To demonstrate the flexibility of modeling the discretized sphere by a graph, we collected historical measurements from $n \approx 10,000$ weather stations scattered across the Earth.\footnote{\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
 The spherical data is heavily non-uniformly sampled, with a much higher density of weather stations over North America than the Pacific (\figref{examples:ghcn:tmax}).
 For illustration, we devised two artificial tasks.
-A dense regression that consists of predicting the temperature on a given day knowing the temperature on the 5 previous days.
-A global regression that consists of predicting the day (represented as one period of a sine over the year) from temperature or precipitations.
-
-The graph is built with \eqnref{weights:khasanova} and \todo{$k = ?$} neighbors.
-The kernel width $t$ is set as the average of the distances.
+A dense regression: predict the temperature on a given day knowing the temperature on the previous 5 days.
+A global regression: predict the day (represented as one period of a sine over the year) from temperature or precipitations.
+Predicting from temperature is much easier as it has a clear yearly pattern.
+
+The graph is built with \eqnref{weights:belkin}, $k = 5$ neighbors, and a kernel width $t$ set to the average of the distances.
 The equivariance property of the resulting graph has not been tested, and we don't expect it to be good due to the heavily non-uniform sampling.
@@
 		Prediction results on data from weather stations.
-		Structure always helps.
+		Structure always improves performance.
 	}
@@
 
-Results from \tabref{ghcn} show that treating the times series as a time-varying spherical signal (with filters of polynomial order $K>0$) yields higher performance than treating each time series independently ($K=0$).
-Note that predicting the day from temperature is much easier as temperature has a yearly pattern.
-Still, structure helps.
+Results are shown in \tabref{ghcn}.
+While using a polynomial order $K=0$ is like modeling each time series independently with an MLP, orders $K>0$ integrate neighborhood information.
+Results show that using the structure induced by the spherical geometry always yields better performance.
 
 % * increasing order is good until threshold \\
-% * equivariance to be verified in this case (next paper) -> in conclusion \\
 % * The NN indeed predicts the correct temperature at day T, and not day T-1 (baseline) even though there is small difference. \\

### 2019-09-25 main.tex
Updates from Overleaf

--- 2019-09-25 main.tex
@@
 Naturally, \cite{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude and latitude axis. 
-Working specifically with the equiangular sampling, they consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East).
+Working specifically with the equiangular sampling, they consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, South, West, East).
 % and propose a weighting scheme $w_{ij}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude latitude axis.
@@
 We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme.
-Given a sampling scheme $V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\R^3$ containing $\sigma_i$.
+Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area and $d_i$ the radius of the smallest ball in $\R^3$ containing $\sigma_i$.
 Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
 \begin{theorem}
-	For a sampling $V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$  for $n\to\infty$:
+	For a sampling $\V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$ such that
+% 	the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$  
 	\begin{equation*}
-	 \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} T_V f [i] =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.
+	 \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} T_\V f [i] =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.
 	\end{equation*} 
+% 	for $n\to\infty$.
 	\label{theo:pointwise convergence for a regular sampling}
 \end{theorem}
-This theorem implies immediately that $\b{L}$ converges pointwisely toward an operator ($\Delta_{\S^2}$) commuting with rotation and hence is a strong hint for equivariance.
+As a direct implication of this theorem, $\b{L}$ converges pointwisely toward the Laplace-Beltrami operator ($\Delta_{\S^2}$).
+This operator commutes with rotation and hence this convergence is a strong hint for equivariance.
 Importantly, the proof of Theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix \ref{sec: appendix: proof of theorem} inspires us in the construction of our graph Laplacian.
-It gives us a strong hint how the parameter $t$ needs to be adjusted with respect to the number of points $n$.
-
-It is important to keep in mind the limits of Theorem \ref{theo:pointwise convergence for a regular sampling}.
+It is inspirational for the graph construction and for how the parameter $t$ needs to be adjusted with respect to the number of points $n$.
+
+Nevetheless, it is important to keep in mind the limits of Theorem \ref{theo:pointwise convergence for a regular sampling}.
 First, it is \emph{not} a proof of equivariance of the graph convolution for a specific sampling.

### 2019-09-25 main.tex
modification cosmo table

@@
 \begin{abstract}
+Selecting the right convolution for a spherical neural network is a delicate trade-off between its efficiency and its exactictude with respect of equivariance.
+DeepSphere, as a graph based method strikes as a controllable balance between these two aspect.
+This contribution study how the construction of its underlying graph both theoretically and empirically.
 
@@
 To construct such a proof, a stronger convergence result is needed, for example uniform convergence (instead of pointwise).
-\todo{Can we intuitively write what pointwise convergence means, and how it is more limited than spectral or uniform convergence?}
-Unfortunately, the graph laplacian does \emph{not} converges uniformly in general \cite{belkin2007convergence}.
-This can probably be overcome by considering a specific class of functions, such as bandlimited function.
+% \todo{Can we intuitively write what pointwise convergence means, and how it is more limited than spectral or uniform convergence?}
+We note that in the random sampling case, the graph laplacian does \emph{not} converges uniformly in general \cite{belkin2007convergence}[Sec 3], but does for a class of Lipschitz functions \cite{belkin2005towards}[Sec 6].
+\todo{Update once discussed with Martino}
 Second, while do not have a proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}.
@@
 % 3.0) explain how we obtained the figures
-We calculated numerically the equivariance error (\ref{eq:mean equivariance error}) by generating $N$ monochromatic signals and $M$ random rotations for each signal.
+We calculated numerically the equivariance error \eqref{eq:mean equivariance error} by generating $N$ monochromatic signals and $M$ random rotations for each signal. 
 The colors that were used were chosen in the range $(0,\  3N_{side}-1)$ to allow for an almost perfect synthesis of the rotated signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ \citep{gorski1999healpixprimer}.
@@
     \centering
-    \begin{tabular}{l c c c}
+    \begin{tabular}{l c c c c}
 		\toprule
-		& accuracy & conv. equiv. error & NN inv. error \\
-		\midrule
-		2D CNN baseline \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{can we?} \\
-		8 neighbors, $\hat{t} = ??$, CNN variant, \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{??} \\
-		8 neighbors, $\hat{t} = ??$, FCN variant, \citep{perraudin2019deepspherecosmo} & 83.8 & \todo{??} \\
-		8 neighbors, optimal kernel width $\hat{t} = ??$ & 87.1 & \todo{??} \\
-		20 neighbors, optimal kernel width $\hat{t} = ??$ & 91.25 & \todo{??} \\
-		40 neighbors, optimal kernel width $\hat{t} = ??$ & \todo{??} & \todo{??} \\
+		& accuracy & conv. equiv. error & inference \\ % & training time & NN inv. error
+		\midrule
+		2D CNN baseline \citep{perraudin2019deepspherecosmo} & \todo{??} &  \\ % &  & \todo{can we?}
+		8 neighbors, CNN variant, \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{??} &  \\
+		8 neighbors, FCN variant, \citep{perraudin2019deepspherecosmo} & 83.8 & \todo{??} & 187\,ms \\ % & 1\,h\,45\,m
+		8 neighbors, optimal kernel width & 87.1 & \todo{??} & 185\,ms \\ % & 1\,h\,45\,m
+		20 neighbors, optimal kernel width & 91.3 & \todo{??} & 250\,ms \\ % & 2\,h\,30\,m
+		40 neighbors, optimal kernel width & 92.5 & \todo{??} & 363\,ms\\ % & 3\,h\,45\,m
 		\bottomrule

### 2019-09-25 main.tex
cosmo cost-accuracy figure

@@
 \usepackage[export]{adjustbox} % figure vertical alignment
+%\usepackage{floatrow} % figure and table together
+\usepackage{capt-of} % or \usepackage{caption} % figure and table together
 \usepackage{subfig}
@@
 	\item check experiments section [Frédérick]: all the results numbers and NN + training details
+	\item compute the invariance error of the whole NNs (before and after training, invariance can be learned)
+	\item add it with equivariance error of the convolution to \tabref{cosmo}
 \end{itemize}
@@
 As that is complicated to setup, prediction methods are typically benchmarked on the classification of spherical maps into cosmological model classes \citep{schmelze2017cosmologicalmodel}.
-We used the same task, data, and setup as \citet{perraudin2019deepspherecosmo}: the classification of $720$ partial convergence maps made of $n \approx 10^6$ pixels ($1/12 \approx 8\%$ of a sphere at $N_{side} = 1024$) from two $\Lambda$CDM cosmological models, ($\Omega_m = 0.31$, $\sigma_8 = 0.82)$ and ($\Omega_m = 0.26$, $\sigma_8 = 0.91)$, at a relative noise level of $4$.
+We used the same task, data, and setup as \citet{perraudin2019deepspherecosmo}: the classification of $720$ partial convergence maps made of $n \approx 10^6$ pixels ($1/12 \approx 8\%$ of a sphere at $N_{side} = 1024$) from two $\Lambda$CDM cosmological models, ($\Omega_m = 0.31$, $\sigma_8 = 0.82)$ and ($\Omega_m = 0.26$, $\sigma_8 = 0.91)$, at a relative noise level of $3.5$ (i.e., the signal is hidden in noise of $3.5$ times higher power).
 % 60 maps * 12 parts = 720 parts
@@
 \begin{table}
-    \centering
-    \begin{tabular}{l c c c c}
+	\begin{minipage}[b]{0.7\linewidth}
+    \centering
+    \begin{tabular}{l c c}
 		\toprule
-		& accuracy & conv. equiv. error & inference \\ % & training time & NN inv. error
-		\midrule
-		2D CNN baseline \citep{perraudin2019deepspherecosmo} & \todo{??} &  \\ % &  & \todo{can we?}
-		8 neighbors, CNN variant, \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{??} &  \\
-		8 neighbors, FCN variant, \citep{perraudin2019deepspherecosmo} & 83.8 & \todo{??} & 187\,ms \\ % & 1\,h\,45\,m
-		8 neighbors, optimal kernel width & 87.1 & \todo{??} & 185\,ms \\ % & 1\,h\,45\,m
-		20 neighbors, optimal kernel width & 91.3 & \todo{??} & 250\,ms \\ % & 2\,h\,30\,m
-		40 neighbors, optimal kernel width & 92.5 & \todo{??} & 363\,ms\\ % & 3\,h\,45\,m
+		& accuracy & time \\ % & training time & NN inv. error
+		\midrule
+		\citet{perraudin2019deepspherecosmo}, 2D CNN baseline & \todo{??} & \todo{??} \\
+		\citet{perraudin2019deepspherecosmo}, CNN variant, $k=8$ & \todo{??} & \todo{??} \\
+		\citet{perraudin2019deepspherecosmo}, FCN variant, $k=8$ & 83.8 & 187\,ms \\ % & 1\,h\,45
+		$k=8$  neighbors, $t$ from \secref{optimal} & 87.1 & 185\,ms \\ % & 1\,h\,45
+		$k=20$ neighbors, $t$ from \secref{optimal} & 91.3 & 250\,ms \\ % & 2\,h\,30
+		$k=40$ neighbors, $t$ from \secref{optimal} & 92.5 & 363\,ms \\ % & 3\,h\,45
 		\bottomrule
@@
 		Results on the classification of partial convergence maps.
-		\todo{While extreme non-equivariance (the 2D CNN baseline) penalizes performance, improving equivariance doesn't improve performance.}
-		\todo{add speed to show trade-off}
-	}
-    \label{tab:cosmo}
+		Lower equivariance error translates to higher performance.
+	} \label{tab:cosmo}
+	\end{minipage} \hfill
+	\begin{minipage}[b]{0.25\linewidth}
+		\includegraphics[width=\linewidth]{cosmo_cost_accuracy_tradeoff}
+		\captionof{figure}{Tradeoff between cost and accuracy.}
+		\label{fig:cosmo:tradeoff}
+	\end{minipage}
 \end{table}
 
-\todo{
-}
-
-Results are shown in \tabref{cosmo}.
+Results (\tabref{cosmo}) show that a lower equivariance error for convolution translates to higher performance.
+There is a clear cost-accuracy tradeoff, controlled by the number of neighbors $k$ (\figref{cosmo:tradeoff}).
 \todo{
@@
 	Alternative: DSv2 better than v1 -> equivariance has practical implications.
-	Clear cost-accuracy tradeoff with the number of neighbors.
 }

### 2019-09-25 figures/cosmo_cost_accuracy_tradeoff.py

@@ -1,0 +1,29 @@
+#!/usr/bin/env python3
+
+from os import path
+
+from matplotlib import pyplot as plt
+
+#plt.rc('font', family='Latin Modern Roman')
+#plt.rc('text', usetex=True)
+#plt.rc('text.latex', preamble=r'\usepackage{lmodern}')
+
+neighbors = [8, 20, 40]
+accuracy = [87.1, 91.3, 92.5]
+speed = [185, 250, 363]
+fig, ax = plt.subplots(figsize=(3, 2.74))
+ax.plot(speed, accuracy, '.-')
+ax.set_xlabel('inference time [ms]')
+ax.set_ylabel('accuracy [%]')
+for x, y, k in zip(speed, accuracy, neighbors):
+    align = 'right' if k == 40 else 'left'
+    ax.text(x, y-1.1, f'$k={k}$', horizontalalignment=align)
+#ax.set_ylim(86, 93)
+
+x, y, label = 187, 83.8, 'FCN variant'
+ax.scatter(x, y, c=(1, 0, 0), marker='x')
+ax.text(x, y+0.5, label, horizontalalignment='left')
+
+fig.tight_layout()
+filename = path.splitext(path.basename(__file__))[0] + '.pdf'
+fig.savefig(filename)

### 2019-09-25 main.tex
experiments almost ready for submission

@@
 		%\todo{something from climate, weather?}
-		%\todo{compare ideal full-spheres (like SHREC-17 projection from Esteves, 360 from Coors) to real-world measurements?}
+		%\todo{compare ideal full-spheres (like SHREC'17 projection from Esteves, 360 from Coors) to real-world measurements?}
 		%\todo{horizontal colorbar for brain}
@@
 The HEALPix graph is built with \eqnref{weights:belkin}, $k = 8$, and a kernel width $t$ set to the average of the distances \citep[following][]{perraudin2019deepspherecosmo}.
-\todo{Following Esteves or Cohen?}
-The NN is made of $5$ graph convolutional layers, each followed by a max pooling layer down-sampling by $4$.
+The NN is made of $5$ graph convolutional layers, each followed by a max pooling layer which down-samples by $4$.
 A GAP and a fully connected layer with softmax follow.
-The Chebyshev polynomials are all of order $K=4$ and the number of channels per layer is $16, 32, 64, 128, 256$, respectively.
+The polynomials are all of order $K=4$ and the number of channels per layer is $16, 32, 64, 128, 256$, respectively.
 Following \citet{esteves2018sphericalcnn}, the cross-entropy plus a triplet loss is optimized with Adam for 30 epochs on the dataset augmented by 3 random translations.
@@
     \caption{
-		Results on SHREC'17 (3D shapes): DeepSphere achieves similar performance at a much lower cost, suggesting that anisotropic filters are an unnecessary price to pay.
+		Results on SHREC'17 (3D shapes). DeepSphere achieves similar performance at a much lower cost, suggesting that anisotropic filters are an unnecessary price to pay.
 		% F1-score computed with sklearn, mAP from the official script of the competition.
@@
 Results are shown in \tabref{shrec17}.
-As the network is trained for shape classification rather than retrieval, we report the classification F1 score alongside the mAP used in the retrieval contest.\footnote{We omit the F1 for \citet{cohen2018sphericalcnn} as we didn't get the mAP reported in the paper when running it.}
+As the network is trained for shape classification rather than retrieval, we report the classification F1 alongside the mAP used in the retrieval contest.\footnote{We omit the F1 for \citet{cohen2018sphericalcnn} as we didn't get the mAP reported in the paper when running it.}
 DeepSphere achieves the same performance as \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn} at a much lower cost, suggesting that anisotropic filters are an unnecessary price to pay.
@@
 As the information in those spherical maps resides in the low frequencies (\figref{spectrum}), reducing the equivariance error didn't translate into improved performance.
-For the same reason, using the more uniform HEALPix discretization or lowering the resolution down to $N_{side} = 8$ didn't impact performance.
-\todo{be sure that it fits with the cosmo conclusion}
+For the same reason, using the more uniform HEALPix discretization or lowering the resolution down to $N_{side} = 8$ ($n=768$ pixels) didn't impact performance either.
 %\todo{The same conclusions are drawn from ModelNet40 (\tabref{modelnet40}).}
@@
 % such as Approximate Bayesian computation (ABC)
-As that is complicated to setup, prediction methods are typically benchmarked on the classification of spherical maps into cosmological model classes \citep{schmelze2017cosmologicalmodel}.
-We used the same task, data, and setup as \citet{perraudin2019deepspherecosmo}: the classification of $720$ partial convergence maps made of $n \approx 10^6$ pixels ($1/12 \approx 8\%$ of a sphere at $N_{side} = 1024$) from two $\Lambda$CDM cosmological models, ($\Omega_m = 0.31$, $\sigma_8 = 0.82)$ and ($\Omega_m = 0.26$, $\sigma_8 = 0.91)$, at a relative noise level of $3.5$ (i.e., the signal is hidden in noise of $3.5$ times higher power).
+As that is complicated to setup, prediction methods are typically benchmarked on the classification of spherical maps instead \citep{schmelze2017cosmologicalmodel}.
+We used the same task, data, and setup as \citet{perraudin2019deepspherecosmo}: the classification of $720$ partial convergence maps made of $n \approx 10^6$ pixels ($1/12 \approx 8\%$ of a sphere at $N_{side} = 1024$) from two $\Lambda$CDM cosmological models, ($\Omega_m = 0.31$, $\sigma_8 = 0.82)$ and ($\Omega_m = 0.26$, $\sigma_8 = 0.91)$, at a relative noise level of $3.5$ (i.e., the signal is hidden in noise of $3.5$ times higher standard deviation).
 % 60 maps * 12 parts = 720 parts
@@
 
-Graphs are built with \eqnref{weights:belkin}, $k = 8, 20, 40$ neighbors, and the corresponding optimal kernel widths $t$ given by the procedure in \secref{optimal}.
-Following \citet{perraudin2019deepspherecosmo}, the NN is made of $5$ graph convolutional layers, each followed by a max pooling layer down-sampling by $4$.
+Graphs are built with \eqnref{weights:belkin}, $k = 8, 20, 40$ neighbors, and the corresponding optimal kernel widths $t$ given in \secref{optimal}.
+Following \citet{perraudin2019deepspherecosmo}, the NN is made of $5$ graph convolutional layers, each followed by a max pooling layer which down-samples by $4$.
 A GAP and a fully connected layer with softmax follow.
-The Chebyshev polynomials are all of order $K=5$ and the number of channels per layer is $16, 32, 64, 64, 64$, respectively.
+The polynomials are all of order $K=5$ and the number of channels per layer is $16, 32, 64, 64, 64$, respectively.
 The cross-entropy loss is optimized with Adam for 80 epochs.
@@
 
-Results (\tabref{cosmo}) show that a lower equivariance error for convolution translates to higher performance.
+Unlike on SHREC'17, results (\tabref{cosmo}) show that a lower equivariance error on the convolutions translates to higher performance.
+That is probably due to the high frequency content of those maps (\figref{spectrum}).
 There is a clear cost-accuracy tradeoff, controlled by the number of neighbors $k$ (\figref{cosmo:tradeoff}).
-\todo{
-	While extreme non-equivariance (the 2D CNN baseline) penalizes performance, better equivariance doesn't improve performance.
-	It might be that the lack of built-in equivariance is compensated by learned equivariance (as done when augmenting data during training).}
-\todo{
-	Alternative: DSv2 better than v1 -> equivariance has practical implications.
-}
 This experiment moreover demonstrates DeepSphere's flexibility (using partial spherical maps) and scalability (competing spherical CNNs were tested on maps of at most $10,000$ pixels).
@@
 Details in \secref{climate:appendix}.
-%The encoder is made of $5$ graph convolutional layers, each followed by a \todo{pick-one?} pooling layer down-sampling by $4$.
+%The encoder is made of $5$ graph convolutional layers, each followed by a \todo{pick-one?} pooling layer which down-samples by $4$.
 %the number of channels per layer is $16, 32, 64, 64, 64$, respectively.
 %The decoder is made of
-The Chebyshev polynomials are all of order $K=4$.
+The polynomials are all of order $K=4$.
 The cross-entropy loss (weighted or non-weighted) is optimized with Adam for 30 epochs.
@@
 	\caption{
-		Climate event segmentation results: mean accuracy (over TC, AR, BG) and mean average precision (over TC and AR).
-		DeepSphere achieves state-of-the-art performance. %, suggesting again that anisotropic filters are an unnecessary price to pay.
+		Results on climate event segmentation: mean accuracy (over TC, AR, BG) and mean average precision (over TC and AR).
+		DeepSphere achieves state-of-the-art performance. %, suggesting again that anisotropic filters are not necessary.
 	}
@@
 The NN is made of $3$ graph convolutional layers.
-The Chebyshev polynomials are all of order $K=0$ or $4$ and the number of channels per layer is $50, 100, 100$, respectively.
+The polynomials are all of order $K=0$ or $4$ and the number of channels per layer is $50, 100, 100$, respectively.
 For the global regression, a GAP and a fully connected layer follow.
@@
 Our climate experiments (\secref{exp:climate}) however show that DeepSphere achieves similar performance than their most general convolution.
-% the SHREC17 experiment too shows that isotropic filters are sufficient
+% the SHREC'17 experiment too shows that isotropic filters are sufficient
 Works on shape alignment indicates that anisotropic filters achieve better performance \todo{[Bronstein]}.

### 2019-09-25 main.tex
Updates from Overleaf

--- 2019-09-25 main.tex
@@
 Selecting the right convolution for a spherical neural network is a delicate trade-off between its efficiency and its exactictude with respect of equivariance.
-DeepSphere, as a graph based method strikes as a controllable balance between these two aspect.
-This contribution study how the construction of its underlying graph both theoretically and empirically.
+DeepSphere, as a graph based method strikes as a controllable balance between these two aspects.
+This contribution 1) studies empirically and theoretically how the construction of its underlying graph affects equivariance, and 2) evaluates its performance on a large set of relevant problems.
+Comparison with previous work on shape classification and climate event detection suggests that anisotropic filters are an unnecessary price to pay.
 
@@
 % 3.0) explain how we obtained the figures
-We calculated numerically the equivariance error \eqref{eq:mean equivariance error} by generating $N$ monochromatic signals and $M$ random rotations for each signal. 
-The colors that were used were chosen in the range $(0,\  3N_{side}-1)$ to allow for an almost perfect synthesis of the rotated signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ \citep{gorski1999healpixprimer}.
+We calculated numerically the equivariance error \eqref{eq:mean equivariance error} by doing an empirical average on $N$ random monochromatic signals, and $M$ random rotations for each signal, for different parameter sets of DeepSphere and for the graph of Khasanova, Frossard.
+Results are in figure \ref{fig:equivariance_error}.
+The frequencies of the monochromatic signals, on the x axis in figure \ref{fig:equivariance_error}, were chosen in the range $(0,\  3N_{side}-1)$ to allow for an almost perfect synthesis of the sampled signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ in equation \eqref{eq:mean equivariance error} \citep{gorski1999healpixprimer}.
+In this way all the error measured is due to imperfections in the empirical approximation of the Laplace-Beltrami operator.
 
 % 3.1) explain what the figures tell us
-From 20\% error on V1, we got to less than 2\% error on V2.
-The number of neighbors used for V2 is $50$.
-More neighbors implies naturally more precision, plus a better kernel width obtained by "minimizing" the equivariance error.
-\mart{How to explain how we found the kernel width?
-Micha\"el I need your help here!!} Literally, minimizing the kernel width would lead to a completely disconnected graph.
-What we did was finding a heuristic law (fix neighbors, set the kernel width $\hat t$ by imposing the minimum weight to be equal to $0.1$) and then minimizing the equivariance error in the range $(\hat t / 10, \hat t\cdot 10) $.
-We got better that Khasanova-Frossard \mart{(check the code)} that however uses only 4 neighbors.
-However, it is built to explicitely minimize the equivariance error, so we expect it to be a good benchmark against which to test our construction.
+We observe that by increasing the number of neighbors of the graph from 8 to 40, we are able to decrease the equivariance error by more than one order of magnitude.
+The filtering operation with the graph Laplacian of Khasanova, Frossard is by construction perfectly equivariant to rotations along the vertical axis, and is designed to minimize the filtering error of vertical displacements of the same image.
+While these characteristics are perfect for analysing omnidirectional images that are naturally aligned on the north-south axis, it doesn't perform well on random rotations.
 \begin{figure}
 	\centering
-	\includegraphics[width=0.9\linewidth]{V1.pdf}
-	\caption{V1}
-	\label{fig:deepsphereV1}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.9\linewidth]{V2.pdf}
-	\caption{V2, 20 neighbors}
-	\label{fig:deepsphereV2}
+	\includegraphics[width=0.5\linewidth]{all_in_one.pdf}
+	\caption{Equivariance Error}
+	\label{fig:equivariance_error}
 \end{figure}

### 2019-09-25 main.tex
small edits

@@
 \begin{abstract}
-Selecting the right convolution for a spherical neural network is a delicate trade-off between its efficiency and its exactictude with respect of equivariance.
+Selecting the right convolution for a spherical neural network is a delicate tradeoff between its efficiency and its exactictude with respect of equivariance.
 DeepSphere, as a graph based method strikes as a controllable balance between these two aspects.
@@
 The main idea is to model the discretized sphere as a graph of connected pixels: the length of the shortest path between two pixels is an approximation of the geodesic distance between them.
-We use the graph CNN formulation introduced in \citep{defferrard2016graphnn}, and a pooling strategy that exploits hierarchical pixelizations of the sphere.
+We use the graph CNN formulation introduced in \citep{defferrard2016graphnn} and a pooling strategy that exploits hierarchical pixelizations of the sphere.
 
@@
 %$\b{D} = \diag(\b{A} \b{1})$
-Given a sampling scheme $\V$, usually fixed by the application or the available measurements, the only freedom in constructing $\G$ is in setting $w$.
+Given a sampling scheme $\V$, usually fixed by the application or the available measurements, the freedom in constructing $\G$ is in setting $w$.
 \Secref{equivariance} shows how to set $w$ to minimize the equivariance error.

### 2019-09-25 main.tex
move figures to fit 8 pages
Updates from Overleaf

--- 2019-09-25 main.tex
@@
 % 3.0) explain how we obtained the figures
-We calculated numerically the equivariance error \eqref{eq:mean equivariance error} by doing an empirical average on $N$ random monochromatic signals, and $M$ random rotations for each signal, for different parameter sets of DeepSphere and for the graph of Khasanova, Frossard.
+We calculated numerically the equivariance error \eqref{eq:mean equivariance error} for different parameter sets of DeepSphere and for the graph of Khasanova and Frossard.
+We approximated equation \eqref{eq:mean equivariance error} by calculating the empirical average of the equivariance errors of $N$ random monochromatic signals on $M$ random rotations for each signal.
 Results are in figure \ref{fig:equivariance_error}.
@@
 % 3.1) explain what the figures tell us
-We observe that by increasing the number of neighbors of the graph from 8 to 40, we are able to decrease the equivariance error by more than one order of magnitude.
+We observe that by increasing the number of neighbors of the graph from 8 to 40, the equivariance error decreases by more than one order of magnitude.
+On the other side, by increasing the graph resolution ($N_{side}$) the equivariance error in the high frequencies decreases.
 The filtering operation with the graph Laplacian of Khasanova, Frossard is by construction perfectly equivariant to rotations along the vertical axis, and is designed to minimize the filtering error of vertical displacements of the same image.
-While these characteristics are perfect for analysing omnidirectional images that are naturally aligned on the north-south axis, it doesn't perform well on random rotations.
+While these characteristics are designed for well analysing omnidirectional images, that are naturally aligned on the north-south axis, if tested on random rotations this construction shows its limits: increasing the graph resolution does not seem to improve its equivariance.
 \begin{figure}
@@
 Graphs are built with \eqnref{weights:belkin}, $k = 8, 20, 40$ neighbors, and the corresponding optimal kernel widths $t$ given in \secref{optimal}.
-Following \citet{perraudin2019deepspherecosmo}, the NN is made of $5$ graph convolutional layers, each followed by a max pooling layer which down-samples by $4$.
-A GAP and a fully connected layer with softmax follow.
-The polynomials are all of order $K=5$ and the number of channels per layer is $16, 32, 64, 64, 64$, respectively.
+Following \citet{perraudin2019deepspherecosmo}, the NN is made of $6$ graph convolutional layers, each followed by a max pooling layer which down-samples by $4$.
+A GAP and softmax follow.
+The polynomials are all of order $K=5$ and the number of channels per layer is $16, 32, 64, 64, 64, 2$, respectively.
 The cross-entropy loss is optimized with Adam for 80 epochs.
@@
 		\midrule
-		\citet{perraudin2019deepspherecosmo}, 2D CNN baseline & \todo{??} & \todo{??} \\
-		\citet{perraudin2019deepspherecosmo}, CNN variant, $k=8$ & \todo{??} & \todo{??} \\
-		\citet{perraudin2019deepspherecosmo}, FCN variant, $k=8$ & 83.8 & 187\,ms \\ % & 1\,h\,45
+		\citet{perraudin2019deepspherecosmo}, 2D CNN baseline & 54.2 & 104\,ms \\
+		\citet{perraudin2019deepspherecosmo}, CNN variant, $k=8$ & 62.1 & 185\,ms \\ % & 1\,h\,45
+		\citet{perraudin2019deepspherecosmo}, FCN variant, $k=8$ & 83.8 & 185\,ms \\ % & 1\,h\,45
 		$k=8$  neighbors, $t$ from \secref{optimal} & 87.1 & 185\,ms \\ % & 1\,h\,45
@@
 The proof of theorem \ref{theo:pointwise convergence for a regular sampling} is inspired from the work of \cite{belkin2005towards}. As a result, we start by restating some of their results.
-Given a sampling $V = \{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_\V f = \b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
+Given a sampling $\V = \{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_\V f = \b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
 The proof is constructed by leveraging 3 different operators:
 \begin{itemize}
-    \item The extended graph Laplacian operator is a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$  is defined given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ and $y\in \mathcal{M}$  as
+    \item The extended graph Laplacian operator is a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$  is defined as
 	\begin{equation}
@@
 	\end{equation}
-	where given $\mu$ be the uniform probability measure on the manifold $\mathcal{M}$, and let $\text{vol}(\mathcal{M})$ be the volume of $\mathcal{M}$.
+	where $\mu$ is the uniform probability measure on the manifold $\mathcal{M}$, and $\text{vol}(\mathcal{M})$ is the volume of $\mathcal{M}$.
 	\item
@@
 
-Leveraging these three operators \cite{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian toward the Laplace-Beltrami operator.
-The proofs consists in establishing that \eqref{eq:Heat Kernel Graph Laplacian operator} converges toward \eqref{eq:Functional approximation to the Laplace-Beltrami operator} as $n\rightarrow \infty$ and \eqref{eq:Functional approximation to the Laplace-Beltrami operator} converges toward \eqref{eq:laplace-beltrami} as $t\rightarrow 0$.
+Leveraging these three operators \cite{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian towards the Laplace-Beltrami operator in the general setting of any compact, closed and infinitely differentiable maniform $\mathcal M$ where the sampling scheme $\V$ is drawn at random on the manifold.
+For this reason, their results are all to be interpreted in a probabilistic sense.
+Their proofs consist in establishing that \eqref{eq:Heat Kernel Graph Laplacian operator} converges in probability towards \eqref{eq:Functional approximation to the Laplace-Beltrami operator} as $n\rightarrow \infty$ and \eqref{eq:Functional approximation to the Laplace-Beltrami operator} converges toward \eqref{eq:laplace-beltrami} as $t\rightarrow 0$.
 In particular, this second step is given by the following:
@@
 	\begin{equation*}
-	 \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} T_V f [i] =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.
+	 \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} T_\V f [i] =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.
 	\end{equation*} 

### 2019-09-25 main.tex

@@
 
-\begin{wrapfigure}{r}{5.5cm}
-	\centering
-	\vspace{-0.3cm}
-	\includegraphics[width=5cm]{kernel_widths}
-	\caption{
-		Optimal kernel widths for various resolutions of the HEALPix grid and numbers of neighbors.
-	}
-	\label{fig:kernel_widths}
-\end{wrapfigure}
 % 2) explain our approach
@@
 While these characteristics are designed for well analysing omnidirectional images, that are naturally aligned on the north-south axis, if tested on random rotations this construction shows its limits: increasing the graph resolution does not seem to improve its equivariance.
+
 \begin{figure}
+	\begin{minipage}{0.65\linewidth}
 		\centering
-	\includegraphics[width=0.5\linewidth]{all_in_one.pdf}
-	\caption{Equivariance Error}
+		\includegraphics[width=\linewidth]{all_in_one.pdf}
+		\caption{Equivariance error.}
 		\label{fig:equivariance_error}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.35\linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{kernel_widths}
+		\caption{Optimal kernel widths.}
+		\label{fig:kernel_widths}
+		\vspace{1em}
+		\includegraphics[height=4.5em]{lamp_000018}
+		\hfill
+		\includegraphics[height=4.5em]{lamp_000018_sphere_nobar}
+		\caption{3D object represented as a spherical depth map.}
+		\label{fig:depthmap}
+		\vspace{1em}
+		\includegraphics[width=\linewidth]{spectrum}
+		\caption{Power spectral densities.}
+		\label{fig:spectrum}
+	\end{minipage}
 \end{figure}
 
-\section{Experiments [2 pages]}
+\section{Experiments}
 
@@
 \subsection{3D objects recognition} \label{sec:exp:objects}
-
-\begin{figure}
-%\begin{floatingfigure}[r]{0.5\linewidth}
-%\begin{wrapfigure}{r}{0.5\linewidth}
-	\begin{minipage}[t]{0.57\linewidth}
-		\centering
-		\includegraphics[height=7em]{lamp_000018}
-		\hfill
-		\includegraphics[height=7em]{lamp_000018_sphere_nobar}
-		\caption{Example of a 3D object from SHREC'17 represented as a spherical depth map.}
-		\label{fig:depthmap}
-	\end{minipage}
-	\hfill
-	\begin{minipage}[t]{0.35\linewidth}
-		\centering
-		\includegraphics[height=7em]{spectrum}
-		\caption{Power spectral densities.}
-		\label{fig:spectrum}
-	\end{minipage}
-%\end{wrapfigure}
-%\end{floatingfigure}
-\end{figure}
 
@@
 
-\section{Conclusion [0.5 pages]}
+\section{Conclusion}
 

### 2019-09-25 main.tex
Updates from Overleaf

--- 2019-09-25 main.tex
@@
 Graphs are built with \eqnref{weights:belkin}, $k = 8, 20, 40$ neighbors, and the corresponding optimal kernel widths $t$ given in \secref{optimal}.
-Following \citet{perraudin2019deepspherecosmo}, the NN is made of $6$ graph convolutional layers, each followed by a max pooling layer which down-samples by $4$.
-A GAP and softmax follow.
-The polynomials are all of order $K=5$ and the number of channels per layer is $16, 32, 64, 64, 64, 2$, respectively.
+Following \citet{perraudin2019deepspherecosmo}, the NN is made of $5$ graph convolutional layers, each followed by a max pooling layer which down-samples by $4$.
+A GAP and a fully connected layer with softmax follow.
+The polynomials are all of order $K=5$ and the number of channels per layer is $16, 32, 64, 64, 64$, respectively.
 The cross-entropy loss is optimized with Adam for 80 epochs.
@@
 
-Leveraging these three operators \cite{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian towards the Laplace-Beltrami operator in the general setting of any compact, closed and infinitely differentiable maniform $\mathcal M$ where the sampling scheme $\V$ is drawn at random on the manifold.
+Leveraging these three operators \cite{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian towards the Laplace-Beltrami operator in the general setting of any compact, closed and infinitely differentiable maniform $\mathcal M$, where the sampling scheme $\V$ is drawn randomly on the manifold.
 For this reason, their results are all to be interpreted in a probabilistic sense.
@@
 \end{equation}
-for a particular class of sampling and b) apply Proposition \ref{prop:3}.
+for a particular class of \emph{deterministic} sampling schemes and b) apply Proposition \ref{prop:3}.
 
@@
 
-We start by proving that for smooth functions, the sum converges toward an integral as the sampling increase in size.
+We start by proving that for smooth functions, for any fixed $t$, the extended graph Laplacian $L^t_n$ converges towards its continuous counterpart $L^t$ as the sampling increases in size.
 \begin{prop}\label{prop:1}
@@
 
-\nati{@martino, actually we do not need $ d^{(n)}\leq \frac{1}{\sqrt{n}}$, we only need $ d^{(n)}\leq \frac{1}{n^\alpha}$, where $\alpha>0$.
+% I don't really have time 
+% \nati{@martino, actually we do not need $ d^{(n)}\leq \frac{1}{\sqrt{n}}$, we only need $ d^{(n)}\leq \frac{1}{n^\alpha}$, where $\alpha>0$.
 As the $\S^2$ is of dimension $2$, $\alpha$ cannot be larger than $\linefrac{1}{2}$.

### 2019-09-25 main.tex

@@
 We note that in the random sampling case, the graph laplacian does \emph{not} converges uniformly in general \cite{belkin2007convergence}[Sec 3], but does for a class of Lipschitz functions \cite{belkin2005towards}[Sec 6].
-\todo{Update once discussed with Martino}
 Second, while do not have a proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}.
-This is discussed in Appendix \ref{sec: appendix: proof of theorem}.
+The empirical results discussed in the next paragraph also point in this direction.
+This is further discussed in Appendix \ref{sec: appendix: proof of theorem}.
 
@@
 
-% I don't really have time 
+% I don't really have time to think clearly about this sorry
+
 % \nati{@martino, actually we do not need $ d^{(n)}\leq \frac{1}{\sqrt{n}}$, we only need $ d^{(n)}\leq \frac{1}{n^\alpha}$, where $\alpha>0$.
@@
 
-The proof of Proposition \ref{prop:2} is instructive.
-First, we note that some regularity conditions on the sampling are needed.
-If the sampling is equal area as HEALPix, meaning that all the patches $\sigma_i$ have the same area, then we need to impose that $ d^{(n)}\leq \frac{1}{\sqrt{n}}$.
-\\
 In the work of \cite{belkin2005towards} the sampling is drawn form a uniform random distribution on the sphere, and their proof heavily relies on the uniformity properties of the distribution from which the sampling is drawn.
-In our case the sampling is deterministic, and the fact that for a sphere there doesn't exist a regular sampling with more than 12 points (the vertices of a icosahedron) is indeed a problem that we need to overcome by imposing the regularity conditions above.
+In our case the sampling is deterministic, and this is indeed a problem that we need to overcome by imposing the regularity conditions above.
 
 To conclude, we can see that the result obtained has the same form than the result obtained in \cite{belkin2005towards}.
-Given the kernel density $t(n)=n^\beta$, if Belkin et al.
-proved convergence in the random case for $\beta \in (-\frac{1}{4}, 0)$, we proved convergence in the deterministic case for $\beta \in (-\frac{1}{5}, 0)$.
-This kind of result can be interpreted in the following way.
-In order to have this pointwise convergence, we need to reduce the kernel width but \emph{not so fast} compared to the resolution of the graph.
-In other words, the kernel width has to be reduced but is somewhat limited by the resolution of the graph.
+Given the kernel density $t(n)=n^\beta$, if Belkin and Nyiogi proved convergence in the random case for $\beta \in (-\frac{1}{4}, 0)$, we proved convergence in the deterministic case for $\beta \in (-\frac{1}{5}, 0)$.
 

### 2019-09-25 main.tex
cleaned abstract
Updates from Overleaf

@@
 % 3.0) explain how we obtained the figures
-We calculated numerically the equivariance error \eqref{eq:mean equivariance error} for different parameter sets of DeepSphere and for the graph of Khasanova and Frossard.
+We calculated numerically the equivariance error \eqref{eq:mean equivariance error} for monochromatic signals, for different parameter sets of DeepSphere and for the graph of Khasanova and Frossard.
 We approximated equation \eqref{eq:mean equivariance error} by calculating the empirical average of the equivariance errors of $N$ random monochromatic signals on $M$ random rotations for each signal.
@@
 		\centering
-		\includegraphics[width=\linewidth]{all_in_one.pdf}
-		\caption{Equivariance error.}
+		\includegraphics[width=0.9\linewidth]{all_in_one.pdf}
+		\caption{Equivariance error. The number of pixels is $4*s^2$ equiangular =
+
+Npix for healpix = 12*nside**2}
 		\label{fig:equivariance_error}

### 2019-09-25 main.tex
intro ready for submission

@@
 \end{description}
+
+story: there are tradeoffs when designing a spherical CNN -> DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
+% DSv2 has a clear tradeoff between equivariance and computational cost
+
+* method development: tool that solve a need (balance btw the desiderata: equiv vs cost)\\
+* research question: anisotropy (highlight from the start or leave it as a dangling question in the end)\\
+
+contributions:\\
+* theory $\Rightarrow$ convergence (better graph)\\
+* experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata\\
+  * surprising: anisotropy doesn't seem useful\\
 
@@
 	\item add it with equivariance error of the convolution to \tabref{cosmo}
+	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
 \end{itemize}
@@
 Comparison with previous work on shape classification and climate event detection suggests that anisotropic filters are an unnecessary price to pay.
-
-story: there are tradeoffs when designing a spherical CNN -> DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
-% DSv2 has a clear tradeoff between equivariance and computational cost
-
-* method development: tool that solve a need (balance btw the desiderata: equiv vs cost)\\
-* research question: anisotropy (highlight from the start or leave it as a dangling question in the end)\\
-
-contributions:\\
-* theory $\Rightarrow$ convergence (better graph)\\
-* experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata\\
-  * surprising: anisotropy doesn't seem useful\\
-
-Experiments on xxx show
-Comparison with previous work on shape classification and climate event detection suggests that anisotropic filters are an unnecessary price to pay.
 % memory, computations, implementation complexity
-
 \end{abstract}
@@
 
-Spherical data is found in many applications.
+Spherical data is found in many applications (\figref{examples}).
 % spherical data f: S^2 -> R, projection from R^3
@@
 The observation of the universe, LIDAR scans, and the digitalization of 3D objects are examples of projections due to observation.
-See \figref{examples}.
-In many applications, labels or variables are to be inferred from spherical data.
+Labels or variables are often to be inferred from them.
 Examples are the inference of cosmological parameters from the distribution of mass in the universe \citep{perraudin2019deepspherecosmo}, the segmentation of omnidirectional images \citep{khasanova2017sphericalcnn}, and the segmentation of cyclones from Earth observation \citep{mudigonda2017climateevents}.
@@
 	\caption{
-		Examples of intrinsically spherical data:
+		Examples of spherical data:
 		(a) brain activity recorded through magnetoencephalography (MEG),\protect\footnotemark
@@
 		A rigid full-sphere pixelization is not ideal: brain activity is only measured on the scalp, the Milky Way's galactic plane masks observations, climate scientists desire a variable resolution, and the position of weather stations is arbitrary and changes over time.
-		(e) Graphs can faithfully and efficiently represent sampled spherical data by placing vertices where data has been measured.
-		%\todo{something from climate, weather?}
-		%\todo{compare ideal full-spheres (like SHREC'17 projection from Esteves, 360 from Coors) to real-world measurements?}
+		(e) Graphs can faithfully and efficiently represent sampled spherical data by placing vertices where it matters.
 		%\todo{horizontal colorbar for brain}
@@
 On the other side of this tradeoff, \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn} proposed to perform proper spherical convolutions through the spherical harmonic transform.
-While equivariant to rotations, those convolutions are expensive.
+While equivariant to rotations, those convolutions are expensive (\secref{method:convolution}).
 
@@
 
-As the lack of equivariance penalizes performance (\secref{exp:cosmo}) and expensive convolutions prohibit their application to some real-world problems, methods standing between those two extremes are desired.
-\citet{cohen2019gauge} proposed to reduce costs by limiting the size of the representation of the symmetry group.
+As a lack of equivariance can penalize performance (\secref{exp:cosmo}) and expensive convolutions prohibit their application to some real-world problems, methods standing between those two extremes are desired.
+\citet{cohen2019gauge} proposed to reduce costs by limiting the size of the representation of the symmetry group by projecting the data from the sphere to the icosahedron.
+The distortions introduced by this projection might however hinder performance (\secref{exp:climate}).
 % (from the continuous rotation group SO(3) to a discrete rotation group)
@@
 % the representation of its symmetry group is much smaller than SO(3)
-\todo{not all rotations, subset of SO(3)?}
-The projection of the data from the sphere to the icosahedron however introduces distortions that might hinder performance (see the experiments in \secref{exp:climate}).
-\todo{Where does Jiang fit? Need a global coordinate system (ok for planets, not projections like cosmo)}
-
-Another approach represents the discretized sphere as a graph connecting pixels according to the distance between them \citep{bruna2013gnn, khasanova2017sphericalcnn, perraudin2019deepspherecosmo}.
+%\todo{not all rotations, subset of SO(3)?}
+
+Another approach is to represent the discretized sphere as a graph connecting pixels according to the distance between them \citep{bruna2013gnn, khasanova2017sphericalcnn, perraudin2019deepspherecosmo}.
 While Laplacian-based graph convolutions are more efficient than spherical convolutions, they are not exactly equivariant \citep{defferrard2019deepsphereequiv}.
-In this work, we argue that graph-based spherical CNNs strike an interesting balance, with a controllable tradeoff between cost and equivariance.
+In this work, we argue that graph-based spherical CNNs strike an interesting balance, with a controllable tradeoff between cost and performance (linked to equivariance).
 Experiments on multiple problems of practical interest show the competitiveness and flexibility of this approach.
@@
 
-\paragraph{Convolution.}
+\paragraph{Convolution.} \label{sec:method:convolution}
 On Euclidean domains, convolutions are efficiently implemented by sliding a window in the signal domain.

### 2019-09-25 main.tex
Updates from Overleaf

--- 2019-09-25 main.tex
@@
 % 3.0) explain how we obtained the figures
-We calculated numerically the equivariance error \eqref{eq:mean equivariance error} for monochromatic signals, for different parameter sets of DeepSphere and for the graph of Khasanova and Frossard.
-We approximated equation \eqref{eq:mean equivariance error} by calculating the empirical average of the equivariance errors of $N$ random monochromatic signals on $M$ random rotations for each signal.
+We calculated numerically the equivariance error $\bar{E}_{\b L,C(\ell)}$ \eqref{eq:mean equivariance error} as a function of the frequency (degree) $\ell$ of monochromatic signals $C(\ell)$, for different parameter sets of DeepSphere and for the graph of Khasanova and Frossard too.
 Results are in figure \ref{fig:equivariance_error}.
-The frequencies of the monochromatic signals, on the x axis in figure \ref{fig:equivariance_error}, were chosen in the range $(0,\  3N_{side}-1)$ to allow for an almost perfect synthesis of the sampled signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ in equation \eqref{eq:mean equivariance error} \citep{gorski1999healpixprimer}.
+The frequencies $\ell$ of the monochromatic signals were chosen in the range $(0,\  3N_{side}-1)$ for the Healpix sampling, and in the range $(0, b)$ for the equiangular sampling, to allow for an almost perfect synthesis of the sampled signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ in equation \eqref{eq:mean equivariance error} \citep{gorski1999healpixprimer}.
 In this way all the error measured is due to imperfections in the empirical approximation of the Laplace-Beltrami operator.
@@
 % 3.1) explain what the figures tell us
-We observe that by increasing the number of neighbors of the graph from 8 to 40, the equivariance error decreases by more than one order of magnitude.
+By fixing the number of neighbors to 8, we already observe a first improvement compared to the previous version of DeepSphere, whose graph also was constructed to have at maximum 8 neighbors.
+By increasing the number of neighbors of the graph the equivariance error decreases by more than one order of magnitude.
 On the other side, by increasing the graph resolution ($N_{side}$) the equivariance error in the high frequencies decreases.
@@
 		\includegraphics[width=0.9\linewidth]{all_in_one.pdf}
-		\caption{Equivariance error. The number of pixels is $4*s^2$ equiangular =
-
-Npix for healpix = 12*nside**2}
+		\caption{Normalized mean equivariance error \eqref{eq:mean equivariance error}. The number of pixels is $4s^2$ for the equiangular sampling and $12s^2$ for the Healpix sampling.}
 		\label{fig:equivariance_error}
@@
 A GAP and a fully connected layer with softmax follow.
-The polynomials are all of order $K=4$ and the number of channels per layer is $16, 32, 64, 128, 256$, respectively.
+The polynomials are all of order $K=3$ and the number of channels per layer is $16, 32, 64, 128, 256$, respectively.
 Following \citet{esteves2018sphericalcnn}, the cross-entropy plus a triplet loss is optimized with Adam for 30 epochs on the dataset augmented by 3 random translations.
@@
 A GAP and a fully connected layer with softmax follow.
-The polynomials are all of order $K=5$ and the number of channels per layer is $16, 32, 64, 64, 64$, respectively.
+The polynomials are all of order $K=4$ and the number of channels per layer is $16, 32, 64, 64, 64$, respectively.
 The cross-entropy loss is optimized with Adam for 80 epochs.
@@
 %The decoder is made of
-The polynomials are all of order $K=4$.
+The polynomials are all of order $K=3$.
 The cross-entropy loss (weighted or non-weighted) is optimized with Adam for 30 epochs.
@@
 		\midrule
-		$0$ & 10.88 & 2.42 & 0.896 & 0.10 & 0.10 & 0.881 & 0.58 & 0.42 & -0.920 \\
+		$0$ & 10.88 & 2.42 & 0.896 & 0.10 & 0.10 & 0.882 & 0.58 & 0.42 & -0.980 \\
 		%%$1$ &  8.91 & 2.20 & 0.906 & - & - & - & - & - & - \\
-		$4$ &  8.20 & 2.11 & 0.919 & 0.05 & 0.06 & 0.969 & 0.50 & 0.18 &  0.597 \\
+		$4$ &  8.20 & 2.11 & 0.919 & 0.05 & 0.05 & 0.969 & 0.50 & 0.18 &  0.597 \\
 		%$9$ &  8.38 & 2.12 & 0.915 & - & - & - & - & - & - \\
@@
 \begin{prop}\label{prop:2}
-	Given a sampling regular enough, i.e., for which we assume $A_i=A_j \ \forall i,j\text{ and }d^{(n)}\leq \frac{C}{\sqrt{n}}$, a Lipschitz function $f$ and a point $y\in\S^2$ there exists a sequence $t_n = n^\beta, \beta<0$ such that
+	Given a sampling regular enough, i.e., for which we assume $A_i=A_j \ \forall i,j\text{ and }d^{(n)}\leq \frac{C}{n^\alpha}, 0<\alpha\leq\linefrac{1}{2}$, a Lipschitz function $f$ and a point $y\in\S^2$ there exists a sequence $t_n = n^\beta, \beta<0$ such that
 \begin{equation*}
@@
 	&\leq  \frac{C}{\sqrt{n}} \left( (2et)^{-\frac{1}{2}} \norm{f}_\infty + C_f \right)\\
-	&\leq \frac{C \norm{f}_\infty}{\sqrt{n}(2et)^{1/2}} +   \frac{C}{\sqrt{n}} C_f.
+	&\leq \frac{C \norm{f}_\infty}{n^\alpha(2et)^{1/2}} +   \frac{C}{n^\alpha} C_f.
 \end{align*}
@@
 	\norm{\frac{1}{4\pi t^2}\left(L_n^tf-L^tf\right)}_\infty&\leq \frac{1}{4\pi t^2}\norm{\left(L_n^tf-L^tf\right)}_\infty \\
-	&\leq \frac{C}{4\pi}\left[\frac{\norm{f}_\infty}{\sqrt{2e}}\frac{1}{\sqrt{n}t^{5/2}} + \frac{C_f}{\sqrt{n}t^2}\right].
+	&\leq \frac{C}{4\pi}\left[\frac{\norm{f}_\infty}{\sqrt{2e}}\frac{1}{n^\alpha t^{5/2}} + \frac{C_f}{n^\alpha t^2}\right].
 \end{align*}
-In order for $ \frac{C}{4\pi}\left[\frac{\norm{f}_\infty}{\sqrt{2e}}\frac{1}{\sqrt{n}t^{5/2}} + \frac{C_f}{\sqrt{n}t^2}\right] \xrightarrow[t\to 0 ]{n\to\infty}0$, 
+In order for $ \frac{C}{4\pi}\left[\frac{\norm{f}_\infty}{\sqrt{2e}}\frac{1}{n^\alpha t^{5/2}} + \frac{C_f}{n^\alpha t^2}\right] \xrightarrow[t\to 0 ]{n\to\infty}0$, 
 we need $\begin{cases}
@@
 % n \rightarrow \infty\\
-\sqrt{n}t^{5/2} \rightarrow \infty\\
-\sqrt{n}t^2 \rightarrow \infty
+n^\alpha t^{5/2} \rightarrow \infty\\
+n^\alpha t^2 \rightarrow \infty
 \end{cases}$ \\
 It happens if $\begin{cases}
-t(n) = n^\beta, &\beta\in(-\frac{1}{5}, 0) \\
-t(n) = n^\beta, &\beta\in(-\frac{1}{4}, 0)
-\end{cases} \implies t(n) = n^\beta, \quad \beta\in(-\frac{1}{5}, 0)$.\\
+t(n) = n^\beta, &\beta\in(-\frac{2\alpha}{5}, 0) \\
+t(n) = n^\beta, &\beta\in(-\frac{\alpha}{2}, 0)
+\end{cases} \implies t(n) = n^\beta, \quad \beta\in(-\frac{2\alpha}{5}, 0)$.\\
 Indeed, we have\\
-$\sqrt{n}t^{5/2}=n^{5/2\beta+1/2}\xrightarrow{n \to \infty} \infty$ since $\frac{5}{2}\beta+1/2>0 \iff \beta>-\frac{1}{5}$\\
-and $\sqrt{n}t^2=n^{2\beta+1/2}\xrightarrow {n \to \infty} \infty$ since $2\beta+1/2>0 \iff \beta>-\frac{1}{4}$.\\
+$n^\alpha t^{5/2}=n^{5/2\beta+\alpha}\xrightarrow{n \to \infty} \infty$ since $\frac{5}{2}\beta+\alpha>0 \iff \beta>-\frac{2\alpha}{5}$\\
+and $n^\alpha t^2=n^{2\beta+\alpha}\xrightarrow {n \to \infty} \infty$ since $2\beta+\alpha>0 \iff \beta>-\frac{\alpha}{2}$.\\
 As a result, for $t=n^\beta$ with $\beta\in(-\frac{1}{5}, 0)$ we have
@@
 To conclude, we can see that the result obtained has the same form than the result obtained in \cite{belkin2005towards}.
-Given the kernel density $t(n)=n^\beta$, if Belkin and Nyiogi proved convergence in the random case for $\beta \in (-\frac{1}{4}, 0)$, we proved convergence in the deterministic case for $\beta \in (-\frac{1}{5}, 0)$.
+Given the kernel density $t(n)=n^\beta$, if Belkin and Nyiogi proved convergence in the random case for $\beta \in (-\frac{1}{4}, 0)$, we proved convergence in the deterministic case for $\beta \in (-\frac{2\alpha}{5}, 0)$, where $\alpha \in (0, \linefrac{1}{2}]$.
 

### 2019-09-25 main.tex
conclusion ready

@@
 
-As a lack of equivariance can penalize performance (\secref{exp:cosmo}) and expensive convolutions prohibit their application to some real-world problems, methods standing between those two extremes are desired.
+As a lack of equivariance can penalize performance (\secref{exp:cosmo}) and expensive convolutions prohibit their application to some real-world problems, methods standing between these two extremes are desired.
+%Such high resolutions are not necessary to represent the depth maps of 3D objects, but are required to faithfully represent cosmological and climate data.
 \citet{cohen2019gauge} proposed to reduce costs by limiting the size of the representation of the symmetry group by projecting the data from the sphere to the icosahedron.
@@
 While Laplacian-based graph convolutions are more efficient than spherical convolutions, they are not exactly equivariant \citep{defferrard2019deepsphereequiv}.
-In this work, we argue that graph-based spherical CNNs strike an interesting balance, with a controllable tradeoff between cost and performance (linked to equivariance).
+In this work, we argue that graph-based spherical CNNs strike an interesting balance, with a controllable tradeoff between cost and equivariance (which is linked to performance).
 Experiments on multiple problems of practical interest show the competitiveness and flexibility of this approach.
@@
 
-\subsection{3D objects recognition} \label{sec:exp:objects}
+\subsection{3D objects recognition} \label{sec:exp:shrec}
 
@@
 
-This work showed that DeepSphere strikes an interesting balance between desiderata for a spherical CNN.
-A single parameter, the number of neighbors a pixel is connected to in the graph, controls the tradeoff between \todo{performance and efficiency}.
+This work showed that DeepSphere strikes an interesting, and we think currently optimal, balance between desiderata for a spherical CNN.
+A single parameter, the number of neighbors $k$ a pixel is connected to in the graph, controls the tradeoff between cost and equivariance (which is linked to performance).
 % vague words
-As computational cost and memory consumption scales linearly with the number of pixels, DeepSphere easily deals with spherical maps made of millions of pixels.
-Such high resolutions are not necessary to represent the depth maps of 3D objects, but are required to faithfully represent cosmological and climate data.
-% That has to do with the frequency content of the signals (see fig xx)
 % cannot do better
-Also relevant in scientific applications is the flexibility offered by a graph representation to deal with partial coverage and non-uniform samplings.
+As computational cost and memory consumption scales linearly with the number of pixels, DeepSphere scales to spherical maps made of millions of pixels, a required resolution to faithfully represent cosmological and climate data.
+Also relevant in scientific applications is the flexibility offered by a graph representation (for partial coverage, missing data, and non-uniform samplings).
 % partial coverage / missing data
-Finally, the implementation of Laplacian-based graph convolutions is straightforward.
-The ubiquity of graph neural networks, pushing for a first-class support in Deep Learning frameworks, will make implementations even easier and more efficient.
-
-A potential drawback of graph Laplacian-based approaches is that graph filters are isotropic, reducing the expressive power of the NN.
+Finally, the implementation of the graph convolution is straightforward, and the ubiquity of graph neural networks --- pushing for their first-class support in DL frameworks --- will make implementations even easier and more efficient.
+
+A potential drawback of graph Laplacian-based approaches is the isotropy of graph filters, reducing in principle the expressive power of the NN.
 % in principle -> may in fact not
@@
 %Why anisotropic filters?
-Experiments from \citet{cohen2019gauge} suggest that more general convolutions achieve better performance.
-Our climate experiments (\secref{exp:climate}) however show that DeepSphere achieves similar performance than their most general convolution.
+Experiments from \citet{cohen2019gauge} and \citet{boscaini2016anisotropicgraphnn} indeed suggest that more general convolutions achieve better performance.
+Our experiments on 3D shapes (\secref{exp:shrec}) and climate (\secref{exp:climate}) however show that DeepSphere's isotropic filters do not hinder performance.
 % the SHREC'17 experiment too shows that isotropic filters are sufficient
-Works on shape alignment indicates that anisotropic filters achieve better performance \todo{[Bronstein]}.
+%Works on shape alignment indicates that anisotropic filters achieve better performance \todo{[Bronstein]}.
 Possible explanations for this discrepancy are that NNs somehow compensate for the lack of anisotropic filters, or that some tasks can be solved with isotropic filters.
 % why: icosahedron, can do anisotropy with isotropy + non-linearity + pooling
-The distortions induced by the icosahedral projection in \citep{cohen2019gauge} or the leakage of curvature information in \todo{[Bronstein]} might also be explanations.
-Further research is needed to determine if anisotropic filters are an unnecessary price to pay or if they are needed for some applications.
+The distortions induced by the icosahedral projection in \citet{cohen2019gauge} or the leakage of curvature information in \citet{boscaini2016anisotropicgraphnn} might also alter performance.
+%Further research is needed to determine if anisotropic filters are an unnecessary price to pay or if they are needed in some applications.
 % As was recently shown for graph NNs used for graph classification, most general might not be the best, when the ultimate goal is generalization [Andreas paper? + previous by xx]
 
-Developing graph convolutions on irregular samplings that still respect the geometry of the sphere is another research direction of importance.
+Developing graph convolutions on irregular samplings that respect the geometry of the sphere is another research direction of importance.
 % known underlying manifold
@@
 This practice either results in a waste of precision or computational and storage resources.
-Our ultimate goal is for practitioners to be able to work directly on their measurement, however distributed.
+Our ultimate goal is for practitioners to be able to work directly on their measurements, however distributed.
 

### 2019-09-25 main.tex
crop equivariance figure
Updates from Overleaf

--- 2019-09-25 main.tex
@@
 
-\begin{description}
-	\item[git] \url{https://github.com/nperraud/deepsphere_v2_paper}
-	\item[overleaf] \url{https://www.overleaf.com/project/5d31d2fbd6859d54cb707212}
-\end{description}
-
-story: there are tradeoffs when designing a spherical CNN -> DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
-% DSv2 has a clear tradeoff between equivariance and computational cost
-
-* method development: tool that solve a need (balance btw the desiderata: equiv vs cost)\\
-* research question: anisotropy (highlight from the start or leave it as a dangling question in the end)\\
-
-contributions:\\
-* theory $\Rightarrow$ convergence (better graph)\\
-* experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata\\
-  * surprising: anisotropy doesn't seem useful\\
-
-\todo{
-\begin{itemize}
-	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN.
-	\item adjacency matrix: $A$ instead of $W$?
-	\item anonymize DeepSphere citation
-% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
-	\item citet for inline, citep for parenthesis
-	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
-	\item PSD of climate data: how does it compare to cosmo and 3D objects?
-	\item align the spheres in figure 1
-	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
-	\item check footnotes
-	\item climate data on spectrum plot
-	\item result tables: only what supports the main message in the text, everything we have in the appendix
-	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
-	\item check English vs American English
-	\item unify enumerations. I like (i), (ii), etc.
-	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness?
-	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere.
-	\item figure placements
-	\item do the experiments on the icosahedral grid with the pooling as defined in the paper
-	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
-	\item update pygsp and merge sphere branch
-	\item check that NN architectures and hyper-params are correctly reported
-	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space.
-	%\item shall we still site adam and batch norm? no, mainstream enough
-	\item check results for ModelNet40 and integrate in text
-	\item Check that HEALPix is introduced in the introduction
-	\item heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison.
-	\item check experiments section [Frédérick]: all the results numbers and NN + training details
-	\item compute the invariance error of the whole NNs (before and after training, invariance can be learned)
-	\item add it with equivariance error of the convolution to \tabref{cosmo}
-	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
-\end{itemize}
-}
-\newpage
-
 \maketitle
@@
 \begin{abstract}
-Selecting the right convolution for a spherical neural network is a delicate tradeoff between its efficiency and its exactictude with respect of equivariance.
-DeepSphere, as a graph based method strikes as a controllable balance between these two aspects.
-This contribution 1) studies empirically and theoretically how the construction of its underlying graph affects equivariance, and 2) evaluates its performance on a large set of relevant problems.
+Selecting the right convolution for a spherical neural network is a delicate tradeoff between efficiency and  exactitude with respect of equivariance.
+DeepSphere, as a graph based method strikes as a controllable balance between these two desiderata.
+This contribution (i) studies empirically and theoretically how the construction of its underlying graph affects equivariance, and (ii) evaluates its performance on a large set of relevant problems.
 Comparison with previous work on shape classification and climate event detection suggests that anisotropic filters are an unnecessary price to pay.
@@
 \begin{theorem}
-	For a sampling $\V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$ such that
+	For a sampling $\V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$ such that
 % 	the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$  
@@
 % \todo{Can we intuitively write what pointwise convergence means, and how it is more limited than spectral or uniform convergence?}
-We note that in the random sampling case, the graph laplacian does \emph{not} converges uniformly in general \cite{belkin2007convergence}[Sec 3], but does for a class of Lipschitz functions \cite{belkin2005towards}[Sec 6].
-Second, while do not have a proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}.
+We note that in the random sampling case, the graph laplacian does \emph{not} converges uniformly in general \cite[Sec.
+3]{belkin2007convergence}, but does for a class of Lipschitz functions \cite[Sec.
+6]{belkin2005towards}.
+Second, while do not have a formal proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$ with $\alpha$ very close or equal to $\linefrac{1}{2}$.
 The empirical results discussed in the next paragraph also point in this direction.
@@
 % 3.0) explain how we obtained the figures
-We calculated numerically the equivariance error $\bar{E}_{\b L,C(\ell)}$ \eqref{eq:mean equivariance error} as a function of the frequency (degree) $\ell$ of monochromatic signals $C(\ell)$, for different parameter sets of DeepSphere and for the graph of Khasanova and Frossard too.
-Results are in figure \ref{fig:equivariance_error}.
-The frequencies $\ell$ of the monochromatic signals were chosen in the range $(0,\  3N_{side}-1)$ for the Healpix sampling, and in the range $(0, b)$ for the equiangular sampling, to allow for an almost perfect synthesis of the sampled signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ in equation \eqref{eq:mean equivariance error} \citep{gorski1999healpixprimer}.
-In this way all the error measured is due to imperfections in the empirical approximation of the Laplace-Beltrami operator.
+In \figref{equivariance_error}, we present the equivariance error $\bar{E}_{\b L,C(\ell)}$ \eqref{eq:mean equivariance error} computed numerically as a function of the frequency (degree) $\ell$, for different parameter sets of DeepSphere as well as for graph construction of \cite{khasanova2017sphericalcnn}.
+The error depends of the number of pixels: $12N_{side}^2$ for HEALPix and $4b^2$ for the equiangular sampling. Here $N_{side}$ and $b$ are the sampling parameters determining their precision.
+The frequencies $\ell$ of the monochromatic signals were chosen in the range $(0,\  3N_{side}-1)$ for the Healpix sampling, and in the range $(0, b)$ for the equiangular sampling, to allow for an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ in equation \eqref{eq:mean equivariance error} \citep{gorski1999healpixprimer}.
+Using these parameters, the error measured is mostly due to imperfections in the empirical approximation of the Laplace-Beltrami operator and not to the sampling.
 
 % 3.1) explain what the figures tell us
-By fixing the number of neighbors to 8, we already observe a first improvement compared to the previous version of DeepSphere, whose graph also was constructed to have at maximum 8 neighbors.
-By increasing the number of neighbors of the graph the equivariance error decreases by more than one order of magnitude.
-On the other side, by increasing the graph resolution ($N_{side}$) the equivariance error in the high frequencies decreases.
-The filtering operation with the graph Laplacian of Khasanova, Frossard is by construction perfectly equivariant to rotations along the vertical axis, and is designed to minimize the filtering error of vertical displacements of the same image.
-While these characteristics are designed for well analysing omnidirectional images, that are naturally aligned on the north-south axis, if tested on random rotations this construction shows its limits: increasing the graph resolution does not seem to improve its equivariance.
+For 8 neighbors, selecting the optimal value of $t$ already leads to an improvement compared to \cite{perraudin2019deepspherecosmo}, whose graph also was constructed to have at maximum 8 neighbors. 
+With higher the number of neighbors, the equivariance error decreases by more than one order of magnitude. 
+Furthermore, increasing the graph resolution ($N_{side}$) leads to an improvement in the high frequencies as well. 
+Increasing the graph resolution of the graph of \cite{khasanova2017sphericalcnn} does not seem to improve its equivariance.
+We note that in our numerical test, this graph was perfectly equivariant to rotations along the horizontal and vertical axis as it should be by design.
+Nevertheless, it is simply not equivariant along the last rotation.
+Such equivariance properties might be sufficient for analysing omnidirectional images (that are naturally aligned on the north-south axis).
 
 \begin{figure}
-	\begin{minipage}{0.65\linewidth}
+	\begin{minipage}{0.6\linewidth}
 		\centering
-		\includegraphics[width=0.9\linewidth]{all_in_one.pdf}
+		\includegraphics[width=1\linewidth]{all_in_one.pdf}
 		\caption{Normalized mean equivariance error \eqref{eq:mean equivariance error}. The number of pixels is $4s^2$ for the equiangular sampling and $12s^2$ for the Healpix sampling.}
@@
 	\end{minipage}
+	\vspace{-0.5cm}
 \end{figure}
@@
 \begin{prop}\label{prop:2}
-	Given a sampling regular enough, i.e., for which we assume $A_i=A_j \ \forall i,j\text{ and }d^{(n)}\leq \frac{C}{n^\alpha}, 0<\alpha\leq\linefrac{1}{2}$, a Lipschitz function $f$ and a point $y\in\S^2$ there exists a sequence $t_n = n^\beta, \beta<0$ such that
+	Given a sampling regular enough, i.e., for which we assume $A_i=A_j \ \forall i,j\text{ and }d^{(n)}\leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, a Lipschitz function $f$ and a point $y\in\S^2$ there exists a sequence $t_n = n^\beta, \beta<0$ such that
 \begin{equation*}
@@
 
-To conclude, we can see that the result obtained has the same form than the result obtained in \cite{belkin2005towards}.
-Given the kernel density $t(n)=n^\beta$, if Belkin and Nyiogi proved convergence in the random case for $\beta \in (-\frac{1}{4}, 0)$, we proved convergence in the deterministic case for $\beta \in (-\frac{2\alpha}{5}, 0)$, where $\alpha \in (0, \linefrac{1}{2}]$.
+To conclude, we see that the result obtained is of similar form than the result obtained in \cite{belkin2005towards}.
+Given the kernel density $t(n)=n^\beta$, \cite{belkin2005towards} proved convergence in the random case for $\beta \in (-\frac{1}{4}, 0)$ and we proved convergence in the deterministic case for $\beta \in (-\frac{2\alpha}{5}, 0)$, where $\alpha \in (0, \linefrac{1}{2}]$ (for the spherical Manifold).
 
@@
 
-* Jiang rerun with a batch size of 64 instead of 256 due to memory limit.\\
-* DS-jiang is the similar architecture as \cite{jiang2019sphericalcnn}. \\
-* DS-optimal has 2 times the number of feature maps of DS. \\
-* \todo{What is DS and DS-Cohen?} DS has 4 times more feature maps and one more layer than DS-Jiang.
+The experiment with the model from \cite{jiang2019sphericalcnn} was rerun in order to obtain the AP metrics, but with a batch size of 64 instead of 256 due to GPU memory limit.
+
+Several experiments were run with different architectures for DeepSphere (DS).
+Jiang architecture use a similar one as \cite{jiang2019sphericalcnn}, with only the convolutional operators replaced.
+DeepSphere only is the original architecture giving the best results, deeper and with four times more feature maps than Jiang architecture.
+And DeepSphere with a wider architecture is the same with two times the number of feature maps.
+
+Regarding the weighted loss, the weights are chosen with \texttt{scikit-learn} function \texttt{compute\_class\_weight} on the training set.
+
+% * Jiang rerun with a batch size of 64 instead of 256 due to memory limit.\\
+% * DS-jiang is the similar architecture as \cite{jiang2019sphericalcnn}. \\
+% * DS-optimal has 2 times the number of feature maps of DS. \\
+% * \todo{What is DS and DS-Cohen?} DS has 4 times more feature maps and one more layer than DS-Jiang.
 DS-optimal has still 2 times more feature maps.
@@
 \\
-* \todo{Is (equi non-weighted) the full resolution?} Yes, but less feature maps and layers. Can run, but not enough GPU memory for an optimal architecture. \\
-* \todo{check column order for DS} \\
-* perf with same arch as Jiang in appendix => not enough channels!\\
-* even more feature maps give us one more point in perf\\
+% * \todo{Is (equi non-weighted) the full resolution?} Yes, but less feature maps and layers. Can run, but not enough GPU memory for an optimal architecture. \\
+% * perf with same arch as Jiang in appendix => not enough channels!\\
+% * even more feature maps give us one more point in perf\\
 
@@
         DS (wider architecture, non-weighted loss) & 73.4 & 92.7 & 99.8 & 88.7 \\
-		\midrule
-		\todo{DS (Cohen architecture, weighted loss)} & 95.5 & 96.9 & 93.9 & 95.4 \\
-		\todo{DS (Cohen architecture, non-weighted loss)} & 56.4 & 90.0 & 98.9 & 81.8 \\
-		\todo{DS (full dataset, non-weighted loss)} & 31.3 & 75.2 & 99.9 & 68.80 \\
+% 		\midrule
+% 		\todo{DS (Cohen architecture, weighted loss)} & 95.5 & 96.9 & 93.9 & 95.4 \\
+% 		\todo{DS (Cohen architecture, non-weighted loss)} & 56.4 & 90.0 & 98.9 & 81.8 \\
+% 		\todo{DS (full dataset, non-weighted loss)} & 31.3 & 75.2 & 99.9 & 68.80 \\
 		\bottomrule
@@
         DS (wider architecture, weighted loss) & 52.80 & 94.78 & 73.79 \\
-		\midrule
-		\todo{DS (Cohen architecture, weighted loss)} & 13.1 & 80.3 & 46.7 \\
-		\todo{DS (Cohen architecture, non-weighted loss)} & 59.8 & 85.0 & 72.4 \\
-		\todo{DS (full dataset, non-weighted loss)} & 55.53 & 94.85 & 75.19 \\
+% 		\midrule
+% 		\todo{DS (Cohen architecture, weighted loss)} & 13.1 & 80.3 & 46.7 \\
+% 		\todo{DS (Cohen architecture, non-weighted loss)} & 59.8 & 85.0 & 72.4 \\
+% 		\todo{DS (full dataset, non-weighted loss)} & 55.53 & 94.85 & 75.19 \\
 		\bottomrule
@@
 		DeepSphere (wider architecture) & 52\,M & 50\,ms & 20\,h \\
-		\todo{DS (Cohen architecture)} & 2\,M & 11\,ms & 4\,h \\
-		\todo{DS (full dataset)} & - & 567\,ms & 48\,h \\
+% 		\todo{DS (Cohen architecture)} & 2\,M & 11\,ms & 4\,h \\
+% 		\todo{DS (full dataset)} & - & 567\,ms & 48\,h \\
 		\bottomrule
@@
 
-\subsubsection*{DS Icosahedron architecture}
-
-icosahedron sampling, level-5 resolution
-
-CNN with encoder decoder architecture
+% \subsubsection*{DS Icosahedron architecture}
+
+Original DeepSphere architecture with encoder decoder\\
 encoder:\\
@@
 
-concat the results of the corresponding encoder layer before the graph convolution. Not similar to Jiang and 4 times the feature maps.
-
-batch size 64, adam optimizer, constant learning rate of $1 \cdot 10{-3}$, cross-entropy loss, both weighted and non weighted.
-Weight chosen with scikit-learn "compute\_class\_weight" on the training set
-
-30 epochs
-
-wider architecture is the same, but with 2 time the feature maps.
-\subsubsection*{DS (Jiang architecture)}
+concat is the operation that concatenate the results of the corresponding encoder layer.
+% Not similar to Jiang and 4 times the feature maps.
+
+% batch size 64, adam optimizer, constant learning rate of $1 \cdot 10{-3}$, cross-entropy loss, both weighted and non weighted.
+
+% 30 epochs
+
+% DeepSphere with a wider architecture is exactly the same, but with 2 times the number of feature maps.
+% \subsubsection*{DS (Jiang architecture)}
+
+DeepSphere with Jiang architecture\\
 encoder:\\
@@
 
-concat the results of the corresponding encoder layer after the graph convolution. Similar to ``Jiang et al.''
-\subsubsection*{Full dataset - Equiangular architecture}
-Equiangular sampling, with a latitude bandwidth 384 and longitude bandwidth 576.
-
-Due to memory problem, could not use the same architecture
-
-8 epochs
-
-encoder:\\
-\begin{dmath}
-    [GC_{16}\, +\, BN\, +\, ReLU]_{bw}\,+\, [GC_{16}\, +\, BN\, +\, ReLU]_{bw}\, +\, \textrm{Pool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{bw/16}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{bw/64}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{bw/64}
-\end{dmath}
-decoder:\\
-\begin{dmath}
-    \textrm{Unpool}\, +\,[GC_{128}\, +\, BN\, +\, ReLU]_{bw/64}\, +\, \textrm{concat}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{bw/64}\, +\, \textrm{Unpool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{bw/64}\, +\, \textrm{concat}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{bw/64}\, +\, \textrm{Unpool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{bw/16}\, +\, \textrm{concat}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{bw/16}\, +\,\textrm{Unpool}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{bw}\,+\, \textrm{concat}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{bw}\, +\,\textrm{Unpool}\,  +\, [GC_{16}\, +\, BN\, +\, ReLU]_{bw}\,+\,[GC_3]_{bw}
-\end{dmath}
-
-batch size 1
+% concat the results of the corresponding encoder layer after the graph convolution. Similar to ``Jiang et al.''
+% \subsubsection*{Full dataset - Equiangular architecture}
+% Equiangular sampling, with a latitude bandwidth 384 and longitude bandwidth 576.
+
+% Due to memory problem, could not use the same architecture
+
+% 8 epochs
+
+% encoder:\\
+% \begin{dmath}
+%     [GC_{16}\, +\, BN\, +\, ReLU]_{bw}\,+\, [GC_{16}\, +\, BN\, +\, ReLU]_{bw}\, +\, \textrm{Pool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{bw/16}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{bw/64}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{bw/64}
+% \end{dmath}
+% decoder:\\
+% \begin{dmath}
+%     \textrm{Unpool}\, +\,[GC_{128}\, +\, BN\, +\, ReLU]_{bw/64}\, +\, \textrm{concat}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{bw/64}\, +\, \textrm{Unpool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{bw/64}\, +\, \textrm{concat}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{bw/64}\, +\, \textrm{Unpool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{bw/16}\, +\, \textrm{concat}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{bw/16}\, +\,\textrm{Unpool}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{bw}\,+\, \textrm{concat}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{bw}\, +\,\textrm{Unpool}\,  +\, [GC_{16}\, +\, BN\, +\, ReLU]_{bw}\,+\,[GC_3]_{bw}
+% \end{dmath}
+
+% batch size 1
 
@@
 
+\clearpage
+\newpage
+
+\begin{description}
+	\item[git] \url{https://github.com/nperraud/deepsphere_v2_paper}
+	\item[overleaf] \url{https://www.overleaf.com/project/5d31d2fbd6859d54cb707212}
+\end{description}
+
+story: there are tradeoffs when designing a spherical CNN -> DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
+% DSv2 has a clear tradeoff between equivariance and computational cost
+
+* method development: tool that solve a need (balance btw the desiderata: equiv vs cost)\\
+* research question: anisotropy (highlight from the start or leave it as a dangling question in the end)\\
+
+contributions:\\
+* theory $\Rightarrow$ convergence (better graph)\\
+* experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata\\
+  * surprising: anisotropy doesn't seem useful\\
+
+\todo{
+\begin{itemize}
+% 	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN. [Yes]
+% 	\item adjacency matrix: $A$ instead of $W$? nath: I am for W
+% 	\item anonymize DeepSphere citation - Not doing that
+% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
+	\item citet for inline, citep for parenthesis
+	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
+	\item PSD of climate data: how does it compare to cosmo and 3D objects?
+	\item align the spheres in figure 1
+	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
+	\item check footnotes
+	\item climate data on spectrum plot
+	\item result tables: only what supports the main message in the text, everything we have in the appendix
+	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
+	\item check English vs American English
+	\item unify enumerations. I like (i), (ii), etc.
+	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness?
+	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere.
+	\item figure placements
+	\item do the experiments on the icosahedral grid with the pooling as defined in the paper
+	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
+	\item update pygsp and merge sphere branch
+	\item check that NN architectures and hyper-params are correctly reported
+	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space.
+	%\item shall we still site adam and batch norm? no, mainstream enough
+	\item check results for ModelNet40 and integrate in text
+	\item Check that HEALPix is introduced in the introduction
+	\item heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison.
+% 	\item check experiments section [Frédérick]: all the results numbers and NN + training details
+	\item compute the invariance error of the whole NNs (before and after training, invariance can be learned)
+	\item add it with equivariance error of the convolution to \tabref{cosmo}
+	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
+\end{itemize}
+}
+
 \end{document}

### 2019-09-25 main.tex

@@
 \begin{figure}
+
 	\begin{minipage}{0.6\linewidth}
@@
 		\includegraphics[width=1\linewidth]{all_in_one.pdf}
+
 		\caption{Normalized mean equivariance error \eqref{eq:mean equivariance error}. The number of pixels is $4s^2$ for the equiangular sampling and $12s^2$ for the Healpix sampling.}

### 2019-09-25 main.tex
Updates from Overleaf

@@
 \begin{abstract}
-Selecting the right convolution for a spherical neural network is a delicate tradeoff between efficiency and  exactitude with respect of equivariance.
+Selecting the right convolution for a spherical neural network is a delicate tradeoff between efficiency and  exactitude with respect to equivariance.
 DeepSphere, as a graph based method strikes as a controllable balance between these two desiderata.
+% Say something here about isotropy?
 This contribution (i) studies empirically and theoretically how the construction of its underlying graph affects equivariance, and (ii) evaluates its performance on a large set of relevant problems.
+
 Comparison with previous work on shape classification and climate event detection suggests that anisotropic filters are an unnecessary price to pay.
@@
 DeepSphere only is the original architecture giving the best results, deeper and with four times more feature maps than Jiang architecture.
-And DeepSphere with a wider architecture is the same with two times the number of feature maps.
+And the wider architecture is the same as the previous one with two times the number of feature maps.
 

### 2019-09-25 main.tex
Updates from Overleaf

@@
 \begin{abstract}
-Selecting the right convolution for a spherical neural network is a delicate tradeoff between efficiency and  exactitude with respect to equivariance.
-DeepSphere, as a graph based method strikes as a controllable balance between these two desiderata.
+% We have to submit soon... The last sentence is a bit disconnected. Yep
+Designing a convolution for a spherical neural network requires a delicate tradeoff between efficiency and rotation equivariance. % exactitude with respect to equivariance.
+DeepSphere, a method based on a graph representation of the discretized sphere, strikes a controllable balance between these two desiderata.
 % Say something here about isotropy?
-This contribution (i) studies empirically and theoretically how the construction of its underlying graph affects equivariance, and (ii) evaluates its performance on a large set of relevant problems.
-
-Comparison with previous work on shape classification and climate event detection suggests that anisotropic filters are an unnecessary price to pay.
+This contribution is twofold.
+First, we study both theoretically and empirically how equivariance is affected by the underlying graph with respect to the number of pixels and neighbors.
+% 
+Second, we evaluate DeepSphere on relevant problems.
+Experiments show state-of-the-art performance and demonstrates the efficiency and flexibility of this formulation.
+In particular, comparison with previous work on shape classification and climate event detection suggests that anisotropic filters are an unnecessary price to pay. 
+%Say something about speed here... Not sure what?
 % memory, computations, implementation complexity
@@
 \Tabref{shrec17_retrieval} shows the results obtained from the competition's official evaluation script.
-\Tabref{modelnet40} shows results on ModelNet40.
+% \Tabref{modelnet40} shows results on ModelNet40.
 
@@
 
-\begin{table}
-    \centering
-    \begin{tabular}{l cccc}
-	\toprule
-    & no/no & z/z & SO3/SO3 & z/SO3 \\
-	\midrule
-	\citet{cohen2018sphericalcnn} & 85.0 & - & - & - \\
-	\citet{jiang2019sphericalcnn} & 90.5 & - & - & - \\
-	\citet{esteves2018sphericalcnn} & - & 88.9 & 86.9 & 76.7 \\
-	%Esteves \emph{MVCNN} & 94.69 & - & - & - \\
-	DeepSphere & 87.8 & 86.8 & 86.7 & 76.9 \\
-	\bottomrule
-    \end{tabular}
-    \caption{
-		Accuracy results on ModelNet40.
-		``no'' denotes no augmentation, ``z'' is augmented with rotations around the Z-axis, and ``SO3'' with ZYZ rotations.
-		\todo{The first is training time augmentation, the second test time augmentation.}
-	}
-    \label{tab:modelnet40}
-\end{table}
+% \begin{table}
+%     \centering
+%     \begin{tabular}{l cccc}
+% 	\toprule
+%     & no/no & z/z & SO3/SO3 & z/SO3 \\
+% 	\midrule
+% 	\citet{cohen2018sphericalcnn} & 85.0 & - & - & - \\
+% 	\citet{jiang2019sphericalcnn} & 90.5 & - & - & - \\
+% 	\citet{esteves2018sphericalcnn} & - & 88.9 & 86.9 & 76.7 \\
+% 	%Esteves \emph{MVCNN} & 94.69 & - & - & - \\
+% 	DeepSphere & 87.8 & 86.8 & 86.7 & 76.9 \\
+% 	\bottomrule
+%     \end{tabular}
+%     \caption{
+% 		Accuracy results on ModelNet40.
+% 		``no'' denotes no augmentation, ``z'' is augmented with rotations around the Z-axis, and ``SO3'' with ZYZ rotations.
+% 		\todo{The first is training time augmentation, the second test time augmentation.}
+% 	}
+%     \label{tab:modelnet40}
+% \end{table}
 
@@
 		Tropical cyclones (TC) and atmospheric rivers (AR) are the two positive classes, against the background (BG).
-		\todo{\citet{mudigonda2017climateevents} is not directly comparable as they don't use the same input feature maps.}
+		\citet{mudigonda2017climateevents} is not directly comparable as they don't use the same input feature maps.
 		Note that a non-weighted cross-entropy loss is not optimal for the accuracy metric.
@@
 \end{table}
+\pagebreak
+% \subsubsection*{DS (Jiang architecture)}
+
+DeepSphere with Jiang architecture\\
+encoder:\\
+\begin{dmath}
+    [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{Pool}\,+\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\, \textrm{Pool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\,\textrm{Pool}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Pool}\,  +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L0}
+\end{dmath}
+decoder:\\
+\begin{dmath}
+    \textrm{Unpool}\, +\,[GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{concat}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Unpool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{concat}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{Unpool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{concat}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\,\textrm{Unpool}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\,+\, \textrm{concat}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\,\textrm{Unpool}\,  +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{concat}\, +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\, + \,[GC_3]_{L5}
+\end{dmath}
+% number of parameters: 590'976  % more feat is 16 times more
+Concat is the operation that concatenate the results of the corresponding encoder layer.
+% concat the results of the corresponding encoder layer after the graph convolution. Similar to ``Jiang et al.''
 
@@
 
-concat is the operation that concatenate the results of the corresponding encoder layer.
 % Not similar to Jiang and 4 times the feature maps.
@@
 % DeepSphere with a wider architecture is exactly the same, but with 2 times the number of feature maps.
-% \subsubsection*{DS (Jiang architecture)}
-
-DeepSphere with Jiang architecture\\
-encoder:\\
-\begin{dmath}
-    [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{Pool}\,+\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\, \textrm{Pool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\,\textrm{Pool}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Pool}\,  +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L0}
-\end{dmath}
-decoder:\\
-\begin{dmath}
-    \textrm{Unpool}\, +\,[GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{concat}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Unpool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{concat}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{Unpool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{concat}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\,\textrm{Unpool}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\,+\, \textrm{concat}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\,\textrm{Unpool}\,  +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{concat}\, +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\, + \,[GC_3]_{L5}
-\end{dmath}
-% number of parameters: 590'976  % more feat is 16 times more
-
-% concat the results of the corresponding encoder layer after the graph convolution. Similar to ``Jiang et al.''
+
 % \subsubsection*{Full dataset - Equiangular architecture}
@@
 
-\clearpage
-\newpage
-
-\begin{description}
-	\item[git] \url{https://github.com/nperraud/deepsphere_v2_paper}
-	\item[overleaf] \url{https://www.overleaf.com/project/5d31d2fbd6859d54cb707212}
-\end{description}
-
-story: there are tradeoffs when designing a spherical CNN -> DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
-% DSv2 has a clear tradeoff between equivariance and computational cost
-
-* method development: tool that solve a need (balance btw the desiderata: equiv vs cost)\\
-* research question: anisotropy (highlight from the start or leave it as a dangling question in the end)\\
-
-contributions:\\
-* theory $\Rightarrow$ convergence (better graph)\\
-* experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata\\
-  * surprising: anisotropy doesn't seem useful\\
-
-\todo{
-\begin{itemize}
-% 	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN. [Yes]
-% 	\item adjacency matrix: $A$ instead of $W$? nath: I am for W
-% 	\item anonymize DeepSphere citation - Not doing that
-% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
-	\item citet for inline, citep for parenthesis
-	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
-	\item PSD of climate data: how does it compare to cosmo and 3D objects?
-	\item align the spheres in figure 1
-	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
-	\item check footnotes
-	\item climate data on spectrum plot
-	\item result tables: only what supports the main message in the text, everything we have in the appendix
-	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
-	\item check English vs American English
-	\item unify enumerations. I like (i), (ii), etc.
-	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness?
-	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere.
-	\item figure placements
-	\item do the experiments on the icosahedral grid with the pooling as defined in the paper
-	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
-	\item update pygsp and merge sphere branch
-	\item check that NN architectures and hyper-params are correctly reported
-	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space.
-	%\item shall we still site adam and batch norm? no, mainstream enough
-	\item check results for ModelNet40 and integrate in text
-	\item Check that HEALPix is introduced in the introduction
-	\item heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison.
-% 	\item check experiments section [Frédérick]: all the results numbers and NN + training details
-	\item compute the invariance error of the whole NNs (before and after training, invariance can be learned)
-	\item add it with equivariance error of the convolution to \tabref{cosmo}
-	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
-\end{itemize}
-}
-
+%\clearpage
+%\newpage
+%
+%\begin{description}
+%	\item[git] \url{https://github.com/nperraud/deepsphere_v2_paper}
+%	\item[overleaf] \url{https://www.overleaf.com/project/5d31d2fbd6859d54cb707212}
+%\end{description}
+%
+%story: there are tradeoffs when designing a spherical CNN -> DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
+%% DSv2 has a clear tradeoff between equivariance and computational cost
+%
+%* method development: tool that solve a need (balance btw the desiderata: equiv vs cost)\\
+%* research question: anisotropy (highlight from the start or leave it as a dangling question in the end)\\
+%
+%contributions:\\
+%* theory $\Rightarrow$ convergence (better graph)\\
+%* experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata\\
+%  * surprising: anisotropy doesn't seem useful\\
+%
+%\todo{
+%\begin{itemize}
+%% 	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN. [Yes]
+%% 	\item adjacency matrix: $A$ instead of $W$? nath: I am for W
+%% 	\item anonymize DeepSphere citation - Not doing that
+%% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
+%	\item citet for inline, citep for parenthesis
+%	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
+%	\item PSD of climate data: how does it compare to cosmo and 3D objects?
+%	\item align the spheres in figure 1
+%	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
+%	\item check footnotes
+%	\item climate data on spectrum plot
+%	\item result tables: only what supports the main message in the text, everything we have in the appendix
+%	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
+%	\item check English vs American English
+%	\item unify enumerations. I like (i), (ii), etc.
+%	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness?
+%	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere.
+%	\item figure placements
+%	\item do the experiments on the icosahedral grid with the pooling as defined in the paper
+%	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
+%	\item update pygsp and merge sphere branch
+%	\item check that NN architectures and hyper-params are correctly reported
+%	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space.
+%	%\item shall we still site adam and batch norm? no, mainstream enough
+%	\item check results for ModelNet40 and integrate in text
+%	\item Check that HEALPix is introduced in the introduction
+%	\item heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison.
+%% 	\item check experiments section [Frédérick]: all the results numbers and NN + training details
+%	\item compute the invariance error of the whole NNs (before and after training, invariance can be learned)
+%	\item add it with equivariance error of the convolution to \tabref{cosmo}
+%	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
+%\end{itemize}
+%}
+%
 \end{document}

### 2019-11-07 main.tex
version submitted to ICLR'20
Updates from Overleaf

@@
 %\title{DeepSphere, an efficient (& equivariant) graph-based spherical CNN}
-
 \author{Michaël Defferrard, Martino Milani \& Frédérick Gusset \\
@@
 \begin{abstract}
-% We have to submit soon... The last sentence is a bit disconnected. Yep
-Designing a convolution for a spherical neural network requires a delicate tradeoff between efficiency and rotation equivariance. % exactitude with respect to equivariance.
+% We have to submit soon... The last sentence is a bit disconnected. Yep, better... Let submit... It is time.... Submit Submit Submit Submit 2 minutes... DONE!!!!! 
+Designing a convolution for a spherical neural network requires a delicate tradeoff between efficiency and rotation equivariance.
+% exactitude with respect to equivariance.
 DeepSphere, a method based on a graph representation of the discretized sphere, strikes a controllable balance between these two desiderata.
@@
 First, we study both theoretically and empirically how equivariance is affected by the underlying graph with respect to the number of pixels and neighbors.
-% 
 Second, we evaluate DeepSphere on relevant problems.
 Experiments show state-of-the-art performance and demonstrates the efficiency and flexibility of this formulation.
-In particular, comparison with previous work on shape classification and climate event detection suggests that anisotropic filters are an unnecessary price to pay. 
+Perhaps surprisingly, comparison with previous work suggests that anisotropic filters might be an unnecessary price to pay.
 %Say something about speed here... Not sure what?
@@
 \begin{theorem}
-	For a sampling $\V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$ such that
+	For a sampling $\V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$ such that
 % 	the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$  
@@
 	\end{equation*}
-	where $\sigma_i\subset \S^2$ is the subset of the sphere corresponding to the patch arround $x_i$. Remember that the sampling is equal area.
+	where $\sigma_i\subset \S^2$ is the subset of the sphere corresponding to the patch around $x_i$. Remember that the sampling is equal area.
 	Hence, using the triangular inequality and summing all the contributions of the $n$ patches, we obtain
@@
 	\begin{equation*}
-	\forall f \text{ Lipschiz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{\|x_i-y\|^2}{4t}}\rightarrow   \int e^{-\frac{\|x-y\|^2}{4t}}d\mu(x) 
+	\forall f \text{ Lipschitz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{\|x_i-y\|^2}{4t}}\rightarrow   \int e^{-\frac{\|x-y\|^2}{4t}}d\mu(x) 
 	\end{equation*}
     \begin{equation*}
-    \forall f \text{ Lipschiz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}f(x_i)\rightarrow   \int e^{-\frac{\|x-y\|^2}{4t}}f(x)d\mu(x)        
+    \forall f \text{ Lipschitz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}f(x_i)\rightarrow   \int e^{-\frac{\|x-y\|^2}{4t}}f(x)d\mu(x)        
     \end{equation*}
@@
 \begin{align*}
-	C_{\phi^t_y} &= \|\partial_x\phi^t(\cdot;y)|\_\infty\\&
+	C_{\phi^t_y} &= \|\partial_x\phi^t(\cdot;y)\|_\infty\\&
 	= \|\partial_x\left(K^t(\cdot;y)f\right)\|_\infty\\&
@@
 Indeed, we have\\
-$n^\alpha t^{5/2}=n^{5/2\beta+\alpha}\xrightarrow{n \to \infty} \infty$ since $\frac{5}{2}\beta+\alpha>0 \iff \beta>-\frac{2\alpha}{5}$\\
+$n^alpha t^{5/2}=n^{5/2\beta+\alpha}\xrightarrow{n \to \infty} \infty$ since $\frac{5}{2}\beta+\alpha>0 \iff \beta>-\frac{2\alpha}{5}$\\
 and $n^\alpha t^2=n^{2\beta+\alpha}\xrightarrow {n \to \infty} \infty$ since $2\beta+\alpha>0 \iff \beta>-\frac{\alpha}{2}$.\\

### 2019-11-07 rebuttal.md
rebuttal

## Two Questions about Rotation Equivariance
Jialin Liu
07 Nov 2019ICLR 2020 Conference Paper2413 Public CommentReaders: Everyone
Comment: Really interesting work.
I've got 2 questions:
1, As for efficiency, why not use GCN proposed by T.K. Kipf, the successor of ChebNet?
2. As for rotation equivariance, CCN states that "It is, however, possible to construct a CNN in which the activations transform in a predictable and reversible way," I understand what is reversible(invertible) in this work is what CCN calls activation, what is reversible in CCN is the rotation operator in this work, are they same?

Thanks.

Ref.
1. Semi-Supervised Classification with Graph Convolutional Networks. ICLR'17.
2. Covariant Compositional Networks For Learning Graphs. ICLR'18

## Official Blind Review #2
ICLR 2020 Conference Paper2413 AnonReviewer2
24 Oct 2019 (modified: 05 Nov 2019)ICLR 2020 Conference Paper2413 Official ReviewReaders: Everyone
Experience Assessment: I have read many papers in this area.
Rating: 8: Accept
Review Assessment: Thoroughness In Paper Reading: I read the paper at least twice and used my best judgement in assessing the paper.
Review Assessment: Checking Correctness Of Experiments: I assessed the sensibility of the experiments.
Review Assessment: Checking Correctness Of Derivations And Theory: I assessed the sensibility of the derivations and theory.
Review:
The paper presents DeepSphere, a method for learning over spherical data via a graphical representation and graph-convolutions. The primary goal is to develop a method that encodes equivariance to rotations, cheaply. The graph is formed by sampling the surface of the sphere and connecting neighbors according to a distance-based similarity measure. The equivariance of the representation is demonstrated empirically and theoretical background on its convergence properties are shown. DeepSphere is then demonstrated on several problems as well as shown how it applies to non-uniform data.

The paper is interesting and clear. The projection of structured data to graphical representations is both efficient in utilizing existing algorithmic techniques for graph convolutions and useful for approaching the spherical structure of the data. The theoretical analysis and discussion of sampling is interesting, though should be more clearly stated throughout and potentially visualized in figures.

The experiments performed are thorough and interesting. The approach both outperforms baselines in inference time and accuracy. However, one wonders the performance on the well-researched tasks such as the performance on 3D imagery, e.g., Su & Grauman, 2017; Coors et al., 2018.

The unevenly sampled data is a nice extension showing the generality of the approach. How does the approach work for data connected within a radius rather than a k-nearest approach?

Minor:
- A figure detailing the parameters and setup for theorem 3.1 and figure 2 would be useful.
- The statement on the dispersion of the sampling sequence states “the smallest ball in \R^3 containing \sigma_i”, but I believe it should be “containing only \sigma_i”.

## Official Blind Review #3
ICLR 2020 Conference Paper2413 AnonReviewer3
23 Oct 2019 (modified: 05 Nov 2019)ICLR 2020 Conference Paper2413 Official ReviewReaders: Everyone
Experience Assessment: I have published one or two papers in this area.
Rating: 6: Weak Accept
Review Assessment: Thoroughness In Paper Reading: I read the paper thoroughly.
Review Assessment: Checking Correctness Of Experiments: I carefully checked the experiments.
Review Assessment: Checking Correctness Of Derivations And Theory: I carefully checked the derivations and theory.
Review: The paper studies the problem of designing a convolution for a spherical neural network. The authors use the existing graph CNN formulation and a pooling strategy that exploits hierarchical pixelations of the sphere to learn from the discretized sphere. The main idea is to model the discretized sphere as a graph of connected pixels: the length of the shortest path between two pixels is an approximation of the geodesic distance between them. To show the computational efficiency, sampling flexibility and rotation equivariance, extensive experiments are conducted, including 3D object recognition, cosmological mode classification, climate event segmentation and uneven sampling.
Pros: 
1. The application and combination of different techniques in this paper are smart.
2. The experiments show that the proposed method outperforms other baseline methods.
3. The paper is well organized and written. 
Cons:
1. It is a good application of known techniques, but the novelty is limited.
2. It is suggested to add more baselines in the experiments.

[1] Michael Defferrard, Xavier Bresson, and Pierre Vandergheynst. Convolutional neural networks on graphs with fast localized spectral filtering. In Advances in Neural Information ProcessingSystems, 2016

## Official Blind Review #1
ICLR 2020 Conference Paper2413 AnonReviewer1
22 Oct 2019 (modified: 05 Nov 2019)ICLR 2020 Conference Paper2413 Official ReviewReaders: Everyone
Rating: 6: Weak Accept
Experience Assessment: I do not know much about this area.
Review Assessment: Checking Correctness Of Derivations And Theory: I assessed the sensibility of the derivations and theory.
Review Assessment: Checking Correctness Of Experiments: I did not assess the experiments.
Review Assessment: Thoroughness In Paper Reading: I made a quick assessment of this paper.
Review: In this paper, CNNs specialized for spherical data are studied. The proposed architecture is a combination of existing frameworks based on the discretization of a sphere as a graph. As a main result, the paper shows a convergence result, which is related to the rotation equivalence on a sphere. The experiments show the proposed model achieves a good tradeoff between the prediction performance and the computational cost.

Although the theoretical result is not strong enough, the empirical results show the proposed approach is promising. Therefore I vote for acceptance.

The paper is overall clearly written. It is nice that the authors try to mitigate from overclaiming of the analysis.

As a non-expert of spherical CNN, I don't understand clearly the gap between the result Theorem 3.1 and showing the rotation equivalence. It would be nice to add some counterexample (i.e., in what situation the proposed approach does not have rotational equivalence while Theorem 3.1 holds).

### 2019-11-07 main.tex
Updates from Overleaf

--- 2019-09-25 main.tex
@@
 
+\clearpage
+\newpage
+
+\begin{description}
+	\item[git] \url{https://github.com/nperraud/deepsphere_v2_paper}
+	\item[overleaf] \url{https://www.overleaf.com/project/5d31d2fbd6859d54cb707212}
+	\item[openreview] \url{https://openreview.net/forum?id=B1e3OlStPB}
+\end{description}
+
+story: there are tradeoffs when designing a spherical CNN -> DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
+% DSv2 has a clear tradeoff between equivariance and computational cost
+
+* method development: tool that solve a need (balance btw the desiderata: equiv vs cost)\\
+* research question: anisotropy (highlight from the start or leave it as a dangling question in the end)\\
+
+contributions:\\
+* theory $\Rightarrow$ convergence (better graph)\\
+* experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata\\
+  * surprising: anisotropy doesn't seem useful\\
+
+\todo{
+\begin{itemize}
+% 	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN. [Yes]
+% 	\item adjacency matrix: $A$ instead of $W$? nath: I am for W
+% 	\item anonymize DeepSphere citation - Not doing that
+% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
+	\item citet for inline, citep for parenthesis
+	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
+	\item PSD of climate data: how does it compare to cosmo and 3D objects?
+	\item align the spheres in figure 1
+	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
+	\item check footnotes
+	\item climate data on spectrum plot
+	\item result tables: only what supports the main message in the text, everything we have in the appendix
+	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
+	\item check English vs American English
+	\item unify enumerations. I like (i), (ii), etc.
+	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness?
+	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere.
+	\item figure placements
+	\item do the experiments on the icosahedral grid with the pooling as defined in the paper
+	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
+	\item update pygsp and merge sphere branch
+	\item check that NN architectures and hyper-params are correctly reported
+	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space.
+	%\item shall we still site adam and batch norm? no, mainstream enough
+	\item check results for ModelNet40 and integrate in text
+	\item Check that HEALPix is introduced in the introduction
+	\item heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison.
+% 	\item check experiments section [Frédérick]: all the results numbers and NN + training details
+	\item compute the invariance error of the whole NNs (before and after training, invariance can be learned)
+	\item add it with equivariance error of the convolution to \tabref{cosmo}
+	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
+\end{itemize}
+}
+
+\todo{
+rebuttal:
+\begin{itemize}
+    \item answer Jialin Liu [mdeff] -> 1) need to be a Laplacian, Kipft is K=1
+\end{itemize}
+}
+
 \maketitle
@@
 \begin{abstract}
-Selecting the right convolution for a spherical neural network is a delicate tradeoff between efficiency and  exactitude with respect to equivariance.
-DeepSphere, as a graph based method strikes as a controllable balance between these two desiderata.
+% We have to submit soon... The last sentence is a bit disconnected. Yep, better... Let submit... It is time.... Submit Submit Submit Submit 2 minutes... DONE!!!!! 
+Designing a convolution for a spherical neural network requires a delicate tradeoff between efficiency and rotation equivariance.
+% exactitude with respect to equivariance.
+DeepSphere, a method based on a graph representation of the discretized sphere, strikes a controllable balance between these two desiderata.
 % Say something here about isotropy?
-This contribution (i) studies empirically and theoretically how the construction of its underlying graph affects equivariance, and (ii) evaluates its performance on a large set of relevant problems.
-
-Comparison with previous work on shape classification and climate event detection suggests that anisotropic filters are an unnecessary price to pay.
+This contribution is twofold.
+First, we study both theoretically and empirically how equivariance is affected by the underlying graph with respect to the number of pixels and neighbors.
+Second, we evaluate DeepSphere on relevant problems.
+Experiments show state-of-the-art performance and demonstrates the efficiency and flexibility of this formulation.
+Perhaps surprisingly, comparison with previous work suggests that anisotropic filters might be an unnecessary price to pay.
+%Say something about speed here... Not sure what?
 % memory, computations, implementation complexity
@@
 
-\clearpage
-\newpage
-
-\begin{description}
-	\item[git] \url{https://github.com/nperraud/deepsphere_v2_paper}
-	\item[overleaf] \url{https://www.overleaf.com/project/5d31d2fbd6859d54cb707212}
-\end{description}
-
-story: there are tradeoffs when designing a spherical CNN -> DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
-% DSv2 has a clear tradeoff between equivariance and computational cost
-
-* method development: tool that solve a need (balance btw the desiderata: equiv vs cost)\\
-* research question: anisotropy (highlight from the start or leave it as a dangling question in the end)\\
-
-contributions:\\
-* theory $\Rightarrow$ convergence (better graph)\\
-* experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata\\
-  * surprising: anisotropy doesn't seem useful\\
-
-\todo{
-\begin{itemize}
-% 	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN. [Yes]
-% 	\item adjacency matrix: $A$ instead of $W$? nath: I am for W
-% 	\item anonymize DeepSphere citation - Not doing that
-% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
-	\item citet for inline, citep for parenthesis
-	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
-	\item PSD of climate data: how does it compare to cosmo and 3D objects?
-	\item align the spheres in figure 1
-	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
-	\item check footnotes
-	\item climate data on spectrum plot
-	\item result tables: only what supports the main message in the text, everything we have in the appendix
-	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
-	\item check English vs American English
-	\item unify enumerations. I like (i), (ii), etc.
-	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness?
-	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere.
-	\item figure placements
-	\item do the experiments on the icosahedral grid with the pooling as defined in the paper
-	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
-	\item update pygsp and merge sphere branch
-	\item check that NN architectures and hyper-params are correctly reported
-	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space.
-	%\item shall we still site adam and batch norm? no, mainstream enough
-	\item check results for ModelNet40 and integrate in text
-	\item Check that HEALPix is introduced in the introduction
-	\item heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison.
-% 	\item check experiments section [Frédérick]: all the results numbers and NN + training details
-	\item compute the invariance error of the whole NNs (before and after training, invariance can be learned)
-	\item add it with equivariance error of the convolution to \tabref{cosmo}
-	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
-\end{itemize}
-}
-
 \end{document}

### 2019-11-08 rebuttal.md
rebuttal meeting

@@
+# ICLR'20 rebuttal
+
 ## Two Questions about Rotation Equivariance
+
 Jialin Liu
 07 Nov 2019ICLR 2020 Conference Paper2413 Public CommentReaders: Everyone
+
 Comment: Really interesting work.
@@
 
+### Answer
+
+1) need to be a Laplacian (not their single-parameter variant), Kipf's two-parameter variant is ChebNet with a  polynomial order K=1.
+The method scales linearly with K, which is an hyper-parameter to be set (analogous to the kernel size in classical CNNs)
+2) don't understand the question
+
 ## Official Blind Review #2
+
 ICLR 2020 Conference Paper2413 AnonReviewer2
@@
 Review Assessment: Checking Correctness Of Derivations And Theory: I assessed the sensibility of the derivations and theory.
+
 Review:
@@
 
+### Answer
+
+* "The theoretical analysis and discussion of sampling is interesting, though should be more clearly stated throughout and potentially visualized in figures."
+* "How does the approach work for data connected within a radius rather than a k-nearest approach?" => that shouldn't change much rigth? Especially on HEALPix.
+
+Minor issues have been addressed. Thanks for pointing them out.
+
 ## Official Blind Review #3
+
 ICLR 2020 Conference Paper2413 AnonReviewer3
@@
 Review Assessment: Checking Correctness Of Derivations And Theory: I carefully checked the derivations and theory.
+
 Review: The paper studies the problem of designing a convolution for a spherical neural network.
@@
 
+### Answer
+
+Thanks for your review.
+
+Baselines: I don't think so.
+
 ## Official Blind Review #1
+
 ICLR 2020 Conference Paper2413 AnonReviewer1
@@
 Review Assessment: Thoroughness In Paper Reading: I made a quick assessment of this paper.
+
 Review: In this paper, CNNs specialized for spherical data are studied.
@@
 The experiments show the proposed model achieves a good tradeoff between the prediction performance and the computational cost.
-
 Although the theoretical result is not strong enough, the empirical results show the proposed approach is promising. Therefore I vote for acceptance.
@@
 It would be nice to add some counterexample (i.e., in what situation the proposed approach does not have rotational equivalence while Theorem 3.1 holds).
+
+### Answer
+
+We have a stronger theorem that [...]. No more gap.We have a stronger theorem that [...]. No more gap.

### 2019-11-09 rebuttal.md
update rebuttal

@@
 # ICLR'20 rebuttal
+
+## General comment about revised manuscript
+
+We uploaded an improved manuscript thanks to the reviewers' comments.
+The following has been updated:
+* New proof
+
+A link to a public git repository containing all the code will be added to the camera-ready version.
 
@@
 
-1) need to be a Laplacian (not their single-parameter variant), Kipf's two-parameter variant is ChebNet with a  polynomial order K=1.
-The method scales linearly with K, which is an hyper-parameter to be set (analogous to the kernel size in classical CNNs)
-2) don't understand the question
+1.
+First of all, the operator needs to be a Laplacian (why?), excluding the single-parameter variant of GCN.
+The two-parameter variant is ChebNet with a polynomial order of K=1.
+The method scales linearly with K, which is an hyper-parameter to be set (analogous to the kernel size in classical CNNs).
+TODO: check GCN paper for the variants
+
+2. TODO: Don't understand the question. Read the CCN paper.
 
@@
 
-* "The theoretical analysis and discussion of sampling is interesting, though should be more clearly stated throughout and potentially visualized in figures."
-* "How does the approach work for data connected within a radius rather than a k-nearest approach?" => that shouldn't change much rigth? Especially on HEALPix.
+"The theoretical analysis and discussion of sampling is interesting, though should be more clearly stated throughout and potentially visualized in figures."
+TODO: What should we do?
 
-Minor issues have been addressed. Thanks for pointing them out.
+We deliberately excluded experiments on omnidirectional imagery.
+In our opinion, those don't possess full spherical symmetries as gravity is orienting the objects.
+We encourage you to check the work of Khasanova and Frossard, who explicitly designed graph-based spherical CNNs for omnidirectional imaging.
+In [1], they designed a graph that yields an equivariant convolution to a subgroup of SO(3).
+Longitudinal rotations are equivariant by construction of the equiangular sampling, and they optimized the graph for latitudinal equivariance.
+Their scheme is presented in section 3.2 of our paper.
+While their convolution is not equivariant to the whole of SO(3), that is not an issue for this application as gravity prevents objects from rotating around the third axis.
+It may even be beneficial.
+Moreover, the orientation given by gravity allows to factorize the spherical graph and design anisotropic filters [2].
+
+The choice of
+redius or kNN in uneven sampling setting
+Sparsifying the graph with a radius or kNN approach doesn't change much. Sparsification is
+
+"A figure detailing the parameters and setup for theorem 3.1 and figure 2 would be useful." What does it mean?
+
+We thinks the statement about the dispersion of the sampling sequence. Thanks for pointing it out.
+
+[1] Renata Khasanova and Pascal Frossard. Graph-based classification of omnidirectional images. In Proceedings of the IEEE International Conference on Computer Vision, 2017.
+[2] Renata Khasanova and Pascal Frossard. Geometry Aware Convolutional Filters for Omnidirectional Images Representation. In International Conference on Machine Learning. 2019.
 

### 2019-11-09 main.tex
rebuttal meeting
fix escape
update rebuttal

@@
 \begin{document}
-
-\clearpage
-\newpage
 
@@
 \begin{itemize}
-    \item answer Jialin Liu [mdeff] -> 1) need to be a Laplacian, Kipft is K=1
+    \item answer reviewers and commenters [mdeff \& nath]
+    \item update the proof [nath \& martino]
+    \item better link between the proof and equivarian
+    \item publish the code and link it here
+	\item swap AR and TC on figure 1
+	\item add somewhere: exploit symmetries to reduce sample cost
 \end{itemize}
 }
+
+\clearpage
+\newpage
 
@@
 We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme.
-Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area and $d_i$ the radius of the smallest ball in $\R^3$ containing $\sigma_i$.
+Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area and $d_i$ the radius of the smallest ball in $\R^3$ containing only $\sigma_i$.
 Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.

### 2019-11-09 rebuttal.md
update rebuttal

@@
 The method scales linearly with K, which is an hyper-parameter to be set (analogous to the kernel size in classical CNNs).
-TODO: check GCN paper for the variants
+TODO{mdeff}: check GCN paper for the variants
 
-2. TODO: Don't understand the question. Read the CCN paper.
+2. TODO{mdeff}: Don't understand the question. Read the CCN paper.
 
@@
 
+We thank the reviewer for their time assessing our work and their feedback.
+
 "The theoretical analysis and discussion of sampling is interesting, though should be more clearly stated throughout and potentially visualized in figures."
-TODO: What should we do?
+TODO{mdeff}: What should we do?
 
@@
 
-The choice of
-redius or kNN in uneven sampling setting
-Sparsifying the graph with a radius or kNN approach doesn't change much. Sparsification is
+Radius or kNN graphs are means to get a sparse graph for O(n) matrix multiplication, instead of O(n²) for the full distance-based similarity graph.
+The choice of one or the other doesn't really matter.
+Sparsification can be seen as a numerical approximation that replaces small values by zeroes.
+The kNN scheme is often preferred in practice as the choice of k is directly linked to the computational cost, while the choice of a radius large enough to avoid disconnected vertices might include many more edges than necessary on denser areas.
 
-"A figure detailing the parameters and setup for theorem 3.1 and figure 2 would be useful." What does it mean?
+"A figure detailing the parameters and setup for theorem 3.1 and figure 2 would be useful."
+TODO{mdeff): What does it mean?
 
-We thinks the statement about the dispersion of the sampling sequence. Thanks for pointing it out.
+We fixed the statement about the dispersion of the sampling sequence. Thanks for pointing it out.
+TODO{mdeff): Nath, is he correct?
 
@@
 
-Thanks for your review.
+We thank the reviewer for their time assessing our work and their feedback.
 
-Baselines: I don't think so.
+While novelty might be limited (although we'd argue that designing a good graph is not trivial), potential impact is certainly not.
+Researchers working with large spherical maps, in multiple fields, will benefit from the possibility to tackle their problems with a neural network.
+
+Which other baselines would you like to see? We compared with previous works that tackled the same tasks. It is difficult (and probably unfair) to adapt baselines not designed to solve those tasks.
 
@@
 
-We have a stronger theorem that [...]. No more gap.We have a stronger theorem that [...]. No more gap.
+We thank the reviewer for their time assessing our work and their feedback.
+
+"the theoretical result is not strong enough"
+TODO(mdeff): Nath, can you answer?
+
+We have a stronger theorem that [...]. There is no more gap between Theorem 3.1 and equivariance.
+TODO{mdeff}: Nath, is it true? Do we have spectral convergence? Or uniform is sufficient? Can you complete the answer?

### 2019-11-10 rebuttal.md
some update to the rebuttal

@@
 
-We thank the reviewer for their time assessing our work and their feedback.
+We thank the reviewer for their time assessing our work and their constructive feedback.
 
@@
 TODO{mdeff}: What should we do? 
+{nati}: I think we should say that it is beyond the scope of this paper… We already have a loooot of appendices.
 
@@
 In our opinion, those don't possess full spherical symmetries as gravity is orienting the objects.
-We encourage you to check the work of Khasanova and Frossard, who explicitly designed graph-based spherical CNNs for omnidirectional imaging.
+We encourage the reviewer to check the work of Khasanova and Frossard, who explicitly designed graph-based spherical CNNs for omnidirectional imaging.
 In [1], they designed a graph that yields an equivariant convolution to a subgroup of SO(3).
@@
 It may even be beneficial.
-Moreover, the orientation given by gravity allows to factorize the spherical graph and design anisotropic filters [2].
+Moreover, the orientation given by gravity allows factorizing the spherical graph and design anisotropic filters [2].
 
 Radius or kNN graphs are means to get a sparse graph for O(n) matrix multiplication, instead of O(n²) for the full distance-based similarity graph.
-The choice of one or the other doesn't really matter.
+We believe that the choice of one or the other doesn't really matter.
 Sparsification can be seen as a numerical approximation that replaces small values by zeroes.
@@
 TODO{mdeff): What does it mean? 
+nati: I am not sure. We might just want to ask him?
+I think he wants the value of t that we used... Hence, we should make it clear that we did not use directly theorem 3.1 to make figure 2, but that we selected value for t that lead to good results.
 
@@
 TODO{mdeff): Nath, is he correct?
+{nati}: I think our original version is correct.
+Given a small surface sigma_i and its corresponding point x_i, d_i defines the biggest distance to the center.
+Hence, we do not care if the ball contains other points surfaces.
+However, we should add that the ball needs to be centered in x_i.
+(Can you just check with Martino to be on the safe side?)
 
@@
 
-We thank the reviewer for their time assessing our work and their feedback.
+We thank the reviewer for their time assessing our work and their constructive feedback.
 
 "the theoretical result is not strong enough"
-TODO(mdeff): Nath, can you answer?
+Since the first submission of the paper, we have made some progress with respect of the theoretical contributions. 
+In the new version of the paper, we add a new theorem that shows equivariance at the limit where the sampling is infinite.
+This new result is a pointwise convergence, meaning that for a fixed function f, RLf(x) -> LRf(x).
+To answer the last point of the reviewer, thanks to this new result, we know that there does not exist any counterexample where Theorem 3.1 holds while having no rotational equivariance.
+(Check with Martino to be on the safe side)
 
-We have a stronger theorem that [...]. There is no more gap between Theorem 3.1 and equivariance.
 TODO{mdeff}: Nath, is it true? Do we have spectral convergence? Or uniform is sufficient? Can you complete the answer?
+{nati}: I would not speak about spectral convergence as it is complicated...

### 2019-11-11 rebuttal.md
add answer 1 of Jian Liu

@@
 ### Answer
+Dear Jialin Liu,
+Thank you for your interest and questions.
 
@@
 The method scales linearly with K, which is an hyper-parameter to be set (analogous to the kernel size in classical CNNs).
+For the theory
+{nati version} : Practically, we believe that any graph neural network variant may work and some might even slightly beat ChebyNet. 
+However, our equivariance theory utilizes the graph Laplacian as a base building block. 
+Hence, we do not know the theoretical properties of other GCNs such as the single parameter variant from T.K. Kipf. 
+Note that the two-parameter variant from T.K. Kipf is ChebNet with a polynomial order of K=1. 
+Eventually, the method we use scales linearly with K, which is an hyper-parameter to be set (analogous to the kernel size in classical CNNs).
+
 TODO{mdeff}: check GCN paper for the variants

### 2019-11-11 main.tex
update rebuttal
small modification

@@
 We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme.
-Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area and $d_i$ the radius of the smallest ball in $\R^3$ containing only $\sigma_i$.
+Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area and $d_i$ the radius of the smallest ball in $\R^3$ containing $\sigma_i$ and centered at $x_i$.
 Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
@@
 %We thank Taco Cohen for his inputs on the intriguing results of our comparison with \citet{cohen2019gauge}.
+%We thank the anonymous reviewers for their constructive feedback.
 %We used the Python Graph Signal Processing package (PyGSP) \citep{pygsp} for computations and plots.

### 2019-11-11 rebuttal.md
another pass on the rebuttal

@@
 The method scales linearly with K, which is an hyper-parameter to be set (analogous to the kernel size in classical CNNs).
-For the theory
-{nati version} : Practically, we believe that any graph neural network variant may work and some might even slightly beat ChebyNet. 
+TODO(mdeff): check GCN paper for the variants
+TODO(nati) my version:
+Practically, we believe that any graph neural network variant may work and some might even slightly beat ChebyNet.
 However, our equivariance theory utilizes the graph Laplacian as a base building block.
@@
 
-TODO{mdeff}: check GCN paper for the variants
-
-2. TODO{mdeff}: Don't understand the question. Read the CCN paper.
+2. TODO(mdeff): Don't understand the question. Read the CCN paper.
 
@@
 "The theoretical analysis and discussion of sampling is interesting, though should be more clearly stated throughout and potentially visualized in figures."
-TODO{mdeff}: What should we do? 
-{nati}: I think we should say that it is beyond the scope of this paper… We already have a loooot of appendices.
+TODO(mdeff): What should we do?
+TODO(nati): I think we should say that it is beyond the scope of this paper… We already have a loooot of appendices.
+TODO(mdeff): I mean, I don't understand what he would like us to do.
 
@@
 "A figure detailing the parameters and setup for theorem 3.1 and figure 2 would be useful."
-TODO{mdeff): What does it mean? 
-nati: I am not sure. We might just want to ask him?
+TODO(mdeff): What does it mean?
+TODO(nati): I am not sure. We might just want to ask him?
 I think he wants the value of t that we used... Hence, we should make it clear that we did not use directly theorem 3.1 to make figure 2, but that we selected value for t that lead to good results.
@@
 We fixed the statement about the dispersion of the sampling sequence. Thanks for pointing it out.
-TODO{mdeff): Nath, is he correct?
-{nati}: I think our original version is correct.
+TODO(mdeff): Nath, is he correct?
+TODO(nati): I think our original version is correct.
 Given a small surface sigma_i and its corresponding point x_i, d_i defines the biggest distance to the center.
@@
 (Can you just check with Martino to be on the safe side?)
+TODO(mdeff): Ok so if I understood correctly, d_i is the largest distance between the center x_i and any point on the surface sigma_i.
+(That also corresponds to what I remember from past discussions.) Martino, do you confirm?
+If true, we should formulate it better in the paper.
+
+A revised manuscript will be uploaded shortly.
 
@@
 
-While novelty might be limited (although we'd argue that designing a good graph is not trivial), potential impact is certainly not.
+While novelty might be limited (although we'd argue that designing a good graph is non-trivial, if only by checking how many papers have been written on the convergence / consistency of discrete Laplacians), potential impact is certainly not.
 Researchers working with large spherical maps, in multiple fields, will benefit from the possibility to tackle their problems with a neural network.
@@
 
-"the theoretical result is not strong enough"
-Since the first submission of the paper, we have made some progress with respect of the theoretical contributions. 
-In the new version of the paper, we add a new theorem that shows equivariance at the limit where the sampling is infinite.
-This new result is a pointwise convergence, meaning that for a fixed function f, RLf(x) -> LRf(x).
-To answer the last point of the reviewer, thanks to this new result, we know that there does not exist any counterexample where Theorem 3.1 holds while having no rotational equivariance.
-(Check with Martino to be on the safe side)
+A revised manuscript, to be uploaded shortly, contains a stronger theoretical result.
+The new theorem proves that for a fixed function f, RLf(x) = LRf(x) in the limit of infinite sampling.
+That is, it proves equivariance (in addition to convergence to the Laplace-Beltrami proved by Theorem 3.1).
 
-TODO{mdeff}: Nath, is it true? Do we have spectral convergence? Or uniform is sufficient? Can you complete the answer?
-{nati}: I would not speak about spectral convergence as it is complicated...
+Thanks to this new result, we know that there does not exist any counterexample where Theorem 3.1 holds while not having rotational equivariance.
+
+TODO(nati): check with Martino to be on the safe side

### 2019-11-11 main.tex

@@
 \newcommand{\E}{\mathcal{E}}  % edge set
+\newcommand{\laplacian}{\Delta_{\mathbb S^2}}
+\newcommand{\Rg}{\mathcal R_g}
+\newcommand{\seminorm}[1]{\left|#1\right|}
+\newcommand{\Ln}{L_n^{t_n}}
+
 \DeclareMathOperator*{\diag}{diag}
@@
 We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme.
-Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area and $d_i$ the radius of the smallest ball in $\R^3$ containing $\sigma_i$ and centered at $x_i$.
+\mart{Here we insert the definition of the extended graph laplacian and of the rotation operator Rg} Following their setting, we define the extended graph Laplacian operator as a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
+	\begin{equation}
+	\label{eq:Heat Kernel Graph Laplacian operator}
+	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
+	\end{equation}
+Note that we have the following relation $\b{L}_n^t \b{f} = T_\V L_n^t f$.
+Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, we also define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area and $d_i$ the radius of the smallest ball in $\R^3$ containing only $\sigma_i$.
 Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
+Given any rotation $g\in SO(3)$, we define the corresponding rotation operator $\mathcal R_g$ such that for any function $f$ on the sphere
+\begin{equation}\label{eq:rotation operator}
+\mathcal R_g f(x) := f(g^{-1}(x)).
+\end{equation}
 \begin{theorem}
@@
 	\begin{equation*}
-	 \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} T_\V f [i] =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.
+		\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) = \frac{1}{|\S^2|}\triangle_{\S^2}f(y)
 	\end{equation*} 
@@
 \end{theorem}
-As a direct implication of this theorem, $\b{L}$ converges pointwisely toward the Laplace-Beltrami operator ($\Delta_{\S^2}$).
-This operator commutes with rotation and hence this convergence is a strong hint for equivariance.
+As a direct implication of this theorem, $\b{L}$ converges pointwisely toward the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \cite{belkin2007convergence}.
+\mart{here we insert the link between consistency and equivariance} This operator commutes with rotation and hence this convergence is a strong hint for equivariance, as formalized in the following proposition.
+%%%%%%%%%%%%%%%%%%%%%%%  link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{prop}\label{prop:equivariance}
+Under the hypothesis of theorem \ref{theo:pointwise convergence for a regular sampling}, we have the following pointwise convergence
+\begin{equation*}
+\forall x\in\mathbb S^2\quad\left| \mathcal R_g L_n^{t_n} f (x) - L_n^{t_n} \mathcal R_g f(x) \right| \xrightarrow{n\to\infty}0.
+\end{equation*}
+\end{prop}
+%%%%%%%%%%%%%%%%%%%%%%% end of link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%
+
 Importantly, the proof of Theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix \ref{sec: appendix: proof of theorem} inspires us in the construction of our graph Laplacian.
@@
 
-Nevetheless, it is important to keep in mind the limits of Theorem \ref{theo:pointwise convergence for a regular sampling}.
+Nevertheless, it is important to keep in mind the limits of Theorem \ref{theo:pointwise convergence for a regular sampling}.
 First, it is \emph{not} a proof of equivariance of the graph convolution for a specific sampling.
-To construct such a proof, a stronger convergence result is needed, for example uniform convergence (instead of pointwise).
+To construct such a proof, a stronger convergence result is needed, for example spectral convergence (instead of pointwise).
 % \todo{Can we intuitively write what pointwise convergence means, and how it is more limited than spectral or uniform convergence?}
-We note that in the random sampling case, the graph laplacian does \emph{not} converges uniformly in general \cite[Sec.
+We note that in the random sampling case, the graph laplacian does \emph{not} converge uniformly in general \cite[Sec.
 3]{belkin2007convergence}, but does for a class of Lipschitz functions \cite[Sec.
@@
 Second, while do not have a formal proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$ with $\alpha$ very close or equal to $\linefrac{1}{2}$.
-The empirical results discussed in the next paragraph also point in this direction.
+The empirical results discussed in the next paragraph also points in this direction.
 This is further discussed in Appendix \ref{sec: appendix: proof of theorem}.
@@
 \begin{itemize}
-    \item The extended graph Laplacian operator is a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$  is defined as
+    \item The extended graph Laplacian operator
 	\begin{equation}
@@
 	\end{equation}
-	Note that we have the following relation $\b{L}_n^t \b{f} = T_\V L_n^t f$.
 	\item The functional approximation to the Laplace-Beltrami operator is a linear operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined  as
@@
 	\end{equation*}
-	Eventually selecting $y$ as a point of the sampling, we obtain
-	\begin{equation*}
-	 \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} T_\V f [i] =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.
-	\end{equation*} 
 \end{proof}
@@
 Given the kernel density $t(n)=n^\beta$, \cite{belkin2005towards} proved convergence in the random case for $\beta \in (-\frac{1}{4}, 0)$ and we proved convergence in the deterministic case for $\beta \in (-\frac{2\alpha}{5}, 0)$, where $\alpha \in (0, \linefrac{1}{2}]$ (for the spherical Manifold).
+
+\subsection{Proof of proposition \ref{prop:equivariance}}
+\begin{proof}
+Fix $x\in \mathbb S^2$.
+Since any rotation $\mathcal R_g$ is an isometry, and the Laplacian $\Delta$ commutes with all isometries of a Riemanniann manifold \cite{shubin}, and defining $\mathcal R_g f =: f'$ for ease of notation, we can write that
+	\begin{align*}
+			\seminorm{\Rg \Ln f (x) - \Ln \Rg f(x) } &\leq \seminorm{\Rg \Ln f (x) - \Rg \laplacian f(x)} + \seminorm{\Rg \laplacian f (x) - \Ln \Rg f(x)} =\\
+			& =\seminorm{\Rg (\Ln f - \laplacian f ) (x)} + \seminorm{ \laplacian f' (x) - \Ln f'(x)} \leq \\
+			& \leq \seminorm{(\Ln f - \laplacian f ) (g^{-1}(x))} + \seminorm{ \laplacian f' (x) - \Ln f'(x)}
+	\end{align*}
+
+Since $g^{-1}(x)\in\mathbb{S}^2$ and $f'$ still satisfies hypothesis, we can apply theorem \ref{theo:pointwise convergence for a regular sampling} to conclude that
+\begin{align*}
+ &\seminorm{(\Ln f - \laplacian f ) (g^{-1}(x))} \to 0\\
+  &\seminorm{ \laplacian f' (x) - \Ln f'(x)}\to 0
+\end{align*}
+to conclude that $$\forall x\in\mathbb S^2 \quad\seminorm{\Rg \Ln f (x) - \Ln \Rg f(x) } \xrightarrow{n\to\infty}0$$
+
+\end{proof}
 

### 2019-11-11 rebuttal.md
update rebuttal according to call (mdeff & nati)

@@
 
-"The theoretical analysis and discussion of sampling is interesting, though should be more clearly stated throughout and potentially visualized in figures."
-TODO(mdeff): What should we do?
-TODO(nati): I think we should say that it is beyond the scope of this paper… We already have a loooot of appendices.
-TODO(mdeff): I mean, I don't understand what he would like us to do.
-
 We deliberately excluded experiments on omnidirectional imagery.
@@
 
-"A figure detailing the parameters and setup for theorem 3.1 and figure 2 would be useful."
-TODO(mdeff): What does it mean?
-TODO(nati): I am not sure. We might just want to ask him?
-I think he wants the value of t that we used... Hence, we should make it clear that we did not use directly theorem 3.1 to make figure 2, but that we selected value for t that lead to good results.
+Thanks for pointing out an unclear statement about the dispersion of the sampling sequence.
+d_i should be thought of as the largest distance between the center x_i and any point on the surface sigma_i.
+Hence, we define d_i to be the radius of the smallest ball centered at x_i containing sigma_i.
+We'll clarify.
+TODO: Martino, do you approve?
 
-We fixed the statement about the dispersion of the sampling sequence. Thanks for pointing it out.
-TODO(mdeff): Nath, is he correct?
-TODO(nati): I think our original version is correct.
-Given a small surface sigma_i and its corresponding point x_i, d_i defines the biggest distance to the center.
-Hence, we do not care if the ball contains other points surfaces.
-However, we should add that the ball needs to be centered in x_i.
-(Can you just check with Martino to be on the safe side?)
-TODO(mdeff): Ok so if I understood correctly, d_i is the largest distance between the center x_i and any point on the surface sigma_i.
-(That also corresponds to what I remember from past discussions.) Martino, do you confirm?
-If true, we should formulate it better in the paper.
+From the following two sentences, we don't understand what could be improved.
+* "The theoretical analysis and discussion of sampling is interesting, though should be more clearly stated throughout and potentially visualized in figures."
+* "A figure detailing the parameters and setup for theorem 3.1 and figure 2 would be useful."
+We would be glad if the reviewer could elaborate.
 
@@
 A revised manuscript, to be uploaded shortly, contains a stronger theoretical result.
-The new theorem proves that for a fixed function f, RLf(x) = LRf(x) in the limit of infinite sampling.
-That is, it proves equivariance (in addition to convergence to the Laplace-Beltrami proved by Theorem 3.1).
+We proved that for a fixed function f, RLf(x) = LRf(x) in the limit of infinite sampling.
+That is, we proved equivariance (using the convergence to the Laplace-Beltrami proved by Theorem 3.1).
 
-Thanks to this new result, we know that there does not exist any counterexample where Theorem 3.1 holds while not having rotational equivariance.
+Thanks to this new result, there is no gap anymore. Hence, there does not exist any counterexample where Theorem 3.1 holds while not having rotational equivariance.
 
-TODO(nati): check with Martino to be on the safe side
+TODO: Martino, do you approve?

### 2019-11-11 main.tex
update rebuttal according to call (mdeff & nati)

@@
 Note that we have the following relation $\b{L}_n^t \b{f} = T_\V L_n^t f$.
-Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, we also define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area and $d_i$ the radius of the smallest ball in $\R^3$ containing only $\sigma_i$.
+Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, we also define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area and $d_i$ the radius of the smallest ball in $\R^3$ containing $\sigma_i$ and centered at $x_i$.
 Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
@@
 
-\subsection{Proof of proposition \ref{prop:equivariance}}
+\section{Proof of proposition \ref{prop:equivariance}}
 \begin{proof}
@@
 \begin{align*}
- &\seminorm{(\Ln f - \laplacian f ) (g^{-1}(x))} \to 0\\
-  &\seminorm{ \laplacian f' (x) - \Ln f'(x)}\to 0
+ &\seminorm{(\Ln f - \laplacian f ) (g^{-1}(x))} \xrightarrow{n\to\infty}0\\
+  &\seminorm{ \laplacian f' (x) - \Ln f'(x)}\xrightarrow{n\to\infty}0
 \end{align*}

### 2019-11-11 rebuttal.md
Updates from Overleaf

@@
 The following has been updated:
-* New proof
+* Slightly (very slightly) different statement of theorem 3.1
+* new proposition (now called prop 1) formalizing the relation between theorem 3.1 and rotation equivariance
 
@@
 We'll clarify.
-TODO: Martino, do you approve?
+TODO: Martino, do you approve? YES I APPROVE
 
@@
 
-A revised manuscript, to be uploaded shortly, contains a stronger theoretical result.
-We proved that for a fixed function f, RLf(x) = LRf(x) in the limit of infinite sampling.
-That is, we proved equivariance (using the convergence to the Laplace-Beltrami proved by Theorem 3.1).
-
-Thanks to this new result, there is no gap anymore. Hence, there does not exist any counterexample where Theorem 3.1 holds while not having rotational equivariance.
-
-TODO: Martino, do you approve?
+We prepared a revised manuscript, to be uploaded shortly, containing a deeper theoretical discussion about the gap between the result Theorem 3.1 and rotation equivariance.
+In a small proposition, to be added after theorem 3.1, we precise mathematically the relationship between these two concepts.
+In short, we proved that, if theorem 3.1 holds, our graph Laplacian L commutes with any rotation operator R in the limit of infinite sampling (pointwise), i.e.
+LRf(x)-RLf(x) \to 0, thus answering the reviewer's concerns about this subject.

### 2019-11-11 main.tex
small update
Updates from Overleaf

@@
 	\item add somewhere: exploit symmetries to reduce sample cost
+	\item proposition 1 -> corollary 3.1?
 \end{itemize}
@@
 \begin{theorem}
-	For a sampling $\V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$ such that
+	For a sampling $\V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$, $\beta\in\mathbb R$ such that
 % 	the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$  
@@
 \end{theorem}
-As a direct implication of this theorem, $\b{L}$ converges pointwisely toward the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \cite{belkin2007convergence}.
+As a direct implication of this theorem, $\b{L}$ converges pointwise towards the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \cite{belkin2007convergence}.
 \mart{here we insert the link between consistency and equivariance} This operator commutes with rotation and hence this convergence is a strong hint for equivariance, as formalized in the following proposition.
@@
 
-		\caption{Normalized mean equivariance error \eqref{eq:mean equivariance error}. The number of pixels is $4s^2$ for the equiangular sampling and $12s^2$ for the Healpix sampling.}
+		\caption{Normalized mean equivariance error \eqref{eq:mean equivariance error}. The number of pixels is $n = 4 s^2$ for the equiangular sampling and $n = 12 s^2$ for the HEALPix sampling.}
 		\label{fig:equivariance_error}
@@
 %We thank the anonymous reviewers for their constructive feedback.
+%The following packages were used for computation and plotting: pygsp, numpy, tensorflow, scipy, etc.
 %We used the Python Graph Signal Processing package (PyGSP) \citep{pygsp} for computations and plots.

### 2019-11-11 rebuttal.md
update

@@
 
-We prepared a revised manuscript, to be uploaded shortly, containing a deeper theoretical discussion about the gap between the result Theorem 3.1 and rotation equivariance.
+We prepared a revised manuscript, to be uploaded shortly, containing a deeper theoretical discussion closing the gap between the result Theorem 3.1 and rotation equivariance.
 In a small proposition, to be added after theorem 3.1, we precise mathematically the relationship between these two concepts.

### 2019-11-11 rebuttal.md
last pass on the rebuttal

--- 2019-11-11 rebuttal.md
@@
 ### Answer
-Dear Jialin Liu,
+
 Thank you for your interest and questions.
@@
 It may even be beneficial.
-Moreover, the orientation given by gravity allows factorizing the spherical graph and design anisotropic filters [2].
+Moreover, the orientation given by gravity allows to factorize the spherical graph and design anisotropic filters [2].
 
@@
 We believe that the choice of one or the other doesn't really matter.
-Sparsification can be seen as a numerical approximation that replaces small values by zeroes.
+Sparsification can be seen as a numerical approximation that replaces small values by zeros.
 The kNN scheme is often preferred in practice as the choice of k is directly linked to the computational cost, while the choice of a radius large enough to avoid disconnected vertices might include many more edges than necessary on denser areas.
@@
 Thanks for pointing out an unclear statement about the dispersion of the sampling sequence.
-d_i should be thought of as the largest distance between the center x_i and any point on the surface sigma_i.
+d_i should be understood as the largest distance between the center x_i and any point on the surface sigma_i.
 Hence, we define d_i to be the radius of the smallest ball centered at x_i containing sigma_i.
 We'll clarify.
-TODO: Martino, do you approve? YES I APPROVE
 
@@
 
-We prepared a revised manuscript, to be uploaded shortly, containing a deeper theoretical discussion about the gap between the result Theorem 3.1 and rotation equivariance.
+We prepared a revised manuscript, to be uploaded shortly, containing a deeper theoretical discussion closing the gap between Theorem 3.1 and rotation equivariance.
 In a small proposition, to be added after theorem 3.1, we precise mathematically the relationship between these two concepts.
-In short, we proved that, if theorem 3.1 holds, our graph Laplacian L commutes with any rotation operator R in the limit of infinite sampling (pointwise), i.e.
-LRf(x)-RLf(x) \to 0, thus answering the reviewer's concerns about this subject.
+In short, we proved that, if theorem 3.1 holds, our graph Laplacian L commutes with any rotation operator R in the limit of infinite sampling (pointwise), i.e., |LRf(x) - RLf(x)| -> 0, thus answering the reviewer's concerns about this subject.

### 2019-11-11 main.tex
last pass on the rebuttal

@@
 Note that we have the following relation $\b{L}_n^t \b{f} = T_\V L_n^t f$.
-Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, we also define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area and $d_i$ the radius of the smallest ball in $\R^3$ containing $\sigma_i$ and centered at $x_i$.
+Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, we define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area, and $d_i$ the radius of the smallest ball in $\R^3$ containing $\sigma_i$ and centered at $x_i$.%\footnote{$d_i$ should be understood as the largest distance between the center $x_i$ and any point on the surface $sigma_i$.}
 Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
@@
 	\begin{equation*}
-		\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) = \frac{1}{|\S^2|}\triangle_{\S^2}f(y)
+		\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) = \frac{1}{|\S^2|}\triangle_{\S^2}f(y).
 	\end{equation*} 
-% 	for $n\to\infty$.
 	\label{theo:pointwise convergence for a regular sampling}

### 2019-11-12 main.tex
Updates from Overleaf

--- 2019-11-11 main.tex
@@
 \newcommand{\seminorm}[1]{\left|#1\right|}
-\newcommand{\Ln}{L_n^{t_n}}
+\newcommand{\Ln}{\hat L_n^{t_n}}
 
@@
 \end{theorem}
-As a direct implication of this theorem, $\b{L}$ converges pointwise towards the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \cite{belkin2007convergence}.
-\mart{here we insert the link between consistency and equivariance} This operator commutes with rotation and hence this convergence is a strong hint for equivariance, as formalized in the following proposition.
+As a direct implication of this theorem, the rescaled operator $\hat L_n^{t_n} := \frac{|\mathbb S^2|}{4\pi t^2}L_n^{t_n}$ (and its discrete counterpart $ \mathbf{\hat L} = \frac{|\mathbb S^2|}{4\pi t^2} \mathbf L$) converges pointwise towards the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \cite{belkin2007convergence}.
+This operator commutes with rotation and hence this convergence is a strong hint for equivariance, as formalized in the following proposition.
 %%%%%%%%%%%%%%%%%%%%%%%  link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{prop}\label{prop:equivariance}
-Under the hypothesis of theorem \ref{theo:pointwise convergence for a regular sampling}, we have the following pointwise convergence
+Under the hypothesis of theorem \ref{theo:pointwise convergence for a regular sampling}, we have the following pointwise convergence for the rescaled graph Laplacian 
 \begin{equation*}
-\forall x\in\mathbb S^2\quad\left| \mathcal R_g L_n^{t_n} f (x) - L_n^{t_n} \mathcal R_g f(x) \right| \xrightarrow{n\to\infty}0.
+\forall y\in\mathbb S^2\quad\left| \mathcal R_g \hat L_n^{t_n} f (y) - \hat L_n^{t_n} \mathcal R_g f(y) \right| \xrightarrow{n\to\infty}0.
 \end{equation*}
@@
 Fix $x\in \mathbb S^2$.
-Since any rotation $\mathcal R_g$ is an isometry, and the Laplacian $\Delta$ commutes with all isometries of a Riemanniann manifold \cite{shubin}, and defining $\mathcal R_g f =: f'$ for ease of notation, we can write that
+Since any rotation $\mathcal R_g$ is an isometry, and the Laplacian $\Delta$ commutes with all isometries of a Riemanniann manifold, and defining $\mathcal R_g f =: f'$ for ease of notation, we can write that
 	\begin{align*}
@@
 
-Since $g^{-1}(x)\in\mathbb{S}^2$ and $f'$ still satisfies hypothesis, we can apply theorem \ref{theo:pointwise convergence for a regular sampling} to conclude that
+Since $g^{-1}(x)\in\mathbb{S}^2$ and $f'$ still satisfies hypothesis, we can apply theorem \ref{theo:pointwise convergence for a regular sampling} to say that
 \begin{align*}

### 2019-11-12 figures/kernel_widths.py
optimal kernel width as function of pixels (instead of Nside)

@@ -4,7 +4,8 @@ from os import path
 
 from matplotlib import pyplot as plt
 
-#plt.rc('font', family='Latin Modern Roman')
+plt.rc('font', family='Latin Modern Roman')  # Latin Modern for text
+plt.rc('mathtext', fontset='cm')  # Computer Modern for math (default is dejavusans)
 #plt.rc('text', usetex=True)
 #plt.rc('text.latex', preamble=r'\usepackage{lmodern}')
 
@@ -45,14 +46,14 @@ kernel_width_optimal = {
     },
 }
 
-fig, ax = plt.subplots(figsize=(5, 3))
+fig, ax = plt.subplots(figsize=(4, 2.3))
 for neighbors, optimums in sorted(kernel_width_optimal.items(), reverse=True):
-    nside = list(optimums.keys())
+    nside = [12*n**2 for n in optimums.keys()]
     width = list(optimums.values())
     ax.loglog(nside, width, '.-', label=f'$k={neighbors}$ neighbors')
 ax.legend(loc='upper right')
-ax.set_xlabel('$N_{side}$ ($n = 12 N_{side}^2$ pixels)')
-ax.set_ylabel('kernel width $t$')
+ax.set_xlabel('$n = 12 N_{side}^2$ pixels', fontsize=14)
+ax.set_ylabel('kernel width $t$', fontsize=14)
 #ax.set_title('optimal kernel widths')
 
 fig.tight_layout()

### 2019-11-13 main.tex
optimal kernel width as function of pixels (instead of Nside)
Updates from Overleaf

--- 2019-11-12 main.tex
@@
 We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme.
-\mart{Here we insert the definition of the extended graph laplacian and of the rotation operator Rg} Following their setting, we define the extended graph Laplacian operator as a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
+For this purpose we need now to introduce some definitions.
+Following their setting, we define the extended graph Laplacian operator as the linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
 	\begin{equation}
 	\label{eq:Heat Kernel Graph Laplacian operator}
-	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
+	 L_n^t f(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
 	\end{equation}
-Note that we have the following relation $\b{L}_n^t \b{f} = T_\V L_n^t f$.
-Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, we also define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area and $d_i$ the radius of the smallest ball in $\R^3$ containing $\sigma_i$ and centered at $x_i$.
+and the rescaled graph Laplacian operator
+    \begin{equation}
+	\label{eq:rescaled Heat Kernel Graph Laplacian operator}
+	 \hat L_n^t := \frac{|\mathbb S^2|}{4\pi t^2}L_n^t
+	\end{equation}
+Note that we have the following relations $\b{L}_n^t \b{f} = T_\V L_n^t f$, $\b{\hat L} = \frac{|\mathbb S^2|}{4\pi t^2}\b L_n^t$.
+Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, we define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area, and $d_i$ as the largest distance between the center $x_i$ and any point on the surface $\sigma_i$.
  Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
@@
 	\begin{equation*}
-		\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) = \frac{1}{|\S^2|}\triangle_{\S^2}f(y)
+		\lim_{n\to\infty}\hat L_n^{t_n}f(y) = \triangle_{\S^2}f(y).
 	\end{equation*} 
-% 	for $n\to\infty$.
 	\label{theo:pointwise convergence for a regular sampling}
 \end{theorem}
-As a direct implication of this theorem, the rescaled operator $\hat L_n^{t_n} := \frac{|\mathbb S^2|}{4\pi t^2}L_n^{t_n}$ (and its discrete counterpart $ \mathbf{\hat L} = \frac{|\mathbb S^2|}{4\pi t^2} \mathbf L$) converges pointwise towards the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \cite{belkin2007convergence}.
-This operator commutes with rotation and hence this convergence is a strong hint for equivariance, as formalized in the following proposition.
+As a direct implication of this theorem, the discrete counterpart $ \mathbf{\hat L}$ converges pointwise towards the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \cite{belkin2007convergence}.
+This operator commutes with rotation and hence theorem \ref{theo:pointwise convergence for a regular sampling} is a strong hint for equivariance, as formalized in the following proposition.
 %%%%%%%%%%%%%%%%%%%%%%%  link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{prop}\label{prop:equivariance}
-Under the hypothesis of theorem \ref{theo:pointwise convergence for a regular sampling}, we have the following pointwise convergence for the rescaled graph Laplacian 
+Under the hypothesis of theorem \ref{theo:pointwise convergence for a regular sampling}, the rescaled graph Laplacian commutes with any rotation, in the limit of infinite sampling, i.e.,
 \begin{equation*}
@@
 This is further discussed in Appendix \ref{sec: appendix: proof of theorem}.
-
 % 3) Show experimental results
@@
 \begin{itemize}
-    \item The extended graph Laplacian operator
-	\begin{equation}
-	\label{eq:Heat Kernel Graph Laplacian operator}
-	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
-	\end{equation}
+    \item The extended graph Laplacian operator \eqref{eq:Heat Kernel Graph Laplacian operator}
 	\item The functional approximation to the Laplace-Beltrami operator is a linear operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined  as

### 2019-11-13 main.tex
edit main body for new theorem

@@
 \paragraph{Theoretical convergence.}
-We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme.
-For this purpose we need now to introduce some definitions.
-Following their setting, we define the extended graph Laplacian operator as the linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
+We extend the work of \citep{belkin2005towards} to a sufficiently regular, deterministic sampling scheme. 
+Following their setting, we will work with the extended graph Laplacian operator as the linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
 	\begin{equation}
@@
 	\end{equation}
-and the rescaled graph Laplacian operator
-    \begin{equation}
-	\label{eq:rescaled Heat Kernel Graph Laplacian operator}
-	 \hat L_n^t := \frac{|\mathbb S^2|}{4\pi t^2}L_n^t
-	\end{equation}
-Note that we have the following relations $\b{L}_n^t \b{f} = T_\V L_n^t f$, $\b{\hat L} = \frac{|\mathbb S^2|}{4\pi t^2}\b L_n^t$.
+This operator extends the graph Laplacian operator previously defined with the weight scheme of \eqref{eqn:weights:belkin} to each point of the manifold, i.e. the sphere. 
+As the radius of the kernel $t$ will be adapted to the number of sample, we also rescale the graph Laplacian operator as
+    % \begin{equation}
+	% \label{eq:rescaled Heat Kernel Graph Laplacian operator}
+	 $\hat{L}_n^t := \frac{|\mathbb S^2|}{4\pi t^2}L_n^t$
+	% \end{equation}
+Hence, we have the following relations $\b{L}_n^t \b{f} = T_\V L_n^t f$. 
+% $\b{\hat L} = \frac{|\mathbb S^2|}{4\pi t^2}\b L_n^t$. \nati{why define this, we are not using it}
 Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, we define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area, and $d_i$ as the largest distance between the center $x_i$ and any point on the surface $\sigma_i$.
@@
 	\begin{equation*}
-		\lim_{n\to\infty}\hat L_n^{t_n}f(y) = \triangle_{\S^2}f(y).
+		\lim_{n\to\infty}\hat{L}_n^{t_n}f(y) = \triangle_{\S^2}f(y).
 	\end{equation*} 
@@
 \end{theorem}
-As a direct implication of this theorem, the discrete counterpart $ \mathbf{\hat L}$ converges pointwise towards the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \cite{belkin2007convergence}.
-This operator commutes with rotation and hence theorem \ref{theo:pointwise convergence for a regular sampling} is a strong hint for equivariance, as formalized in the following proposition.
+As a direct implication of this theorem, the discrete counterpart of $ \mathbf{\hat L}$ converges pointwise towards the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \cite{belkin2007convergence}.
+This operator commutes with rotation and hence Theorem \ref{theo:pointwise convergence for a regular sampling} is a strong step toward equivariance.
+We formalize in the following proposition.
 %%%%%%%%%%%%%%%%%%%%%%%  link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{prop}\label{prop:equivariance}
+\begin{theorem}\label{theo:equivariance}
 Under the hypothesis of theorem \ref{theo:pointwise convergence for a regular sampling}, the rescaled graph Laplacian commutes with any rotation, in the limit of infinite sampling, i.e.,
@@
 \end{equation*}
-\end{prop}
+\end{theorem}
 %%%%%%%%%%%%%%%%%%%%%%% end of link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%
 
-Importantly, the proof of Theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix \ref{sec: appendix: proof of theorem} inspires us in the construction of our graph Laplacian.
-It is inspirational for the graph construction and for how the parameter $t$ needs to be adjusted with respect to the number of points $n$.
-
-Nevertheless, it is important to keep in mind the limits of Theorem \ref{theo:pointwise convergence for a regular sampling}.
-First, it is \emph{not} a proof of equivariance of the graph convolution for a specific sampling.
+Importantly, one of the important benefit of Theorem \ref{theo:pointwise convergence for a regular sampling} is that its proof (in Appendix \ref{sec: appendix: proof of theorem}) inspires us in the construction of our graph Laplacian.
+In particular, it gives us insides for how the parameter $t$ needs to be adjusted with respect to the number of points $n$.
+
+% Nevertheless, it is important to keep in mind the limits of Theorem \ref{theo:pointwise convergence for a regular sampling}.
+% First, it is \emph{not} a proof of equivariance of the graph convolution for a specific sampling.
 To construct such a proof, a stronger convergence result is needed, for example spectral convergence (instead of pointwise).
@@
 % 3) Show experimental results
+
 \paragraph{Empirical convergence.}
@@
 \begin{figure}
-
 	\begin{minipage}{0.6\linewidth}
@@
 	\end{minipage}
-	\vspace{-0.5cm}
 \end{figure}
@@
 
-\section{Proof of proposition \ref{prop:equivariance}}
+\section{Proof of Theorem~\ref{theo:equivariance}}
 \begin{proof}

### 2019-11-13 main.tex
update a bit the appendix

@@
 \begin{itemize}
-    \item The extended graph Laplacian operator \eqref{eq:Heat Kernel Graph Laplacian operator}
+  \item As a reminder of \eqref{eq:Heat Kernel Graph Laplacian operator}, the extended graph Laplacian operator is a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$  is defined as
+	\begin{equation}
+	\label{eq:Heat Kernel Graph Laplacian operator}
+	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
+	\end{equation}
+	Note that we have the following relation $\b{L}_n^t \b{f} = T_\V L_n^t f$.
 	\item The functional approximation to the Laplace-Beltrami operator is a linear operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined  as

### 2019-11-13 main.tex
update checklist

@@
 	\item citet for inline, citep for parenthesis
-	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
+	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method. \nati{I would drop this.}
 	\item PSD of climate data: how does it compare to cosmo and 3D objects?
@@
 	\item check footnotes
-	\item climate data on spectrum plot
-	\item result tables: only what supports the main message in the text, everything we have in the appendix
+	\item climate data on spectrum plot \nati{I would drop this}
+	\item result tables: only what supports the main message in the text, everything we have in the appendix \nati{I think this is done now}
 	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
@@
 	\item unify enumerations. I like (i), (ii), etc.
-	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness?
-	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere.
-	\item figure placements
-	\item do the experiments on the icosahedral grid with the pooling as defined in the paper
+	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness? \nati{I think this is already done.}
+	\item add \citet{bruna2013gnn} in equivariance?
+They were the first to do a spherical CNN with graphs.
+Graph is built from a uniform random sampling of the sphere.
+\nati{Where do you want to add them?}
+	\item figure placements \nati{Good according to me}
+	\item do the experiments on the icosahedral grid with the pooling as defined in the paper \nati{I guess we are not doing that.}
 	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
@@
 	\item check that NN architectures and hyper-params are correctly reported
-	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space.
+	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space. \nati{I think this does not apply anymore}
 	%\item shall we still site adam and batch norm? no, mainstream enough
-	\item check results for ModelNet40 and integrate in text
+	\item check results for ModelNet40 and integrate in text \nati{I would drop this}
 	\item Check that HEALPix is introduced in the introduction
-	\item heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison.
+	\item heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison.  \nati{Bit syre what you mean here...}
 % 	\item check experiments section [Frédérick]: all the results numbers and NN + training details
-	\item compute the invariance error of the whole NNs (before and after training, invariance can be learned)
+	\item compute the invariance error of the whole NNs (before and after training, invariance can be learned) \nati{I guess we are not doing that}
 	\item add it with equivariance error of the convolution to \tabref{cosmo}

### 2019-11-13 figures/example_climate_TMQ.py
fix climate sphere figure

@@ -1,31 +1,39 @@
 #!/usr/bin/env python3
-# coding: utf-8
 
-# # Climate event detection
-#
-# https://portal.nersc.gov/project/dasrepo/deepcam/segm_h5_v3_reformat/gb_data_readme
-#
-# The 16 features are:
-#
-# * TMQ: Total (vertically integrated) precipitatable water
-# * U850: Zonal wind at 850 mbar pressure surface
-# * V850: Meridional wind at 850 mbar pressure surface
-# * UBOT: Lowest model level zonal wind
-# * VBOT: Lowest model level meridional wind
-# * QREFHT: Reference height humidity
-# * PS: Surface pressure
-# * PSL: sea level pressure
-# * T200: temp at 200 mbar pressure surface
-# * T500: temp at 500 mbar pressure surface
-# * PRECT: Total (convective and large-scale) precipitation rate (liq + ice)
-# * TS: Surface temperature (radiative)
-# * Z100: Geopotential Z at 100 mbar pressure surface
-# * Z200: Geopotential Z at 200 mbar pressure surface
-# * ZBOT: Lowest model level height
-#
-# resolution of 768 x 1152 equirectangular grid (25-km at equator)
+r"""Climate event detection
 
-# The labels are 0 for background class, 1 for tropical cyclone (TC), and 2 for atmoshperic river (AR)
+Simulation data from the HAPPI20 run of the Community Atmospheric Model (CAM5).
+
+URLs:
+* https://portal.nersc.gov/project/dasrepo/deepcam/segm_h5_v3_reformat/gb_data_readme
+* https://github.com/hpcac/ISC19-SCC
+
+The 16 features are:
+
+01. TMQ: Total (vertically integrated) precipitable water [kg/m^2]
+         the total amount of water vapor at that lat/lon grid cell
+02. U850: Zonal wind at 850 mbar pressure surface [m/s]
+03. V850: Meridional wind at 850 mbar pressure surface [m/s]
+04. UBOT: lowest level zonal wind [m/s]
+05. VBOT: Lowest model level meridional wind [m/s]
+06. QREFHT: reference height humidity [kg/kg]
+07. PS: surface pressure [Pa]
+08. PSL: sea level pressure [Pa]
[…]

### 2019-11-13 figures/example_ghcn_daily_tmax.py

@@ -30,7 +30,8 @@ from matplotlib import pyplot as plt
 import cartopy.crs as ccrs
 
 
-# plt.rc('font', family='Latin Modern Roman')
+# plt.rc('font', family='Latin Modern Roman')  # Latin Modern for text
+# plt.rc('mathtext', fontset='cm')  # Computer Modern for math (default is dejavusans)
 plt.rc('text', usetex=True)
 plt.rc('text.latex', preamble=r'\usepackage{lmodern}')
 

### 2019-11-13 figures/cosmo_cost_accuracy_tradeoff.py
better cost-accuracy tradoff figure

@@ -4,25 +4,34 @@ from os import path
 
 from matplotlib import pyplot as plt
 
-#plt.rc('font', family='Latin Modern Roman')
-#plt.rc('text', usetex=True)
-#plt.rc('text.latex', preamble=r'\usepackage{lmodern}')
+#plt.rc('font', family='Latin Modern Roman')  # Latin Modern for text
+plt.rc('mathtext', fontset='cm')  # Computer Modern for math (default is dejavusans)
+# plt.rc('text', usetex=True)
+# plt.rc('text.latex', preamble=r'\usepackage{lmodern}')
 
 neighbors = [8, 20, 40]
 accuracy = [87.1, 91.3, 92.5]
 speed = [185, 250, 363]
-fig, ax = plt.subplots(figsize=(3, 2.74))
+fig, ax = plt.subplots(figsize=(2.5, 2.25))
 ax.plot(speed, accuracy, '.-')
 ax.set_xlabel('inference time [ms]')
 ax.set_ylabel('accuracy [%]')
-for x, y, k in zip(speed, accuracy, neighbors):
-    align = 'right' if k == 40 else 'left'
-    ax.text(x, y-1.1, f'$k={k}$', horizontalalignment=align)
+#for x, y, k in zip(speed, accuracy, neighbors):
+#    align = 'right' if k == 40 else 'left'
+#    ax.text(x, y-1.1, f'$k={k}$', horizontalalignment=align)
+ax.text(speed[0]+10, accuracy[0], f'$k={neighbors[0]}$')
+ax.text(speed[1], accuracy[1]-0.7, f'$k={neighbors[1]}$')
+ax.text(speed[2]+4, accuracy[2]-1., f'$k={neighbors[2]}$', horizontalalignment='right')
 #ax.set_ylim(86, 93)
 
-x, y, label = 187, 83.8, 'FCN variant'
-ax.scatter(x, y, c=(1, 0, 0), marker='x')
-ax.text(x, y+0.5, label, horizontalalignment='left')
+# baselines = [
+#     (104, 54.2, '2D CNN baseline'),
+#     (185, 62.1, 'DSv1 CNN variant'),
+#     (185, 83.8, 'DSv1 FCN variant'),
+# ]
+# for x, y, label in baselines:
+#     ax.scatter(x, y, c=(1, 0, 0), marker='x')
+#     ax.text(x, y+0.5, label, horizontalalignment='left')
 
 fig.tight_layout()
 filename = path.splitext(path.basename(__file__))[0] + '.pdf'

### 2019-11-14 main.tex
fix climate sphere figure
replace \cite by \citet or \citep

@@
 % 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
-	\item citet for inline, citep for parenthesis
 	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method. \nati{I would drop this.}
@@
     \item publish the code and link it here
-	\item swap AR and TC on figure 1
 	\item add somewhere: exploit symmetries to reduce sample cost
 	\item proposition 1 -> corollary 3.1?
+	\item \citet{Mudigonda} used Integrated Water Vapor (IWV) only. That most probably is the same as our TMQ, which is most probably the most informative feature. TODO: run ours with TMQ alone.
 \end{itemize}
@@
 % 	\includegraphics[width=\linewidth]{figure_architecture_v3}
-% 	\caption{Example architecture from \cite{perraudin2019deepspherecosmo}.
+% 	\caption{Example architecture from \citet{perraudin2019deepspherecosmo}.
 % 		Global tasks need a spatial summarization: the FCN variant is rotation invariant (and accepts inputs of varying sizes), while the CNN variant is not.
@@
 For most sampling schemes, it is not known if $F_\V$ exists and hence if $T_\V$ is invertible.
-A special case is the equiangular sampling scheme where a sampling theorem holds, and thus a closed form of $T_\V^{-1}$ is known. % \cite{driscoll1994Fouriersphere}
+A special case is the equiangular sampling scheme where a sampling theorem holds, and thus a closed form of $T_\V^{-1}$ is known. % \citep{driscoll1994Fouriersphere}
 For sampling schemes where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\b{f}=T_\V f$, thus approximating $T_\V^{-1}$.
@@
 % 1) summary the work of Khasanova
-Naturally, \cite{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude and latitude axis. 
+Naturally, \citet{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude and latitude axis. 
 Working specifically with the equiangular sampling, they consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, South, West, East).
@@
 % 2) explain our approach
-We chose a different approach and take inspiration from \cite{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling points goes to infinity.
+We chose a different approach and take inspiration from \citet{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling points goes to infinity.
 This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics.
@@
 \end{theorem}
-As a direct implication of this theorem, the discrete counterpart of $ \mathbf{\hat L}$ converges pointwise towards the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \cite{belkin2007convergence}.
+As a direct implication of this theorem, the discrete counterpart of $ \mathbf{\hat L}$ converges pointwise towards the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \citep{belkin2007convergence}.
 This operator commutes with rotation and hence Theorem \ref{theo:pointwise convergence for a regular sampling} is a strong step toward equivariance.
@@
 % 3.0) explain how we obtained the figures
-In \figref{equivariance_error}, we present the equivariance error $\bar{E}_{\b L,C(\ell)}$ \eqref{eq:mean equivariance error} computed numerically as a function of the frequency (degree) $\ell$, for different parameter sets of DeepSphere as well as for graph construction of \cite{khasanova2017sphericalcnn}.
+In \figref{equivariance_error}, we present the equivariance error $\bar{E}_{\b L,C(\ell)}$ \eqref{eq:mean equivariance error} computed numerically as a function of the frequency (degree) $\ell$, for different parameter sets of DeepSphere as well as for graph construction of \citet{khasanova2017sphericalcnn}.
 The error depends of the number of pixels: $12N_{side}^2$ for HEALPix and $4b^2$ for the equiangular sampling. Here $N_{side}$ and $b$ are the sampling parameters determining their precision.
@@
 % 3.1) explain what the figures tell us
-For 8 neighbors, selecting the optimal value of $t$ already leads to an improvement compared to \cite{perraudin2019deepspherecosmo}, whose graph also was constructed to have at maximum 8 neighbors. 
+For 8 neighbors, selecting the optimal value of $t$ already leads to an improvement compared to \citet{perraudin2019deepspherecosmo}, whose graph also was constructed to have at maximum 8 neighbors. 
 With higher the number of neighbors, the equivariance error decreases by more than one order of magnitude. 
 Furthermore, increasing the graph resolution ($N_{side}$) leads to an improvement in the high frequencies as well. 
-Increasing the graph resolution of the graph of \cite{khasanova2017sphericalcnn} does not seem to improve its equivariance.
+Increasing the graph resolution of the graph of \citet{khasanova2017sphericalcnn} does not seem to improve its equivariance.
 We note that in our numerical test, this graph was perfectly equivariant to rotations along the horizontal and vertical axis as it should be by design.
@@
 The SHREC'17 shape retrieval contest \citep{shrec17} contains 51,300 randomly oriented 3D models from ShapeNet \citep{shapenet}, to be classified in 55 categories (tables, lamps, airplanes, etc.).
-As in \citet{cohen2018sphericalcnn}, objects are represented by 6 spherical maps.
+As in \citep{cohen2018sphericalcnn}, objects are represented by 6 spherical maps.
 At each pixel, a ray is traced towards the center of the sphere.
@@
 	\midrule
-	%\cite{jiang2019sphericalcnn} (paper) & 94.67 & - \\
-	\cite{jiang2019sphericalcnn} (rerun) & 94.95 & 38.41 \\
-	\cite{cohen2019gauge} (S2R) & 97.5 & 68.6 \\
-	\cite{cohen2019gauge} (R2R) & 97.7 & 75.9 \\
+	%\citet{jiang2019sphericalcnn} (paper) & 94.67 & - \\
+	\citet{jiang2019sphericalcnn} (rerun) & 94.95 & 38.41 \\
+	\citet{cohen2019gauge} (S2R) & 97.5 & 68.6 \\
+	\citet{cohen2019gauge} (R2R) & 97.7 & 75.9 \\
 	DeepSphere (weighted loss) & $97.8\pm 0.3$ & $77.15\pm 1.94$ \\
@@
 % why: icosahedron, can do anisotropy with isotropy + non-linearity + pooling
-The distortions induced by the icosahedral projection in \citet{cohen2019gauge} or the leakage of curvature information in \citet{boscaini2016anisotropicgraphnn} might also alter performance.
+The distortions induced by the icosahedral projection in \citep{cohen2019gauge} or the leakage of curvature information in \citep{boscaini2016anisotropicgraphnn} might also alter performance.
 %Further research is needed to determine if anisotropic filters are an unnecessary price to pay or if they are needed in some applications.
@@
 \paragraph{Preliminaries.}
-The proof of theorem \ref{theo:pointwise convergence for a regular sampling} is inspired from the work of \cite{belkin2005towards}. As a result, we start by restating some of their results.
+The proof of theorem \ref{theo:pointwise convergence for a regular sampling} is inspired from the work of \citet{belkin2005towards}. As a result, we start by restating some of their results.
 Given a sampling $\V = \{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_\V f = \b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
@@
 
-Leveraging these three operators \cite{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian towards the Laplace-Beltrami operator in the general setting of any compact, closed and infinitely differentiable maniform $\mathcal M$, where the sampling scheme $\V$ is drawn randomly on the manifold.
+Leveraging these three operators, \citet{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian towards the Laplace-Beltrami operator in the general setting of any compact, closed and infinitely differentiable maniform $\mathcal M$, where the sampling scheme $\V$ is drawn randomly on the manifold.
 For this reason, their results are all to be interpreted in a probabilistic sense.
@@
 \begin{prop}
-[\cite{belkin2005towards}, Proposition 4.4]
+[\citet{belkin2005towards}, Proposition 4.4]
 Let $\mathcal{M}$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb{R}^N$, and fix $y\in\mathcal{M}$. Let $f\in\mathcal{C}_\infty(\mathcal{M)}$. Then
@@
 
-% it is known that  (\cite{belkin2005towards}) to prove the convergence of $(\b {L}_n^t \b f) _i$ to $\Delta_{\S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\S^2}f(x)$
+% it is known that \citep{belkin2005towards} to prove the convergence of $(\b {L}_n^t \b f) _i$ to $\Delta_{\S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\S^2}f(x)$
 % where $L_n^t$ is defined as follows:
@@
 % This proof consists in two steps: first, we prove that $L_n^t \rightarrow L^t$, and second, we use proposition \ref{prop:3} to prove \eqref{eq:continuous convergence}.
-This equation, as already explained in \cite{belkin2007convergence}, directly implies theorem \ref{theo:pointwise convergence for a regular sampling}.
+This equation, as already explained in \citep{belkin2007convergence}, directly implies theorem \ref{theo:pointwise convergence for a regular sampling}.
 
@@
 
-In the work of \cite{belkin2005towards} the sampling is drawn form a uniform random distribution on the sphere, and their proof heavily relies on the uniformity properties of the distribution from which the sampling is drawn.
+In \citep{belkin2005towards}, the sampling is drawn from a uniform random distribution on the sphere, and their proof heavily relies on the uniformity properties of the distribution from which the sampling is drawn.
 In our case the sampling is deterministic, and this is indeed a problem that we need to overcome by imposing the regularity conditions above.
 
-To conclude, we see that the result obtained is of similar form than the result obtained in \cite{belkin2005towards}.
-Given the kernel density $t(n)=n^\beta$, \cite{belkin2005towards} proved convergence in the random case for $\beta \in (-\frac{1}{4}, 0)$ and we proved convergence in the deterministic case for $\beta \in (-\frac{2\alpha}{5}, 0)$, where $\alpha \in (0, \linefrac{1}{2}]$ (for the spherical Manifold).
+To conclude, we see that the result obtained is of similar form than the result obtained in \citep{belkin2005towards}.
+Given the kernel density $t(n)=n^\beta$, \citet{belkin2005towards} proved convergence in the random case for $\beta \in (-\frac{1}{4}, 0)$ and we proved convergence in the deterministic case for $\beta \in (-\frac{2\alpha}{5}, 0)$, where $\alpha \in (0, \linefrac{1}{2}]$ (for the spherical manifold).
 
@@
 
-The experiment with the model from \cite{jiang2019sphericalcnn} was rerun in order to obtain the AP metrics, but with a batch size of 64 instead of 256 due to GPU memory limit.
+The experiment with the model from \citet{jiang2019sphericalcnn} was rerun in order to obtain the AP metrics, but with a batch size of 64 instead of 256 due to GPU memory limit.
 
 Several experiments were run with different architectures for DeepSphere (DS).
-Jiang architecture use a similar one as \cite{jiang2019sphericalcnn}, with only the convolutional operators replaced.
+Jiang architecture use a similar one as \citet{jiang2019sphericalcnn}, with only the convolutional operators replaced.
 DeepSphere only is the original architecture giving the best results, deeper and with four times more feature maps than Jiang architecture.
@@
 % * Jiang rerun with a batch size of 64 instead of 256 due to memory limit.\\
-% * DS-jiang is the similar architecture as \cite{jiang2019sphericalcnn}. \\
+% * DS-jiang is the similar architecture as \citet{jiang2019sphericalcnn}. \\
 % * DS-optimal has 2 times the number of feature maps of DS. \\
@@
 		\midrule
-		\cite{mudigonda2017climateevents} & 74 & 65 & 97 & 78.67 \\
-		\cite{jiang2019sphericalcnn} (paper) & 94 & 93 & 97 & 94.67 \\
-		\cite{jiang2019sphericalcnn} (rerun) & 93.9 & 95.7 & 95.2 & 94.95 \\
-        \cite{cohen2019gauge} (S2R) & 97.8 & 97.3 & 97.3 & 97.5 \\
-        \cite{cohen2019gauge} (R2R) & 97.9 & 97.8 & 97.4 & 97.7 \\
+		\citet{mudigonda2017climateevents} & 74 & 65 & 97 & 78.67 \\
+		\citet{jiang2019sphericalcnn} (paper) & 94 & 93 & 97 & 94.67 \\
+		\citet{jiang2019sphericalcnn} (rerun) & 93.9 & 95.7 & 95.2 & 94.95 \\
+        \citet{cohen2019gauge} (S2R) & 97.8 & 97.3 & 97.3 & 97.5 \\
+        \citet{cohen2019gauge} (R2R) & 97.9 & 97.8 & 97.4 & 97.7 \\
 		\midrule
@@
 		\midrule
-		\cite{jiang2019sphericalcnn} (rerun) & 11.08 & 65.21 & 38.41 \\
-        \cite{cohen2019gauge} (S2R) & - & -& 68.6 \\
-        \cite{cohen2019gauge} (R2R) & - & -& 75.9 \\
+		\citet{jiang2019sphericalcnn} (rerun) & 11.08 & 65.21 & 38.41 \\
+        \citet{cohen2019gauge} (S2R) & - & -& 68.6 \\
+        \citet{cohen2019gauge} (R2R) & - & -& 75.9 \\
 		\midrule
@@
         %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
-		\cite{jiang2019sphericalcnn} & 330\,k & 10\,ms & 10\,h \\ % 328'339
-		% \cite{cohen2019gauge} (S2R) & - & - & - \\
-        % \cite{cohen2019gauge} (R2R) & - & - & - \\
+		\citet{jiang2019sphericalcnn} & 330\,k & 10\,ms & 10\,h \\ % 328'339
+		% \citet{cohen2019gauge} (S2R) & - & - & - \\
+        % \citet{cohen2019gauge} (R2R) & - & - & - \\
 		DeepSphere (Jiang architecture) & 590\,k & 5\,ms & 3\,h \\ % 590k

### 2019-11-14 main.tex
remove trailing whitespace
indices from 1 to n for compactness

@@
 	\item unify enumerations. I like (i), (ii), etc.
-	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness? \nati{I think this is already done.}
 	\item add \citet{bruna2013gnn} in equivariance?
@@
 	\label{eq:Heat Kernel Graph Laplacian operator}
-	 L_n^t f(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
+	 L_n^t f(y) := \frac{1}{n}\sum_{i=1}^{n} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
 	\end{equation}
@@
     % \begin{equation}
-	% \label{eq:rescaled Heat Kernel Graph Laplacian operator}
 	 $\hat{L}_n^t := \frac{|\mathbb S^2|}{4\pi t^2}L_n^t$
@@
 % $\b{\hat L} = \frac{|\mathbb S^2|}{4\pi t^2}\b L_n^t$. \nati{why define this, we are not using it}
-Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, we define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area, and $d_i$ as the largest distance between the center $x_i$ and any point on the surface $\sigma_i$.
- Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
+Given a sampling scheme $\V = \{x_1, \dots, x_n\}$, we define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area, and $d_i$ as the largest distance between the center $x_i$ and any point on the surface $\sigma_i$.
+Define $d^{(n)} := \max_{i=1, \dots, n} d_i$ and $A^{(n)} := \max_{i=1, \dots, n} A_i$.
 Given any rotation $g\in SO(3)$, we define the corresponding rotation operator $\mathcal R_g$ such that for any function $f$ on the sphere
@@
 \begin{theorem}
-	For a sampling $\V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$, $\beta\in\mathbb R$ such that
+	For a sampling $\V = \{x_i\in\S^2\}_{i=1}^n$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$, $\beta\in\mathbb R$ such that
 % 	the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$
@@
 The proof of theorem \ref{theo:pointwise convergence for a regular sampling} is inspired from the work of \citet{belkin2005towards}. As a result, we start by restating some of their results.
-Given a sampling $\V = \{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_\V f = \b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
+Given a sampling $\V = \{x_i\in\mathcal M\}_{i=1}^n$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_\V f = \b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
 The proof is constructed by leveraging 3 different operators:
 \begin{itemize}
-  \item As a reminder of \eqref{eq:Heat Kernel Graph Laplacian operator}, the extended graph Laplacian operator is a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$  is defined as
+  \item As a reminder of \eqref{eq:Heat Kernel Graph Laplacian operator}, the extended graph Laplacian operator is a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined as
 	\begin{equation}
-	\label{eq:Heat Kernel Graph Laplacian operator}
-	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
+%	\label{eq:Heat Kernel Graph Laplacian operator}
+	 L_n^t f(y) := \frac{1}{n}\sum_{i=1}^{n} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
 	\end{equation}
@@
         \label{eq:laplace-beltrami}
-        \Delta_{\mathcal M}f(y):= -\text{div}(\nabla_{\mathcal M}f)
+        \Delta_{\mathcal M}f(y) := -\text{div}(\nabla_{\mathcal M}f)
     \end{equation}
@@
 % 	\label{def:Heat Kernel Graph Laplacian operator}
-% 	\text{Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of the manifold we define the \textbf{operator} }$L_n^t$ such that
-% 	$$L_n^tf(y) := \frac{1}{n}\left[ \sum_{i=0}^{n-1} \exp \left\{ {-\frac{||x_i-y||^2}{4t}}\right\}\left(f(y)-f(x_i)\right)\right]$$
+% 	\text{Given a sampling $\{x_i\in\mathcal M\}_{i=1}^n$ of the manifold we define the \textbf{operator} }$L_n^t$ such that
+% 	$$L_n^tf(y) := \frac{1}{n}\left[ \sum_{i=1}^n \exp \left\{ {-\frac{||x_i-y||^2}{4t}}\right\}\left(f(y)-f(x_i)\right)\right]$$
 % \end{definition}
@@
 \begin{prop}\label{prop:1}
-	For an equal area sampling $\{x_i\in\S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance $\|\cdot\|$ with Lipschitz constant $C_f$
+	For an equal area sampling $\{x_i\in\S^2\}_{i=1}^n: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance $\|\cdot\|$ with Lipschitz constant $C_f$
 	\begin{equation*}

### 2019-11-14 main.tex
fix footnote number
typos from JB

@@
 \end{equation}
-where $\b{R}_\V(g) = T_\V R(g) T_\V^{-1}$. For practical a evaluation of the equivariance, we define the \textit{normalized equivariance error} for a signal $\b{f}$, and a  rotation $g$ as:
+where $\b{R}_\V(g) = T_\V R(g) T_\V^{-1}$. For an empirical evaluation of the equivariance, we define the \textit{normalized equivariance error} for a signal $\b{f}$, and a  rotation $g$ as:
 \begin{equation} \label{eq:equivariance error}
@@
 6]{belkin2005towards}.
-Second, while do not have a formal proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$ with $\alpha$ very close or equal to $\linefrac{1}{2}$.
+Second, while we do not have a formal proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$ with $\alpha$ very close or equal to $\linefrac{1}{2}$.
 The empirical results discussed in the next paragraph also points in this direction.
@@
 % 3.1) explain what the figures tell us
-For 8 neighbors, selecting the optimal value of $t$ already leads to an improvement compared to \citet{perraudin2019deepspherecosmo}, whose graph also was constructed to have at maximum 8 neighbors.
+For 8 neighbors, selecting the optimal value of $t$ already leads to an improvement compared to \citet{perraudin2019deepspherecosmo}, whose graph also was constructed to have at most 8 neighbors.
 With higher the number of neighbors, the equivariance error decreases by more than one order of magnitude.
@@
 \end{table}
-\footnotetext[5]{As implemented in \url{https://github.com/jonas-koehler/s2cnn}.}
+\footnotetext[7]{As implemented in \url{https://github.com/jonas-koehler/s2cnn}.}
 

### 2019-11-14 main.tex
HealPix -> HEALPix

@@
 The error depends of the number of pixels: $12N_{side}^2$ for HEALPix and $4b^2$ for the equiangular sampling. Here $N_{side}$ and $b$ are the sampling parameters determining their precision.
-The frequencies $\ell$ of the monochromatic signals were chosen in the range $(0,\  3N_{side}-1)$ for the Healpix sampling, and in the range $(0, b)$ for the equiangular sampling, to allow for an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ in equation \eqref{eq:mean equivariance error} \citep{gorski1999healpixprimer}.
+The frequencies $\ell$ of the monochromatic signals were chosen in the range $(0,\  3N_{side}-1)$ for the HEALPix sampling, and in the range $(0, b)$ for the equiangular sampling, to allow for an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ in equation \eqref{eq:mean equivariance error} \citep{gorski1999healpixprimer}.
 Using these parameters, the error measured is mostly due to imperfections in the empirical approximation of the Laplace-Beltrami operator and not to the sampling.
@@
 Please confirm ASAP, so we can update the Proposition and the text bellow.
-For HealPix sampling, we could say that while we have not proof, it make sense that it statisfies the hypothesis probably with $\alpha=\linefrac{1}{2}$.}
+For HEALPix sampling, we could say that while we have not proof, it make sense that it statisfies the hypothesis probably with $\alpha=\linefrac{1}{2}$.}
 

### 2019-11-14 main.tex
small edits

@@
 		\citet{esteves2018sphericalcnn} ($b=64$) & 79.4 & 68.5 & 500\,k & 9.8\,ms & 3\,h \\
-		DeepSphere (equiangular $b=64$) & 79.4 & 66.5 & 190\,k & 0.9\,ms & 50\,m \\
-		DeepSphere (HEALPix $N_{side}=32$) & 80.7 & 68.6 & 190\,k & 0.9\,ms & 50\,m \\
+		DeepSphere (equiangular, $b=64$) & 79.4 & 66.5 & 190\,k & 0.9\,ms & 50\,m \\
+		DeepSphere (HEALPix, $N_{side}=32$) & 80.7 & 68.6 & 190\,k & 0.9\,ms & 50\,m \\
 		\bottomrule
@@
 
-\Tabref{shrec17_retrieval} shows the results obtained from the competition's official evaluation script.
+\Tabref{shrec17_retrieval} shows the results obtained from the SHREC'17 competition's official evaluation script.
 % \Tabref{modelnet40} shows results on ModelNet40.

### 2019-11-14 main.tex
organize todos

@@
 \newcommand{\mart}[1]{{\color[rgb]{.9,.5,.3}{#1}}}
+\newcommand{\mdeff}[1]{{\color[rgb]{.3,.8,.3}{#1}}}
 
@@
 
-story: there are tradeoffs when designing a spherical CNN -> DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
-% DSv2 has a clear tradeoff between equivariance and computational cost
-
-* method development: tool that solve a need (balance btw the desiderata: equiv vs cost)\\
-* research question: anisotropy (highlight from the start or leave it as a dangling question in the end)\\
-
-contributions:\\
-* theory $\Rightarrow$ convergence (better graph)\\
-* experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata\\
-  * surprising: anisotropy doesn't seem useful\\
+story: there are tradeoffs when designing a spherical CNN $\Rightarrow$ DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
+\begin{itemize}
+	\item method development: tool that solve a need (balance btw the desiderata: equiv vs cost)
+	\item research question: anisotropy (highlight from the start or leave it as a dangling question at the end)
+\end{itemize}
+
+contributions:
+\begin{itemize}
+	\item theory $\Rightarrow$ convergence (better graph)
+	\item experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata
+	\item surprising: anisotropy doesn't seem useful
+\end{itemize}
 
 \todo{
+TODO:
 \begin{itemize}
-% 	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN. [Yes]
-% 	\item adjacency matrix: $A$ instead of $W$? nath: I am for W
-% 	\item anonymize DeepSphere citation - Not doing that
-% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
-	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method. \nati{I would drop this.}
-	\item PSD of climate data: how does it compare to cosmo and 3D objects?
-	\item align the spheres in figure 1
-	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
-	\item check footnotes
-	\item climate data on spectrum plot \nati{I would drop this}
-	\item result tables: only what supports the main message in the text, everything we have in the appendix \nati{I think this is done now}
-	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
+	\item PSD of climate data: how does it compare to cosmo and 3D objects? Climate data on spectrum plot. \nati{I would drop this}
+	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, fields, functions. Irregular, uneven. Coarsening, down-sampling. Sample, vertex, node, pixel, point.
 	\item check English vs American English
-	\item unify enumerations. I like (i), (ii), etc.
-	\item add \citet{bruna2013gnn} in equivariance?
-They were the first to do a spherical CNN with graphs.
-Graph is built from a uniform random sampling of the sphere.
-\nati{Where do you want to add them?}
-	\item figure placements \nati{Good according to me}
-	\item do the experiments on the icosahedral grid with the pooling as defined in the paper \nati{I guess we are not doing that.}
+	\item Explain heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison. \nati{Not sure what you mean here.}
 	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
 	\item update pygsp and merge sphere branch
-	\item check that NN architectures and hyper-params are correctly reported
-	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space. \nati{I think this does not apply anymore}
-	%\item shall we still site adam and batch norm? no, mainstream enough
-	\item check results for ModelNet40 and integrate in text \nati{I would drop this}
-	\item Check that HEALPix is introduced in the introduction
-	\item heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison.  \nati{Bit syre what you mean here...}
-% 	\item check experiments section [Frédérick]: all the results numbers and NN + training details
-	\item compute the invariance error of the whole NNs (before and after training, invariance can be learned) \nati{I guess we are not doing that}
-	\item add it with equivariance error of the convolution to \tabref{cosmo}
+	\item Compute the invariance error of the whole NNs (before and after training, invariance can be learned).
+Add it with equivariance error of the convolution to \tabref{cosmo}.
+\nati{I guess we are not doing that}
 	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
+	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
 \end{itemize}
@@
 \begin{itemize}
-    \item answer reviewers and commenters [mdeff \& nath]
-    \item update the proof [nath \& martino]
-    \item better link between the proof and equivarian
-    \item publish the code and link it here
-	\item add somewhere: exploit symmetries to reduce sample cost
-	\item proposition 1 -> corollary 3.1?
-	\item \citet{Mudigonda} used Integrated Water Vapor (IWV) only. That most probably is the same as our TMQ, which is most probably the most informative feature. TODO: run ours with TMQ alone.
+    \item answer commenter
+	\item add somewhere (intro?): exploit symmetries to reduce sample cost $\Rightarrow$ we don't discuss symmetries much
+	\item \citet{mudigonda2017climateevents} use Integrated Water Vapor (IWV) only.
+That most probably is the same as our TMQ, which is most probably the most informative feature.
+TODO: run ours with TMQ alone.
+	\item Show the three samplings in a figure?
+	\item better abstract (Friday's talk abstract?)
+	\item conclusion: less speculation?
+	\item check feedback from ICLR'20 LTS2 reading group
+	\item \mdeff{check my Telegram notes}
+\end{itemize}
+}
+
+\todo{
+last pass:
+\begin{itemize}
+	\item figure placement
+	\item check footnotes
+\end{itemize}
+}
+
+\todo{
+Not done:
+\begin{itemize}
+	\item Do the experiments on the icosahedral grid with the pooling as defined in the paper (i.e., not Jiang's specialty of taking the value of a pre-chosen sub-pixel).
+\nati{I guess we are not doing that.} \mdeff{I'm not sure what is the state of this, and Frédérick is not with us anymore.
+It's quite minor.}
+	\item Check results for ModelNet40 and integrate in text. \nati{I would drop this.} \mdeff{Yeah, those results are not mature enough.}
+	\item Add \citet{bruna2013gnn} in equivariance?
+They were the first to do a spherical CNN with graphs.
+Graph is built from a uniform random sampling of the sphere.
+\nati{Where do you want to add them?} \mdeff{They don't write how their Laplacian was built.
+Also, they only did MNIST on the sphere...}
 \end{itemize}
@@
 \begin{abstract}
-% We have to submit soon... The last sentence is a bit disconnected. Yep, better... Let submit... It is time.... Submit Submit Submit Submit 2 minutes... DONE!!!!!
 Designing a convolution for a spherical neural network requires a delicate tradeoff between efficiency and rotation equivariance.

### 2019-11-14 main.tex
small modification in the proof

@@
 \begin{itemize}
-  \item As a reminder of \eqref{eq:Heat Kernel Graph Laplacian operator}, the extended graph Laplacian operator is a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined as
+  \item The extended graph Laplacian operator, already presented in \eqref{eq:Heat Kernel Graph Laplacian operator}, is a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined as
 	\begin{equation}

### 2019-11-14 figures/spectrum.py
add climate to spectrum figure

@@ -5,10 +5,13 @@ import pickle
 
 import numpy as np
 from matplotlib import pyplot as plt
+import h5py
+import pyshtools
 
-#plt.rc('font', family='Latin Modern Roman')
-#plt.rc('text', usetex=True)
-#plt.rc('text.latex', preamble=r'\usepackage{lmodern}')
+# plt.rc('font', family='Latin Modern Roman')  # Latin Modern for text
+# plt.rc('mathtext', fontset='cm')  # Computer Modern for math (default is dejavusans)
+# plt.rc('text', usetex=True)
+# plt.rc('text.latex', preamble=r'\usepackage{lmodern}')
 
 def plot_with_std(x, y, color=None, alpha=0.2, ax=None, **kwargs):
     ystd = np.std(y, axis=0)
@@ -20,41 +23,57 @@ def plot_with_std(x, y, color=None, alpha=0.2, ax=None, **kwargs):
     ax.fill_between(x, ymean - ystd, ymean + ystd, alpha=alpha, color=color)
     return ax
 
+def compute_spectrum_climate():
+    # Data is from year, month, day, hour, run = 2106, 1, 1, 0, 1
+    h5f = h5py.File('example_climate_data.h5', mode='r')
+    data = h5f['climate']['data']  # (16,768,1152) numpy array
+    spectrum = list()
+    for d in data:
+        d = d[::2, ::3]  # Make it square (needed for pyshtools).
+        d = (d - d.min()) / (d.max() - d.min()) * 2 - 1  # Standardize.
+        grid = pyshtools.SHGrid.from_array(d, grid='DH')
+        clm = grid.expand(normalization='4pi')
+        spectrum.append(clm.spectrum())
+    return spectrum
+
 # 1000 objects out of 30k were randomly sampled to be analyzed.
 # The mean was subtracted from each signal in a preprocessing step.
 # The spectrum was computed by healpy.anafast up to lmax=nside (since there's nothing beyond).
 # cl is a dictionary with keys = {0, 1, 2}. cl[feature] is a matrix of shape [1000, 33] where each row is the spectrum of one signal.
-spectrum_shrec17 = pickle.load(open('../figures/spectrum_shrec17.pickle', 'rb'))
+spectrum_shrec17 = pickle.load(open('spectrum_shrec17.pickle', 'rb'))
[…]

### 2019-11-14 main.tex
add climate to spectrum figure
update kernels

@@
 \begin{itemize}
-	\item PSD of climate data: how does it compare to cosmo and 3D objects? Climate data on spectrum plot. \nati{I would drop this}
 	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, fields, functions. Irregular, uneven. Coarsening, down-sampling. Sample, vertex, node, pixel, point.
@@
 In practice, because of the exponential, most of the weights are very close to $0$. Hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
+In~\cite{perraudin2019deepspherecosmo}, the parameter $t$ was heuristically set to $0.5$ times the average squared distances over all connected pixels.
+In this work, we decided to use a more refined method.
 Given $k$, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
 \Figref{kernel_widths} shows the optimal kernel widths found for various resolutions of the HEALPix grid. 
+% We observe that with a small kernel size $t$, \cite{perraudin2019deepspherecosmo} would probably be more equivariant.
 
@@
 		\includegraphics[width=\linewidth]{kernel_widths}
-		\caption{Optimal kernel widths.}
+		\caption{Optimal kernel widths. For comparizon, we added the kernel used by~\cite{perraudin2019deepspherecosmo}}
 		\label{fig:kernel_widths}

### 2019-11-14 figures/kernel_widths.py

@@ -1,6 +1,7 @@
 #!/usr/bin/env python3
 
 from os import path
+import numpy as np
 
 from matplotlib import pyplot as plt
 
@@ -46,11 +47,16 @@ kernel_width_optimal = {
     },
 }
 
+v1_data = np.load('deepsphere_v1_kernel.npz')
+v1_t = v1_data['t']
+v1_nside = v1_data['nside']
+
 fig, ax = plt.subplots(figsize=(4, 2.3))
 for neighbors, optimums in sorted(kernel_width_optimal.items(), reverse=True):
-    nside = [12*n**2 for n in optimums.keys()]
-    width = list(optimums.values())
+    nside = np.array([12*n**2 for n in optimums.keys()])
+    width = np.array(list(optimums.values()))**2/(4*np.log(2))
     ax.loglog(nside, width, '.-', label=f'$k={neighbors}$ neighbors')
+ax.loglog(12*v1_nside[5:]**2, v1_t[5:], '.-', label=f'Perraudin et. al.')
 ax.legend(loc='upper right')
 ax.set_xlabel('$n = 12 N_{side}^2$ pixels', fontsize=14)
 ax.set_ylabel('kernel width $t$', fontsize=14)

### 2019-11-14 main.tex
small modifications
update

--- 2019-11-14 main.tex
@@
 \end{equation}
-In practice, because of the exponential, most of the weights are very close to $0$. Hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
-Given $k$, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
+In practice, because of the exponential, most of the weights are very close to $0$. Hence, to optimize for computational efficiency, we limit ourselves to only a few neighbors.
+In~\cite{perraudin2019deepspherecosmo}, each pixels is connected to their 8 adjacent pixels\footnote{It is slightly more complex than that and we invite the curious reader to read~\cite{perraudin2019deepspherecosmo}.} and the parameter $t$ was heuristically set to $0.5$ times the average squared distances over all connected pixels.
+This heuristic however seems to over-estimate $t$ (see \Figref{kernel_widths}). 
+In this work, we decided to use a more refined method.
+Given the $k$ nearest neighbors, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
 \Figref{kernel_widths} shows the optimal kernel widths found for various resolutions of the HEALPix grid. 
+% We observe that using a small kernel size $t$, \cite{perraudin2019deepspherecosmo} would probably be more equivariant.
 
@@
 		\includegraphics[width=\linewidth]{kernel_widths}
-		\caption{Optimal kernel widths.}
+		\caption{Optimal kernel widths. For comparizon, we added the kernel widths used by~\cite{perraudin2019deepspherecosmo} (8 neighbors).}
 		\label{fig:kernel_widths}

### 2019-11-14 figures/kernel_widths.py
better kernel width figure

@@ -55,8 +55,8 @@ fig, ax = plt.subplots(figsize=(4, 2.3))
 for neighbors, optimums in sorted(kernel_width_optimal.items(), reverse=True):
     nside = np.array([12*n**2 for n in optimums.keys()])
     width = np.array(list(optimums.values()))**2/(4*np.log(2))
-    ax.loglog(nside, width, '.-', label=f'$k={neighbors}$ neighbors')
-ax.loglog(12*v1_nside[5:]**2, v1_t[5:], '.-', label=f'Perraudin et. al.')
+    ax.loglog(nside, width, '.-', label=f'kNN graph, $k={neighbors}$')
+ax.loglog(12*v1_nside[5:]**2, v1_t[5:], '.--', label=f'Perraudin et. al., $k=8$')
 ax.legend(loc='upper right')
 ax.set_xlabel('$n = 12 N_{side}^2$ pixels', fontsize=14)
 ax.set_ylabel('kernel width $t$', fontsize=14)

### 2019-11-15 main.tex
better kernel width figure
first big pass on section 3 and around

--- 2019-11-14 main.tex
@@
 \newcommand{\mart}[1]{{\color[rgb]{.9,.5,.3}{#1}}}
-\newcommand{\mdeff}[1]{{\color[rgb]{.3,.8,.3}{#1}}}
+\newcommand{\mdeff}[1]{{\color[rgb]{.8,.3,.2}{#1}}}
 
@@
 %\newcommand{\secref}[1]{\S\ref{sec:#1}}
-\newcommand{\eqnref}[1]{equation~(\ref{eqn:#1})}
-\newcommand{\Eqnref}[1]{Equation~(\ref{eqn:#1})}
+\newcommand{\eqnref}[1]{(\ref{eqn:#1})}
+%\newcommand{\eqnref}[1]{equation~(\ref{eqn:#1})}
+%\newcommand{\Eqnref}[1]{Equation~(\ref{eqn:#1})}
 
@@
 \begin{itemize}
-	\item PSD of climate data: how does it compare to cosmo and 3D objects? Climate data on spectrum plot. \nati{I would drop this}
-	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, fields, functions. Irregular, uneven. Coarsening, down-sampling. Sample, vertex, node, pixel, point.
+	\item Unify vocabulary and avoid synonyms.
+		Sampling, grid, discretization, pixelization $\Rightarrow$ sampling (sampling schemes when not a particular set of vertices?)
+		Signal, maps, fields, functions.
+		Irregular, uneven, non-uniform.
+		Coarsening, down-sampling.
+		Sample, vertex, node, pixel, point $\Rightarrow$ vertex
 	\item check English vs American English
-	\item Explain heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison. \nati{Not sure what you mean here.}
 	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
@@
 \begin{itemize}
+	\item \mdeff{Why two definitions of rotations, $R(g)$ and $\mathcal{R}_g$?} [Martino]
     \item answer commenter
@@
 \begin{itemize}
-	\item Do the experiments on the icosahedral grid with the pooling as defined in the paper (i.e., not Jiang's specialty of taking the value of a pre-chosen sub-pixel).
+	\item Do the experiments on the icosahedral sampling with the pooling as defined in the paper (i.e., not Jiang's specialty of taking the value of a pre-chosen sub-pixel).
 \nati{I guess we are not doing that.} \mdeff{I'm not sure what is the state of this, and Frédérick is not with us anymore.
@@
 % exactitude with respect to equivariance.
-DeepSphere, a method based on a graph representation of the discretized sphere, strikes a controllable balance between these two desiderata.
+DeepSphere, a method based on a graph representation of the sampled sphere, strikes a controllable balance between these two desiderata.
 % Say something here about isotropy?
 This contribution is twofold.
-First, we study both theoretically and empirically how equivariance is affected by the underlying graph with respect to the number of pixels and neighbors.
+First, we study both theoretically and empirically how equivariance is affected by the underlying graph with respect to the number of vertices and neighbors.
 Second, we evaluate DeepSphere on relevant problems.
@@
 		(d) daily maximum temperature from the Global Historical Climatology Network (GHCN).\protect\footnotemark
-		A rigid full-sphere pixelization is not ideal: brain activity is only measured on the scalp, the Milky Way's galactic plane masks observations, climate scientists desire a variable resolution, and the position of weather stations is arbitrary and changes over time.
+		A rigid full-sphere sampling is not ideal: brain activity is only measured on the scalp, the Milky Way's galactic plane masks observations, climate scientists desire a variable resolution, and the position of weather stations is arbitrary and changes over time.
 		(e) Graphs can faithfully and efficiently represent sampled spherical data by placing vertices where it matters.
@@
 As neural networks (NNs) have proved to be great tools for inference, variants have been developed to handle spherical data.
-Exploiting the locally Euclidean property of the sphere, early attempts used standard 2D convolutions on a grid discretization of the sphere \citep{boomsma2017sphericalcnn, su2017sphericalcnn, coors2018sphericalcnn}.
+Exploiting the locally Euclidean property of the sphere, early attempts used standard 2D convolutions on a grid sampling of the sphere \citep{boomsma2017sphericalcnn, su2017sphericalcnn, coors2018sphericalcnn}.
 While simple and efficient, those convolutions are not equivariant to rotations.
@@
 \citet{cohen2019gauge} proposed to reduce costs by limiting the size of the representation of the symmetry group by projecting the data from the sphere to the icosahedron.
+% not sure if true
 The distortions introduced by this projection might however hinder performance (\secref{exp:climate}).
@@
 
-Another approach is to represent the discretized sphere as a graph connecting pixels according to the distance between them \citep{bruna2013gnn, khasanova2017sphericalcnn, perraudin2019deepspherecosmo}.
+Another approach is to represent the sampled sphere as a graph connecting pixels according to the distance between them \citep{bruna2013gnn, khasanova2017sphericalcnn, perraudin2019deepspherecosmo}.
 While Laplacian-based graph convolutions are more efficient than spherical convolutions, they are not exactly equivariant \citep{defferrard2019deepsphereequiv}.
@@
 % An example architecture is shown in \figref{architecture}.
-The main idea is to model the discretized sphere as a graph of connected pixels: the length of the shortest path between two pixels is an approximation of the geodesic distance between them.
-We use the graph CNN formulation introduced in \citep{defferrard2016graphnn} and a pooling strategy that exploits hierarchical pixelizations of the sphere.
+The main idea is to model the sampled sphere as a graph of connected pixels: the length of the shortest path between two pixels is an approximation of the geodesic distance between them.
+We use the graph CNN formulation introduced in \citep{defferrard2016graphnn} and a pooling strategy that exploits hierarchical samplings of the sphere.
 
 \paragraph{Sampling.}
-Given a sampling scheme $\V = \{x_i \in \S^2\}_{i=1}^n$, a function $f : \S^2 \supset F_\V \to \R$ is sampled as $T_\V(f) = \b{f}$ by the sampling operator $T_\V: L^2(\S^2) \supset F_\V \to \R^n$ defined as $\b{f}: f_i=f(x_i)$, where $F_\V$ will be specified in \secref{equivariance}.
-As there is no analogue of uniform sampling on the sphere, many schemes have been proposed with different tradeoffs.
-In this work, depending on the considered application, we will use the equiangular \citep{driscoll1994Fouriersphere}, HEALPix \citep{gorski2005healpix}, and icosahedral \citep{baumgardner1985icosahedral} grids.
+Given a sampling $\V = \{x_i \in \S^2\}_{i=1}^n$, a function $f : \S^2 \supset F_\V \to \R$ is sampled as $T_\V(f) = \b{f}$ by the sampling operator $T_\V: L^2(\S^2) \supset F_\V \to \R^n$ defined as $\b{f}: f_i=f(x_i)$, where $F_\V$ will be specified in \secref{equivariance}.
+As there is no analogue of uniform sampling on the sphere, many samplings have been proposed with different tradeoffs.
+In this work, depending on the considered application, we will use the equiangular \citep{driscoll1994Fouriersphere}, HEALPix \citep{gorski2005healpix}, and icosahedral \citep{baumgardner1985icosahedral} samplings.
 
@@
 %$\b{D} = \diag(\b{A} \b{1})$
-Given a sampling scheme $\V$, usually fixed by the application or the available measurements, the freedom in constructing $\G$ is in setting $w$.
+Given a sampling $\V$, usually fixed by the application or the available measurements, the freedom in constructing $\G$ is in setting $w$.
 \Secref{equivariance} shows how to set $w$ to minimize the equivariance error.
@@
 Convolutions are most often performed in the spectral domain through a spherical harmonic transform (SHT).
-That is the approach taken by \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn}, which has a computational cost of $\bO(n^{3/2})$ on isolatitude pixelizations (such as the HEALPix and equiangular grids) and $\bO(n^2)$ in general.
+That is the approach taken by \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn}, which has a computational cost of $\bO(n^{3/2})$ on isolatitude samplings (such as the HEALPix and equiangular samplings) and $\bO(n^2)$ in general.
 On the other hand, following \citet{defferrard2016graphnn}, graph convolutions can be defined as
@@
 \paragraph{Pooling.}
-Down- and up-sampling is natural for hierarchical pixelizations,\footnote{The equiangular, HEALPix, and icosahedral schemes are of this kind.} where each subdivision divides a pixel in (an equal number of) child sub-pixels.
+Down- and up-sampling is natural for hierarchical samplings,\footnote{The equiangular, HEALPix, and icosahedral samplings are of this kind.} where each subdivision divides a pixel in (an equal number of) child sub-pixels.
 To pool (down-sample), the data supported on the sub-pixels is summarized by a permutation invariant function such as the maximum or the average.
@@
 \section{Graph convolution and equivariance} \label{sec:equivariance}
-%\section{Is graph convolution equivariant to rotation? [2 pages]} \label{sec:equivariance}
+%\section{Is graph convolution equivariant to rotation? [2 pages]}
 
@@
 We require $F_\V$ to be a suitable subspace of $L^2(\S^2)$ such that $T_\V$ is invertible, i.e., the function $f \in F_\V$ can be unambiguously reconstructed from its sampled values $\b{f}$.
-The existence of such a subspace depends on the sampling scheme $\V$, and its characterization is a common problem in signal processing \citep{driscoll1994Fouriersphere}.
-For most sampling schemes, it is not known if $F_\V$ exists and hence if $T_\V$ is invertible.
-A special case is the equiangular sampling scheme where a sampling theorem holds, and thus a closed form of $T_\V^{-1}$ is known. % \citep{driscoll1994Fouriersphere}
-For sampling schemes where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\b{f}=T_\V f$, thus approximating $T_\V^{-1}$.
+The existence of such a subspace depends on the sampling $\V$, and its characterization is a common problem in signal processing \citep{driscoll1994Fouriersphere}.
+For most samplings, it is not known if $F_\V$ exists and hence if $T_\V$ is invertible.
+A special case is the equiangular sampling where a sampling theorem holds, and thus a closed-form of $T_\V^{-1}$ is known. % \citep{driscoll1994Fouriersphere}
+For samplings where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\b{f}=T_\V f$, thus approximating $T_\V^{-1}$.
 For all theoretical considerations, we assume that $F_\V$ exists and $f \in F_\V$.
@@
 % 0.2 Explain why the Laplacian is so important...
-By definition, the (spherical) graph convolution is rotation equivariant, if and only if, it commutes with the rotation operator defined as $R(g), g\in SO(3)$: $R(g) f(x) = f\left(g^{-1} x \right)$.
+By definition, the (spherical) graph convolution is rotation equivariant if and only if it commutes with the rotation operator defined as $R(g), g\in SO(3)$: $R(g) f(x) = f\left(g^{-1} x \right)$.
 In the context of this work, graph convolution is performed by recursive applications of the graph Laplacian (\eqnref{graph_conv}).
-Hence, if $\b{L}$ commutes with the rotation operator, then, by recursion, it will also commute with the convolution $h(\b{L})$.
-As a result, to simplify our analysis, we concentrate on the graph Laplacian and $h(\b{L})$ is rotational invariant if and only if
+Hence, if $R(g)$ commutes with $\b{L}$, then, by recursion, it will also commute with the convolution $h(\b{L})$.
+As a result, $h(\b{L})$ is rotation equivariant if and only if
 % 0.3 Formulate the problem
-\begin{equation} \label{eq:equivariance}
-	\b{R}_\V(g) \b{L} \b{f} = \b{L} \b{R}_\V(g) \b{f} \hspace{1cm} \forall f\in F_\V \text{ and } \forall g\in SO(3),
+\begin{equation*} %\label{eq:equivariance}
+	\b{R}_\V(g) \b{L} \b{f} = \b{L} \b{R}_\V(g) \b{f}, \hspace{1cm} \forall f\in F_\V \text{ and } \forall g\in SO(3),
+\end{equation*}
+where $\b{R}_\V(g) = T_\V R(g) T_\V^{-1}$.
+For an empirical evaluation of equivariance, we define the \textit{normalized equivariance error} for a signal $\b{f}$ and a  rotation $g$ as
+\begin{equation} \label{eq:equivariance error}
+	E_{\b{L}}(\b{f}, g) = \left(\frac{ \norm {\b{R}_\V(g) \b{L} \b{f} - \b{L} \b{R}_\V(g) \b{f}} }{\norm {\b{L} \b{f}}}\right)^2.
 \end{equation}
-where $\b{R}_\V(g) = T_\V R(g) T_\V^{-1}$. For an empirical evaluation of the equivariance, we define the \textit{normalized equivariance error} for a signal $\b{f}$, and a  rotation $g$ as:
-\begin{equation} \label{eq:equivariance error}
-	E_{\b{L}}(\b{f}, g) = \left(\frac{ \norm {\b{R}_\V(g) \b{L} \b{f} - \b{L} \b{R}_\V(g) \b{f}} }{\norm {\b{L} \b{f}}}\right)^2,
+More generally for a class of signals $f \in C \subset F_\V$, the \textit{mean equivariance error} defined as
+\begin{equation} \label{eq:mean equivariance error}
+	\overline E_{\b{L}, C} = \mathbb E_{\b{f}\in C, g\in SO(3)} \ E_{\b{L}}(\b{f}, g)
 \end{equation}
-More generally for a class of signal $f \in C \subset F_\V$, the \textit{mean equivariance error} defined as
-\begin{equation} \label{eq:mean equivariance error}
-	\overline E_{\b{L}, C} = \mathbb E_{\b{f}\in C, g\in SO(3)} \ E_{\b{L}}(\b{f}, g),
+represents the overall equivariance error.
+The expected value is obtained by averaging over a finite number of random functions and random rotations.
+
+%\subsection{Finding the optimal edge weights} \label{sec:optimal}
+\subsection{Finding the optimal weighting scheme} \label{sec:optimal}
+
+% 1) summarize the work of Khasanova
+Considering the equiangular sampling and graphs where each vertex is connected to 4 neighbors (north, south, east, west), \citet{khasanova2017sphericalcnn} designed a weighting scheme to minimize \eqref{eq:mean equivariance error} for longitudinal and latitudinal rotations\footnote{Equivariance to longitudinal rotation is essentially given by the equiangular sampling.}.
+% because longitudinal rotation can be discrete
+Their solution gives weights inversely proportional to Euclidean distances:
+\begin{equation} \label{eqn:weights:khasanova}
+	w_{ij} = \frac{1}{\norm{x_i-x_j}}.
 \end{equation}
-represents well the overall equivariance error.
-In practice, we analyse this error with respect of the frequency by setting the set $C$ to functions $f$ made of single degree spherical harmonic.
-The expected value is obtained by averaging over a finite number of random functions and random rotations.
-
-\subsection{Finding the optimal set of weights}  \label{sec:optimal}
-% 1) summary the work of Khasanova
-Naturally, \citet{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude and latitude axis.
-Working specifically with the equiangular sampling, they consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, South, West, East).
-% and propose a weighting scheme $w_{ij}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude latitude axis.
-Their approach leads to weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
-\begin{equation} \label{eqn:weights:khasanova}
-	w_{ij} = \frac{1}{\norm{x_i-x_j}}
+%leading to a high mean equivariance error if the mean is computed over rotations in SO(3).
+Note that while the resulting convolution is not equivariant to the whole of $SO(3)$, that is enough for omnidirectional imaging because, as gravity consistently orients the sphere, objects only rotate longitudinally or latitudinally.
+
+% 2) explain our approach
+To achieve equivariance to all rotations, we take inspiration from \citet{belkin2005towards}.
+They prove that for a \emph{random uniform sampling}, the graph Laplacian $\b{L}$ built from weights
+\begin{equation} \label{eqn:weights:belkin}
+	w_{ij} = e^{- \frac{1}{4t} \norm{x_i - x_j}^2}
 \end{equation}
-
-% 2) explain our approach
-We chose a different approach and take inspiration from \citet{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling points goes to infinity.
-This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics.
-In this case the weighting scheme is full (every node is connected to every node) and is based on the exponential kernel:
-\begin{equation} \label{eqn:weights:belkin}
-w_{ij} = e^{-\frac{1}{4t} \norm{x_i-x_j}^2}
-\end{equation}
-In practice, because of the exponential, most of the weights are very close to $0$. Hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
-Given $k$, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
-\Figref{kernel_widths} shows the optimal kernel widths found for various resolutions of the HEALPix grid.
+converges to the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of samples grows to infinity.
+This result is a good starting point as $\Delta_{\mathbb{S}^2}$ commutes with rotation, i.e., $\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$.
+% and (ii) is diagonalized by the spherical harmonics.
+While the weighting scheme is full (i.e., every vertex is connected to every vertex), most weights are small due to the exponential.
+We hence make an approximation to limit the cost of the convolution \eqnref{graph_conv} by only considering the $k$ nearest neighbors to each vertex.
+%In practice, the tricky part is to set $t$ in a non-asymptotic regime.
+Given $k$, the optimal kernel width $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
+\Figref{kernel_widths} shows the optimal kernel widths found for various resolutions of the HEALPix sampling.
+As predicted by the theory, $t_n \propto n^\beta, \beta \in \R$.
+Importantly however, the optimal $t$ also depends on the number of neighbors $k$.
+
+Considering the HEALPix sampling, \citet{perraudin2019deepspherecosmo} connected each vertex to their 8 adjacent vertices, computed the weights with \eqnref{weights:belkin}, and heuristically set $t$ to half the average squared Euclidean distance between connected vertices.
+This heuristic however seems to over-estimate $t$ (see \figref{kernel_widths}).
+% We observe that using a small kernel size $t$, \cite{perraudin2019deepspherecosmo} would probably be more equivariant.
 
 \subsection{Analysis of the proposed weighting scheme}
-We analyse our proposed weighting scheme both theoretically and empirically.
+
+We analyze the proposed weighting scheme both theoretically and empirically.
 
 \paragraph{Theoretical convergence.}
-We extend the work of \citep{belkin2005towards} to a sufficiently regular, deterministic sampling scheme.
+We extend the work of \citep{belkin2005towards} to a sufficiently regular, deterministic sampling.
 Following their setting, we will work with the extended graph Laplacian operator as the linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
-	\begin{equation}
-	\label{eq:Heat Kernel Graph Laplacian operator}
+\begin{equation} \label{eq:Heat Kernel Graph Laplacian operator}
 	 L_n^t f(y) := \frac{1}{n}\sum_{i=1}^{n} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
 \end{equation}
-This operator extends the graph Laplacian operator previously defined with the weight scheme of \eqref{eqn:weights:belkin} to each point of the manifold, i.e. the sphere.
-As the radius of the kernel $t$ will be adapted to the number of sample, we also rescale the graph Laplacian operator as
-    % \begin{equation}
-	 $\hat{L}_n^t := \frac{|\mathbb S^2|}{4\pi t^2}L_n^t$
-	% \end{equation}
-Hence, we have the following relations $\b{L}_n^t \b{f} = T_\V L_n^t f$.
+This operator extends the graph Laplacian operator previously defined with the weighting scheme \eqnref{weights:belkin} to each point of the manifold, i.e., the sphere.
+\mdeff{Can we avoid to introduce general manifolds and stay on the sphere?}
+As the radius of the kernel $t$ will be adapted to the number of samples, we also rescale the graph Laplacian operator as $\hat{L}_n^t := \frac{|\mathbb S^2|}{4\pi t^2}L_n^t$.
+Hence, we have $\b{L}_n^t \b{f} = T_\V L_n^t f$.
 % $\b{\hat L} = \frac{|\mathbb S^2|}{4\pi t^2}\b L_n^t$. \nati{why define this, we are not using it}
-Given a sampling scheme $\V = \{x_1, \dots, x_n\}$, we define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area, and $d_i$ as the largest distance between the center $x_i$ and any point on the surface $\sigma_i$.
+Given a sampling $\V$, we define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area, and $d_i$ the largest distance between the center $x_i$ and any point on the surface $\sigma_i$.
 Define $d^{(n)} := \max_{i=1, \dots, n} d_i$ and $A^{(n)} := \max_{i=1, \dots, n} A_i$.
-Given any rotation $g\in SO(3)$, we define the corresponding rotation operator $\mathcal R_g$ such that for any function $f$ on the sphere
-\begin{equation}\label{eq:rotation operator}
-	\mathcal R_g f(x) := f(g^{-1}(x)).
-\end{equation}
+%Given any rotation $g\in SO(3)$, we define the corresponding rotation operator $\mathcal R_g$ such that for any function $f$ on the sphere
+%\mdeff{Already defined in problem formulation.}
+%\begin{equation} \label{eq:rotation operator}
+%	\mathcal R_g f(x) := f(g^{-1}(x)).
+%\end{equation}
 \begin{theorem}
-	For a sampling $\V = \{x_i\in\S^2\}_{i=1}^n$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$, $\beta\in\mathbb R$ such that
+	For a sampling $\V$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$, $\beta\in\mathbb R$ such that
 % 	the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$
@@
 \end{theorem}
-As a direct implication of this theorem, the discrete counterpart of $ \mathbf{\hat L}$ converges pointwise towards the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \citep{belkin2007convergence}.
-This operator commutes with rotation and hence Theorem \ref{theo:pointwise convergence for a regular sampling} is a strong step toward equivariance.
-We formalize in the following proposition.
-%%%%%%%%%%%%%%%%%%%%%%%  link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%
+As a direct implication of this theorem, the discrete counterpart of $\mathbf{\hat L}$ \mdeff{(that's already discrete no?)} converges pointwise towards the Laplace-Beltrami operator $\Delta_{\S^2}$ in the sense explained in \citep{belkin2007convergence}.
+This operator commutes with rotation and hence Theorem \ref{theo:pointwise convergence for a regular sampling} is a strong step towards equivariance. We formalize it in the following theorem.
+\mdeff{This transition should be done better.}
 \begin{theorem}\label{theo:equivariance}
-Under the hypothesis of theorem \ref{theo:pointwise convergence for a regular sampling}, the rescaled graph Laplacian commutes with any rotation, in the limit of infinite sampling, i.e.,
+Under the hypothesis of theorem~\ref{theo:pointwise convergence for a regular sampling}, the rescaled graph Laplacian commutes with any rotation, in the limit of infinite sampling, i.e.,
 \begin{equation*}
@@
 \end{theorem}
-%%%%%%%%%%%%%%%%%%%%%%% end of link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%
-
-Importantly, one of the important benefit of Theorem \ref{theo:pointwise convergence for a regular sampling} is that its proof (in Appendix \ref{sec: appendix: proof of theorem}) inspires us in the construction of our graph Laplacian.
-In particular, it gives us insides for how the parameter $t$ needs to be adjusted with respect to the number of points $n$.
+
+Importantly, the proof of Theorem~\ref{theo:pointwise convergence for a regular sampling} (in Appendix~\ref{sec: appendix: proof of theorem}) inspires our construction of the graph Laplacian.
+In particular, it gives insights on how the parameter $t$ needs to be adjusted with respect to the number of points $n$.
 
@@
 % \todo{Can we intuitively write what pointwise convergence means, and how it is more limited than spectral or uniform convergence?}
-We note that in the random sampling case, the graph laplacian does \emph{not} converge uniformly in general \cite[Sec.
-3]{belkin2007convergence}, but does for a class of Lipschitz functions \cite[Sec.
+
+We note that in the random sampling case, the graph laplacian does \emph{not} converge uniformly in general \citep[Sec.
+3]{belkin2007convergence}, but does for a class of Lipschitz functions \citep[Sec.
 6]{belkin2005towards}.
-Second, while we do not have a formal proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$ with $\alpha$ very close or equal to $\linefrac{1}{2}$.
+Second, while we do not have a formal proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, with $\alpha$ very close or equal to $\linefrac{1}{2}$.
 The empirical results discussed in the next paragraph also points in this direction.
 This is further discussed in Appendix \ref{sec: appendix: proof of theorem}.
+
 % 3) Show experimental results
-
 \paragraph{Empirical convergence.}
@@
 % 3.0) explain how we obtained the figures
-In \figref{equivariance_error}, we present the equivariance error $\bar{E}_{\b L,C(\ell)}$ \eqref{eq:mean equivariance error} computed numerically as a function of the frequency (degree) $\ell$, for different parameter sets of DeepSphere as well as for graph construction of \citet{khasanova2017sphericalcnn}.
-The error depends of the number of pixels: $12N_{side}^2$ for HEALPix and $4b^2$ for the equiangular sampling. Here $N_{side}$ and $b$ are the sampling parameters determining their precision.
-The frequencies $\ell$ of the monochromatic signals were chosen in the range $(0,\  3N_{side}-1)$ for the HEALPix sampling, and in the range $(0, b)$ for the equiangular sampling, to allow for an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ in equation \eqref{eq:mean equivariance error} \citep{gorski1999healpixprimer}.
-Using these parameters, the error measured is mostly due to imperfections in the empirical approximation of the Laplace-Beltrami operator and not to the sampling.
-
-% 3.1) explain what the figures tell us
-For 8 neighbors, selecting the optimal value of $t$ already leads to an improvement compared to \citet{perraudin2019deepspherecosmo}, whose graph also was constructed to have at most 8 neighbors.
-With higher the number of neighbors, the equivariance error decreases by more than one order of magnitude.
-Furthermore, increasing the graph resolution ($N_{side}$) leads to an improvement in the high frequencies as well.
-Increasing the graph resolution of the graph of \citet{khasanova2017sphericalcnn} does not seem to improve its equivariance.
-We note that in our numerical test, this graph was perfectly equivariant to rotations along the horizontal and vertical axis as it should be by design.
-Nevertheless, it is simply not equivariant along the last rotation.
-Such equivariance properties might be sufficient for analysing omnidirectional images (that are naturally aligned on the north-south axis).
+\Figref{equivariance_error} shows the equivariance error \eqref{eq:mean equivariance error} for different parameter sets of DeepSphere for the HEALPix sampling as well as for the graph construction of \citet{khasanova2017sphericalcnn} for the equiangular sampling.
+The error is estimated as a function of the sampling resolution and signal frequency.
+The resolution is controlled by the number of pixels $n = 12N_{side}^2$ for HEALPix and $n = 4b^2$ for the equiangular sampling.
+The frequency is controlled by setting the set $C$ to functions $f$ made of spherical harmonics of a single degree $\ell$.
+To allow for an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$, the degree $\ell$ was chosen in the range $(0, 3N_{side}-1)$ for HEALPix and $(0, b)$ for the equiangular sampling \citep{gorski1999healpixprimer}.
+Using these parameters, the measured error is mostly due to imperfections in the empirical approximation of the Laplace-Beltrami operator and not to the sampling.
+
+% 3.1) explain what the figure tells us
+For $k=8$ neighbors, selecting the optimal value of $t$ improves on \citet{perraudin2019deepspherecosmo}, whose graph also was constructed to have at most 8 neighbors.
+The equivariance error further decreases by connecting more neighbors,  at the expense of computations.
+Increasing the resolution decreases the equivariance error in the high frequencies.
+% Increasing the graph resolution of the graph of \citet{khasanova2017sphericalcnn} does not seem to improve its equivariance.
+Moreover, we observe that the weighting scheme \eqnref{weights:khasanova} does indeed not lead to convolutions that are equivariant to all rotations $g \in SO(3)$.
+We however verified that the convolutions are equivariant to longitudinal and latitudinal rotations, as intended.
 
@@
 		\includegraphics[width=1\linewidth]{all_in_one.pdf}
-
-		\caption{Normalized mean equivariance error \eqref{eq:mean equivariance error}. The number of pixels is $n = 4 s^2$ for the equiangular sampling and $n = 12 s^2$ for the HEALPix sampling.}
+		\caption{
+			Mean equivariance error \eqref{eq:mean equivariance error}.
+			The number of pixels is $n = 4 s^2$ for the equiangular sampling and $n = 12 s^2$ for the HEALPix.
+		}
 		\label{fig:equivariance_error}
@@
 		\includegraphics[width=\linewidth]{kernel_widths}
-		\caption{Optimal kernel widths.}
+		\caption{Kernel widths.}
 		\label{fig:kernel_widths}
@@
 The same is done for the object's convex hull.\footnote{Albeit we didn't observe much improvement by using the convex hull.}
-The maps are discretized using either an equiangular grid with bandwidth $b = 64$ ($n = 4 b^2 = 16,384$ pixels) or an HEALPix grid with $N_{side} = 32$ ($n = 12 N_{side}^2 = 12,288$ pixels).
+The maps are sampled by an equiangular sampling with bandwidth $b = 64$ ($n = 4 b^2 = 16,384$ pixels) or an HEALPix sampling with $N_{side} = 32$ ($n = 12 N_{side}^2 = 12,288$ pixels).
 
@@
 As the information in those spherical maps resides in the low frequencies (\figref{spectrum}), reducing the equivariance error didn't translate into improved performance.
-For the same reason, using the more uniform HEALPix discretization or lowering the resolution down to $N_{side} = 8$ ($n=768$ pixels) didn't impact performance either.
+For the same reason, using the more uniform HEALPix sampling or lowering the resolution down to $N_{side} = 8$ ($n=768$ pixels) didn't impact performance either.
 %\todo{The same conclusions are drawn from ModelNet40 (\tabref{modelnet40}).}
@@
 %\url{http://island.me.berkeley.edu/ugscnn/data/climate_sphere_l5.zip}
-There is 1,072,805 spherical maps, down-sampled to a level-5 icosahedral grid ($n = 10 \cdot 4^l + 2 = 10,242$ pixels).
+There is 1,072,805 spherical maps, down-sampled to a level-5 icosahedral sampling ($n = 10 \cdot 4^l + 2 = 10,242$ pixels).
 The labels are heavily unbalanced with 0.1\% TC, 2.2\% AR, and 97.7\% background (BG) pixels.
@@
 
-To demonstrate the flexibility of modeling the discretized sphere by a graph, we collected historical measurements from $n \approx 10,000$ weather stations scattered across the Earth.\footnote{\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
+To demonstrate the flexibility of modeling the sampled sphere by a graph, we collected historical measurements from $n \approx 10,000$ weather stations scattered across the Earth.\footnote{\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
 The spherical data is heavily non-uniformly sampled, with a much higher density of weather stations over North America than the Pacific (\figref{examples:ghcn:tmax}).
@@
 Practitioners currently interpolate their measurements (coming from arbitrarily positioned weather stations, satellites or telescopes) to regular samplings.
-This practice either results in a waste of precision or computational and storage resources.
+This practice either results in a waste of resolution or computational and storage resources.
 Our ultimate goal is for practitioners to be able to work directly on their measurements, however distributed.
@@
 
-Leveraging these three operators, \citet{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian towards the Laplace-Beltrami operator in the general setting of any compact, closed and infinitely differentiable maniform $\mathcal M$, where the sampling scheme $\V$ is drawn randomly on the manifold.
+Leveraging these three operators, \citet{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian towards the Laplace-Beltrami operator in the general setting of any compact, closed and infinitely differentiable manifold $\mathcal M$, where the sampling $\V$ is drawn randomly on the manifold.
 For this reason, their results are all to be interpreted in a probabilistic sense.
-Their proofs consist in establishing that \eqref{eq:Heat Kernel Graph Laplacian operator} converges in probability towards \eqref{eq:Functional approximation to the Laplace-Beltrami operator} as $n\rightarrow \infty$ and \eqref{eq:Functional approximation to the Laplace-Beltrami operator} converges toward \eqref{eq:laplace-beltrami} as $t\rightarrow 0$.
+Their proofs consist in establishing that \eqref{eq:Heat Kernel Graph Laplacian operator} converges in probability towards \eqref{eq:Functional approximation to the Laplace-Beltrami operator} as $n\rightarrow \infty$ and \eqref{eq:Functional approximation to the Laplace-Beltrami operator} converges towards \eqref{eq:laplace-beltrami} as $t\rightarrow 0$.
 In particular, this second step is given by the following:
@@
 As the sphere is a compact smooth manifold embedded in $\mathbb{R}^3$, we can reuse proposition \ref{prop:3}.
-Thus, our strategy to prove Theorem \ref{theo:pointwise convergence for a regular sampling} is to a) show that
+Thus, our strategy to prove Theorem \ref{theo:pointwise convergence for a regular sampling} is to (i) show that
 \begin{equation}\label{eq:continuous convergence}
@@
 \end{equation}
-for a particular class of \emph{deterministic} sampling schemes and b) apply Proposition \ref{prop:3}.
+for a particular class of \emph{deterministic} samplings, and (ii) apply Proposition \ref{prop:3}.
 

### 2019-11-15 main.tex
small updates

@@
 \end{equation}
-This operator extends the graph Laplacian operator previously defined with the weighting scheme \eqnref{weights:belkin} to each point of the manifold, i.e., the sphere.
-\mdeff{Can we avoid to introduce general manifolds and stay on the sphere?}
+This operator extends the graph Laplacian operator previously defined with the weighting scheme \eqnref{weights:belkin} to each point of the the sphere.
+% \mdeff{Can we avoid to introduce general manifolds and stay on the sphere?} \nati{yes}
 As the radius of the kernel $t$ will be adapted to the number of samples, we also rescale the graph Laplacian operator as $\hat{L}_n^t := \frac{|\mathbb S^2|}{4\pi t^2}L_n^t$.
@@
 \end{theorem}
-As a direct implication of this theorem, the discrete counterpart of $\mathbf{\hat L}$ \mdeff{(that's already discrete no?)} converges pointwise towards the Laplace-Beltrami operator $\Delta_{\S^2}$ in the sense explained in \citep{belkin2007convergence}.
-This operator commutes with rotation and hence Theorem \ref{theo:pointwise convergence for a regular sampling} is a strong step towards equivariance. We formalize it in the following theorem.
-\mdeff{This transition should be done better.}
+As a direct implication of this theorem, $\hat L$, the continuous rescaled counterpart of $\mathbf{L}$, 
+% \mdeff{(that's already discrete no?)} \nati{good catch, fixed}
+converges pointwise towards the Laplace-Beltrami operator $\Delta_{\S^2}$ in the sense explained in \citep{belkin2007convergence}.
+This is a major step towards equivariance as the Laplace-Beltrami operator does commute with rotation.
+Based on this property, we show that the graph Laplacian is equivariant to rotation in the limit of infinite sampling.
+% \mdeff{This transition should be done better.} \nati{Done}
 \begin{theorem}\label{theo:equivariance}

### 2019-11-15 main.tex
remove hugly large space after 4 figures
martinos corrections to michaels remarks

@@
 \newcommand{\laplacian}{\Delta_{\mathbb S^2}}
-\newcommand{\Rg}{\mathcal R_g}
+\newcommand{\Rg}{\mathcal R (g)}
 \newcommand{\seminorm}[1]{\left|#1\right|}
@@
 \paragraph{Sampling.}
-Given a sampling $\V = \{x_i \in \S^2\}_{i=1}^n$, a function $f : \S^2 \supset F_\V \to \R$ is sampled as $T_\V(f) = \b{f}$ by the sampling operator $T_\V: L^2(\S^2) \supset F_\V \to \R^n$ defined as $\b{f}: f_i=f(x_i)$, where $F_\V$ will be specified in \secref{equivariance}.
+A sampling scheme $\V = \{x_i \in \S^2\}_{i=1}^n$ is defined to be the discrete subset of the sphere containing the $n$ points where the values of the signals that we want to analyse are known.
+For a given continuous signal $f$, we represent such values in a vector $\b{f}\in\mathbb R^n$.
 As there is no analogue of uniform sampling on the sphere, many samplings have been proposed with different tradeoffs.
@@
 %As the graph convolution acts on a sampled version of the function $\b{f}$ and the rotation on its continuous counterpart $f$, a sampling operator is needed.
-
-We require $F_\V$ to be a suitable subspace of $L^2(\S^2)$ such that $T_\V$ is invertible, i.e., the function $f \in F_\V$ can be unambiguously reconstructed from its sampled values $\b{f}$.
+A continuous function $f : \mathcal C(\S^2) \supset F_\V \to \R$ is sampled as $T_\V(f) = \b{f}$ by the sampling operator $T_\V: C(\S^2) \supset F_\V \to \R^n$ defined as $\b{f}: f_i=f(x_i)$.
+We require $F_\V$ to be a suitable subspace of continuous functions such that $T_\V$ is invertible, i.e., the function $f \in F_\V$ can be unambiguously reconstructed from its sampled values $\b{f}$.
 The existence of such a subspace depends on the sampling $\V$, and its characterization is a common problem in signal processing \citep{driscoll1994Fouriersphere}.
@@
 \end{equation}
-This operator extends the graph Laplacian operator previously defined with the weighting scheme \eqnref{weights:belkin} to each point of the the sphere.
-% \mdeff{Can we avoid to introduce general manifolds and stay on the sphere?} \nati{yes}
+This operator extends the graph Laplacian operator previously defined with the weighting scheme \eqnref{weights:belkin} to each point of the sphere.
 As the radius of the kernel $t$ will be adapted to the number of samples, we also rescale the graph Laplacian operator as $\hat{L}_n^t := \frac{|\mathbb S^2|}{4\pi t^2}L_n^t$.
@@
 \end{theorem}
-As a direct implication of this theorem, $\hat L$, the continuous rescaled counterpart of $\mathbf{L}$, 
-% \mdeff{(that's already discrete no?)} \nati{good catch, fixed}
-converges pointwise towards the Laplace-Beltrami operator $\Delta_{\S^2}$ in the sense explained in \citep{belkin2007convergence}.
-This is a major step towards equivariance as the Laplace-Beltrami operator does commute with rotation.
-Based on this property, we show that the graph Laplacian is equivariant to rotation in the limit of infinite sampling.
-% \mdeff{This transition should be done better.} \nati{Done}
+As a direct implication of this theorem, the discrete counterpart of $\hat L^t_n$ converges pointwise towards the Laplace-Beltrami operator $\Delta_{\S^2}$ in the sense explained in \citep{belkin2007convergence}.
+This operator commutes with rotation and hence Theorem \ref{theo:pointwise convergence for a regular sampling} is a strong step towards equivariance, that we proved pointwisely in the limit of infinite sampling in the following theorem.
 \begin{theorem}\label{theo:equivariance}
@@
 \begin{equation*}
-	\forall y\in\mathbb S^2\quad\left| \mathcal R_g \hat L_n^{t_n} f (y) - \hat L_n^{t_n} \mathcal R_g f(y) \right| \xrightarrow{n\to\infty}0.
+	\forall y\in\mathbb S^2\quad\left| \mathcal R(g) \hat L_n^{t_n} f (y) - \hat L_n^{t_n} \mathcal R(g) f(y) \right| \xrightarrow{n\to\infty}0.
 \end{equation*}
@@
 
-% Nevertheless, it is important to keep in mind the limits of Theorem \ref{theo:pointwise convergence for a regular sampling}.
+Nevertheless, it is important to keep in mind the limits of Theorem \ref{theo:pointwise convergence for a regular sampling} and \ref{theo:equivariance}.
+Both theorems present asymptotic results, and in practice we will always test them on finite samplings.
+Furthermore, since this method is based on the capability of the eigenvectors of the graph Laplacian to approximate the spherical harmonics, a stronger type of convergence of the graph Laplacian would be preferable, i.e.
+spectral convergence (that is proved for a full graph in the case of random sampling for a class of Lipschitz functions in \citep{belkin2007convergence}).
 % First, it is \emph{not} a proof of equivariance of the graph convolution for a specific sampling.
@@
 % \todo{Can we intuitively write what pointwise convergence means, and how it is more limited than spectral or uniform convergence?}
-
-We note that in the random sampling case, the graph laplacian does \emph{not} converge uniformly in general \citep[Sec.
+%We note that in the random sampling case, the graph laplacian does \emph{not} converge uniformly in general \citep[Sec.
 3]{belkin2007convergence}, but does for a class of Lipschitz functions \citep[Sec.

### 2019-11-15 main.tex

@@
 \end{equation}
-This operator extends the graph Laplacian operator previously defined with the weighting scheme \eqnref{weights:belkin} to each point of the sphere.
+
+This operator extends the graph Laplacian operator previously defined with the weighting scheme \eqnref{weights:belkin} to each point of the the sphere.
+% \mdeff{Can we avoid to introduce general manifolds and stay on the sphere?} \nati{yes}
 As the radius of the kernel $t$ will be adapted to the number of samples, we also rescale the graph Laplacian operator as $\hat{L}_n^t := \frac{|\mathbb S^2|}{4\pi t^2}L_n^t$.
@@
 \end{theorem}
-As a direct implication of this theorem, the discrete counterpart of $\hat L^t_n$ converges pointwise towards the Laplace-Beltrami operator $\Delta_{\S^2}$ in the sense explained in \citep{belkin2007convergence}.
-This operator commutes with rotation and hence Theorem \ref{theo:pointwise convergence for a regular sampling} is a strong step towards equivariance, that we proved pointwisely in the limit of infinite sampling in the following theorem.
+As a direct implication of this theorem, the rescaled graph Laplacian (the discrete counterpart of $\hat L^t_n$) converges pointwise towards the Laplace-Beltrami operator $\Delta_{\S^2}$ in the sense explained in \citep{belkin2007convergence}.
+This is a major step towards equivariance as the Laplace-Beltrami operator does commute with rotation.
+Based on this property, we show that the graph Laplacian is equivariant to rotation in the limit of infinite sampling.
+
 \begin{theorem}\label{theo:equivariance}
@@
 	\end{minipage}
+\vspace{-0.5cm}
 \end{figure}

### 2019-11-15 main.tex
small fix
added figure sigma_i

@@
 \paragraph{Theoretical convergence.}
+\begin{wrapfigure}{r}{5cm}
+	\centering
+	\includegraphics[width=\linewidth]{d_iA_i}
+	\caption{The patch around the $i$th sampling point.}
+\end{wrapfigure}
 We extend the work of \citep{belkin2005towards} to a sufficiently regular, deterministic sampling.
@@
 \end{equation}
-
 This operator extends the graph Laplacian operator previously defined with the weighting scheme \eqnref{weights:belkin} to each point of the the sphere.
@@
 We start by proving that for smooth functions, for any fixed $t$, the extended graph Laplacian $L^t_n$ converges towards its continuous counterpart $L^t$ as the sampling increases in size.
+
 \begin{prop}\label{prop:1}

### 2019-11-15 main.tex
comment on theorems

@@
 In particular, it gives insights on how the parameter $t$ needs to be adjusted with respect to the number of points $n$.
-
 Nevertheless, it is important to keep in mind the limits of Theorem \ref{theo:pointwise convergence for a regular sampling} and \ref{theo:equivariance}.
-Both theorems present asymptotic results, and in practice we will always test them on finite samplings.
-Furthermore, since this method is based on the capability of the eigenvectors of the graph Laplacian to approximate the spherical harmonics, a stronger type of convergence of the graph Laplacian would be preferable, i.e.
+Both theorems present asymptotic results, but in practice we will always work with finite samplings.
+Furthermore, since this method is based on the capability of the eigenvectors of the graph Laplacian to approximate the spherical harmonics,
+% maybe erase the previous sentence?
+a stronger type of convergence of the graph Laplacian would be preferable, i.e.
 spectral convergence (that is proved for a full graph in the case of random sampling for a class of Lipschitz functions in \citep{belkin2007convergence}).
@@
 6]{belkin2005towards}.
-Second, while we do not have a formal proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, with $\alpha$ very close or equal to $\linefrac{1}{2}$.
+While we do not have a formal proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, with $\alpha$ very close or equal to $\linefrac{1}{2}$.
 The empirical results discussed in the next paragraph also points in this direction.
@@
 	\end{minipage}
-\vspace{-0.5cm}
+% \vspace{-0.5cm}
 \end{figure}

### 2019-11-15 main.tex
figure 2: rename
polynomial order P instead of K to avoid confusion with k neighbors

@@
 \begin{equation} \label{eqn:graph_conv}
-	h(\b{L}) \b{f} = \left(\sum_{i=0}^K \alpha_i \b{L}^i\right) \b{f},
+	h(\b{L}) \b{f} = \left(\sum_{i=0}^P \alpha_i \b{L}^i\right) \b{f},
 \end{equation}
-where $K$ is the polynomial order (which corresponds to the filter's size) and $\alpha_i$ are the coefficients to be optimized during training.\footnote{In practice, training with Chebyshev polynomials (instead of monomials) is slightly more stable.
+where $P$ is the polynomial order (which corresponds to the filter's size) and $\alpha_i$ are the coefficients to be optimized during training.\footnote{In practice, training with Chebyshev polynomials (instead of monomials) is slightly more stable.
 We believe it to be due to their orthogonality and uniformity.}
@@
 	\centering
-	\includegraphics[width=\linewidth]{d_iA_i}
+	\includegraphics[width=\linewidth]{patch}
 	\caption{The patch around the $i$th sampling point.}
@@
 A GAP and a fully connected layer with softmax follow.
-The polynomials are all of order $K=3$ and the number of channels per layer is $16, 32, 64, 128, 256$, respectively.
+The polynomials are all of order $P=3$ and the number of channels per layer is $16, 32, 64, 128, 256$, respectively.
 Following \citet{esteves2018sphericalcnn}, the cross-entropy plus a triplet loss is optimized with Adam for 30 epochs on the dataset augmented by 3 random translations.
@@
 A GAP and a fully connected layer with softmax follow.
-The polynomials are all of order $K=4$ and the number of channels per layer is $16, 32, 64, 64, 64$, respectively.
+The polynomials are all of order $P=4$ and the number of channels per layer is $16, 32, 64, 64, 64$, respectively.
 The cross-entropy loss is optimized with Adam for 80 epochs.
@@
 %The decoder is made of
-The polynomials are all of order $K=3$.
+The polynomials are all of order $P=3$.
 The cross-entropy loss (weighted or non-weighted) is optimized with Adam for 30 epochs.
@@
 The NN is made of $3$ graph convolutional layers.
-The polynomials are all of order $K=0$ or $4$ and the number of channels per layer is $50, 100, 100$, respectively.
+The polynomials are all of order $P=0$ or $4$ and the number of channels per layer is $50, 100, 100$, respectively.
 For the global regression, a GAP and a fully connected layer follow.
@@
 		\cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10}
-		order $K$ & {MSE} & {MAE} & {R2} & {MSE} & {MAE} & {R2} & {MSE} & {MAE} & {R2} \\
+		order $P$ & {MSE} & {MAE} & {R2} & {MSE} & {MAE} & {R2} & {MSE} & {MAE} & {R2} \\
 		\midrule
@@
 Results are shown in \tabref{ghcn}.
-While using a polynomial order $K=0$ is like modeling each time series independently with an MLP, orders $K>0$ integrate neighborhood information.
+While using a polynomial order $P=0$ is like modeling each time series independently with an MLP, orders $P>0$ integrate neighborhood information.
 Results show that using the structure induced by the spherical geometry always yields better performance.

### 2019-11-15 main.tex
fix R(g)

@@
 \newcommand{\laplacian}{\Delta_{\mathbb S^2}}
-\newcommand{\Rg}{\mathcal R (g)}
+\newcommand{\Rg}{\mathcal{R}(g)}
 \newcommand{\seminorm}[1]{\left|#1\right|}
@@
 \begin{itemize}
-	\item \mdeff{Why two definitions of rotations, $R(g)$ and $\mathcal{R}_g$?} [Martino]
     \item answer commenter
@@
 % 0.2 Explain why the Laplacian is so important...
-By definition, the (spherical) graph convolution is rotation equivariant if and only if it commutes with the rotation operator defined as $R(g), g\in SO(3)$: $R(g) f(x) = f\left(g^{-1} x \right)$.
+By definition, the (spherical) graph convolution is rotation equivariant if and only if it commutes with the rotation operator defined as $\Rg, g\in SO(3)$: $\Rg f(x) = f\left(g^{-1} x \right)$.
 In the context of this work, graph convolution is performed by recursive applications of the graph Laplacian (\eqnref{graph_conv}).
-Hence, if $R(g)$ commutes with $\b{L}$, then, by recursion, it will also commute with the convolution $h(\b{L})$.
+Hence, if $\Rg$ commutes with $\b{L}$, then, by recursion, it will also commute with the convolution $h(\b{L})$.
 As a result, $h(\b{L})$ is rotation equivariant if and only if
@@
 \end{equation*}
-where $\b{R}_\V(g) = T_\V R(g) T_\V^{-1}$.
+where $\b{R}_\V(g) = T_\V \Rg T_\V^{-1}$.
 For an empirical evaluation of equivariance, we define the \textit{normalized equivariance error} for a signal $\b{f}$ and a  rotation $g$ as
@@
 converges to the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of samples grows to infinity.
-This result is a good starting point as $\Delta_{\mathbb{S}^2}$ commutes with rotation, i.e., $\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$.
+This result is a good starting point as $\Delta_{\mathbb{S}^2}$ commutes with rotation, i.e., $\Delta_{\mathbb{S}^2}\Rg = \Rg\Delta_{\mathbb{S}^2}$.
 % and (ii) is diagonalized by the spherical harmonics.
@@
 Define $d^{(n)} := \max_{i=1, \dots, n} d_i$ and $A^{(n)} := \max_{i=1, \dots, n} A_i$.
-%Given any rotation $g\in SO(3)$, we define the corresponding rotation operator $\mathcal R_g$ such that for any function $f$ on the sphere
+%Given any rotation $g\in SO(3)$, we define the corresponding rotation operator $\Rg$ such that for any function $f$ on the sphere
 %\mdeff{Already defined in problem formulation.}
 %\begin{equation} \label{eq:rotation operator}
-%	\mathcal R_g f(x) := f(g^{-1}(x)).
+%	\Rg f(x) := f(g^{-1}(x)).
 %\end{equation}
@@
 \begin{equation*}
-	\forall y\in\mathbb S^2\quad\left| \mathcal R(g) \hat L_n^{t_n} f (y) - \hat L_n^{t_n} \mathcal R(g) f(y) \right| \xrightarrow{n\to\infty}0.
+	\forall y\in\mathbb S^2\quad\left| \Rg \hat L_n^{t_n} f (y) - \hat L_n^{t_n} \Rg f(y) \right| \xrightarrow{n\to\infty}0.
 \end{equation*}
@@
 Fix $x\in \mathbb S^2$.
-Since any rotation $\mathcal R_g$ is an isometry, and the Laplacian $\Delta$ commutes with all isometries of a Riemanniann manifold, and defining $\mathcal R_g f =: f'$ for ease of notation, we can write that
+Since any rotation $\Rg$ is an isometry, and the Laplacian $\Delta$ commutes with all isometries of a Riemanniann manifold, and defining $\Rg f =: f'$ for ease of notation, we can write that
 	\begin{align*}

### 2019-11-15 figures/spectrum.py
power spectrum figure: consistent axis labels

@@ -78,8 +78,9 @@ ax.set_xlim([1, 1e3])
 ax.set_ylim([1e-3, 5e1])
 ax.set_yscale('log')
 ax.set_xscale('log')
-ax.set_xlabel('$\ell$: spherical harmonic index')
-ax.set_ylabel('$C_\ell$: power spectrum')
+ax.set_xlabel('spherical harmonic degree $\ell$')
+#ax.set_ylabel('power spectrum $C_\ell$')
+ax.set_ylabel('power spectrum')
 #ax.set_ylabel('$C_\ell \cdot \ell \cdot (\ell+1)$')
 #ax.set_title('Power Spectrum Density, 3-arcmin smoothing, noiseless, Nside=1024')
 

### 2019-11-15 figures/kernel_widths.py
kernel widths figure: consistent legend

@@ -55,8 +55,8 @@ fig, ax = plt.subplots(figsize=(4, 2.3))
 for neighbors, optimums in sorted(kernel_width_optimal.items(), reverse=True):
     nside = np.array([12*n**2 for n in optimums.keys()])
     width = np.array(list(optimums.values()))**2/(4*np.log(2))
-    ax.loglog(nside, width, '.-', label=f'kNN graph, $k={neighbors}$')
-ax.loglog(12*v1_nside[5:]**2, v1_t[5:], '.--', label=f'Perraudin et. al., $k=8$')
+    ax.loglog(nside, width, '.-', label=f'$k$-NN graph, $k={neighbors}$')
+ax.loglog(12*v1_nside[5:]**2, v1_t[5:], '.--', label=f'Perraudin et al., $k=8$')
 ax.legend(loc='upper right')
 ax.set_xlabel('$n = 12 N_{side}^2$ pixels', fontsize=14)
 ax.set_ylabel('kernel width $t$', fontsize=14)

### 2019-11-15 figures/spectrum.py
power spectrum figure: larger axis labels

@@ -78,9 +78,9 @@ ax.set_xlim([1, 1e3])
 ax.set_ylim([1e-3, 5e1])
 ax.set_yscale('log')
 ax.set_xscale('log')
-ax.set_xlabel('spherical harmonic degree $\ell$')
+ax.set_xlabel('spherical harmonic degree $\ell$', fontsize=14)
 #ax.set_ylabel('power spectrum $C_\ell$')
-ax.set_ylabel('power spectrum')
+ax.set_ylabel('power spectrum', fontsize=14)
 #ax.set_ylabel('$C_\ell \cdot \ell \cdot (\ell+1)$')
 #ax.set_title('Power Spectrum Density, 3-arcmin smoothing, noiseless, Nside=1024')
 

### 2019-11-15 figures/equivariance_error.py
extract code for the equivariance error figure

@@ -1,0 +1,111 @@
+import matplotlib
+from matplotlib.lines import Line2D
+plt.rcParams['figure.figsize'] = (9,9)
+
+font = {'family': 'serif',
+        'color':  'black',
+        'weight': 'normal',
+        'size': 20,
+        }
+matplotlib.rcParams.update({'font.size': 18})
+# -------------- khasanova-Frossard ------------------
+equiv_error_KF = pickle.load(open('khasanova_frossard.pickle', 'rb'))
+degree_step = {
+    32: 3,
+    64: 6,
+    128: 12,
+    256: 25}
+
+bw = 64
+lmax = bw
+degrees = np.arange(0, lmax, degree_step[bw])
+degrees = degrees[1:]
+l1, = plt.loglog(degrees, equiv_error_KF[bw][1:], 'mv-')
+
+bw = 128
+lmax = bw
+degrees = np.arange(0, lmax, degree_step[bw])
+degrees = degrees[1:]
+plt.loglog(degrees, equiv_error_KF[bw][1:], 'mx-', )
+
+bw = 256
+lmax = bw
+degrees = np.arange(0, lmax, degree_step[bw])
+degrees = degrees[1:]
+plt.loglog(degrees, equiv_error_KF[bw][1:], 'mo-', )
+
+
+# ----------------- healpix ----------------------
+nsides = [32, 64, 128]
+
+degree_step = {
+            32: 10,
+            64: 10,
+            128: 50,
+            256: 50,
+            512: 100,
+            1024: 200,
+}
+
+equiv_error_V1 = pickle.load(open('V1 - ||Lf||.pickle', 'rb'))
+equiv_error_8 = pickle.load(open('V2 - 8 neighbors - ||Lf||.pickle', 'rb'))
+equiv_error_20 = pickle.load(open('V2 - 20 neighbors - ||Lf||.pickle', 'rb'))
+equiv_error_40 = pickle.load(open('V2 - 40 neighbors - ||Lf||.pickle', 'rb'))
+
+nside = 32
+lmax = 3*nside-1
+degrees = np.arange(0, lmax+1, degree_step[nside])
+degrees = degrees[1:]
+l2, = plt.loglog(degrees, equiv_error_V1[nside][1:], 'gv-', label='V1')
+l3, = plt.loglog(degrees, equiv_error_8[nside][1:], 'cv-', label='8 neighbors')
+l4, = plt.loglog(degrees, equiv_error_20[nside][1:], 'rv-', label='20 neighbors')
[…]

### 2019-11-15 figures/equivariance_error.py
make it a standalone script

@@ -1,5 +1,13 @@
-import matplotlib
+#!/usr/bin/env python3
+
+from os import path
+import pickle
+
+import numpy as np
+import matplotlib.pyplot as plt
 from matplotlib.lines import Line2D
+
+
 plt.rcParams['figure.figsize'] = (9,9)
 
 font = {'family': 'serif',
@@ -7,9 +15,9 @@ font = {'family': 'serif',
         'weight': 'normal',
         'size': 20,
         }
-matplotlib.rcParams.update({'font.size': 18})
+plt.rcParams.update({'font.size': 18})
 # -------------- khasanova-Frossard ------------------
-equiv_error_KF = pickle.load(open('khasanova_frossard.pickle', 'rb'))
+equiv_error_KF = pickle.load(open('equivariance_error/khasanova_frossard.pickle', 'rb'))
 degree_step = {
     32: 3,
     64: 6,
@@ -47,10 +55,10 @@ degree_step = {
             1024: 200,
 }
 
-equiv_error_V1 = pickle.load(open('V1 - ||Lf||.pickle', 'rb'))
-equiv_error_8 = pickle.load(open('V2 - 8 neighbors - ||Lf||.pickle', 'rb'))
-equiv_error_20 = pickle.load(open('V2 - 20 neighbors - ||Lf||.pickle', 'rb'))
-equiv_error_40 = pickle.load(open('V2 - 40 neighbors - ||Lf||.pickle', 'rb'))
+equiv_error_V1 = pickle.load(open('equivariance_error/V1 - ||Lf||.pickle', 'rb'))
+equiv_error_8 = pickle.load(open('equivariance_error/V2 - 8 neighbors - ||Lf||.pickle', 'rb'))
+equiv_error_20 = pickle.load(open('equivariance_error/V2 - 20 neighbors - ||Lf||.pickle', 'rb'))
+equiv_error_40 = pickle.load(open('equivariance_error/V2 - 40 neighbors - ||Lf||.pickle', 'rb'))
 
 nside = 32
 lmax = 3*nside-1
@@ -101,11 +109,10 @@ legend_elements_2 = [Line2D([0], [0], color='k', marker='v', markersize=8),
                    Line2D([0], [0], color='k', marker='x', markersize=8),
                    Line2D([0], [0], color='k', marker='o', markersize=8)]
 
-leg2 = ax.legend(legend_elements, ['$s=32$', '$s=64$', '$s=128$'],loc='upper right')
[…]

### 2019-11-15 figures/kernel_widths.py

@@ -1,9 +1,10 @@
 #!/usr/bin/env python3
 
 from os import path
-import numpy as np
 
+import numpy as np
 from matplotlib import pyplot as plt
+
 
 plt.rc('font', family='Latin Modern Roman')  # Latin Modern for text
 plt.rc('mathtext', fontset='cm')  # Computer Modern for math (default is dejavusans)

### 2019-11-15 figures/equivariance_error.py
equivariance error figure: better legends and axis labels

@@ -89,8 +89,9 @@ plt.loglog(degrees, equiv_error_40[nside][1:], 'bo-', )
 
 # -------------- final parameters ------------------
 
-plt.xlabel('Degree $\ell$', fontdict=font,)
-plt.ylabel('Equivariance Error', fontdict=font, )
+plt.xlabel(r'spherical harmonic degree $\ell$', fontdict=font,)
+#plt.ylabel(r'mean equivariance error $\overline{E}_{\mathbf{L}, C}$', fontdict=font, )
+plt.ylabel(r'mean equivariance error $\overline{E}_{L, C}$', fontdict=font, )
 plt.tick_params(axis='both', which='major')
 plt.grid()
 plt.xlim([10,np.max(degrees)])
@@ -102,14 +103,17 @@ legend_elements_1 = [Line2D([0], [0], color='m', marker='', markersize=8),
                    Line2D([0], [0], color='r', marker='', markersize=8),
                    Line2D([0], [0], color='b', marker='', markersize=8)]
 # Add first legend:  only labeled data is included
-leg1 = ax.legend(legend_elements_1,['Khasanova, Frossard','Perraudin et al.', 'This paper - 8 neighbors', 'This paper - 20 neighbors', 'This paper - 40 neighbors'], loc='lower left')
+leg1 = ['Khasanova & Frossard, $k=4$', 'Perraudin et al., $k=8$']
+leg1.extend([f'$k$-NN graph, $k={k}$ neighbors' for k in [8, 20, 40]])
+leg1 = ax.legend(legend_elements_1, leg1, loc='lower left')
 # Add second legend for the maxes and mins.
 # leg1 will be removed from figure
 legend_elements_2 = [Line2D([0], [0], color='k', marker='v', markersize=8),
                    Line2D([0], [0], color='k', marker='x', markersize=8),
                    Line2D([0], [0], color='k', marker='o', markersize=8)]
 
-leg2 = ax.legend(legend_elements_2, ['$s=32$', '$s=64$', '$s=128$'],loc='upper right')
+#leg2 = ax.legend(legend_elements_2, ['$s=32$', '$s=64$', '$s=128$'],loc='upper right')
+leg2 = ax.legend(legend_elements_2, [rf'$n \propto {s}^2$' for s in [32, 64, 128]], loc='upper right')
 # Manually add the first legend back
 ax.add_artist(leg1)
 

### 2019-11-15 figures/equivariance_error.py
equivariance error figure: use mpl object API

@@ -8,7 +8,7 @@ import matplotlib.pyplot as plt
 from matplotlib.lines import Line2D
 
 
-plt.rcParams['figure.figsize'] = (9,9)
+fig, ax = plt.subplots(figsize=(9, 9))
 
 font = {'family': 'serif',
         'color':  'black',
@@ -28,19 +28,19 @@ bw = 64
 lmax = bw
 degrees = np.arange(0, lmax, degree_step[bw])
 degrees = degrees[1:]
-l1, = plt.loglog(degrees, equiv_error_KF[bw][1:], 'mv-')
+l1, = ax.loglog(degrees, equiv_error_KF[bw][1:], 'mv-')
 
 bw = 128
 lmax = bw
 degrees = np.arange(0, lmax, degree_step[bw])
 degrees = degrees[1:]
-plt.loglog(degrees, equiv_error_KF[bw][1:], 'mx-', )
+ax.loglog(degrees, equiv_error_KF[bw][1:], 'mx-', )
 
 bw = 256
 lmax = bw
 degrees = np.arange(0, lmax, degree_step[bw])
 degrees = degrees[1:]
-plt.loglog(degrees, equiv_error_KF[bw][1:], 'mo-', )
+ax.loglog(degrees, equiv_error_KF[bw][1:], 'mo-', )
 
 
 # ----------------- healpix ----------------------
@@ -64,39 +64,38 @@ nside = 32
 lmax = 3*nside-1
 degrees = np.arange(0, lmax+1, degree_step[nside])
 degrees = degrees[1:]
-l2, = plt.loglog(degrees, equiv_error_V1[nside][1:], 'gv-', label='V1')
-l3, = plt.loglog(degrees, equiv_error_8[nside][1:], 'cv-', label='8 neighbors')
-l4, = plt.loglog(degrees, equiv_error_20[nside][1:], 'rv-', label='20 neighbors')
-l5, = plt.loglog(degrees, equiv_error_40[nside][1:], 'bv-', label='40 neighbors')
+l2, = ax.loglog(degrees, equiv_error_V1[nside][1:], 'gv-', label='V1')
+l3, = ax.loglog(degrees, equiv_error_8[nside][1:], 'cv-', label='8 neighbors')
+l4, = ax.loglog(degrees, equiv_error_20[nside][1:], 'rv-', label='20 neighbors')
+l5, = ax.loglog(degrees, equiv_error_40[nside][1:], 'bv-', label='40 neighbors')
 
 nside = 64
 lmax = 3*nside-1
[…]

### 2019-11-15 rebuttal.md
edits in the rebuttal

@@
 TODO(mdeff): check GCN paper for the variants
-TODO(nati) my version:
-Practically, we believe that any graph neural network variant may work and some might even slightly beat ChebyNet.
+TODO(nati version):
+1. Practically, we believe that any graph neural network variant may work and some might even slightly beat ChebyNet.
 However, our equivariance theory utilizes the graph Laplacian as a base building block.
@@
 Eventually, the method we use scales linearly with K, which is an hyper-parameter to be set (analogous to the kernel size in classical CNNs).
+2. Regarding the sentence 
+"It is, however, possible to construct a CNN in which the activations transform in a predictable and reversible way,",
+we read in the same paper, two sensences above:
+"It can be shown that one cannot construct a CNN for images that behaves in a quasi-invariant way with respect to both translations and rotations unless every filter is directionless.".
+In the case of our contribution, the graph convolution we use can be considered as directionless (isotropic convolution kernel). Hence, we do not need any special activation functions to be invariant.
+
+Note also that on the sphere and the plane the meaning of rotation is different. 
+The plane has 2 axes for translation and 1 axis for rotation, while the sphere has only 3 axes of rotation. 
+In the context of this question, we assume that the axes of rotation on the sphere correspond to both rotation and translation on the plane.
 

### 2019-11-15 figures/equivariance_error.py
equivariance error figure: simplify code

@@ -16,105 +16,85 @@ font = {'family': 'serif',
         'size': 20,
         }
 plt.rcParams.update({'font.size': 18})
+
 # -------------- khasanova-Frossard ------------------
+
 equiv_error_KF = pickle.load(open('equivariance_error/khasanova_frossard.pickle', 'rb'))
+
+markers = ['v', 'x', 'o']
+
 degree_step = {
     32: 3,
     64: 6,
     128: 12,
-    256: 25}
+    256: 25,
+}
 
-bw = 64
-lmax = bw
-degrees = np.arange(0, lmax, degree_step[bw])
-degrees = degrees[1:]
-l1, = ax.loglog(degrees, equiv_error_KF[bw][1:], 'mv-')
-
-bw = 128
-lmax = bw
-degrees = np.arange(0, lmax, degree_step[bw])
-degrees = degrees[1:]
-ax.loglog(degrees, equiv_error_KF[bw][1:], 'mx-', )
-
-bw = 256
-lmax = bw
-degrees = np.arange(0, lmax, degree_step[bw])
-degrees = degrees[1:]
-ax.loglog(degrees, equiv_error_KF[bw][1:], 'mo-', )
-
+for bw, marker in zip([64, 128, 256], markers):
+    lmax = bw
+    degrees = np.arange(0, lmax, degree_step[bw])
+    degrees = degrees[1:]
+    ax.loglog(degrees, equiv_error_KF[bw][1:], f'm{marker}-')
 
 # ----------------- healpix ----------------------
-nsides = [32, 64, 128]
-
-degree_step = {
-            32: 10,
-            64: 10,
-            128: 50,
-            256: 50,
-            512: 100,
-            1024: 200,
-}
 
 equiv_error_V1 = pickle.load(open('equivariance_error/V1 - ||Lf||.pickle', 'rb'))
 equiv_error_8 = pickle.load(open('equivariance_error/V2 - 8 neighbors - ||Lf||.pickle', 'rb'))
 equiv_error_20 = pickle.load(open('equivariance_error/V2 - 20 neighbors - ||Lf||.pickle', 'rb'))
 equiv_error_40 = pickle.load(open('equivariance_error/V2 - 40 neighbors - ||Lf||.pickle', 'rb'))
 
-nside = 32
-lmax = 3*nside-1
-degrees = np.arange(0, lmax+1, degree_step[nside])
-degrees = degrees[1:]
-l2, = ax.loglog(degrees, equiv_error_V1[nside][1:], 'gv-', label='V1')
[…]

### 2019-11-15 figures/equivariance_error.py
equivariance error figure: right font

@@ -8,14 +8,14 @@ import matplotlib.pyplot as plt
 from matplotlib.lines import Line2D
 
 
-fig, ax = plt.subplots(figsize=(9, 9))
+plt.rc('font', family='Latin Modern Roman')  # Latin Modern for text
+plt.rc('mathtext', fontset='cm')  # Computer Modern for math (default is dejavusans)
+#plt.rc('text', usetex=True)
+#plt.rc('text.latex', preamble=r'\usepackage{lmodern}')
 
-font = {'family': 'serif',
-        'color':  'black',
-        'weight': 'normal',
-        'size': 20,
-        }
-plt.rcParams.update({'font.size': 18})
+fig, ax = plt.subplots(figsize=(5, 5))
+
+params = dict(linewidth=0.8, markersize=3)
 
 # -------------- khasanova-Frossard ------------------
 
@@ -34,7 +34,7 @@ for bw, marker in zip([64, 128, 256], markers):
     lmax = bw
     degrees = np.arange(0, lmax, degree_step[bw])
     degrees = degrees[1:]
-    ax.loglog(degrees, equiv_error_KF[bw][1:], f'm{marker}-')
+    ax.loglog(degrees, equiv_error_KF[bw][1:], f'm{marker}-', **params)
 
 # ----------------- healpix ----------------------
 
@@ -58,29 +58,29 @@ for nside, marker in zip(nsides, markers):
     lmax = 3 * nside - 1
     degrees = np.arange(0, lmax+1, degree_step[nside])
     degrees = degrees[1:]
-    ax.loglog(degrees, equiv_error_V1[nside][1:], f'g{marker}-')
-    ax.loglog(degrees, equiv_error_8[nside][1:], f'c{marker}-')
-    ax.loglog(degrees, equiv_error_20[nside][1:], f'r{marker}-')
-    ax.loglog(degrees, equiv_error_40[nside][1:], f'b{marker}-')
+    ax.loglog(degrees, equiv_error_V1[nside][1:], f'g{marker}-', **params)
+    ax.loglog(degrees, equiv_error_8[nside][1:], f'c{marker}-', **params)
+    ax.loglog(degrees, equiv_error_20[nside][1:], f'r{marker}-', **params)
+    ax.loglog(degrees, equiv_error_40[nside][1:], f'b{marker}-', **params)
 
 # -------------- final parameters ------------------
 
-ax.set_xlabel(r'spherical harmonic degree $\ell$', fontdict=font,)
[…]

### 2019-11-15 main.tex
make it a standalone script
fix notation laplacian
edit on text related to equivariance figure

@@
 %leading to a high mean equivariance error if the mean is computed over rotations in SO(3).
-Note that while the resulting convolution is not equivariant to the whole of $SO(3)$, that is enough for omnidirectional imaging because, as gravity consistently orients the sphere, objects only rotate longitudinally or latitudinally.
+While the resulting convolution is not equivariant to the whole of $SO(3)$ (\figref{equivariance_error}), it is enough for omnidirectional imaging because, as gravity consistently orients the sphere, objects only rotate longitudinally or latitudinally.
 
@@
 % and (ii) is diagonalized by the spherical harmonics.
-While the weighting scheme is full (i.e., every vertex is connected to every vertex), most weights are small due to the exponential.
-We hence make an approximation to limit the cost of the convolution \eqnref{graph_conv} by only considering the $k$ nearest neighbors to each vertex.
+While the weighting scheme is full (i.e., every vertex is connected to every other vertex), most weights are small due to the exponential.
+We hence make an approximation to limit the cost of the convolution \eqnref{graph_conv} by only considering the $k$ nearest neighbors ($k$-NN) of each vertex.
 %In practice, the tricky part is to set $t$ in a non-asymptotic regime.
@@
 
-Considering the HEALPix sampling, \citet{perraudin2019deepspherecosmo} connected each vertex to their 8 adjacent vertices, computed the weights with \eqnref{weights:belkin}, and heuristically set $t$ to half the average squared Euclidean distance between connected vertices.
-This heuristic however seems to over-estimate $t$ (see \figref{kernel_widths}).
+Considering the HEALPix sampling, \citet{perraudin2019deepspherecosmo} connected each vertex to their 8 adjacent vertices in the tiling of the sphere, computed the weights with \eqnref{weights:belkin}, and heuristically set $t$ to half the average squared Euclidean distance between connected vertices.
+This heuristic however over-estimates $t$ (\figref{kernel_widths}) and leads to an increased equivariance error (\figref{equivariance_error}).
 % We observe that using a small kernel size $t$, \cite{perraudin2019deepspherecosmo} would probably be more equivariant.
@@
 	\begin{equation*}
-		\lim_{n\to\infty}\hat{L}_n^{t_n}f(y) = \triangle_{\S^2}f(y).
+		\lim_{n\to\infty}\hat{L}_n^{t_n}f(y) = \laplacian f(y).
 	\end{equation*}
@@
 % 3.1) explain what the figure tells us
-For $k=8$ neighbors, selecting the optimal value of $t$ improves on \citet{perraudin2019deepspherecosmo}, whose graph also was constructed to have at most 8 neighbors.
-The equivariance error further decreases by connecting more neighbors,  at the expense of computations.
-Increasing the resolution decreases the equivariance error in the high frequencies.
-% Increasing the graph resolution of the graph of \citet{khasanova2017sphericalcnn} does not seem to improve its equivariance.
-Moreover, we observe that the weighting scheme \eqnref{weights:khasanova} does indeed not lead to convolutions that are equivariant to all rotations $g \in SO(3)$.
-We however verified that the convolutions are equivariant to longitudinal and latitudinal rotations, as intended.
+\Figref{equivariance_error} shows that the weighting scheme \eqnref{weights:khasanova} from \citep{khasanova2017sphericalcnn} does indeed not lead to a convolution that is equivariant to all rotations $g \in SO(3)$.\footnote{We however verified that the convolution is equivariant to longitudinal and latitudinal rotations, as intended.}
+For $k=8$ neighbors, selecting the optimal kernel width $t$ improves on \citep{perraudin2019deepspherecosmo} at no cost, highlighting the importance of this parameter.
+Increasing the resolution decreases the equivariance error in the high frequencies, an effect most probably due to the sampling.
+Most importantly, the equivariance error decreases when connecting more neighbors.
+Hence, the number of neighbors $k$ gives us a precise control of the tradeoff between cost and equivariance.
 
@@
 		\centering
-		\includegraphics[width=1\linewidth]{all_in_one.pdf}
+		\includegraphics[width=\linewidth]{equivariance_error}
 		\caption{
 			Mean equivariance error \eqref{eq:mean equivariance error}.
-			The number of pixels is $n = 4 s^2$ for the equiangular sampling and $n = 12 s^2$ for the HEALPix.
+			There is a clear tradeoff between equivariance and computational cost, governed by the number of vertices $n$ and edges $kn$.
 		}
@@
 	\begin{equation*}
-	\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) =  \lim_{n\to\infty}\frac{1}{4\pi t_n^2} L^{t_n}f(y) = \frac{1}{|\S^2|}\triangle_{\S^2}f(y)
+	\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) =  \lim_{n\to\infty}\frac{1}{4\pi t_n^2} L^{t_n}f(y) = \frac{1}{|\S^2|}\laplacian f(y)
 	\end{equation*}

### 2019-11-15 main.tex
avoid talking about manifold in main text

@@
 We extend the work of \citep{belkin2005towards} to a sufficiently regular, deterministic sampling.
-Following their setting, we will work with the extended graph Laplacian operator as the linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
+Following their setting, we will work with the extended graph Laplacian operator as the linear operator $L_n^t: L^{2}(\S^2) \rightarrow L^{2}(\S^2)$ such that
 \begin{equation} \label{eq:Heat Kernel Graph Laplacian operator}
@@
 This operator extends the graph Laplacian operator previously defined with the weighting scheme \eqnref{weights:belkin} to each point of the the sphere.
-% \mdeff{Can we avoid to introduce general manifolds and stay on the sphere?} \nati{yes}
-As the radius of the kernel $t$ will be adapted to the number of samples, we also rescale the graph Laplacian operator as $\hat{L}_n^t := \frac{|\mathbb S^2|}{4\pi t^2}L_n^t$.
 Hence, we have $\b{L}_n^t \b{f} = T_\V L_n^t f$.
+As the radius of the kernel $t$ will be adapted to the number of samples, we scale the extended graph Laplacian operator as $\hat{L}_n^t := \frac{|\mathbb S^2|}{4\pi t^2}L_n^t$.
 % $\b{\hat L} = \frac{|\mathbb S^2|}{4\pi t^2}\b L_n^t$. \nati{why define this, we are not using it}

### 2019-11-15 main.tex
todos
adjust patch figure
pass on theory

@@
 \usepackage{subfig}
-%\usepackage{wrapfig}
+\usepackage{wrapfig}
 %\usepackage{floatflt}
@@
 \usepackage{amssymb}
-\usepackage{wrapfig}
 
@@
 	\item \mdeff{check my Telegram notes}
+	\item argue against more generality
+	\item figure that show the three samplings? (suggested by reviewer \#2)
 \end{itemize}
@@
 \paragraph{Theoretical convergence.}
-\begin{wrapfigure}{r}{5cm}
+\begin{wrapfigure}[10]{r}{3cm}
 	\centering
-	\includegraphics[width=\linewidth]{patch}
-	\caption{The patch around the $i$th sampling point.}
+	\includegraphics[width=0.9\linewidth]{patch}
+	\caption{Patch.}
+	\label{fig:patch}
 \end{wrapfigure}
 We extend the work of \citep{belkin2005towards} to a sufficiently regular, deterministic sampling.
-Following their setting, we will work with the extended graph Laplacian operator as the linear operator $L_n^t: L^{2}(\S^2) \rightarrow L^{2}(\S^2)$ such that
+Following their setting, we work with the \emph{extended graph Laplacian} operator as the linear operator $L_n^t: L^{2}(\S^2) \rightarrow L^{2}(\S^2)$ such that
 \begin{equation} \label{eq:Heat Kernel Graph Laplacian operator}
@@
 \end{equation}
-This operator extends the graph Laplacian operator previously defined with the weighting scheme \eqnref{weights:belkin} to each point of the the sphere.
-Hence, we have $\b{L}_n^t \b{f} = T_\V L_n^t f$.
-As the radius of the kernel $t$ will be adapted to the number of samples, we scale the extended graph Laplacian operator as $\hat{L}_n^t := \frac{|\mathbb S^2|}{4\pi t^2}L_n^t$.
+This operator extends the graph Laplacian with the weighting scheme \eqnref{weights:belkin} to each point of the sphere (i.e., $\b{L}_n^t \b{f} = T_\V L_n^t f$).
+As the radius of the kernel $t$ will be adapted to the number of samples, we scale the operator as $\hat{L}_n^t := |\S^2| (4\pi t^2)^{-1} L_n^t$.  % \frac{|\S^2|}{4\pi t^2}
 % $\b{\hat L} = \frac{|\mathbb S^2|}{4\pi t^2}\b L_n^t$. \nati{why define this, we are not using it}
@@
 \end{theorem}
-As a direct implication of this theorem, the rescaled graph Laplacian (the discrete counterpart of $\hat L^t_n$) converges pointwise towards the Laplace-Beltrami operator $\Delta_{\S^2}$ in the sense explained in \citep{belkin2007convergence}.
-This is a major step towards equivariance as the Laplace-Beltrami operator does commute with rotation.
-Based on this property, we show that the graph Laplacian is equivariant to rotation in the limit of infinite sampling.
-
+%As a direct implication of this theorem, the scaled graph Laplacian (the discrete counterpart of $\hat L^t_n$) converges pointwise towards the Laplace-Beltrami operator $\Delta_{\S^2}$.
+This is a major step towards equivariance, as the Laplace-Beltrami operator commutes with rotation.
+Based on this property, we show the equivariance of the scaled extended graph Laplacian.
 \begin{theorem}\label{theo:equivariance}
-Under the hypothesis of theorem~\ref{theo:pointwise convergence for a regular sampling}, the rescaled graph Laplacian commutes with any rotation, in the limit of infinite sampling, i.e.,
+Under the hypothesis of theorem~\ref{theo:pointwise convergence for a regular sampling}, the scaled graph Laplacian commutes with any rotation, in the limit of infinite sampling, i.e.,
 \begin{equation*}
@@
 \end{theorem}
+From this theorem, it follows that the discrete graph Laplacian will be equivariant in the limit of $n \rightarrow \infty$ as by construction $\b{L}_n^t \b{f} = T_\V L_n^t f$ and as the scaling does not affect the equivariance property of $\b{L}_n^t$.
 
 Importantly, the proof of Theorem~\ref{theo:pointwise convergence for a regular sampling} (in Appendix~\ref{sec: appendix: proof of theorem}) inspires our construction of the graph Laplacian.
-In particular, it gives insights on how the parameter $t$ needs to be adjusted with respect to the number of points $n$.
+In particular, it tells us that $t$ should scale as $n^\beta$, which has been empirically verified (\figref{kernel_widths}).
+%In particular, it gives insights on how the parameter $t$ needs to be adjusted with respect to the number of points $n$.
 Nevertheless, it is important to keep in mind the limits of Theorem \ref{theo:pointwise convergence for a regular sampling} and \ref{theo:equivariance}.
@@
 % maybe erase the previous sentence?
-a stronger type of convergence of the graph Laplacian would be preferable, i.e.
-spectral convergence (that is proved for a full graph in the case of random sampling for a class of Lipschitz functions in \citep{belkin2007convergence}).
+a stronger type of convergence of the graph Laplacian would be preferable, i.e., spectral convergence (that is proved for a full graph in the case of random sampling for a class of Lipschitz functions in \citep{belkin2007convergence}).
 % First, it is \emph{not} a proof of equivariance of the graph convolution for a specific sampling.
@@
 6]{belkin2005towards}.
-While we do not have a formal proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, with $\alpha$ very close or equal to $\linefrac{1}{2}$.
+Finally, while we do not have a formal proof for it, we strongly believe that the HEALPix sampling does satisfy the hypothesis $d^{(n)}\leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, with $\alpha$ very close or equal to $\linefrac{1}{2}$.
 The empirical results discussed in the next paragraph also points in this direction.

### 2019-11-15 main.tex
move big figure and remove newpage
comment todos for submission

@@
 
-\begin{description}
-	\item[git] \url{https://github.com/nperraud/deepsphere_v2_paper}
-	\item[overleaf] \url{https://www.overleaf.com/project/5d31d2fbd6859d54cb707212}
-	\item[openreview] \url{https://openreview.net/forum?id=B1e3OlStPB}
-\end{description}
-
-story: there are tradeoffs when designing a spherical CNN $\Rightarrow$ DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
-\begin{itemize}
-	\item method development: tool that solve a need (balance btw the desiderata: equiv vs cost)
-	\item research question: anisotropy (highlight from the start or leave it as a dangling question at the end)
-\end{itemize}
-
-contributions:
-\begin{itemize}
-	\item theory $\Rightarrow$ convergence (better graph)
-	\item experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata
-	\item surprising: anisotropy doesn't seem useful
-\end{itemize}
-
-\todo{
-TODO:
-\begin{itemize}
-	\item Unify vocabulary and avoid synonyms.
-		Sampling, grid, discretization, pixelization $\Rightarrow$ sampling (sampling schemes when not a particular set of vertices?)
-		Signal, maps, fields, functions.
-		Irregular, uneven, non-uniform.
-		Coarsening, down-sampling.
-		Sample, vertex, node, pixel, point $\Rightarrow$ vertex
-	\item check English vs American English
-	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
-	\item update pygsp and merge sphere branch
-	\item Compute the invariance error of the whole NNs (before and after training, invariance can be learned).
+%\begin{description}
+%	\item[git] \url{https://github.com/nperraud/deepsphere_v2_paper}
+%	\item[overleaf] \url{https://www.overleaf.com/project/5d31d2fbd6859d54cb707212}
+%	\item[openreview] \url{https://openreview.net/forum?id=B1e3OlStPB}
+%\end{description}
+%
+%story: there are tradeoffs when designing a spherical CNN $\Rightarrow$ DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
+%\begin{itemize}
+%	\item method development: tool that solve a need (balance btw the desiderata: equiv vs cost)
+%	\item research question: anisotropy (highlight from the start or leave it as a dangling question at the end)
+%\end{itemize}
+%
+%contributions:
+%\begin{itemize}
+%	\item theory $\Rightarrow$ convergence (better graph)
+%	\item experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata
+%	\item surprising: anisotropy doesn't seem useful
+%\end{itemize}
+%
+%\todo{
+%TODO:
+%\begin{itemize}
+%	\item Unify vocabulary and avoid synonyms.
+%		Sampling, grid, discretization, pixelization $\Rightarrow$ sampling (sampling schemes when not a particular set of vertices?)
+%		Signal, maps, fields, functions.
+%		Irregular, uneven, non-uniform.
+%		Coarsening, down-sampling.
+%		Sample, vertex, node, pixel, point $\Rightarrow$ vertex
+%	\item check English vs American English
+%	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
+%	\item update pygsp and merge sphere branch
+%	\item Compute the invariance error of the whole NNs (before and after training, invariance can be learned).
 Add it with equivariance error of the convolution to \tabref{cosmo}.
 \nati{I guess we are not doing that}
-	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
-	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
-\end{itemize}
-}
-
-\todo{
-rebuttal:
-\begin{itemize}
-    \item answer commenter
-	\item add somewhere (intro?): exploit symmetries to reduce sample cost $\Rightarrow$ we don't discuss symmetries much
-	\item \citet{mudigonda2017climateevents} use Integrated Water Vapor (IWV) only.
+%	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
+%	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
+%\end{itemize}
+%}
+%
+%\todo{
+%rebuttal:
+%\begin{itemize}
+%    \item answer commenter
+%	\item add somewhere (intro?): exploit symmetries to reduce sample cost $\Rightarrow$ we don't discuss symmetries much
+%	\item \citet{mudigonda2017climateevents} use Integrated Water Vapor (IWV) only.
 That most probably is the same as our TMQ, which is most probably the most informative feature.
 TODO: run ours with TMQ alone.
-	\item Show the three samplings in a figure?
-	\item better abstract (Friday's talk abstract?)
-	\item conclusion: less speculation?
-	\item check feedback from ICLR'20 LTS2 reading group
-	\item \mdeff{check my Telegram notes}
-	\item argue against more generality
-	\item figure that show the three samplings? (suggested by reviewer \#2)
-\end{itemize}
-}
-
-\todo{
-last pass:
-\begin{itemize}
-	\item figure placement
-	\item check footnotes
-\end{itemize}
-}
-
-\todo{
-Not done:
-\begin{itemize}
-	\item Do the experiments on the icosahedral sampling with the pooling as defined in the paper (i.e., not Jiang's specialty of taking the value of a pre-chosen sub-pixel).
+%	\item Show the three samplings in a figure?
+%	\item better abstract (Friday's talk abstract?)
+%	\item conclusion: less speculation?
+%	\item check feedback from ICLR'20 LTS2 reading group
+%	\item \mdeff{check my Telegram notes}
+%	\item argue against more generality
+%	\item figure that show the three samplings? (suggested by reviewer \#2)
+%\end{itemize}
+%}
+%
+%\todo{
+%last pass:
+%\begin{itemize}
+%	\item figure placement
+%	\item check footnotes
+%\end{itemize}
+%}
+%
+%\todo{
+%Not done:
+%\begin{itemize}
+%	\item Do the experiments on the icosahedral sampling with the pooling as defined in the paper (i.e., not Jiang's specialty of taking the value of a pre-chosen sub-pixel).
 \nati{I guess we are not doing that.} \mdeff{I'm not sure what is the state of this, and Frédérick is not with us anymore.
 It's quite minor.}
-	\item Check results for ModelNet40 and integrate in text. \nati{I would drop this.} \mdeff{Yeah, those results are not mature enough.}
-	\item Add \citet{bruna2013gnn} in equivariance?
+%	\item Check results for ModelNet40 and integrate in text. \nati{I would drop this.} \mdeff{Yeah, those results are not mature enough.}
+%	\item Add \citet{bruna2013gnn} in equivariance?
 They were the first to do a spherical CNN with graphs.
@@
 Also, they only did MNIST on the sphere...}
-\end{itemize}
-}
-
-\clearpage
-\newpage
+%\end{itemize}
+%}
+%
+%\clearpage
+%\newpage
 
@@
 % We observe that using a small kernel size $t$, \cite{perraudin2019deepspherecosmo} would probably be more equivariant.
+
+\begin{figure}
+	\begin{minipage}{0.6\linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{equivariance_error}
+		\caption{
+			Mean equivariance error \eqref{eq:mean equivariance error}.
+			There is a clear tradeoff between equivariance and computational cost, governed by the number of vertices $n$ and edges $kn$.
+		}
+		\label{fig:equivariance_error}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.35\linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{kernel_widths}
+		\caption{Kernel widths.}
+		\label{fig:kernel_widths}
+		\vspace{1em}
+		\includegraphics[height=4.5em]{lamp_000018}
+		\hfill
+		\includegraphics[height=4.5em]{lamp_000018_sphere_nobar}
+		\caption{3D object represented as a spherical depth map.}
+		\label{fig:depthmap}
+		\vspace{1em}
+		\includegraphics[width=\linewidth]{spectrum}
+		\caption{Power spectral densities.}
+		\label{fig:spectrum}
+	\end{minipage}
+\end{figure}
 
@@
 
-\begin{figure}
-	\begin{minipage}{0.6\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{equivariance_error}
-		\caption{
-			Mean equivariance error \eqref{eq:mean equivariance error}.
-			There is a clear tradeoff between equivariance and computational cost, governed by the number of vertices $n$ and edges $kn$.
-		}
-		\label{fig:equivariance_error}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.35\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{kernel_widths}
-		\caption{Kernel widths.}
-		\label{fig:kernel_widths}
-		\vspace{1em}
-		\includegraphics[height=4.5em]{lamp_000018}
-		\hfill
-		\includegraphics[height=4.5em]{lamp_000018_sphere_nobar}
-		\caption{3D object represented as a spherical depth map.}
-		\label{fig:depthmap}
-		\vspace{1em}
-		\includegraphics[width=\linewidth]{spectrum}
-		\caption{Power spectral densities.}
-		\label{fig:spectrum}
-	\end{minipage}
-% \vspace{-0.5cm}
-\end{figure}
-
 \section{Experiments}
@@
 
-\newpage
 \subsubsection*{Author Contributions}

### 2019-11-15 rebuttal.md
rebuttal: comment about revised manuscript

@@
 We uploaded an improved manuscript thanks to the reviewers' comments.
-The following has been updated:
-* Slightly (very slightly) different statement of theorem 3.1
-* new proposition (now called prop 1) formalizing the relation between theorem 3.1 and rotation equivariance
 
-A link to a public git repository containing all the code will be added to the camera-ready version.
+The main update is the addition of theorem 3.2 that formalizes the relation between theorem 3.1 and rotation equivariance.
+Small changes across the text have been made to clarify the exposition further.
+
+A link to a public git repository containing all the code will be added after the blind-review process.
 

### 2019-11-20 rebuttal.md
rebuttal: update answer to comment

--- 2019-11-11 rebuttal.md
@@
 1.
-First of all, the operator needs to be a Laplacian (why?), excluding the single-parameter variant of GCN.
-The two-parameter variant is ChebNet with a polynomial order of K=1.
-The method scales linearly with K, which is an hyper-parameter to be set (analogous to the kernel size in classical CNNs).
-TODO(mdeff): check GCN paper for the variants
-TODO(nati) my version:
-Practically, we believe that any graph neural network variant may work and some might even slightly beat ChebyNet.
-However, our equivariance theory utilizes the graph Laplacian as a base building block.
-Hence, we do not know the theoretical properties of other GCNs such as the single parameter variant from T.K. Kipf.
-Note that the two-parameter variant from T.K. Kipf is ChebNet with a polynomial order of K=1.
-Eventually, the method we use scales linearly with K, which is an hyper-parameter to be set (analogous to the kernel size in classical CNNs).
+The two-parameter variant of GCN is ChebNet with a polynomial order of P=1.
+The method scales linearly with P, and that is an hyper-parameter to be set (analogous to the kernel size in classical CNNs).
+Note that the single-parameter variant of GCN doesn't fit our theory as we rely on the convergence of the operator to the Laplace-Beltrami to prove its equivariance.
 
-2. TODO(mdeff): Don't understand the question. Read the CCN paper.
+2.
+What should be predictable and revertible is the transformation applied to the output activations given a transformation applied to the input activations.
+In our case, both transformations are 3D rotations.
+That is, if the input activations are rotated by R, the output will be rotated by the same R.
 

### 2020-02-14 main.tex
rotation matrix in regular font
Revert "comment todos for submission"
This reverts commit 72052dcf02c1c9492d34b1c65a4832360cf6ade3.
update todos

--- 2019-11-15 main.tex
@@
 \newcommand{\laplacian}{\Delta_{\mathbb S^2}}
-\newcommand{\Rg}{\mathcal{R}(g)}
+\newcommand{\Rg}{R(g)}
 \newcommand{\seminorm}[1]{\left|#1\right|}
@@
 	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
-\end{itemize}
-}
-
-\todo{
-rebuttal:
-\begin{itemize}
-    \item answer commenter
 	\item add somewhere (intro?): exploit symmetries to reduce sample cost $\Rightarrow$ we don't discuss symmetries much
@@
 	\item better abstract (Friday's talk abstract?)
+	\item abstract: tackle impactful / important problems in cosmology and climatology (Earth sciences)
 	\item conclusion: less speculation?
@@
 	\item figure that show the three samplings? (suggested by reviewer \#2)
+	\item add the eigenfunction alignment in the appendix
+	\item Shouldn't theorem 3.2 be a corollary?
+	\item Experiments: organize per problem or desideratum?
+	\item Articulate the story around the desiderata. Add "most general / powerful" as one (for isotropy).
+	\item Better motivate the method (i.e., don't present our work as just the analysis of one method).
+Why is it a good method?
+It allows for a linear time implementation of operators on scalar fields.
+Need to show that functions of the Laplace-Beltrami $h(\Delta)$ can indeed implement any equivariant (gauge invariant \citep{cohen2019gauge}) linear operations on scalar fields.
+Restructure the method section to show how the cost is reduced to $\bO(pkn)$: (i) discretization ($n$ vertices), (ii) sparsification ($k$ neighbors), (iii) reduction of the class of operators / filters (polynomial order $p$).
+	\item A filter operating on scalar fields has to be isotropic / directionless to be equivariant \citep{cohen2019gauge}) [Kondor CCN]
+		A cheap solution: if the domain can be globally oriented (e.g., by gravity for 2D or omnidirectional images), then the spatial dimension can be factorized (think of the up, down, right, left directions in 2D images).
+The sphere could be factorized has two oriented lines for the vertical axis, and a circle horizontally.
+That is exploited by Khasanova to create anisotropic filters on the sphere for omnidirectional imaging.
+That of course reduces the symmetry group the NN is to be equivariant to.
+		Otherwise there is a price to pay.
+		If not but the domain has global symmetries, activations can be lifted to the symmetry group \citep{cohen2018sphericalcnn} [Kondor CCN].
+That is however memory and computationally expensive, as the activations must have the size of the symmetry group.
+		Without global symmetries, tensor activations are needed \citep{cohen2019gauge}.
+	\item Paragraph about cost reduction strategies (discretize, sparsify, polynomial). C.f. notes.
+	\item Write why we don't tackle omnidirectional imaging.
+Same reason as images.
+Factor the manifold.
+For some samplings their graph discretization can be factored, yielding anisotropic filters.
+(c.f.
+answer to reviewer 1)
 \end{itemize}

### 2020-02-14 main.tex
small edits

@@
 We require $F_\V$ to be a suitable subspace of continuous functions such that $T_\V$ is invertible, i.e., the function $f \in F_\V$ can be unambiguously reconstructed from its sampled values $\b{f}$.
-The existence of such a subspace depends on the sampling $\V$, and its characterization is a common problem in signal processing \citep{driscoll1994Fouriersphere}.
+The existence of such a subspace depends on the sampling $\V$ and its characterization is a common problem in signal processing \citep{driscoll1994Fouriersphere}.
 For most samplings, it is not known if $F_\V$ exists and hence if $T_\V$ is invertible.
@@
 By definition, the (spherical) graph convolution is rotation equivariant if and only if it commutes with the rotation operator defined as $\Rg, g\in SO(3)$: $\Rg f(x) = f\left(g^{-1} x \right)$.
-In the context of this work, graph convolution is performed by recursive applications of the graph Laplacian (\eqnref{graph_conv}).
+In the context of this work, graph convolution is performed by recursive applications of the graph Laplacian \eqnref{graph_conv}.
 Hence, if $\Rg$ commutes with $\b{L}$, then, by recursion, it will also commute with the convolution $h(\b{L})$.

### 2020-02-14 main.tex
deanonymize

@@
 \author{Michaël Defferrard, Martino Milani \& Frédérick Gusset \\
-Institute of Electrical Engineering, EPFL, Lausanne, Switzerland \\
+École Polytechnique Fédérale de Lausanne (EPFL), Switzerland \\
 \texttt{\{michael.defferrard,martino.milani,frederick.gusset\}@epfl.ch}
@@
 Nathanaël Perraudin \\
-Swiss Data Science Center (SDSC), Zurich, Switzerland \\
+Swiss Data Science Center (SDSC), Switzerland \\
 \texttt{nathanael.perraudin@sdsc.ethz.ch}
@@
 
-%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
+\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
 \begin{document}
@@
 
-\subsubsection*{Author Contributions}
-Left blank for anonymity reason.
+%\subsubsection*{Author Contributions}
+%Left blank for anonymity reason.
 % If you'd like to, you may include a section for author contributions as is done
@@
 \subsubsection*{Acknowledgments}
-Left blank for anonymity reason.
-
-%We thank Pierre Vandergheynst for advices, and Andreas Loukas for having processed the GHCN data.
-%We thank Taco Cohen for his inputs on the intriguing results of our comparison with \citet{cohen2019gauge}.
-%We thank the anonymous reviewers for their constructive feedback.
-%The following packages were used for computation and plotting: pygsp, numpy, tensorflow, scipy, etc.
+
+We thank Pierre Vandergheynst for advices.
+%and Andreas Loukas for having processed the GHCN data.
+We thank Taco Cohen for his inputs on the intriguing results of our comparison with \citet{cohen2019gauge}.
+We thank the anonymous reviewers for their constructive feedback.
+%The following software packages were used for computation and plotting: pygsp, scipy, numpy, tensorflow, etc.
 %We used the Python Graph Signal Processing package (PyGSP) \citep{pygsp} for computations and plots.
-%The Python Graph Signal Processing package (PyGSP) \citep{pygsp} was used to build graphs, compute the Laplacian and Fourier basis, and perform graph convolutions.
 

### 2020-02-14 main.tex
acknowledge software

@@
 
-We thank Pierre Vandergheynst for advices.
+We thank Pierre Vandergheynst for advices,
 %and Andreas Loukas for having processed the GHCN data.
-We thank Taco Cohen for his inputs on the intriguing results of our comparison with \citet{cohen2019gauge}.
+and Taco Cohen for his inputs on the intriguing results of our comparison with \citet{cohen2019gauge}.
 We thank the anonymous reviewers for their constructive feedback.
-%The following software packages were used for computation and plotting: pygsp, scipy, numpy, tensorflow, etc.
+The following software packages were used for computation and plotting: PyGSP \citep{pygsp}, healpy \citep{healpy}, matplotlib \citep{matplotlib}, SciPy \citep{scipy}, NumPy \citep{numpy}, TensorFlow \citep{tensorflow}.
 %We used the Python Graph Signal Processing package (PyGSP) \citep{pygsp} for computations and plots.

### 2020-02-15 main.tex
code link
update todos

@@
 		Sample, vertex, node, pixel, point $\Rightarrow$ vertex
-	\item check English vs American English
 	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
@@
 TODO: run ours with TMQ alone.
-	\item Show the three samplings in a figure?
 	\item better abstract (Friday's talk abstract?)
@@
 	\item argue against more generality
-	\item figure that show the three samplings? (suggested by reviewer \#2)
+	\item figure that shows the three samplings? (suggested by reviewer \#2)
 	\item add the eigenfunction alignment in the appendix
@@
 Need to show that functions of the Laplace-Beltrami $h(\Delta)$ can indeed implement any equivariant (gauge invariant \citep{cohen2019gauge}) linear operations on scalar fields.
-Restructure the method section to show how the cost is reduced to $\bO(pkn)$: (i) discretization ($n$ vertices), (ii) sparsification ($k$ neighbors), (iii) reduction of the class of operators / filters (polynomial order $p$).
+	\item Restructure the method section to show how the cost is reduced to $\bO(pkn)$: (i) discretization ($n$ vertices), (ii) sparsification ($k$ neighbors), (iii) reduction of the class of operators / filters (polynomial order $p$).
 	\item A filter operating on scalar fields has to be isotropic / directionless to be equivariant \citep{cohen2019gauge}) [Kondor CCN]
 		A cheap solution: if the domain can be globally oriented (e.g., by gravity for 2D or omnidirectional images), then the spatial dimension can be factorized (think of the up, down, right, left directions in 2D images).
-The sphere could be factorized has two oriented lines for the vertical axis, and a circle horizontally.
+The sphere could be factorized as two oriented lines for the vertical axis, and a circle horizontally.
 That is exploited by Khasanova to create anisotropic filters on the sphere for omnidirectional imaging.
@@
 		Without global symmetries, tensor activations are needed \citep{cohen2019gauge}.
-	\item Paragraph about cost reduction strategies (discretize, sparsify, polynomial). C.f. notes.
 	\item Write why we don't tackle omnidirectional imaging.
@@
 % memory, computations, implementation complexity
+Our code is available at \url{https://github.com/deepsphere}.
 \end{abstract}

### 2020-02-15 main.tex
move todos in a dedicated file

@@
 \begin{document}
-
-\begin{description}
-	\item[git] \url{https://github.com/nperraud/deepsphere_v2_paper}
-	\item[overleaf] \url{https://www.overleaf.com/project/5d31d2fbd6859d54cb707212}
-	\item[openreview] \url{https://openreview.net/forum?id=B1e3OlStPB}
-\end{description}
-
-story: there are tradeoffs when designing a spherical CNN $\Rightarrow$ DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
-\begin{itemize}
-	\item method development: tool that solve a need (balance btw the desiderata: equiv vs cost)
-	\item research question: anisotropy (highlight from the start or leave it as a dangling question at the end)
-\end{itemize}
-
-contributions:
-\begin{itemize}
-	\item theory $\Rightarrow$ convergence (better graph)
-	\item experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata
-	\item surprising: anisotropy doesn't seem useful
-\end{itemize}
-
-\todo{
-TODO:
-\begin{itemize}
-	\item Unify vocabulary and avoid synonyms.
-		Sampling, grid, discretization, pixelization $\Rightarrow$ sampling (sampling schemes when not a particular set of vertices?)
-		Signal, maps, fields, functions.
-		Irregular, uneven, non-uniform.
-		Coarsening, down-sampling.
-		Sample, vertex, node, pixel, point $\Rightarrow$ vertex
-	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
-	\item update pygsp and merge sphere branch
-	\item Compute the invariance error of the whole NNs (before and after training, invariance can be learned).
-Add it with equivariance error of the convolution to \tabref{cosmo}.
-\nati{I guess we are not doing that}
-	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
-	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
-	\item add somewhere (intro?): exploit symmetries to reduce sample cost $\Rightarrow$ we don't discuss symmetries much
-	\item \citet{mudigonda2017climateevents} use Integrated Water Vapor (IWV) only.
-That most probably is the same as our TMQ, which is most probably the most informative feature.
-TODO: run ours with TMQ alone.
-	\item better abstract (Friday's talk abstract?)
-	\item abstract: tackle impactful / important problems in cosmology and climatology (Earth sciences)
-	\item conclusion: less speculation?
-	\item check feedback from ICLR'20 LTS2 reading group
-	\item \mdeff{check my Telegram notes}
-	\item argue against more generality
-	\item figure that shows the three samplings? (suggested by reviewer \#2)
-	\item add the eigenfunction alignment in the appendix
-	\item Shouldn't theorem 3.2 be a corollary?
-	\item Experiments: organize per problem or desideratum?
-	\item Articulate the story around the desiderata. Add "most general / powerful" as one (for isotropy).
-	\item Better motivate the method (i.e., don't present our work as just the analysis of one method).
-Why is it a good method?
-It allows for a linear time implementation of operators on scalar fields.
-Need to show that functions of the Laplace-Beltrami $h(\Delta)$ can indeed implement any equivariant (gauge invariant \citep{cohen2019gauge}) linear operations on scalar fields.
-	\item Restructure the method section to show how the cost is reduced to $\bO(pkn)$: (i) discretization ($n$ vertices), (ii) sparsification ($k$ neighbors), (iii) reduction of the class of operators / filters (polynomial order $p$).
-	\item A filter operating on scalar fields has to be isotropic / directionless to be equivariant \citep{cohen2019gauge}) [Kondor CCN]
-		A cheap solution: if the domain can be globally oriented (e.g., by gravity for 2D or omnidirectional images), then the spatial dimension can be factorized (think of the up, down, right, left directions in 2D images).
-The sphere could be factorized as two oriented lines for the vertical axis, and a circle horizontally.
-That is exploited by Khasanova to create anisotropic filters on the sphere for omnidirectional imaging.
-That of course reduces the symmetry group the NN is to be equivariant to.
-		Otherwise there is a price to pay.
-		If not but the domain has global symmetries, activations can be lifted to the symmetry group \citep{cohen2018sphericalcnn} [Kondor CCN].
-That is however memory and computationally expensive, as the activations must have the size of the symmetry group.
-		Without global symmetries, tensor activations are needed \citep{cohen2019gauge}.
-	\item Write why we don't tackle omnidirectional imaging.
-Same reason as images.
-Factor the manifold.
-For some samplings their graph discretization can be factored, yielding anisotropic filters.
-(c.f.
-answer to reviewer 1)
-\end{itemize}
-}
-
-\todo{
-last pass:
-\begin{itemize}
-	\item figure placement
-	\item check footnotes
-\end{itemize}
-}
-
-\todo{
-Not done:
-\begin{itemize}
-	\item Do the experiments on the icosahedral sampling with the pooling as defined in the paper (i.e., not Jiang's specialty of taking the value of a pre-chosen sub-pixel).
-\nati{I guess we are not doing that.} \mdeff{I'm not sure what is the state of this, and Frédérick is not with us anymore.
-It's quite minor.}
-	\item Check results for ModelNet40 and integrate in text. \nati{I would drop this.} \mdeff{Yeah, those results are not mature enough.}
-	\item Add \citet{bruna2013gnn} in equivariance?
-They were the first to do a spherical CNN with graphs.
-Graph is built from a uniform random sampling of the sphere.
-\nati{Where do you want to add them?} \mdeff{They don't write how their Laplacian was built.
-Also, they only did MNIST on the sphere...}
-\end{itemize}
-}
-
-\clearpage
-\newpage
 

### 2020-12-30 main.tex
fix: iclr2020_conference.sty was renamed to iclr2020.sty
be a bit more specific about likelihood-free inference and summary statistics

@@
 \documentclass{article} % For LaTeX2e
-\usepackage{iclr2020_conference,times}
+\usepackage{iclr2020,times}
 
@@
 Given observations, cosmologists estimate the posterior probability of cosmological parameters, such as the matter density $\Omega_m$ and the normalization of the matter power spectrum $\sigma_8$.
-Those parameters are typically estimated by likelihood-free inference, which requires a function to predict the parameters from simulations.
+Those parameters are estimated by likelihood-free inference, which requires a method to extract summary statistics to compare simulations and observations.
+As the sufficient and most concise summary statistics are the parameters themselves, one desires a method to predict them from simulations.
 % such as Approximate Bayesian computation (ABC)
@@
 \bibliography{references}
-\bibliographystyle{iclr2020_conference}
+\bibliographystyle{iclr2020}
 
